---
title: "Baseline Analysis of Organ ages"
author: "Your Name"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# Load required libraries
library(tidyverse)
library(survival)
library(lmtest)
library(sandwich)
library(patchwork)
library(svglite)
select = dplyr::select
rename = dplyr::rename
set.seed(964)
```

```{r config}
# Output paths (set these for your environment)
output_root_dir <- "PATH/TO/output"
output_current_health_dir <- file.path(output_root_dir, "current_health")
output_prevalent_disease_dir <- file.path(output_root_dir, "prevalent_disease")

# Backward-compatible aliases used throughout this script
current_health_base <- output_current_health_dir
prevalent_disease_base <- output_prevalent_disease_dir

ensure_dir <- function(path) { dir.create(path, showWarnings = FALSE, recursive = TRUE) }
save_plot <- function(filename, plot, width, height, dpi = 300) {
  ensure_dir(dirname(filename))
  ggplot2::ggsave(filename = filename, plot = plot, width = width, height = height, dpi = dpi)
}
# Disable direct ggsave calls in this Rmd to enforce centralized paths via save_plot
ggsave <- function(...) { invisible(NULL) }
```

## Data Loading and Processing

```{r load_data}
# Input files (set these for your environment)
input_metadata_file <- "PATH/TO/input_metadata.csv"
input_organ_age_file <- "PATH/TO/input_organ_age.csv"
input_diagnosis_file <- "PATH/TO/input_diagnosis.csv"
input_cancer_file <- "PATH/TO/input_cancer.csv"

# Core schema configuration
id_col <- "twin_id"
pair_col <- "pair_id"
sex_col <- "sex"
male_code <- 1
female_code <- 2
age_col <- "age"

# Optional organ-specific columns (set to NULL if not present)
ovary_col <- "Ovary"
prostate_col <- "Prostate"

# Optional prefix to remove from organ-age columns
organ_age_prefix_to_strip <- "tuned_mortality_"

# Load datasets
twins <- read_csv(input_metadata_file)

organ_age_mortality <- read_csv(input_organ_age_file)

# Load disease data
med_history <- read_csv(input_diagnosis_file) |>
  filter(.data[[id_col]] %in% twins[[id_col]])

# Load cancer data
cancer <- read_csv(input_cancer_file) |>
  filter(.data[[id_col]] %in% twins[[id_col]])

# Merge disease and cancer data
med_history <- med_history |>
  left_join(cancer, by = id_col)


# Create twins_analysis dataframe
twins_analysis <- twins |>
  left_join(med_history, by = id_col)

if ("healthspan" %in% names(twins_analysis)) {
  twins_analysis <- twins_analysis |> arrange(desc(healthspan))
}

# Process organ age data
if (!is.null(organ_age_prefix_to_strip) && nzchar(organ_age_prefix_to_strip)) {
  organ_age_mortality <- organ_age_mortality |>
    rename_with(~str_remove(., paste0("^", organ_age_prefix_to_strip)), everything())
}

# Process organ ages based on sex
organ_age_mortality <- organ_age_mortality |>
  left_join(select(twins_analysis, all_of(c(id_col, sex_col))), by = id_col)

if (!is.null(ovary_col) && ovary_col %in% names(organ_age_mortality)) {
  organ_age_mortality <- organ_age_mortality |>
    mutate("{ovary_col}" := if_else(.data[[sex_col]] == male_code, NA_real_, .data[[ovary_col]]))
}

if (!is.null(prostate_col) && prostate_col %in% names(organ_age_mortality)) {
  organ_age_mortality <- organ_age_mortality |>
    mutate("{prostate_col}" := if_else(.data[[sex_col]] == female_code, NA_real_, .data[[prostate_col]]))
}

organ_age_mortality <- organ_age_mortality |>
  select(-all_of(sex_col))

# Create analysis datasets
twins_mortality <- twins_analysis |>
  left_join(organ_age_mortality, by = id_col)

# Get organ age columns
organ_age_cols_mortality <- names(organ_age_mortality)[names(organ_age_mortality) != id_col]

# Create fi_10 variable if fi exists in twins_analysis dataset
if ("fi" %in% names(twins_analysis)) {
  twins_analysis <- twins_analysis |>
    mutate(fi_10 = fi * 10)
}

# Optional label dictionaries (leave empty for identity labels)
clean_names <- function(data) {
  outcome_clean_names <- c()
  organ_clean_names <- c()

  data |>
    mutate(
      outcome_clean = case_when(
        outcome %in% names(outcome_clean_names) ~ outcome_clean_names[outcome],
        TRUE ~ outcome
      ),
      predictor_clean = case_when(
        predictor %in% names(organ_clean_names) ~ organ_clean_names[predictor],
        TRUE ~ predictor
      )
    )
}
```

## Analysis Setup

```{r define_outcomes}
# Define outcomes with grouping (replace placeholders with your variables)
binary_outcomes <- c("binary_outcome_1", "binary_outcome_2")

lifestyle_outcomes <- c("continuous_lifestyle_1", "continuous_lifestyle_2")
clinical_biomarkers <- c("continuous_clinical_1", "continuous_clinical_2")
health_outcomes <- c("continuous_health_1", "continuous_health_2")

# Combine all continuous outcomes
cont_outcomes <- c(lifestyle_outcomes, clinical_biomarkers, health_outcomes)

# Create outcome groups for plotting
outcome_groups <- list(
  "Lifestyle" = lifestyle_outcomes,
  "Clinical Biomarkers" = clinical_biomarkers,
  "Health" = health_outcomes
)

# Covariate sets: choose one and edit as needed
covariate_sets <- list(
  minimal = c("age", "sex"),
  cardiometabolic = c("age", "sex", "bmi"),
  extended = c("age", "sex", "bmi", "edyrs")
)
active_covariate_set <- "minimal"

# Helper function to determine covariates for each outcome
get_covariates <- function(outcome) {
  base_covariates <- covariate_sets[[active_covariate_set]]
  if (is.null(base_covariates)) {
    stop("Invalid `active_covariate_set` in define_outcomes.")
  }
  base_covariates <- base_covariates[base_covariates != outcome]
  base_covariates <- base_covariates[base_covariates %in% names(twins_analysis)]
  return(base_covariates)
}
```

## Analysis Functions

```{r analysis_functions}
# Function to analyze binary outcomes
analyze_binary_outcomes <- function(predictor_df, outcome_vars = binary_outcomes) {
  map_dfr(outcome_vars, function(outcome) {
    predictors <- setdiff(colnames(predictor_df), "twin_id")

    map_dfr(predictors, function(predictor) {
      analysis_data <- twins_analysis |>
        left_join(predictor_df |> select(twin_id, all_of(predictor)), by = "twin_id")

      # Handle sex-specific organ ages
      if (predictor == "Ovary") {
        analysis_data <- analysis_data |> filter(sex == 2)
        if (nrow(analysis_data) < 10) {
          return(tibble(
            outcome = outcome, predictor = predictor,
            estimate = NA_real_, std_error = NA_real_, z_value = NA_real_, p_value = NA_real_,
            odds_ratio = NA_real_, ci_lower = NA_real_, ci_upper = NA_real_,
            standardized_estimate = NA_real_, error_message = "Insufficient data for sex-specific analysis"
          ))
        }
      } else if (predictor == "Prostate") {
        analysis_data <- analysis_data |> filter(sex == 1)
        if (nrow(analysis_data) < 10) {
          return(tibble(
            outcome = outcome, predictor = predictor,
            estimate = NA_real_, std_error = NA_real_, z_value = NA_real_, p_value = NA_real_,
            odds_ratio = NA_real_, ci_lower = NA_real_, ci_upper = NA_real_,
            standardized_estimate = NA_real_, error_message = "Insufficient data for sex-specific analysis"
          ))
        }
      }

      covariates <- get_covariates(outcome)
      formula <- as.formula(paste(outcome, "~", predictor,
                                 if(length(covariates) > 0) paste("+", paste(covariates, collapse = " + ")) else ""))

      tryCatch({
        model <- glm(formula, data = analysis_data, family = binomial)
        cluster_se <- vcovCL(model, cluster = ~pair_id)
        coeftest_model <- coeftest(model, vcov = cluster_se)

        estimate <- coeftest_model[predictor, "Estimate"]
        std_error <- coeftest_model[predictor, "Std. Error"]
        or <- exp(estimate)
        ci_lower <- exp(estimate - 1.96 * std_error)
        ci_upper <- exp(estimate + 1.96 * std_error)

        tibble(
          outcome = outcome, predictor = predictor,
          estimate = estimate, std_error = std_error,
          z_value = coeftest_model[predictor, "z value"],
          p_value = coeftest_model[predictor, "Pr(>|z|)"],
          odds_ratio = or, ci_lower = ci_lower, ci_upper = ci_upper,
          standardized_estimate = estimate, error_message = NA_character_
        )
      }, error = function(e) {
        tibble(
          outcome = outcome, predictor = predictor,
          estimate = NA_real_, std_error = NA_real_, z_value = NA_real_, p_value = NA_real_,
          odds_ratio = NA_real_, ci_lower = NA_real_, ci_upper = NA_real_,
          standardized_estimate = NA_real_, error_message = e$message
        )
      })
    })
  }) |> mutate(FDR = p.adjust(p_value, method = "fdr"))
}

# Function to analyze continuous outcomes
analyze_continuous_outcomes <- function(predictor_df, outcome_vars = cont_outcomes) {
  map_dfr(outcome_vars, function(outcome) {
    if (!(outcome %in% names(twins_analysis))) {
      return(tibble(
        outcome = outcome, predictor = NA_character_,
        estimate = NA_real_, std_error = NA_real_, z_value = NA_real_, p_value = NA_real_,
        standardized_estimate = NA_real_, standardized_ci_lower = NA_real_, standardized_ci_upper = NA_real_,
        error_message = "Variable not found in dataset"
      ))
    }

    outcome_data <- twins_analysis[[outcome]]
    n_unique <- length(unique(outcome_data[!is.na(outcome_data)]))

    if (n_unique < 2) {
      return(tibble(
        outcome = outcome, predictor = NA_character_,
        estimate = NA_real_, std_error = NA_real_, z_value = NA_real_, p_value = NA_real_,
        standardized_estimate = NA_real_, standardized_ci_lower = NA_real_, standardized_ci_upper = NA_real_,
        error_message = paste("Insufficient variation: only", n_unique, "unique values")
      ))
    }

    predictors <- setdiff(colnames(predictor_df), "twin_id")

    map_dfr(predictors, function(predictor) {
      analysis_data <- twins_analysis |>
        left_join(predictor_df |> select(twin_id, all_of(predictor)), by = "twin_id")

      # Handle sex-specific organ ages
      if (predictor == "Ovary") {
        analysis_data <- analysis_data |> filter(sex == 2)
        if (nrow(analysis_data) < 10) {
          return(tibble(
            outcome = outcome, predictor = predictor,
            estimate = NA_real_, std_error = NA_real_, z_value = NA_real_, p_value = NA_real_,
            standardized_estimate = NA_real_, standardized_ci_lower = NA_real_, standardized_ci_upper = NA_real_,
            error_message = "Insufficient data for sex-specific analysis"
          ))
        }
      } else if (predictor == "Prostate") {
        analysis_data <- analysis_data |> filter(sex == 1)
        if (nrow(analysis_data) < 10) {
          return(tibble(
            outcome = outcome, predictor = predictor,
            estimate = NA_real_, std_error = NA_real_, z_value = NA_real_, p_value = NA_real_,
            standardized_estimate = NA_real_, standardized_ci_lower = NA_real_, standardized_ci_upper = NA_real_,
            error_message = "Insufficient data for sex-specific analysis"
          ))
        }
      }

      covariates <- get_covariates(outcome)
      formula <- as.formula(paste(outcome, "~", predictor,
                                 if(length(covariates) > 0) paste("+", paste(covariates, collapse = " + ")) else ""))

      tryCatch({
        model <- glm(formula, data = analysis_data)
        cluster_se <- vcovCL(model, cluster = ~pair_id)
        coeftest_model <- coeftest(model, vcov = cluster_se)

        sd_outcome <- sd(analysis_data[[outcome]], na.rm = TRUE)
        sd_predictor <- sd(analysis_data[[predictor]], na.rm = TRUE)
        estimate <- coeftest_model[predictor, "Estimate"]
        std_error <- coeftest_model[predictor, "Std. Error"]
        standardized_estimate <- estimate * (sd_predictor / sd_outcome)
        standardized_ci_lower <- (estimate - 1.96 * std_error) * (sd_predictor / sd_outcome)
        standardized_ci_upper <- (estimate + 1.96 * std_error) * (sd_predictor / sd_outcome)

        tibble(
          outcome = outcome, predictor = predictor,
          estimate = estimate, std_error = std_error,
          z_value = coeftest_model[predictor, "z value"],
          p_value = coeftest_model[predictor, "Pr(>|z|)"],
          standardized_estimate = standardized_estimate,
          standardized_ci_lower = standardized_ci_lower,
          standardized_ci_upper = standardized_ci_upper,
          error_message = NA_character_
        )
      }, error = function(e) {
        tibble(
          outcome = outcome, predictor = predictor,
          estimate = NA_real_, std_error = NA_real_, z_value = NA_real_, p_value = NA_real_,
          standardized_estimate = NA_real_, standardized_ci_lower = NA_real_, standardized_ci_upper = NA_real_,
          error_message = e$message
        )
      })
    })
  }) |> mutate(FDR = p.adjust(p_value, method = "fdr"))
}
```

## Clinical and Biomarker Associations

**Analysis Structure:**
This section performs univariate linear and logistic regression analyses to examine the association between individual organ ages and baseline clinical and lifestyle outcomes. Each analysis tests whether accelerated organ aging (higher organ age relative to chronological age) is associated with adverse health indicators.

**Model Formula:** 
- **Linear models:** `outcome ~ organ_age + selected_covariates`
- **Logistic models:** `outcome ~ organ_age + selected_covariates`

**Key Components:**
- **Organ age measures:** Mortality-calibrated organ ages (trained on mortality prediction)
- **Outcomes:** Clinical biomarkers, lifestyle factors, and health indicators
- **Covariates:** Age, sex, BMI (when not the outcome), and other relevant confounders
- **Clustering:** Robust standard errors accounting for twin pair clustering
- **Sex-specific handling:** Separate analyses for sex-specific organs (Ovary, Prostate)
- **Standardization:** Effect sizes standardized for interpretation across different outcome scales

**Statistical Approach:**
- **Multiple testing correction:** FDR correction applied to p-values
- **Effect size interpretation:** Standardized coefficients for continuous outcomes, odds ratios for binary outcomes
- **Model validation:** Error handling for insufficient data or convergence issues

```{r clinical_associations}
cont_results <- analyze_continuous_outcomes(organ_age_mortality) |>
  mutate(model_type = "linear", organ_age_model = "mortality")
binary_results <- analyze_binary_outcomes(organ_age_mortality) |>
  mutate(model_type = "logistic", organ_age_model = "mortality")

# Combine results
all_results <- bind_rows(
  cont_results,
  binary_results
)
```

## Results Visualization

```{r prepare_heatmap_data}
# Create heatmap data
mortality_heatmap_data <- all_results |>
  filter(organ_age_model == "mortality", is.na(error_message)) |>
  mutate(
    effect_size = case_when(
      model_type == "linear" ~ standardized_estimate,
      model_type == "logistic" ~ log(odds_ratio)
    ),
    significance = case_when(
      FDR < 0.001 ~ "***",
      FDR < 0.01 ~ "**",
      FDR < 0.05 ~ "*",
      TRUE ~ ""
    ),
    outcome_group = case_when(
      outcome %in% lifestyle_outcomes ~ "Lifestyle",
      outcome %in% clinical_biomarkers ~ "Clinical Biomarkers",
      outcome %in% health_outcomes ~ "Health",
      outcome %in% binary_outcomes ~ "Lifestyle",
      TRUE ~ "Other"
    )
  ) |>
  select(outcome, predictor, effect_size, significance, outcome_group, model_type) |>
  clean_names()
```

```{r heatmap_fixed_organ_order}
# Fixed organ order to use across all heatmaps
fixed_organ_order <- c(
  "Brain", "Cardiovascular", "Kidney and Bladder", "Immune", "Liver",
  "Adipose", "Endocrine", "Gastrointestinal", "Lung", "Muscle", 
  "Nerve", "Pancreas", "Skin", "Ovary", "Prostate"
)
```

```{r group_heatmaps}
# Control variables for heatmap appearance
HEATMAP_TEXT_SIZE <- 14
HEATMAP_SQUARE_SIZE_DIVISOR <- 12

# Function to create heatmap for specific outcome group
create_group_heatmap <- function(data, group_name) {
  group_data <- data |>
    filter(outcome_group == group_name)

  # Create consistent organ order
  all_organs <- unique(group_data$predictor_clean)
  all_organs <- all_organs[!is.na(all_organs)]
  available_fixed <- intersect(fixed_organ_order, all_organs)
  other_organs <- setdiff(all_organs, fixed_organ_order)
  organ_order <- c(available_fixed, other_organs)

  # Prepare matrix and cluster outcomes
  group_matrix <- group_data |>
    select(outcome_clean, predictor_clean, effect_size) |>
    pivot_wider(
      names_from = predictor_clean,
      values_from = effect_size,
      values_fill = 0
    ) |>
    column_to_rownames("outcome_clean") |>
    as.matrix()

  outcome_clusters <- hclust(dist(group_matrix), method = "ward.D2")
  outcome_order <- rownames(group_matrix)[outcome_clusters$order]
  available_organs <- intersect(organ_order, colnames(group_matrix))
  predictor_order <- available_organs

  if (length(outcome_order) == 0 || length(predictor_order) == 0) return(NULL)

  # Panel-style control variables
  text_size_pt <- HEATMAP_TEXT_SIZE
  square_size <- text_size_pt / HEATMAP_SQUARE_SIZE_DIVISOR

  # Prepare data for plotting with numeric coordinates
  group_data_clustered <- group_data |>
    mutate(
      outcome_clean = factor(outcome_clean, levels = outcome_order),
      predictor_clean = factor(predictor_clean, levels = predictor_order),
      outcome_num = (as.numeric(outcome_clean) - 1) * square_size + square_size/2,
      predictor_num = (as.numeric(predictor_clean) - 1) * square_size + square_size/2,
      effect_size_colored = if_else(significance != "", effect_size, NA_real_),
      non_sig_marker = if_else(significance == "", "×", "")
    )

  # Set legend position for all plots
  legend_pos <- "right"

  # Create heatmap with panel styling
  ggplot(group_data_clustered, aes(x = predictor_num, y = outcome_num, fill = effect_size_colored)) +
    geom_tile(width = square_size, height = square_size, color = NA) +
    geom_text(aes(x = predictor_num, y = outcome_num, label = non_sig_marker), size = 5.5, color = "darkgrey", family = "Helvetica", inherit.aes = FALSE) +
    scale_fill_gradientn(
      colors = c(
        "#2166AC",      # Blue for negative values
        "white",        # White at zero
        "#C64D4D",      # Red (mid-high)
        "#B71C1C"       # Darker red (extreme high)
      ),
      values = scales::rescale(c(-0.5, 0, 0.25, 0.5)),
      limits = c(-0.5, 0.5),
      na.value = "white",
      name = "Standardized\nEffect Size",
      breaks = c(-0.5, -0.25, 0, 0.25, 0.5),
      labels = c("-0.5", "-0.25", "0", "0.25", "0.5")
    ) +
    scale_x_continuous(
      breaks = (seq_along(predictor_order) - 1) * square_size + square_size/2,
      labels = predictor_order,
      expand = c(0, 0),
      limits = c(0, length(predictor_order) * square_size)
    ) +
    scale_y_continuous(
      breaks = (seq_along(outcome_order) - 1) * square_size + square_size/2,
      labels = outcome_order,
      expand = c(0, 0),
      limits = c(0, length(outcome_order) * square_size)
    ) +
    theme_minimal(base_family = "Helvetica") +
    theme(
      text = element_text(family = "Helvetica", color = "black"),
      plot.title = element_text(size = 16, face = "bold"),
      plot.subtitle = element_text(size = 12),
      axis.text.x = element_text(angle = 45, hjust = 1, size = HEATMAP_TEXT_SIZE, color = "black", family = "Helvetica"),
      axis.text.y = element_text(size = HEATMAP_TEXT_SIZE, hjust = 0, margin = margin(r = 10), color = "black", family = "Helvetica"),
      axis.title = element_blank(),
      axis.ticks = element_blank(),
      legend.position = legend_pos,
      legend.title = element_text(size = 11, color = "black", family = "Helvetica"),
      legend.text = element_text(size = 9, color = "black", family = "Helvetica"),
      legend.key.height = unit(0.8, "cm"),
      legend.key.width = unit(0.5, "cm"),
      panel.grid = element_blank(),
      panel.spacing = unit(0, "lines"),
      panel.border = element_blank(),
      plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm")
    ) +
    coord_fixed(ratio = 1, expand = FALSE)
}

# Create heatmaps for each group
mortality_lifestyle_heatmap <- create_group_heatmap(mortality_heatmap_data, "Lifestyle")
mortality_clinical_heatmap <- create_group_heatmap(mortality_heatmap_data, "Clinical Biomarkers")
mortality_health_heatmap <- create_group_heatmap(mortality_heatmap_data, "Health")

# Print heatmaps
print(mortality_lifestyle_heatmap)
print(mortality_clinical_heatmap)
print(mortality_health_heatmap)

# Save heatmaps to new structured paths
save_plot(
  filename = file.path(current_health_base, "heatmap", "mortality_organ_age_heatmap_lifestyle.svg"),
  plot = mortality_lifestyle_heatmap,
  width = 12,
  height = 6,
  dpi = 300
)

save_plot(
  filename = file.path(current_health_base, "heatmap", "mortality_organ_age_heatmap_clinical.svg"),
  plot = mortality_clinical_heatmap,
  width = 12,
  height = 6,
  dpi = 300
)

save_plot(
  filename = file.path(current_health_base, "heatmap", "mortality_organ_age_heatmap_health.svg"),
  plot = mortality_health_heatmap,
  width = 12,
  height = 6,
  dpi = 300
)
```


# 8. Forest Tables for Clinical, Health, and Lifestyle Analyses

```{r clinical_forest_helpers}
create_forest_table <- function(data, outcome_name, main_color = "black") {
  
  forest_data <- data |> 
    filter(outcome == outcome_name, organ_age_model == "mortality", is.na(error_message))
  
  if (nrow(forest_data) == 0) return(NULL)
  
  display_name <- case_when(
    outcome_name == "whr" ~ "Waist-Hip Ratio",
    outcome_name == "bmi" ~ "Body Mass Index", 
    outcome_name == "edyrs" ~ "Education Years",
    outcome_name == "glucose" ~ "Glucose",
    outcome_name == "triglycerides" ~ "Triglycerides",
    outcome_name == "hba1c" ~ "HbA1c",
    outcome_name == "crp" ~ "C-Reactive Protein",
    outcome_name == "total_hdl_ratio" ~ "Total/HDL Ratio",
    outcome_name == "egfr_cr_cys" ~ "eGFR",
    outcome_name == "fi_10" ~ "Frailty Index",
    outcome_name == "telomere_length" ~ "Telomere Length",
    outcome_name == "eversmok" ~ "Ever Smoked",
    outcome_name == "exercise_how_often" ~ "Exercise Frequency",
    TRUE ~ outcome_name
  )
  
  is_binary <- all(forest_data$model_type == "logistic")
  
  forest_data <- forest_data |>
    mutate(
      effect_size = if_else(model_type == "linear", standardized_estimate, odds_ratio),
      effect_lower = if_else(model_type == "linear", standardized_ci_lower, ci_lower),
      effect_upper = if_else(model_type == "linear", standardized_ci_upper, ci_upper),
      significant = FDR < 0.05,
      errorbar_color = if_else(FDR < 0.05, "grey30", "gray80"),
      Organ_Display = case_when(
        predictor == "Brain" ~ "Brain",
        predictor == "Heart" ~ "Heart", 
        predictor == "Kidney" ~ "Kidney",
        predictor == "Liver" ~ "Liver",
        predictor == "Lung" ~ "Lung",
        predictor == "Muscle" ~ "Muscle",
        predictor == "Pancreas" ~ "Pancreas",
        predictor == "Prostate" ~ "Prostate",
        predictor == "Ovary" ~ "Ovary",
        TRUE ~ predictor
      )
    ) |>
    arrange(desc(effect_size)) |>
    mutate(
      y_pos = rev(seq_along(predictor)),
      Organ_Display = factor(Organ_Display, levels = unique(Organ_Display))
    )
  
  # Dynamic x-axis limits with hard caps
  base_min <- 0.25
  base_max <- 3
  hard_min <- 0.05
  hard_max <- 10
  
  if (is_binary) {
    x_min <- suppressWarnings(min(forest_data$effect_lower, na.rm = TRUE))
    x_max <- suppressWarnings(max(forest_data$effect_upper, na.rm = TRUE))
    
    if (!is.finite(x_min)) x_min <- base_min
    if (!is.finite(x_max)) x_max <- base_max
    
    x_min <- max(x_min, 0.001)
    
    lower_margin_factor <- 0.9
    upper_margin_factor <- 1.1
    
    x_min <- min(base_min, x_min * lower_margin_factor)
    x_max <- max(base_max, x_max * upper_margin_factor)
    
    x_min <- max(hard_min, x_min)
    x_max <- min(hard_max, x_max)
  } else {
    x_min <- suppressWarnings(min(forest_data$effect_lower, na.rm = TRUE))
    x_max <- suppressWarnings(max(forest_data$effect_upper, na.rm = TRUE))
    
    if (!is.finite(x_min) || !is.finite(x_max)) {
      x_min <- -0.5
      x_max <- 0.5
    }
    
    lower_margin_factor <- 1.1
    upper_margin_factor <- 1.1
    
    x_min <- min(-0.5, x_min * lower_margin_factor)
    x_max <- max(0.5, x_max * upper_margin_factor)
    
    x_min <- max(-hard_max, x_min)
    x_max <- min(hard_max, x_max)
  }
  
  x_breaks <- pretty(c(x_min, x_max), n = 6)
  x_breaks <- x_breaks[x_breaks >= x_min & x_breaks <= x_max]
  
  # Add formatted effect size column and detect if scientific notation is needed
  forest_data <- forest_data |>
    mutate(
      use_sci = pmax(abs(effect_size), abs(effect_lower), abs(effect_upper), na.rm = TRUE) >= 10,
      use_sci = if_else(is.na(use_sci), FALSE, use_sci),
      effect_formatted = if_else(
        use_sci,
        sprintf("%.1e (%.1e-%.1e)", effect_size, effect_lower, effect_upper),
        sprintf("%.2f (%.2f-%.2f)", effect_size, effect_lower, effect_upper)
      )
    )
  
  # Detect if we need wider table for scientific notation
  has_sci_notation <- any(forest_data$use_sci, na.rm = TRUE)
  table_width_ratio <- if (has_sci_notation) 3.2 else 2.5
  
  # Create table data
  tab <- forest_data |>
    transmute(
      y_pos, 
      `Organ age` = Organ_Display, 
      `Effect Size` = effect_formatted,
      `FDR` = sprintf("%.2e", FDR)
    )
  
  x_pos <- tibble(col = c("Organ age", "Effect Size", "FDR"), x = c(1.0, 4.0, 7.5))
  table_long <- tab |>
    pivot_longer(-y_pos, names_to = "col", values_to = "val") |>
    left_join(x_pos, by = "col")
  
  # Table plot
  p_table <- ggplot(table_long, aes(x = x, y = y_pos, label = val)) +
    geom_text(hjust = c(0, 0, 1)[match(table_long$col, x_pos$col)], size = 3) +
    geom_text(
      data = x_pos |> mutate(y_pos = max(forest_data$y_pos) + 1), 
      aes(x = x, y = y_pos, label = col), 
      hjust = c(0, 0, 1), 
      fontface = "bold", 
      inherit.aes = FALSE, 
      size = 3.3
    ) +
    scale_y_continuous(breaks = NULL, limits = c(0.5, max(forest_data$y_pos) + 1.5)) +
    scale_x_continuous(limits = c(0.5, 9.0), expand = c(0, 0)) +
    labs(title = display_name) +
    theme_minimal(base_size = 11) +
    theme(
      plot.title = element_text(hjust = 0.1, size = 12), 
      axis.title = element_blank(), 
      axis.text = element_blank(), 
      axis.ticks = element_blank(), 
      panel.grid = element_blank(), 
      plot.margin = unit(c(12, 6, 6, 6), "pt")
    )
  
  # Determine which points are out of bounds and cap CIs to plot range
  forest_data <- forest_data |>
    mutate(
      out_of_bounds_point = effect_size < x_min | effect_size > x_max,
      effect_lower_capped = pmax(effect_lower, x_min),
      effect_upper_capped = pmin(effect_upper, x_max),
      has_any_value_outside = (effect_size < x_min | effect_size > x_max | effect_lower < x_min | effect_upper > x_max)
    )
  
  # Only plot data where the effect size itself is within bounds
  data_in_bounds <- forest_data |> filter(!out_of_bounds_point)
  
  # Calculate legend positions
  legend_y <- max(forest_data$y_pos) + 1.5
  legend_left_x <- x_min + (x_max - x_min) * 0.03
  legend_right_x <- x_min + (x_max - x_min) * 0.60
  legend_bottom_y <- 0.25
  legend_bottom_x <- x_min + (x_max - x_min) * 0.60
  
  # Forest plot
  p_forest <- ggplot(forest_data, aes(y = y_pos)) +
    geom_rect(
      aes(xmin = -Inf, xmax = Inf, ymin = y_pos - 0.5, ymax = y_pos + 0.5, 
          fill = factor(seq_along(predictor) %% 2)), 
      alpha = 0.6, show.legend = FALSE
    ) +
    scale_fill_manual(values = c("0" = "transparent", "1" = "gray95")) +
    geom_segment(
      aes(x = if (is_binary) 1 else 0, xend = if (is_binary) 1 else 0, 
          y = 0.5, yend = max(forest_data$y_pos) + 0.75), 
      linetype = "33", color = "grey10", size = 0.7
    ) +
    {if (nrow(data_in_bounds) > 0) geom_errorbarh(data = data_in_bounds, aes(xmin = effect_lower_capped, xmax = effect_upper_capped, y = y_pos), color = data_in_bounds$errorbar_color, height = 0.15, size = 0.6, inherit.aes = FALSE)} +
    {if (nrow(data_in_bounds) > 0) geom_point(data = data_in_bounds, aes(x = effect_size, color = significant), size = 2.5, shape = 16)} +
    {if (nrow(data_in_bounds |> filter(has_any_value_outside)) > 0) geom_text(data = data_in_bounds |> filter(has_any_value_outside), aes(x = effect_size, y = y_pos + 0.25), label = "*", size = 3.5, color = "black")} +
    annotate(
      "text", x = legend_left_x, y = legend_y, 
      label = "● Significant (FDR < 0.05)", hjust = 0, size = 2.6, color = main_color
    ) +
    annotate(
      "text", x = legend_right_x, y = legend_y, 
      label = "● Non-significant", hjust = 0, size = 2.6, color = "gray80"
    ) +
    {if (nrow(data_in_bounds |> filter(has_any_value_outside)) > 0) annotate("text", x = legend_bottom_x, y = legend_bottom_y, label = "* Value outside plot range", hjust = 1, size = 2.4, color = "black")} +
    scale_color_manual(values = c("TRUE" = main_color, "FALSE" = "gray80")) +
    scale_x_continuous(
      limits = c(x_min, x_max),
      breaks = x_breaks,
      labels = format(x_breaks, digits = 3, trim = TRUE)
    ) +
    scale_y_continuous(breaks = NULL, limits = c(0.2, max(forest_data$y_pos) + 1.5)) +
    labs(x = if (is_binary) "Odds Ratio (95% CI)" else "Standardized Effect (95% CI)", y = NULL) +
    theme_minimal(base_size = 11) +
    theme(
      axis.text.y = element_blank(), 
      axis.text.x = element_text(size = 9), 
      axis.title.x = element_text(size = 10), 
      panel.grid.major.y = element_blank(), 
      panel.grid.minor = element_blank(), 
      panel.grid.major.x = element_blank(), 
      plot.margin = unit(c(12, 12, 6, 0), "pt"), 
      legend.position = "none"
    ) +
    coord_cartesian(clip = "off")
  
  p_table + p_forest + plot_layout(widths = c(table_width_ratio, 2))
}
```

```{r create_and_save_forest_plots}
# Create output directory
output_dir <- file.path(current_health_base, "forest_table")
dir.create(output_dir, showWarnings = FALSE, recursive = TRUE)

# Define all outcomes to plot
all_outcomes <- c(lifestyle_outcomes, clinical_biomarkers, health_outcomes, binary_outcomes)

# Create and save forest plots
for (outcome_name in all_outcomes) {
  plot <- create_forest_table(all_results, outcome_name)
  
  if (!is.null(plot)) {
    save_plot(
      filename = file.path(output_dir, paste0("forest_", outcome_name, ".svg")),
      plot = plot,
      width = 8,
      height = 5,
      dpi = 300
    )
  }
}

# Create CSV tables directory
csv_dir <- file.path(current_health_base, "tables")
dir.create(csv_dir, showWarnings = FALSE, recursive = TRUE)

# Save table data as CSV for all outcomes
for (outcome_name in all_outcomes) {
  outcome_data <- all_results |> 
    filter(outcome == outcome_name, organ_age_model == "mortality", is.na(error_message))
  
  if (nrow(outcome_data) == 0) next
  
  # Create table data
  tab <- outcome_data |>
    mutate(
      effect_size = if_else(model_type == "linear", standardized_estimate, odds_ratio),
      effect_lower = if_else(model_type == "linear", standardized_ci_lower, ci_lower),
      effect_upper = if_else(model_type == "linear", standardized_ci_upper, ci_upper),
      use_sci = pmax(abs(effect_size), abs(effect_lower), abs(effect_upper), na.rm = TRUE) >= 10,
      effect_formatted = if_else(use_sci,
        sprintf("%.1e (%.1e-%.1e)", effect_size, effect_lower, effect_upper),
        sprintf("%.2f (%.2f-%.2f)", effect_size, effect_lower, effect_upper)),
      Organ_Display = case_when(
        predictor == "Brain" ~ "Brain",
        predictor == "Heart" ~ "Heart",
        predictor == "Kidney" ~ "Kidney",
        predictor == "Liver" ~ "Liver",
        predictor == "Lung" ~ "Lung",
        predictor == "Muscle" ~ "Muscle",
        predictor == "Pancreas" ~ "Pancreas",
        predictor == "Prostate" ~ "Prostate",
        predictor == "Ovary" ~ "Ovary",
        TRUE ~ predictor
      )
    ) |>
    select(Organ = Organ_Display, `Effect Size (95% CI)` = effect_formatted, FDR)
  
  write.csv(tab, file = file.path(csv_dir, paste0(outcome_name, ".csv")), row.names = FALSE)
}
```

# 9. Sex-Stratified Analyses

```{r sex_stratified_analyses}
# Create sex-stratified datasets
twins_analysis_male <- twins_analysis |> filter(sex == 1)
twins_analysis_female <- twins_analysis |> filter(sex == 2)

# Temporarily replace the main dataset for sex-specific analyses
run_sex_stratified <- function(sex_value, sex_label) {
  # Temporarily override twins_analysis in the function environment
  twins_analysis_temp <- twins_analysis
  assign("twins_analysis", if(sex_value == 1) twins_analysis_male else twins_analysis_female, envir = .GlobalEnv)
  
  # Run analyses
  cont_results <- analyze_continuous_outcomes(organ_age_mortality) |>
    mutate(model_type = "linear", organ_age_model = "mortality", sex_strata = sex_label)
  
  binary_results <- analyze_binary_outcomes(organ_age_mortality) |>
    mutate(model_type = "logistic", organ_age_model = "mortality", sex_strata = sex_label)
  
  # Restore original dataset
  assign("twins_analysis", twins_analysis_temp, envir = .GlobalEnv)
  
  bind_rows(cont_results, binary_results)
}

# Run for males and females
male_results <- run_sex_stratified(1, "Male")
female_results <- run_sex_stratified(2, "Female")

all_sex_stratified_results <- bind_rows(male_results, female_results)
```

```{r sex_stratified_heatmaps}
# Prepare heatmap data for each sex
male_heatmap_data <- male_results |>
  filter(organ_age_model == "mortality", is.na(error_message)) |>
  mutate(
    effect_size = case_when(
      model_type == "linear" ~ standardized_estimate,
      model_type == "logistic" ~ log(odds_ratio)
    ),
    significance = case_when(
      FDR < 0.001 ~ "***",
      FDR < 0.01 ~ "**",
      FDR < 0.05 ~ "*",
      TRUE ~ ""
    ),
    outcome_group = case_when(
      outcome %in% lifestyle_outcomes ~ "Lifestyle",
      outcome %in% clinical_biomarkers ~ "Clinical Biomarkers",
      outcome %in% health_outcomes ~ "Health",
      outcome %in% binary_outcomes ~ "Lifestyle",
      TRUE ~ "Other"
    )
  ) |>
  select(outcome, predictor, effect_size, significance, outcome_group, model_type) |>
  clean_names()

female_heatmap_data <- female_results |>
  filter(organ_age_model == "mortality", is.na(error_message)) |>
  mutate(
    effect_size = case_when(
      model_type == "linear" ~ standardized_estimate,
      model_type == "logistic" ~ log(odds_ratio)
    ),
    significance = case_when(
      FDR < 0.001 ~ "***",
      FDR < 0.01 ~ "**",
      FDR < 0.05 ~ "*",
      TRUE ~ ""
    ),
    outcome_group = case_when(
      outcome %in% lifestyle_outcomes ~ "Lifestyle",
      outcome %in% clinical_biomarkers ~ "Clinical Biomarkers",
      outcome %in% health_outcomes ~ "Health",
      outcome %in% binary_outcomes ~ "Lifestyle",
      TRUE ~ "Other"
    )
  ) |>
  select(outcome, predictor, effect_size, significance, outcome_group, model_type) |>
  clean_names()

# Create heatmaps for each group and sex
male_lifestyle_heatmap <- create_group_heatmap(male_heatmap_data, "Lifestyle")
male_clinical_heatmap <- create_group_heatmap(male_heatmap_data, "Clinical Biomarkers")
male_health_heatmap <- create_group_heatmap(male_heatmap_data, "Health")

female_lifestyle_heatmap <- create_group_heatmap(female_heatmap_data, "Lifestyle")
female_clinical_heatmap <- create_group_heatmap(female_heatmap_data, "Clinical Biomarkers")
female_health_heatmap <- create_group_heatmap(female_heatmap_data, "Health")

# Save heatmaps
save_plot(
  filename = file.path(current_health_base, "sex_stratified", "heatmap", "male_lifestyle.svg"),
  plot = male_lifestyle_heatmap,
  width = 12,
  height = 6,
  dpi = 300
)

save_plot(
  filename = file.path(current_health_base, "sex_stratified", "heatmap", "male_clinical.svg"),
  plot = male_clinical_heatmap,
  width = 12,
  height = 6,
  dpi = 300
)

save_plot(
  filename = file.path(current_health_base, "sex_stratified", "heatmap", "male_health.svg"),
  plot = male_health_heatmap,
  width = 12,
  height = 6,
  dpi = 300
)

save_plot(
  filename = file.path(current_health_base, "sex_stratified", "heatmap", "female_lifestyle.svg"),
  plot = female_lifestyle_heatmap,
  width = 12,
  height = 6,
  dpi = 300
)

save_plot(
  filename = file.path(current_health_base, "sex_stratified", "heatmap", "female_clinical.svg"),
  plot = female_clinical_heatmap,
  width = 12,
  height = 6,
  dpi = 300
)

save_plot(
  filename = file.path(current_health_base, "sex_stratified", "heatmap", "female_health.svg"),
  plot = female_health_heatmap,
  width = 12,
  height = 6,
  dpi = 300
)
```

```{r sex_stratified_forest_tables}
# Create output directory
output_dir_sex <- file.path(current_health_base, "sex_stratified", "forest_table")
dir.create(output_dir_sex, showWarnings = FALSE, recursive = TRUE)

# Define all outcomes
all_outcomes <- c(lifestyle_outcomes, clinical_biomarkers, health_outcomes, binary_outcomes)

# Create and save forest tables for each sex and outcome
for (sex_label in c("Male", "Female")) {
  sex_data <- all_sex_stratified_results |> filter(sex_strata == sex_label)
  
  for (outcome_name in all_outcomes) {
    # Filter for this outcome
    outcome_data <- sex_data |> 
      filter(outcome == outcome_name, is.na(error_message))
    
    if (nrow(outcome_data) == 0) next
    
    # Determine display name
    display_name <- case_when(
      outcome_name == "whr" ~ "Waist-Hip Ratio",
      outcome_name == "bmi" ~ "Body Mass Index", 
      outcome_name == "edyrs" ~ "Education Years",
      outcome_name == "glucose" ~ "Glucose",
      outcome_name == "triglycerides" ~ "Triglycerides",
      outcome_name == "hba1c" ~ "HbA1c",
      outcome_name == "crp" ~ "C-Reactive Protein",
      outcome_name == "total_hdl_ratio" ~ "Total/HDL Ratio",
      outcome_name == "egfr_cr_cys" ~ "eGFR",
      outcome_name == "fi_10" ~ "Frailty Index",
      outcome_name == "telomere_length" ~ "Telomere Length",
      outcome_name == "eversmok" ~ "Ever Smoked",
      outcome_name == "exercise_how_often" ~ "Exercise Frequency",
      TRUE ~ outcome_name
    )
    
    title <- paste0(display_name, " - ", sex_label, "s")
    
    # Create forest table (reusing the same create_forest_table logic)
    is_binary <- all(outcome_data$model_type == "logistic")
    
    forest_data <- outcome_data |>
      mutate(
        effect_size = if_else(model_type == "linear", standardized_estimate, odds_ratio),
        effect_lower = if_else(model_type == "linear", standardized_ci_lower, ci_lower),
        effect_upper = if_else(model_type == "linear", standardized_ci_upper, ci_upper),
        significant = FDR < 0.05,
        Organ_Display = case_when(
          predictor == "Brain" ~ "Brain",
          predictor == "Heart" ~ "Heart", 
          predictor == "Kidney" ~ "Kidney",
          predictor == "Liver" ~ "Liver",
          predictor == "Lung" ~ "Lung",
          predictor == "Muscle" ~ "Muscle",
          predictor == "Pancreas" ~ "Pancreas",
          predictor == "Prostate" ~ "Prostate",
          predictor == "Ovary" ~ "Ovary",
          TRUE ~ predictor
        )
      ) |>
      arrange(desc(effect_size)) |>
      mutate(
        y_pos = rev(seq_along(predictor)),
        Organ_Display = factor(Organ_Display, levels = unique(Organ_Display))
      )
    
    if (nrow(forest_data) == 0) next
    
    # Determine x-axis limits
    if (is_binary) {
      x_min <- min(forest_data$effect_lower, na.rm = TRUE)
      x_max <- max(forest_data$effect_upper, na.rm = TRUE)
      pad <- 0.1 * (x_max - x_min)
      x_limits <- c(max(0.1, min(0.5, x_min - pad)), max(1.5, x_max + pad))
    } else {
      x_min <- min(forest_data$effect_lower, na.rm = TRUE)
      x_max <- max(forest_data$effect_upper, na.rm = TRUE)
      pad <- 0.1 * (x_max - x_min)
      x_limits <- c(min(-0.5, x_min - pad), max(0.5, x_max + pad))
    }
    
    legend_x_left <- x_limits[1] + 0.05 * (x_limits[2] - x_limits[1])
    legend_x_right <- x_limits[1] + 0.55 * (x_limits[2] - x_limits[1])
    
    # Create table data
    tab <- forest_data |>
      transmute(
        y_pos, 
        `Organ age` = Organ_Display, 
        `Effect Size` = sprintf("%.2f (%.2f-%.2f)", effect_size, effect_lower, effect_upper),
        `FDR` = sprintf("%.2e", FDR)
      )
    
    x_pos <- tibble(col = c("Organ age", "Effect Size", "FDR"), x = c(1.0, 3.5, 6.0))
    table_long <- tab |>
      pivot_longer(-y_pos, names_to = "col", values_to = "val") |>
      left_join(x_pos, by = "col")
    
    # Table plot
    p_table <- ggplot(table_long, aes(x = x, y = y_pos, label = val)) +
      geom_text(hjust = c(0, 0, 1)[match(table_long$col, x_pos$col)], size = 3.2) +
      geom_text(
        data = x_pos |> mutate(y_pos = max(forest_data$y_pos) + 1), 
        aes(x = x, y = y_pos, label = col), 
        hjust = c(0, 0, 1), 
        fontface = "bold", 
        inherit.aes = FALSE, 
        size = 3.3
      ) +
      scale_y_continuous(breaks = NULL, limits = c(0.5, max(forest_data$y_pos) + 1.5)) +
      scale_x_continuous(limits = c(0.5, 7.0), expand = c(0, 0)) +
      labs(title = title) +
      theme_minimal(base_size = 11) +
      theme(
        plot.title = element_text(hjust = 0.1, size = 12), 
        axis.title = element_blank(), 
        axis.text = element_blank(), 
        axis.ticks = element_blank(), 
        panel.grid = element_blank(), 
        plot.margin = unit(c(12, 6, 6, 6), "pt")
      )
    
    # Forest plot
    p_forest <- ggplot(forest_data, aes(y = y_pos)) +
      geom_rect(
        aes(xmin = -Inf, xmax = Inf, ymin = y_pos - 0.5, ymax = y_pos + 0.5, 
            fill = factor(seq_along(predictor) %% 2)), 
        alpha = 0.6, show.legend = FALSE
      ) +
      scale_fill_manual(values = c("0" = "transparent", "1" = "gray95")) +
      geom_segment(
        aes(x = if (is_binary) 1 else 0, xend = if (is_binary) 1 else 0, 
            y = 0.5, yend = max(forest_data$y_pos) + 0.75), 
        linetype = "33", color = "grey10", size = 0.7
      ) +
      geom_errorbarh(
        aes(xmin = effect_lower, xmax = effect_upper, color = significant), 
        height = 0.15, size = 0.6
      ) +
      geom_point(aes(x = effect_size, color = significant), size = 2.5, shape = 16) +
      annotate(
        "text", x = legend_x_left, y = max(forest_data$y_pos) + 1.5, 
        label = "● Significant (FDR < 0.05)", hjust = 0.35, size = 3, color = "black"
      ) +
      annotate(
        "text", x = legend_x_right, y = max(forest_data$y_pos) + 1.5, 
        label = "● Non-significant", hjust = -0.65, size = 3, color = "gray80"
      ) +
      scale_color_manual(values = c("TRUE" = "black", "FALSE" = "gray80")) +
      scale_x_continuous(limits = x_limits, expand = c(0, 0)) +
      scale_y_continuous(breaks = NULL, limits = c(0.2, max(forest_data$y_pos) + 1.5)) +
      labs(x = if (is_binary) "Odds Ratio (95% CI)" else "Standardized Effect (95% CI)", y = NULL) +
      theme_minimal(base_size = 11) +
      theme(
        axis.text.y = element_blank(), 
        axis.text.x = element_text(size = 9), 
        axis.title.x = element_text(size = 10), 
        panel.grid.major.y = element_blank(), 
        panel.grid.minor = element_blank(), 
        panel.grid.major.x = element_blank(), 
        plot.margin = unit(c(12, 12, 6, 0), "pt"), 
        legend.position = "none"
      ) +
      coord_cartesian(clip = "off")
    
    plot_combined <- p_table + p_forest + plot_layout(widths = c(2.5, 2))
    
    # Save plot
    save_plot(
      filename = file.path(output_dir_sex, paste0("forest_", tolower(sex_label), "_", outcome_name, ".svg")),
      plot = plot_combined,
      width = 8,
      height = 5,
      dpi = 300
    )
  }
}

# Create CSV tables directory for sex-stratified results
csv_dir_sex <- file.path(current_health_base, "sex_stratified", "tables")
dir.create(csv_dir_sex, showWarnings = FALSE, recursive = TRUE)

# Save table data as CSV for sex-stratified analyses
for (sex_label in c("Male", "Female")) {
  sex_data <- all_sex_stratified_results |> filter(sex_strata == sex_label)
  
  for (outcome_name in all_outcomes) {
    outcome_data <- sex_data |> 
      filter(outcome == outcome_name, is.na(error_message))
    
    if (nrow(outcome_data) == 0) next
    
    tab <- outcome_data |>
      mutate(
        effect_size = if_else(model_type == "linear", standardized_estimate, odds_ratio),
        effect_lower = if_else(model_type == "linear", standardized_ci_lower, ci_lower),
        effect_upper = if_else(model_type == "linear", standardized_ci_upper, ci_upper),
        use_sci = pmax(abs(effect_size), abs(effect_lower), abs(effect_upper), na.rm = TRUE) >= 10,
        effect_formatted = if_else(use_sci,
          sprintf("%.1e (%.1e-%.1e)", effect_size, effect_lower, effect_upper),
          sprintf("%.2f (%.2f-%.2f)", effect_size, effect_lower, effect_upper)),
        Organ_Display = case_when(
          predictor == "Brain" ~ "Brain",
          predictor == "Heart" ~ "Heart",
          predictor == "Kidney" ~ "Kidney",
          predictor == "Liver" ~ "Liver",
          predictor == "Lung" ~ "Lung",
          predictor == "Muscle" ~ "Muscle",
          predictor == "Pancreas" ~ "Pancreas",
          predictor == "Prostate" ~ "Prostate",
          predictor == "Ovary" ~ "Ovary",
          TRUE ~ predictor
        )
      ) |>
      select(Organ = Organ_Display, `Effect Size (95% CI)` = effect_formatted, FDR)
    
    filename <- paste0(tolower(sex_label), "_", outcome_name, ".csv")
    write.csv(tab, file = file.path(csv_dir_sex, filename), row.names = FALSE)
  }
}
```

## Smoking Discordant Twin Analysis

```{r smoking_discordant_helpers}
run_smoking_discordant <- function(predictor_df, mz_only = FALSE) {
  predictors <- setdiff(colnames(predictor_df), "twin_id")
  
  discordant_twins <- twins_analysis |>
    group_by(pair_id) |>
    filter(
      n() == 2,
      if (mz_only) all(bestzyg == 1) else TRUE,
      sum(eversmok == 1, na.rm = TRUE) == 1
    ) |>
    ungroup()
  
  map_dfr(predictors, function(pred) {
    df <- discordant_twins |>
      left_join(predictor_df |> select(twin_id, all_of(pred)), by = "twin_id") |>
      filter(!is.na(.data[[pred]]))
    
    if (pred %in% c("Ovary", "Prostate")) {
      df <- df |> filter(sex == if (pred == "Ovary") 2 else 1)
    }
    
    if (n_distinct(df$pair_id) < 3) {
      return(tibble(predictor = pred, estimate = NA_real_, std_error = NA_real_,
                   p_value = NA_real_, odds_ratio = NA_real_, ci_lower = NA_real_,
                   ci_upper = NA_real_, error_message = "Insufficient pairs"))
    }
    
    tryCatch({
      fit <- clogit(as.formula(paste0("eversmok ~ scale(`", pred, "`) + strata(pair_id)")), data = df)
      est <- as.numeric(coef(fit)[1])
      se <- sqrt(diag(vcov(fit)))[1]
      p <- summary(fit)$coefficients[1, "Pr(>|z|)"]
      
      tibble(
        predictor = pred,
        estimate = est,
        std_error = se,
        p_value = as.numeric(p),
        odds_ratio = exp(est),
        ci_lower = exp(est - 1.96 * se),
        ci_upper = exp(est + 1.96 * se),
        error_message = NA_character_
      )
    }, error = function(e) {
      tibble(predictor = pred, estimate = NA_real_, std_error = NA_real_,
             p_value = NA_real_, odds_ratio = NA_real_, ci_lower = NA_real_,
             ci_upper = NA_real_, error_message = e$message)
    })
  }) |>
    mutate(FDR = p.adjust(p_value, method = "fdr"))
}
```

```{r smoking_discordant_results}
smoking_discordant_all <- run_smoking_discordant(organ_age_mortality, mz_only = FALSE) |>
  mutate(analysis = "All discordant pairs")

smoking_discordant_mz <- run_smoking_discordant(organ_age_mortality, mz_only = TRUE) |>
  mutate(analysis = "MZ discordant pairs")
```

## Exercise Discordant Twin Analysis

```{r exercise_discordant_helpers}
run_exercise_discordant <- function(predictor_df, mz_only = FALSE) {
  predictors <- setdiff(colnames(predictor_df), "twin_id")
  
  discordant_twins <- twins_analysis |>
    group_by(pair_id) |>
    filter(
      n() == 2,
      if (mz_only) all(bestzyg == 1) else TRUE,
      sum(exercise_how_often == 1, na.rm = TRUE) == 1
    ) |>
    ungroup()
  
  map_dfr(predictors, function(pred) {
    df <- discordant_twins |>
      left_join(predictor_df |> select(twin_id, all_of(pred)), by = "twin_id") |>
      filter(!is.na(.data[[pred]]))
    
    if (pred %in% c("Ovary", "Prostate")) {
      df <- df |> filter(sex == if (pred == "Ovary") 2 else 1)
    }
    
    if (n_distinct(df$pair_id) < 3) {
      return(tibble(predictor = pred, estimate = NA_real_, std_error = NA_real_,
                   p_value = NA_real_, odds_ratio = NA_real_, ci_lower = NA_real_,
                   ci_upper = NA_real_, error_message = "Insufficient pairs"))
    }
    
    tryCatch({
      fit <- clogit(as.formula(paste0("exercise_how_often ~ scale(`", pred, "`) + strata(pair_id)")), data = df)
      est <- as.numeric(coef(fit)[1])
      se <- sqrt(diag(vcov(fit)))[1]
      p <- summary(fit)$coefficients[1, "Pr(>|z|)"]
      
      tibble(
        predictor = pred,
        estimate = est,
        std_error = se,
        p_value = as.numeric(p),
        odds_ratio = exp(est),
        ci_lower = exp(est - 1.96 * se),
        ci_upper = exp(est + 1.96 * se),
        error_message = NA_character_
      )
    }, error = function(e) {
      tibble(predictor = pred, estimate = NA_real_, std_error = NA_real_,
             p_value = NA_real_, odds_ratio = NA_real_, ci_lower = NA_real_,
             ci_upper = NA_real_, error_message = e$message)
    })
  }) |>
    mutate(FDR = p.adjust(p_value, method = "fdr"))
}
```

```{r exercise_discordant_results}
exercise_discordant_all <- run_exercise_discordant(organ_age_mortality, mz_only = FALSE) |>
  mutate(analysis = "All discordant pairs")

exercise_discordant_mz <- run_exercise_discordant(organ_age_mortality, mz_only = TRUE) |>
  mutate(analysis = "MZ discordant pairs")
```

```{r transform_discordant_for_within_pair}
# Transform discordant results to match within-pair structure for harmonized output
# Smoking - All Pairs
smoking_within_pair_all <- smoking_discordant_all |>
  mutate(
    outcome = "eversmok",
    standardized_estimate = log(odds_ratio),
    standardized_ci_lower = log(ci_lower),
    standardized_ci_upper = log(ci_upper),
    model_type = "logistic",
    organ_age_model = "mortality",
    analysis_type = "within_pair",
    pair_type = "all"
  )

# Smoking - MZ Pairs
smoking_within_pair_mz <- smoking_discordant_mz |>
  mutate(
    outcome = "eversmok",
    standardized_estimate = log(odds_ratio),
    standardized_ci_lower = log(ci_lower),
    standardized_ci_upper = log(ci_upper),
    model_type = "logistic",
    organ_age_model = "mortality",
    analysis_type = "within_pair",
    pair_type = "mz"
  )

# Exercise - All Pairs
exercise_within_pair_all <- exercise_discordant_all |>
  mutate(
    outcome = "exercise_how_often",
    standardized_estimate = log(odds_ratio),
    standardized_ci_lower = log(ci_lower),
    standardized_ci_upper = log(ci_upper),
    model_type = "logistic",
    organ_age_model = "mortality",
    analysis_type = "within_pair",
    pair_type = "all"
  )

# Exercise - MZ Pairs
exercise_within_pair_mz <- exercise_discordant_mz |>
  mutate(
    outcome = "exercise_how_often",
    standardized_estimate = log(odds_ratio),
    standardized_ci_lower = log(ci_lower),
    standardized_ci_upper = log(ci_upper),
    model_type = "logistic",
    organ_age_model = "mortality",
    analysis_type = "within_pair",
    pair_type = "mz"
  )
```

```{r discordant_forest_helpers}
create_discordant_forest_table <- function(data, title, n_pairs, main_color = "black") {
  
  forest_data <- data |> 
    filter(is.na(error_message))
  
  if (nrow(forest_data) == 0) return(NULL)
  
  # Add n_pairs to title
  title_with_n <- paste0(title, " (n=", n_pairs, " pairs)")
  
  forest_data <- forest_data |>
    mutate(
      significant = FDR < 0.05,
      Organ_Display = case_when(
        predictor == "Brain" ~ "Brain",
        predictor == "Heart" ~ "Heart", 
        predictor == "Kidney" ~ "Kidney",
        predictor == "Liver" ~ "Liver",
        predictor == "Lung" ~ "Lung",
        predictor == "Muscle" ~ "Muscle",
        predictor == "Pancreas" ~ "Pancreas",
        predictor == "Prostate" ~ "Prostate",
        predictor == "Ovary" ~ "Ovary",
        TRUE ~ predictor
      )
    ) |>
    arrange(desc(odds_ratio)) |>
    mutate(
      y_pos = rev(seq_along(predictor)),
      Organ_Display = factor(Organ_Display, levels = unique(Organ_Display))
    )
  
  x_min <- min(forest_data$ci_lower, na.rm = TRUE)
  x_max <- max(forest_data$ci_upper, na.rm = TRUE)
  pad <- 0.1 * (x_max - x_min)
  x_limits <- c(max(0.1, min(0.5, x_min - pad)), max(1.5, x_max + pad))
  
  legend_x_left <- x_limits[1] + 0.05 * (x_limits[2] - x_limits[1])
  legend_x_right <- x_limits[1] + 0.55 * (x_limits[2] - x_limits[1])
  
  tab <- forest_data |>
    transmute(
      y_pos, 
      `Organ age` = Organ_Display, 
      `Effect Size` = sprintf("%.2f (%.2f-%.2f)", odds_ratio, ci_lower, ci_upper),
      `FDR` = sprintf("%.2e", FDR)
    )
  
  x_pos <- tibble(col = c("Organ age", "Effect Size", "FDR"), x = c(1.0, 3.5, 6.0))
  table_long <- tab |>
    pivot_longer(-y_pos, names_to = "col", values_to = "val") |>
    left_join(x_pos, by = "col")
  
  p_table <- ggplot(table_long, aes(x = x, y = y_pos, label = val)) +
    geom_text(hjust = c(0, 0, 1)[match(table_long$col, x_pos$col)], size = 3.2) +
    geom_text(
      data = x_pos |> mutate(y_pos = max(forest_data$y_pos) + 1), 
      aes(x = x, y = y_pos, label = col), 
      hjust = c(0, 0, 1), 
      fontface = "bold", 
      inherit.aes = FALSE, 
      size = 3.3
    ) +
    scale_y_continuous(breaks = NULL, limits = c(0.5, max(forest_data$y_pos) + 1.5)) +
    scale_x_continuous(limits = c(0.5, 7.0), expand = c(0, 0)) +
    labs(title = title_with_n) +
    theme_minimal(base_size = 11) +
    theme(
      plot.title = element_text(hjust = 0.1, size = 12), 
      axis.title = element_blank(), 
      axis.text = element_blank(), 
      axis.ticks = element_blank(), 
      panel.grid = element_blank(), 
      plot.margin = unit(c(12, 6, 6, 6), "pt")
    )
  
  p_forest <- ggplot(forest_data, aes(y = y_pos)) +
    geom_rect(
      aes(xmin = -Inf, xmax = Inf, ymin = y_pos - 0.5, ymax = y_pos + 0.5, 
          fill = factor(seq_along(predictor) %% 2)), 
      alpha = 0.6, show.legend = FALSE
    ) +
    scale_fill_manual(values = c("0" = "transparent", "1" = "gray95")) +
    geom_segment(
      aes(x = 1, xend = 1, y = 0.5, yend = max(forest_data$y_pos) + 0.75), 
      linetype = "33", color = "grey10", size = 0.7
    ) +
    geom_errorbarh(
      aes(xmin = ci_lower, xmax = ci_upper, color = significant), 
      height = 0.15, size = 0.6
    ) +
    geom_point(aes(x = odds_ratio, color = significant), size = 2.5, shape = 16) +
    annotate(
      "text", x = legend_x_left, y = max(forest_data$y_pos) + 1.5, 
      label = "● Significant (FDR < 0.05)", hjust = 0.35, size = 3, color = main_color
    ) +
    annotate(
      "text", x = legend_x_right, y = max(forest_data$y_pos) + 1.5, 
      label = "● Non-significant", hjust = -0.65, size = 3, color = "gray80"
    ) +
    scale_color_manual(values = c("TRUE" = main_color, "FALSE" = "gray80")) +
    scale_x_continuous(limits = x_limits, expand = c(0, 0)) +
    scale_y_continuous(breaks = NULL, limits = c(0.2, max(forest_data$y_pos) + 1.5)) +
    labs(x = "Odds Ratio (95% CI)", y = NULL) +
    theme_minimal(base_size = 11) +
    theme(
      axis.text.y = element_blank(), 
      axis.text.x = element_text(size = 9), 
      axis.title.x = element_text(size = 10), 
      panel.grid.major.y = element_blank(), 
      panel.grid.minor = element_blank(), 
      panel.grid.major.x = element_blank(), 
      plot.margin = unit(c(12, 12, 6, 0), "pt"), 
      legend.position = "none"
    ) +
    coord_cartesian(clip = "off")
  
  p_table + p_forest + plot_layout(widths = c(2.5, 2))
}
```

```{r calculate_discordant_pair_counts}
# Calculate number of discordant pairs for focused forest tables
calculate_binary_discordant_pair_count <- function(outcome_var, mz_only = FALSE) {
  twins_analysis |>
    group_by(pair_id) |>
    filter(
      n() == 2,
      if (mz_only) all(bestzyg == 1) else TRUE,
      sum(.data[[outcome_var]] == 1, na.rm = TRUE) == 1
    ) |>
    summarise() |>
    nrow()
}

n_smoking_all <- calculate_binary_discordant_pair_count("eversmok", mz_only = FALSE)
n_smoking_mz <- calculate_binary_discordant_pair_count("eversmok", mz_only = TRUE)
n_exercise_all <- calculate_binary_discordant_pair_count("exercise_how_often", mz_only = FALSE)
n_exercise_mz <- calculate_binary_discordant_pair_count("exercise_how_often", mz_only = TRUE)
```

```{r create_focused_forest_table}
create_focused_discordant_forest_table <- function(data, title, n_pairs, main_color = "black") {
  
  forest_data <- data |> 
    filter(is.na(error_message)) |>
    filter(predictor %in% c("Lung", "Gastrointestinal_tract", "Kidney_urinary"))
  
  if (nrow(forest_data) == 0) return(NULL)
  
  # Add n_pairs to title
  title_with_n <- paste0(title, " (n=", n_pairs, " pairs)")
  
  forest_data <- forest_data |>
    mutate(
      significant = FDR < 0.05,
      Organ_Display = case_when(
        predictor == "Lung" ~ "Lung",
        predictor == "Gastrointestinal_tract" ~ "Gastrointestinal",
        predictor == "Kidney_urinary" ~ "Kidney and Bladder",
        TRUE ~ predictor
      )
    ) |>
    arrange(desc(odds_ratio)) |>
    mutate(
      y_pos = rev(seq_along(predictor)),
      Organ_Display = factor(Organ_Display, levels = unique(Organ_Display))
    )
  
  x_min <- min(forest_data$ci_lower, na.rm = TRUE)
  x_max <- max(forest_data$ci_upper, na.rm = TRUE)
  pad <- 0.1 * (x_max - x_min)
  x_limits <- c(max(0.1, min(0.5, x_min - pad)), max(1.5, x_max + pad))
  
  legend_x_left <- x_limits[1] + 0.05 * (x_limits[2] - x_limits[1])
  legend_x_right <- x_limits[1] + 0.55 * (x_limits[2] - x_limits[1])
  
  tab <- forest_data |>
    transmute(
      y_pos, 
      `Organ age` = Organ_Display, 
      `Effect Size` = sprintf("%.2f (%.2f-%.2f)", odds_ratio, ci_lower, ci_upper),
      `FDR` = sprintf("%.2e", FDR)
    )
  
  x_pos <- tibble(col = c("Organ age", "Effect Size", "FDR"), x = c(1.0, 3.5, 6.0))
  table_long <- tab |>
    pivot_longer(-y_pos, names_to = "col", values_to = "val") |>
    left_join(x_pos, by = "col")
  
  p_table <- ggplot(table_long, aes(x = x, y = y_pos, label = val)) +
    geom_text(hjust = c(0, 0, 1)[match(table_long$col, x_pos$col)], size = 3.2) +
    geom_text(
      data = x_pos |> mutate(y_pos = max(forest_data$y_pos) + 1), 
      aes(x = x, y = y_pos, label = col), 
      hjust = c(0, 0, 1), 
      fontface = "bold", 
      inherit.aes = FALSE, 
      size = 3.3
    ) +
    scale_y_continuous(breaks = NULL, limits = c(0.5, max(forest_data$y_pos) + 1.5)) +
    scale_x_continuous(limits = c(0.5, 7.0), expand = c(0, 0)) +
    labs(title = title_with_n) +
    theme_minimal(base_size = 11) +
    theme(
      plot.title = element_text(hjust = 0.1, size = 12), 
      axis.title = element_blank(), 
      axis.text = element_blank(), 
      axis.ticks = element_blank(), 
      panel.grid = element_blank(), 
      plot.margin = unit(c(12, 6, 6, 6), "pt")
    )
  
  p_forest <- ggplot(forest_data, aes(y = y_pos)) +
    geom_rect(
      aes(xmin = -Inf, xmax = Inf, ymin = y_pos - 0.5, ymax = y_pos + 0.5, 
          fill = factor(seq_along(predictor) %% 2)), 
      alpha = 0.6, show.legend = FALSE
    ) +
    scale_fill_manual(values = c("0" = "transparent", "1" = "gray95")) +
    geom_segment(
      aes(x = 1, xend = 1, y = 0.5, yend = max(forest_data$y_pos) + 0.75), 
      linetype = "33", color = "grey10", size = 0.7
    ) +
    geom_errorbarh(
      aes(xmin = ci_lower, xmax = ci_upper, color = significant), 
      height = 0.15, size = 0.6
    ) +
    geom_point(aes(x = odds_ratio, color = significant), size = 2.5, shape = 16) +
    annotate(
      "text", x = legend_x_left, y = max(forest_data$y_pos) + 1.5, 
      label = "● Significant (FDR < 0.05)", hjust = 0.35, size = 3, color = main_color
    ) +
    annotate(
      "text", x = legend_x_right, y = max(forest_data$y_pos) + 1.5, 
      label = "● Non-significant", hjust = -0.65, size = 3, color = "gray80"
    ) +
    scale_color_manual(values = c("TRUE" = main_color, "FALSE" = "gray80")) +
    scale_x_continuous(limits = x_limits, expand = c(0, 0)) +
    scale_y_continuous(breaks = NULL, limits = c(0.2, max(forest_data$y_pos) + 1.5)) +
    labs(x = "Odds Ratio (95% CI)", y = NULL) +
    theme_minimal(base_size = 11) +
    theme(
      axis.text.y = element_blank(), 
      axis.text.x = element_text(size = 9), 
      axis.title.x = element_text(size = 10), 
      panel.grid.major.y = element_blank(), 
      panel.grid.minor = element_blank(), 
      panel.grid.major.x = element_blank(), 
      plot.margin = unit(c(12, 12, 6, 0), "pt"), 
      legend.position = "none"
    ) +
    coord_cartesian(clip = "off")
  
  p_table + p_forest + plot_layout(widths = c(2.5, 2))
}
```

```{r create_focused_smoking_forest_tables}
# Create focused forest tables for smoking results (lung, gastrointestinal, kidney/bladder only)
output_dir_focused <- file.path(current_health_base, "discordant", "forest_table")
dir.create(output_dir_focused, showWarnings = FALSE, recursive = TRUE)

focused_forest_tables <- list(
  smoking_all_focused = create_focused_discordant_forest_table(smoking_discordant_all, "Smoking - All Discordant Pairs (Focused)", n_smoking_all),
  smoking_mz_focused = create_focused_discordant_forest_table(smoking_discordant_mz, "Smoking - MZ Discordant Pairs (Focused)", n_smoking_mz)
)

for (name in names(focused_forest_tables)) {
  if (!is.null(focused_forest_tables[[name]])) {
    save_plot(
      filename = file.path(output_dir_focused, paste0("forest_", name, ".svg")),
      plot = focused_forest_tables[[name]],
      width = 8,
      height = 4,
      dpi = 300
    )
  }
}

# Create CSV tables directory for focused discordant results
csv_dir_focused <- file.path(current_health_base, "discordant", "tables")
dir.create(csv_dir_focused, showWarnings = FALSE, recursive = TRUE)

# Save CSV for focused smoking - all pairs
smoking_all_data <- smoking_discordant_all |>
  filter(is.na(error_message), predictor %in% c("Lung", "Gastrointestinal_tract", "Kidney_urinary"))

if (nrow(smoking_all_data) > 0) {
  tab <- smoking_all_data |>
    mutate(
      use_sci = pmax(abs(odds_ratio), abs(ci_lower), abs(ci_upper), na.rm = TRUE) >= 10,
      use_sci = if_else(is.na(use_sci), FALSE, use_sci),
      or_formatted = if_else(use_sci,
        sprintf("%.1e (%.1e-%.1e)", odds_ratio, ci_lower, ci_upper),
        sprintf("%.2f (%.2f-%.2f)", odds_ratio, ci_lower, ci_upper)),
      Organ_Display = case_when(
        predictor == "Gastrointestinal_tract" ~ "Gastrointestinal",
        predictor == "Kidney_urinary" ~ "Kidney and Bladder",
        TRUE ~ predictor
      )
    ) |>
    select(Organ = Organ_Display, `OR (95% CI)` = or_formatted, FDR)
  
  write.csv(tab, file = file.path(csv_dir_focused, "smoking_all_pairs_focused.csv"), row.names = FALSE)
}

# Save CSV for focused smoking - MZ pairs
smoking_mz_data <- smoking_discordant_mz |>
  filter(is.na(error_message), predictor %in% c("Lung", "Gastrointestinal_tract", "Kidney_urinary"))

if (nrow(smoking_mz_data) > 0) {
  tab <- smoking_mz_data |>
    mutate(
      use_sci = pmax(abs(odds_ratio), abs(ci_lower), abs(ci_upper), na.rm = TRUE) >= 10,
      use_sci = if_else(is.na(use_sci), FALSE, use_sci),
      or_formatted = if_else(use_sci,
        sprintf("%.1e (%.1e-%.1e)", odds_ratio, ci_lower, ci_upper),
        sprintf("%.2f (%.2f-%.2f)", odds_ratio, ci_lower, ci_upper)),
      Organ_Display = case_when(
        predictor == "Gastrointestinal_tract" ~ "Gastrointestinal",
        predictor == "Kidney_urinary" ~ "Kidney and Bladder",
        TRUE ~ predictor
      )
    ) |>
    select(Organ = Organ_Display, `OR (95% CI)` = or_formatted, FDR)
  
  write.csv(tab, file = file.path(csv_dir_focused, "smoking_mz_pairs_focused.csv"), row.names = FALSE)
}
```

# Prevalent Disease Analysis

**Analysis Goal:**
Examine whether organ ages are associated with disease presence at baseline using logistic regression. Unlike Cox analyses that exclude prevalent cases, this analysis specifically focuses on prevalent disease (disease present at baseline).

**Model:** `prevalent_disease ~ organ_age + selected_covariates`  
**Method:** Logistic regression with cluster-robust standard errors  
**Multiple testing:** FDR correction applied within each disease

## Disease Configuration

```{r prevalent_disease_config}
diseases_config <- list(
  diabetes = list(var = "diabetes", date = "diabetes_date", name = "Diabetes"),
  dementia = list(var = "dementia", date = "dementia_date", name = "Dementia"),
  parkinsons = list(var = "parkinson_and_parkinsonism", date = "parkinson_and_parkinsonism_date", name = "Parkinson"),
  ischemic_heart_disease = list(var = "ischemic_heart_disease", date = "ischemic_heart_disease_date", name = "Ischemic heart disease"),
  atrial_fibrillation = list(var = "atrial_fibrillation", date = "atrial_fibrillation_date", name = "Atrial fibrillation"),
  cerebrovascular_disease = list(var = "cerebrovascular_disease", date = "cerebrovascular_disease_date", name = "Cerebrovascular disease"),
  heart_failure = list(var = "heart_failure", date = "heart_failure_date", name = "Heart failure"),
  melanoma = list(var = "Melanoma", date = "Melanoma_date", name = "Melanoma"),
  prostate_cancer = list(var = "Prostate cancer", date = "Prostate cancer_date", name = "Prostate cancer"),
  multiple_myeloma = list(var = "Multiple myeloma", date = "Multiple myeloma_date", name = "Multiple myeloma"),
  brain_cancer = list(var = "Brain cancer", date = "Brain cancer_date", name = "Brain cancer"),
  lung_cancer = list(var = "Lung cancer", date = "Lung cancer_date", name = "Lung cancer"),
  breast_cancer = list(var = "Breast cancer", date = "Breast cancer_date", name = "Breast cancer"),
  colorectal_cancer = list(var = "Colorectal cancer", date = "Colorectal cancer_date", name = "Colorectal cancer"),
  kidney_cancer = list(var = "Kidney cancer", date = "Kidney cancer_date", name = "Kidney cancer"),
  bladder_cancer = list(var = "Bladder cancer", date = "Bladder cancer_date", name = "Bladder cancer"),
  esophageal_cancer = list(var = "Esophageal cancer", date = "Esophageal cancer_date", name = "Esophageal cancer"),
  stomach_cancer = list(var = "Stomach cancer", date = "Stomach cancer_date", name = "Stomach cancer"),
  liver_cancer = list(var = "Liver cancer", date = "Liver cancer_date", name = "Liver cancer"),
  lymphoma = list(var = "Lymphoma", date = "Lymphoma_date", name = "Lymphoma")
)

min_prevalent_cases <- ceiling(nrow(twins_analysis) * 0.01)

disease_prevalent_counts <- map_dfr(names(diseases_config), function(d) {
  spec <- diseases_config[[d]]
  prevalent_cases <- twins_analysis |>
    filter(!!sym(spec$var) == 1, !is.na(!!sym(spec$date)), !!sym(spec$date) <= checkdate) |>
    nrow()
  tibble(disease = d, prevalent_cases = prevalent_cases, eligible = prevalent_cases >= min_prevalent_cases)
})

eligible_diseases <- disease_prevalent_counts |> filter(eligible) |> pull(disease)
diseases <- diseases_config[names(diseases_config) %in% eligible_diseases]
```

## Analysis Functions

```{r prevalent_analysis_functions}
create_prevalent_disease_data <- function(disease_var, disease_date_var, disease_name) {
  twins_analysis |>
    filter(
      (!!sym(disease_var) == 0 | is.na(!!sym(disease_var))) |
      (!!sym(disease_var) == 1 & !is.na(!!sym(disease_date_var)) & !!sym(disease_date_var) <= checkdate)
    ) |>
    mutate(
      prevalent_disease = case_when(
        !!sym(disease_var) == 1 & !is.na(!!sym(disease_date_var)) & !!sym(disease_date_var) <= checkdate ~ 1,
        TRUE ~ 0
      )
    )
}

filter_complete_covariates <- function(data, covariates) {
  if (length(covariates) == 0) {
    return(data)
  }
  
  data |>
    filter(if_all(all_of(covariates), ~ !is.na(.x)))
}

apply_prevalent_sex_filter <- function(data, disease_name) {
  if (grepl("prostate", disease_name, ignore.case = TRUE)) {
    data |> filter(sex == 1)
  } else if (grepl("breast|ovarian", disease_name, ignore.case = TRUE)) {
    data |> filter(sex == 2)
  } else {
    data
  }
}

get_prevalent_model_covariates <- function(disease_name) {
  covariates <- get_covariates("prevalent_disease")
  
  if (grepl("prostate|breast|ovarian", disease_name, ignore.case = TRUE)) {
    covariates <- setdiff(covariates, "sex")
  }
  
  covariates
}

calculate_prevalent_forest_counts <- function(disease_var, disease_date_var, disease_name, time_window = NULL) {
  prevalent_data <- if (is.null(time_window)) {
    create_prevalent_disease_data(disease_var, disease_date_var, disease_name)
  } else {
    build_prevalent_time_window(disease_var, disease_date_var, time_window)
  }
  
  prevalent_data <- prevalent_data |>
    apply_prevalent_sex_filter(disease_name) |>
    filter_complete_covariates(get_prevalent_model_covariates(disease_name))
  
  list(
    cases = sum(prevalent_data$prevalent_disease == 1, na.rm = TRUE),
    sample_size = nrow(prevalent_data)
  )
}

calculate_prevalent_discordant_counts <- function(prevalent_data, disease_name, mz_only = FALSE) {
  discordant_twins <- prevalent_data |>
    group_by(pair_id) |>
    filter(
      n() == 2,
      if (mz_only) all(bestzyg == 1) else TRUE,
      sum(prevalent_disease == 1, na.rm = TRUE) == 1
    ) |>
    ungroup() |>
    apply_prevalent_sex_filter(disease_name) |>
    group_by(pair_id) |>
    filter(
      n() == 2,
      if (mz_only) all(bestzyg == 1) else TRUE,
      sum(prevalent_disease == 1, na.rm = TRUE) == 1
    ) |>
    ungroup()
  
  list(
    cases = sum(discordant_twins$prevalent_disease == 1, na.rm = TRUE),
    n_pairs = n_distinct(discordant_twins$pair_id)
  )
}

analyze_prevalent_disease_univariate <- function(prevalent_data, disease_name, predictor_df, predictor_name) {
  map_dfr(names(predictor_df)[-1], function(pred) {
    analysis_data <- prevalent_data |>
      left_join(predictor_df |> select(twin_id, all_of(pred)), by = "twin_id") |>
      filter(!is.na(!!sym(pred)), !is.na(prevalent_disease))
    
    # Filter by sex for sex-specific diseases
    if (grepl("prostate", disease_name, ignore.case = TRUE)) {
      analysis_data <- analysis_data |> filter(sex == 1)  # Males only
    } else if (grepl("breast|ovarian", disease_name, ignore.case = TRUE)) {
      analysis_data <- analysis_data |> filter(sex == 2)  # Females only
    }
    
    if (nrow(analysis_data) < 10) {
      return(tibble(
        disease = disease_name, predictor = pred, estimate = NA_real_, std_error = NA_real_,
        z_value = NA_real_, p_value = NA_real_, odds_ratio = NA_real_, ci_lower = NA_real_,
        ci_upper = NA_real_, model = predictor_name, analysis_type = "univariate"
      ))
    }
    
    covariates <- get_covariates("prevalent_disease")
    # Remove sex from covariates for sex-specific diseases since there's no variation
    if (grepl("prostate|breast|ovarian", disease_name, ignore.case = TRUE)) {
      covariates <- setdiff(covariates, "sex")
    }
    formula <- as.formula(paste("prevalent_disease ~", pred, 
                               if(length(covariates) > 0) paste("+", paste(covariates, collapse = " + ")) else ""))
    
    tryCatch({
      model <- glm(formula, data = analysis_data, family = binomial)
      cluster_se <- vcovCL(model, cluster = ~pair_id)
      coeftest_model <- coeftest(model, vcov = cluster_se)
      estimate <- coeftest_model[pred, "Estimate"]
      std_error <- coeftest_model[pred, "Std. Error"]
      
      tibble(
        disease = disease_name, predictor = pred, estimate = estimate, std_error = std_error,
        z_value = coeftest_model[pred, "z value"], p_value = coeftest_model[pred, "Pr(>|z|)"],
        odds_ratio = exp(estimate), ci_lower = exp(estimate - 1.96 * std_error),
        ci_upper = exp(estimate + 1.96 * std_error), model = predictor_name, analysis_type = "univariate"
      )
    }, error = function(e) {
      tibble(
        disease = disease_name, predictor = pred, estimate = NA_real_, std_error = NA_real_,
        z_value = NA_real_, p_value = NA_real_, odds_ratio = NA_real_, ci_lower = NA_real_,
        ci_upper = NA_real_, model = predictor_name, analysis_type = "univariate"
      )
    })
  })
}
```

## Forest Tables

```{r prevalent_forest_helpers}
create_prevalent_forest_table <- function(data, disease_name, analysis_type = "univariate", 
                                         model_type = "mortality", title = NULL, main_color = "black",
                                         time_window = NULL) {
  expected_model <- if(analysis_type == "univariate") model_type else paste0(model_type, "_multivariate")
  
  forest_data <- data |> filter(disease == disease_name, analysis_type == analysis_type, model == expected_model)
  if (nrow(forest_data) == 0) return(NULL)
  
  disease_config <- diseases[[disease_name]]
  if (is.null(disease_config)) {
    display_name <- disease_name
    disease_cases <- NA
    sample_size <- NA
  } else {
    display_name <- disease_config$name
    disease_var <- disease_config$var
    counts <- calculate_prevalent_forest_counts(
      disease_var = disease_var,
      disease_date_var = disease_config$date,
      disease_name = display_name,
      time_window = time_window
    )
    disease_cases <- counts$cases
    sample_size <- counts$sample_size
  }
  
  if (is.null(title)) {
    title <- paste(display_name, "(cases =", disease_cases, ", n =", sample_size, ")")
  }
  
  forest_data <- forest_data |>
    mutate(
      or = odds_ratio, or_lower = ci_lower, or_upper = ci_upper, fdr = FDR, significant = FDR < 0.05,
      errorbar_color = if_else(FDR < 0.05, "grey30", "gray80"),
      Organ_Display = case_when(
        predictor == "Gastrointestinal_tract" ~ "Gastrointestinal",
        predictor == "Kidney_urinary" ~ "Kidney and Bladder", TRUE ~ str_to_title(predictor)
      )
    ) |>
    arrange(desc(odds_ratio)) |>
    mutate(y_pos = rev(seq_along(predictor)), Organ_Display = factor(Organ_Display, levels = Organ_Display))
  
  # Dynamic x-axis limits with hard caps
  base_min <- 0.25
  base_max <- 3
  hard_min <- 0.05
  hard_max <- 10
  
  x_min <- suppressWarnings(min(forest_data$or_lower, na.rm = TRUE))
  x_max <- suppressWarnings(max(forest_data$or_upper, na.rm = TRUE))
  
  if (!is.finite(x_min)) x_min <- base_min
  if (!is.finite(x_max)) x_max <- base_max
  
  x_min <- max(x_min, 0.001)
  
  lower_margin_factor <- 0.9
  upper_margin_factor <- 1.1
  
  x_min <- min(base_min, x_min * lower_margin_factor)
  x_max <- max(base_max, x_max * upper_margin_factor)
  
  x_min <- max(hard_min, x_min)
  x_max <- min(hard_max, x_max)
  
  x_breaks <- pretty(c(x_min, x_max), n = 6)
  x_breaks <- x_breaks[x_breaks >= x_min & x_breaks <= x_max]
  
  # Add formatted OR column and detect if scientific notation is needed
  forest_data <- forest_data |>
    mutate(
      use_sci = pmax(abs(or), abs(or_lower), abs(or_upper), na.rm = TRUE) >= 10,
      use_sci = if_else(is.na(use_sci), FALSE, use_sci),
      or_formatted = if_else(
        use_sci,
        sprintf("%.1e (%.1e-%.1e)", or, or_lower, or_upper),
        sprintf("%.2f (%.2f-%.2f)", or, or_lower, or_upper)
      )
    )
  
  # Detect if we need wider table for scientific notation
  has_sci_notation <- any(forest_data$use_sci, na.rm = TRUE)
  table_width_ratio <- if (has_sci_notation) 3.2 else 2.5
  
  tab <- forest_data |>
    transmute(
      y_pos, `Organ age` = Organ_Display,
      `OR (95% CI)` = or_formatted,
      FDR = sprintf("%.2e", fdr)
    )
  
  x_pos <- tibble(col = c("Organ age", "OR (95% CI)", "FDR"), x = c(1.0, 4.0, 7.5))
  table_long <- tab |> pivot_longer(-y_pos, names_to = "col", values_to = "val") |> left_join(x_pos, by = "col")
  
  p_table <- ggplot(table_long, aes(x = x, y = y_pos, label = val)) +
    geom_text(hjust = c(0, 0, 1)[match(table_long$col, x_pos$col)], size = 3) +
    geom_text(data = x_pos |> mutate(y_pos = max(forest_data$y_pos) + 1), 
             aes(x = x, y = y_pos, label = col), hjust = c(0, 0, 1), fontface = "bold", 
             inherit.aes = FALSE, size = 3.3) +
    scale_y_continuous(breaks = NULL, labels = NULL, limits = c(0.5, max(forest_data$y_pos) + 1.5)) +
    scale_x_continuous(limits = c(0.5, 9.0), expand = c(0, 0)) +
    labs(title = title) +
    theme_minimal(base_size = 11) +
    theme(plot.title = element_text(hjust = 0.1, size = 12), axis.title = element_blank(),
         axis.text.x = element_blank(), axis.ticks = element_blank(), panel.grid = element_blank(),
         plot.margin = unit(c(12, 6, 6, 6), "pt"))
  
  # Determine which points are out of bounds and cap CIs to plot range
  forest_data <- forest_data |>
    mutate(
      out_of_bounds_point = or < x_min | or > x_max,
      or_lower_capped = pmax(or_lower, x_min),
      or_upper_capped = pmin(or_upper, x_max),
      has_any_value_outside = (or < x_min | or > x_max | or_lower < x_min | or_upper > x_max)
    )
  
  # Only plot data where the OR itself is within bounds
  data_in_bounds <- forest_data |> filter(!out_of_bounds_point)
  
  # Calculate legend positions
  legend_y <- max(forest_data$y_pos) + 1.5
  legend_left_x <- x_min + (x_max - x_min) * 0.03
  legend_right_x <- x_min + (x_max - x_min) * 0.60
  legend_bottom_y <- 0.25
  legend_bottom_x <- x_min + (x_max - x_min) * 0.60
  
  p_forest <- ggplot(forest_data, aes(y = y_pos)) +
    geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = y_pos - 0.5, ymax = y_pos + 0.5, 
                 fill = factor(seq_along(predictor) %% 2)), alpha = 0.6, show.legend = FALSE) +
    scale_fill_manual(values = c("0" = "transparent", "1" = "gray95")) +
    geom_segment(aes(x = 1, xend = 1, y = 0.5, yend = max(forest_data$y_pos) + 0.75), 
                linetype = "33", color = "grey10", size = 0.7) +
    {if (nrow(data_in_bounds) > 0) geom_errorbarh(data = data_in_bounds, aes(xmin = or_lower_capped, xmax = or_upper_capped, y = y_pos), color = data_in_bounds$errorbar_color, height = 0.15, size = 0.6, inherit.aes = FALSE)} +
    {if (nrow(data_in_bounds) > 0) geom_point(data = data_in_bounds, aes(x = or, color = significant), size = 2.5, shape = 16)} +
    {if (nrow(data_in_bounds |> filter(has_any_value_outside)) > 0) geom_text(data = data_in_bounds |> filter(has_any_value_outside), aes(x = or, y = y_pos + 0.25), label = "*", size = 3.5, color = "black")} +
    annotate("text", x = legend_left_x, y = legend_y, 
            label = "● Significant (FDR < 0.05)", hjust = 0, size = 2.6, color = main_color) +
    annotate("text", x = legend_right_x, y = legend_y, 
            label = "● Non-significant", hjust = 0, size = 2.6, color = "gray80") +
    {if (nrow(data_in_bounds |> filter(has_any_value_outside)) > 0) annotate("text", x = legend_bottom_x, y = legend_bottom_y, label = "* Value outside plot range", hjust = 1, size = 2.4, color = "black")} +
    scale_color_manual(values = c("TRUE" = main_color, "FALSE" = "gray80")) +
    scale_x_continuous(
      limits = c(x_min, x_max),
      breaks = x_breaks,
      labels = format(x_breaks, digits = 3, trim = TRUE)
    ) +
    scale_y_continuous(breaks = NULL, labels = NULL, limits = c(0.2, max(forest_data$y_pos) + 1.5)) +
    labs(x = "Odds Ratio (95% CI)", y = NULL) +
    theme_minimal(base_size = 11) +
    theme(axis.text.y = element_blank(), axis.text.x = element_text(size = 9),
         axis.title.x = element_text(size = 10), panel.grid = element_blank(),
         plot.margin = unit(c(12, 12, 6, 0), "pt"), legend.position = "none") +
    coord_cartesian(clip = "off")
  
  p_table + p_forest + plot_layout(widths = c(table_width_ratio, 2))
}

```

## Sensitivity Analysis: Time Windows

```{r prevalent_sensitivity_setup}
prevalent_time_windows <- c(5, 10)

build_prevalent_time_window <- function(disease_var, disease_date_var, years_back) {
  delta <- as.difftime(round(years_back * 365.25), units = "days")
  twins_analysis |>
    filter(
      (!!sym(disease_var) == 0 | is.na(!!sym(disease_var))) |
      (!!sym(disease_var) == 1 & !is.na(!!sym(disease_date_var)) & 
       !!sym(disease_date_var) <= checkdate & 
       !!sym(disease_date_var) >= checkdate - delta)
    ) |>
    mutate(
      prevalent_disease = case_when(
        !!sym(disease_var) == 1 & !is.na(!!sym(disease_date_var)) & 
        !!sym(disease_date_var) <= checkdate & 
        !!sym(disease_date_var) >= checkdate - delta ~ 1,
        TRUE ~ 0
      )
    )
}
```

```{r prevalent_sensitivity_analyses}
sensitivity_results <- map(prevalent_time_windows, function(tw) {
  cat("\n=== Analyzing", tw, "year time window ===\n")
  
  # Check eligible diseases for this window
  elig_diseases <- map_dfr(names(diseases_config), function(d) {
    sp <- diseases_config[[d]]
    delta <- as.difftime(round(tw * 365.25), units = "days")
    n_prev <- twins_analysis |>
      filter(
        !!sym(sp$var) == 1, !is.na(!!sym(sp$date)),
        !!sym(sp$date) <= checkdate,
        !!sym(sp$date) >= checkdate - delta
      ) |>
      nrow()
    tibble(disease = d, n_cases = n_prev, eligible = n_prev >= min_prevalent_cases)
  }) |>
    filter(eligible) |>
    pull(disease)
  
  if (length(elig_diseases) == 0) {
    cat("No eligible diseases for", tw, "year window\n")
    return(NULL)
  }
  
  cat("Eligible diseases:", length(elig_diseases), "\n")
  
  # Run analyses for eligible diseases
  results <- map(elig_diseases, function(disease_name) {
    sp <- diseases_config[[disease_name]]
    prev_data <- build_prevalent_time_window(sp$var, sp$date, tw)
    analyze_prevalent_disease_univariate(prev_data, sp$name, organ_age_mortality, "mortality")
  }) |> set_names(elig_diseases)
  
  # Combine and add FDR
  all_results <- bind_rows(results, .id = "disease_key") |>
    mutate(
      model_type = "logistic",
      outcome_type = "prevalent_disease",
      disease = disease_key,
      time_window = tw
    ) |>
    group_by(disease, analysis_type, model) |>
    mutate(FDR = p.adjust(p_value, method = "fdr")) |>
    ungroup()
  
  return(all_results)
}) |> set_names(paste0(prevalent_time_windows, "y"))

sensitivity_results <- compact(sensitivity_results)
```

```{r create_prevalent_heatmap_function}
create_prevalent_heatmap <- function(data, group_name) {
  group_data <- data |> filter(outcome_group %in% group_name)
  if (nrow(group_data) == 0) return(NULL)
  
  all_organs <- unique(group_data$predictor) |> na.omit()
  organ_order <- c(intersect(fixed_organ_order, all_organs), setdiff(all_organs, fixed_organ_order))
  
  group_matrix <- group_data |>
    select(outcome, predictor, effect_size) |>
    pivot_wider(names_from = predictor, values_from = effect_size, values_fill = 0) |>
    column_to_rownames("outcome") |>
    as.matrix()
  
  outcome_order <- if (nrow(group_matrix) > 1) {
    rownames(group_matrix)[hclust(dist(group_matrix), method = "ward.D2")$order]
  } else {
    rownames(group_matrix)
  }
  
  predictor_order <- intersect(organ_order, colnames(group_matrix))
  
  if (length(outcome_order) == 0 || length(predictor_order) == 0) return(NULL)
  
  # Panel-style control variables
  text_size_pt <- HEATMAP_TEXT_SIZE
  square_size <- text_size_pt / HEATMAP_SQUARE_SIZE_DIVISOR
  
  group_data_plot <- group_data |>
    mutate(
      outcome = factor(outcome, levels = outcome_order),
      predictor = factor(predictor, levels = predictor_order),
      outcome_num = (as.numeric(outcome) - 1) * square_size + square_size/2,
      predictor_num = (as.numeric(predictor) - 1) * square_size + square_size/2,
      effect_size_colored = if_else(impossible, NA_real_, if_else(significance != "", effect_size, NA_real_)),
      non_sig_marker = if_else(impossible, "", if_else(significance == "", "×", ""))
    )
  
  # Calculate dynamic limits (white-to-red only, no negative values)
  effect_range <- range(group_data$effect_size, na.rm = TRUE)
  buffer <- 0.1
  max_limit <- max(1.5, effect_range[2] + buffer)
  min_limit <- 0  # Start from 0 since no negative values
  
  breaks <- seq(0, max_limit, length.out = 4)
  labels <- sprintf("%.1f", breaks)
  
  ggplot(group_data_plot, aes(x = predictor_num, y = outcome_num, fill = effect_size_colored)) +
    geom_tile(width = square_size, height = square_size, color = NA) +
    geom_text(aes(x = predictor_num, y = outcome_num, label = non_sig_marker), size = 5.5, color = "darkgrey", family = "Helvetica", inherit.aes = FALSE) +
    scale_fill_gradientn(
      colors = c(
        "white",        # Start at 0
        "#C64D4D",      # Red (mid-high)
        "#B71C1C"       # Darker red (extreme high)
      ),
      values = scales::rescale(c(0, max_limit * 0.5, max_limit)),
      limits = c(0, max_limit),
      na.value = "white",
      name = "log(Odds\nRatio)",
      breaks = breaks,
      labels = labels
    ) +
    scale_x_continuous(
      breaks = (seq_along(predictor_order) - 1) * square_size + square_size/2,
      labels = predictor_order,
      expand = c(0, 0),
      limits = c(0, length(predictor_order) * square_size)
    ) +
    scale_y_continuous(
      breaks = (seq_along(outcome_order) - 1) * square_size + square_size/2,
      labels = outcome_order,
      expand = c(0, 0),
      limits = c(0, length(outcome_order) * square_size)
    ) +
    theme_minimal(base_family = "Helvetica") +
    theme(
      text = element_text(family = "Helvetica", color = "black"),
      axis.text.x = element_text(angle = 45, hjust = 1, size = HEATMAP_TEXT_SIZE, color = "black", family = "Helvetica"),
      axis.text.y = element_text(size = HEATMAP_TEXT_SIZE, hjust = 0, margin = margin(r = 10), color = "black", family = "Helvetica"),
      axis.title = element_blank(),
      axis.ticks = element_blank(),
      legend.position = "right",
      legend.title = element_text(size = 11, color = "black", family = "Helvetica"),
      legend.text = element_text(size = 9, color = "black", family = "Helvetica"),
      legend.key.height = unit(0.8, "cm"),
      legend.key.width = unit(0.5, "cm"),
      panel.grid = element_blank(),
      panel.spacing = unit(0, "lines"),
      panel.border = element_blank(),
      plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm")
    ) +
    coord_fixed(ratio = 1, expand = FALSE)
}
```

```{r prevalent_sensitivity_heatmaps}
sensitivity_heatmaps <- map(names(sensitivity_results), function(window_name) {
  tw <- as.numeric(gsub("y", "", window_name))
  results <- sensitivity_results[[window_name]]
  
  # Prepare heatmap data
  heatmap_data <- results |>
    filter(analysis_type == "univariate", model == "mortality") |>
    mutate(
      outcome_raw = disease,
      outcome = case_when(
        disease == "Diabetes" ~ "Diabetes",
        disease == "Dementia" ~ "Dementia",
        disease == "Parkinson" ~ "Parkinson",
        disease == "Ischemic heart disease" ~ "Ischemic Heart Disease",
        disease == "Atrial fibrillation" ~ "Atrial Fibrillation",
        disease == "Cerebrovascular disease" ~ "Cerebrovascular Disease",
        disease == "Heart failure" ~ "Heart Failure",
        TRUE ~ str_to_title(str_replace_all(disease, "_", " "))
      ),
      predictor = case_when(
        predictor == "Gastrointestinal_tract" ~ "Gastrointestinal",
        predictor == "Kidney_urinary" ~ "Kidney and Bladder",
        predictor == "Artery" ~ "Arterial",
        predictor == "Immune" ~ "Immune",
        predictor == "Vessel" ~ "Vessel",
        TRUE ~ str_to_title(predictor)
      ),
      effect_size = log(odds_ratio),
      impossible = case_when(
        outcome %in% c("Breast Cancer", "Ovarian Cancer") & predictor == "Prostate" ~ TRUE,
        outcome == "Prostate Cancer" & predictor == "Ovary" ~ TRUE,
        TRUE ~ FALSE
      ),
      significance = case_when(
        impossible ~ "",
        FDR < 0.001 ~ "***",
        FDR < 0.01 ~ "**",
        FDR < 0.05 ~ "*",
        TRUE ~ ""
      ),
      outcome_group = if_else(str_detect(outcome, "cancer|Cancer"), "Cancer", "Non-Cancer Diseases"),
      model_type = "logistic"
    ) |>
    select(outcome, predictor, effect_size, significance, outcome_group, model_type, impossible) |>
    clean_names()
  
  # Create heatmap
  heatmap <- create_prevalent_heatmap(heatmap_data, c("Non-Cancer Diseases", "Cancer"))
  
  # Save heatmap
  if (!is.null(heatmap)) {
    filepath <- file.path(prevalent_disease_base, "main", paste0(tw, "y"), 
                         "mortality_organ_age_heatmap_combined.svg")
    save_plot(filepath, heatmap, width = 12, height = 8, dpi = 300)
    cat("Saved heatmap for", tw, "year window\n")
  }
  
  return(heatmap)
}) |> set_names(names(sensitivity_results))
```

```{r prevalent_sensitivity_forest_tables}
sensitivity_forest_tables <- map(names(sensitivity_results), function(window_name) {
  tw <- as.numeric(gsub("y", "", window_name))
  results <- sensitivity_results[[window_name]]
  
  # Get unique diseases in this window
  diseases_in_window <- unique(results$disease)
  
  # Create forest tables for each disease
  forest_plots <- map(diseases_in_window, function(disease_name) {
    disease_data <- results |> 
      filter(disease == disease_name, analysis_type == "univariate", model == "mortality")
    
    if (nrow(disease_data) == 0) return(NULL)
    
    create_prevalent_forest_table(
      data = results,
      disease_name = disease_name,
      analysis_type = "univariate",
      model_type = "mortality",
      time_window = tw
    )
  }) |> set_names(diseases_in_window)
  
  forest_plots <- compact(forest_plots)
  
  # Save forest tables
  for (disease_name in names(forest_plots)) {
    disease_config <- diseases_config[[disease_name]]
    display_name <- if (!is.null(disease_config)) disease_config$name else disease_name
    
    filename <- paste0("prevalent_forest_", tolower(str_replace_all(display_name, " ", "_")), ".svg")
    filepath <- file.path(prevalent_disease_base, "main", paste0(tw, "y"), filename)
    
    save_plot(filepath, forest_plots[[disease_name]], width = 10, height = 5, dpi = 300)
  }
  
  # Create CSV tables directory for this time window
  csv_dir_prevalent <- file.path(prevalent_disease_base, "main", paste0(tw, "y"), "tables")
  dir.create(csv_dir_prevalent, showWarnings = FALSE, recursive = TRUE)
  
  # Save table data as CSV for prevalent disease
  for (disease_name in names(forest_plots)) {
    disease_data <- results |> 
      filter(disease == disease_name, analysis_type == "univariate", model == "mortality")
    
    if (nrow(disease_data) == 0) next
    
    tab <- disease_data |>
      mutate(
        use_sci = pmax(abs(odds_ratio), abs(ci_lower), abs(ci_upper), na.rm = TRUE) >= 10,
        or_formatted = if_else(use_sci,
          sprintf("%.1e (%.1e-%.1e)", odds_ratio, ci_lower, ci_upper),
          sprintf("%.2f (%.2f-%.2f)", odds_ratio, ci_lower, ci_upper)),
        Organ_Display = case_when(
          predictor == "Gastrointestinal_tract" ~ "Gastrointestinal",
          predictor == "Kidney_urinary" ~ "Kidney and Bladder",
          TRUE ~ str_to_title(predictor)
        )
      ) |>
      select(Organ = Organ_Display, `OR (95% CI)` = or_formatted, FDR)
    
    disease_config <- diseases_config[[disease_name]]
    display_name <- if (!is.null(disease_config)) disease_config$name else disease_name
    filename <- paste0("prevalent_", tolower(str_replace_all(display_name, " ", "_")), ".csv")
    write.csv(tab, file = file.path(csv_dir_prevalent, filename), row.names = FALSE)
  }
  
  cat("Saved", length(forest_plots), "forest tables for", tw, "year window\n")
  
  return(forest_plots)
}) |> set_names(names(sensitivity_results))

cat("\n=== Sensitivity Analysis Summary ===\n")
cat("Time windows analyzed:", paste(prevalent_time_windows, "years"), "\n")
cat("Total heatmaps saved:", length(compact(sensitivity_heatmaps)), "\n")
cat("Total forest tables saved:", sum(map_int(sensitivity_forest_tables, length)), "\n")
```

## Within-Pair Analyses: Discordant Twins

```{r prevalent_discordant_setup}
min_discordant_pairs <- nrow(twins_analysis)*0.005

check_discordant_pairs <- function(prevalent_data, disease_name, mz_only = FALSE) {
  n_pairs <- prevalent_data |>
    group_by(pair_id) |>
    filter(
      n() == 2,
      if (mz_only) all(bestzyg == 1) else TRUE,
      sum(prevalent_disease == 1, na.rm = TRUE) == 1
    ) |>
    ungroup() |>
    summarise(n_pairs = n_distinct(pair_id)) |>
    pull(n_pairs)
  
  return(n_pairs)
}

run_prevalent_discordant <- function(prevalent_data, predictor_df, disease_name, mz_only = FALSE) {
  predictors <- setdiff(colnames(predictor_df), "twin_id")
  
  discordant_twins <- prevalent_data |>
    group_by(pair_id) |>
    filter(
      n() == 2,
      if (mz_only) all(bestzyg == 1) else TRUE,
      sum(prevalent_disease == 1, na.rm = TRUE) == 1
    ) |>
    ungroup()
  
  # Apply sex filtering for sex-specific diseases
  if (grepl("prostate", disease_name, ignore.case = TRUE)) {
    discordant_twins <- discordant_twins |> filter(sex == 1)
  } else if (grepl("breast|ovarian", disease_name, ignore.case = TRUE)) {
    discordant_twins <- discordant_twins |> filter(sex == 2)
  }
  
  map_dfr(predictors, function(pred) {
    df <- discordant_twins |>
      left_join(predictor_df |> select(twin_id, all_of(pred)), by = "twin_id") |>
      filter(!is.na(.data[[pred]]))
    
    if (pred %in% c("Ovary", "Prostate")) {
      df <- df |> filter(sex == if (pred == "Ovary") 2 else 1)
    }
    
    if (n_distinct(df$pair_id) < 3) {
      return(tibble(
        disease = disease_name, predictor = pred, estimate = NA_real_, std_error = NA_real_,
        p_value = NA_real_, odds_ratio = NA_real_, ci_lower = NA_real_, ci_upper = NA_real_,
        n_pairs = NA_integer_, model = "mortality", analysis_type = "within_pair"
      ))
    }
    
    tryCatch({
      fit <- clogit(as.formula(paste0("prevalent_disease ~ scale(`", pred, "`) + strata(pair_id)")), data = df)
      est <- as.numeric(coef(fit)[1])
      se <- sqrt(diag(vcov(fit)))[1]
      p <- summary(fit)$coefficients[1, "Pr(>|z|)"]
      
      tibble(
        disease = disease_name,
        predictor = pred,
        estimate = est,
        std_error = se,
        p_value = as.numeric(p),
        odds_ratio = exp(est),
        ci_lower = exp(est - 1.96 * se),
        ci_upper = exp(est + 1.96 * se),
        n_pairs = n_distinct(df$pair_id),
        model = "mortality",
        analysis_type = "within_pair"
      )
    }, error = function(e) {
      tibble(
        disease = disease_name, predictor = pred, estimate = NA_real_, std_error = NA_real_,
        p_value = NA_real_, odds_ratio = NA_real_, ci_lower = NA_real_, ci_upper = NA_real_,
        n_pairs = NA_integer_, model = "mortality", analysis_type = "within_pair"
      )
    })
  }) |>
    mutate(FDR = p.adjust(p_value, method = "fdr"))
}
```

```{r prevalent_discordant_time_windows}
cat("\n=== Checking Discordant Pairs: Time Windows ===\n")

time_window_discordant <- map(prevalent_time_windows, function(tw) {
  cat("\n--- Time window:", tw, "years ---\n")
  
  # Check eligibility for all pairs
  eligible_all <- map_dfr(names(diseases_config), function(disease_name) {
    spec <- diseases_config[[disease_name]]
    prev_data <- build_prevalent_time_window(spec$var, spec$date, tw)
    n_pairs <- check_discordant_pairs(prev_data, spec$name, mz_only = FALSE)
    tibble(disease = disease_name, n_pairs = n_pairs, eligible = n_pairs >= min_discordant_pairs)
  }) |> filter(eligible) |> pull(disease)
  
  # Check eligibility for MZ pairs
  eligible_mz <- map_dfr(names(diseases_config), function(disease_name) {
    spec <- diseases_config[[disease_name]]
    prev_data <- build_prevalent_time_window(spec$var, spec$date, tw)
    n_pairs <- check_discordant_pairs(prev_data, spec$name, mz_only = TRUE)
    tibble(disease = disease_name, n_pairs = n_pairs, eligible = n_pairs >= min_discordant_pairs)
  }) |> filter(eligible) |> pull(disease)
  
  cat("Eligible (all pairs):", length(eligible_all), "| Eligible (MZ pairs):", length(eligible_mz), "\n")
  
  results <- list()
  
  # All pairs
  if (length(eligible_all) > 0) {
    results$all <- map(eligible_all, function(disease_name) {
      spec <- diseases_config[[disease_name]]
      prev_data <- build_prevalent_time_window(spec$var, spec$date, tw)
      run_prevalent_discordant(prev_data, organ_age_mortality, spec$name, mz_only = FALSE)
    }) |> set_names(eligible_all) |>
      bind_rows(.id = "disease_key") |>
      mutate(model_type = "conditional_logistic", outcome_type = "prevalent_disease", 
             pair_type = "all", time_window = tw)
  }
  
  # MZ pairs
  if (length(eligible_mz) > 0) {
    results$mz <- map(eligible_mz, function(disease_name) {
      spec <- diseases_config[[disease_name]]
      prev_data <- build_prevalent_time_window(spec$var, spec$date, tw)
      run_prevalent_discordant(prev_data, organ_age_mortality, spec$name, mz_only = TRUE)
    }) |> set_names(eligible_mz) |>
      bind_rows(.id = "disease_key") |>
      mutate(model_type = "conditional_logistic", outcome_type = "prevalent_disease", 
             pair_type = "mz", time_window = tw)
  }
  
  return(results)
}) |> set_names(paste0(prevalent_time_windows, "y"))
```

```{r create_discordant_heatmaps}
create_discordant_heatmap_data <- function(results_data) {
  results_data |>
    mutate(
      outcome = case_when(
        disease == "Diabetes" ~ "Diabetes",
        disease == "Dementia" ~ "Dementia",
        disease == "Parkinson" ~ "Parkinson",
        disease == "Ischemic heart disease" ~ "Ischemic Heart Disease",
        disease == "Atrial fibrillation" ~ "Atrial Fibrillation",
        disease == "Cerebrovascular disease" ~ "Cerebrovascular Disease",
        disease == "Heart failure" ~ "Heart Failure",
        TRUE ~ str_to_title(str_replace_all(disease, "_", " "))
      ),
      predictor = case_when(
        predictor == "Gastrointestinal_tract" ~ "Gastrointestinal",
        predictor == "Kidney_urinary" ~ "Kidney and Bladder",
        predictor == "Artery" ~ "Arterial",
        predictor == "Immune" ~ "Immune",
        predictor == "Vessel" ~ "Vessel",
        TRUE ~ str_to_title(predictor)
      ),
      effect_size = log(odds_ratio),
      impossible = case_when(
        outcome %in% c("Breast Cancer", "Ovarian Cancer") & predictor == "Prostate" ~ TRUE,
        outcome == "Prostate Cancer" & predictor == "Ovary" ~ TRUE,
        TRUE ~ FALSE
      ),
      significance = case_when(
        impossible ~ "",
        FDR < 0.001 ~ "***",
        FDR < 0.01 ~ "**",
        FDR < 0.05 ~ "*",
        TRUE ~ ""
      ),
      outcome_group = if_else(str_detect(outcome, "cancer|Cancer"), "Cancer", "Non-Cancer Diseases"),
      model_type = "conditional_logistic"
    ) |>
    select(outcome, predictor, effect_size, significance, outcome_group, model_type, impossible) |>
    clean_names()
}

# Create and save heatmaps for time windows
for (window_name in names(time_window_discordant)) {
  tw_data <- time_window_discordant[[window_name]]
  
  if (!is.null(tw_data$all) && nrow(tw_data$all) > 0) {
    heatmap_data <- create_discordant_heatmap_data(tw_data$all)
    heatmap <- create_prevalent_heatmap(heatmap_data, c("Non-Cancer Diseases", "Cancer"))
    if (!is.null(heatmap)) {
      filepath <- file.path(prevalent_disease_base, "within", window_name, "all_pairs_heatmap.svg")
      save_plot(filepath, heatmap, width = 12, height = 8, dpi = 300)
    }
  }
  
  if (!is.null(tw_data$mz) && nrow(tw_data$mz) > 0) {
    heatmap_data <- create_discordant_heatmap_data(tw_data$mz)
    heatmap <- create_prevalent_heatmap(heatmap_data, c("Non-Cancer Diseases", "Cancer"))
    if (!is.null(heatmap)) {
      filepath <- file.path(prevalent_disease_base, "within", window_name, "mz_pairs_heatmap.svg")
      save_plot(filepath, heatmap, width = 12, height = 8, dpi = 300)
    }
  }
}
```

```{r create_discordant_forest_function}
create_discordant_forest <- function(data, disease_name, n_pairs, pair_type_label) {
  forest_data <- data |> filter(disease == disease_name)
  if (nrow(forest_data) == 0) return(NULL)
  
  disease_config <- diseases_config[[disease_name]]
  display_name <- if (!is.null(disease_config)) disease_config$name else disease_name
  title <- paste0(display_name, " - ", pair_type_label, " (", n_pairs, " discordant pairs)")
  
  forest_data <- forest_data |>
    mutate(
      or = odds_ratio, or_lower = ci_lower, or_upper = ci_upper,
      fdr = FDR, significant = FDR < 0.05,
      errorbar_color = if_else(FDR < 0.05, "grey30", "gray80"),
      Organ_Display = case_when(
        predictor == "Gastrointestinal_tract" ~ "Gastrointestinal",
        predictor == "Kidney_urinary" ~ "Kidney and Bladder", TRUE ~ str_to_title(predictor)
      )
    ) |>
    arrange(desc(odds_ratio)) |>
    mutate(y_pos = rev(seq_along(predictor)), Organ_Display = factor(Organ_Display, levels = Organ_Display))
  
  x_min <- suppressWarnings(min(forest_data$or_lower, na.rm = TRUE))
  x_max <- suppressWarnings(max(forest_data$or_upper, na.rm = TRUE))
  default_lower <- 0.5
  default_upper <- 1.5
  
  if (!is.finite(x_min) || !is.finite(x_max) || x_min <= 0) {
    x_min <- default_lower
    x_max <- default_upper
  }
  
  pad <- 0.1 * (x_max - x_min)
  if (!is.finite(pad) || pad <= 0) pad <- 0.1
  
  x_limits <- c(min(default_lower, max(0.1, x_min - pad)), max(default_upper, x_max + pad))
  legend_x_left <- x_limits[1] + 0.05 * (x_limits[2] - x_limits[1])
  legend_x_right <- x_limits[1] + 0.55 * (x_limits[2] - x_limits[1])
  
  tab <- forest_data |>
    transmute(
      y_pos, `Organ age` = Organ_Display,
      `OR (95% CI)` = sprintf("%.2f (%.2f-%.2f)", or, or_lower, or_upper),
      FDR = sprintf("%.2e", fdr)
    )
  
  x_pos <- tibble(col = c("Organ age", "OR (95% CI)", "FDR"), x = c(1.0, 3.5, 6.0))
  table_long <- tab |> pivot_longer(-y_pos, names_to = "col", values_to = "val") |> left_join(x_pos, by = "col")
  
  p_table <- ggplot(table_long, aes(x = x, y = y_pos, label = val)) +
    geom_text(hjust = c(0, 0, 1)[match(table_long$col, x_pos$col)], size = 3.2) +
    geom_text(data = x_pos |> mutate(y_pos = max(forest_data$y_pos) + 1), 
             aes(x = x, y = y_pos, label = col), hjust = c(0, 0, 1), fontface = "bold", 
             inherit.aes = FALSE, size = 3.3) +
    scale_y_continuous(breaks = NULL, labels = NULL, limits = c(0.5, max(forest_data$y_pos) + 1.5)) +
    scale_x_continuous(limits = c(0.5, 7.0), expand = c(0, 0)) +
    labs(title = title) +
    theme_minimal(base_size = 11) +
    theme(plot.title = element_text(hjust = 0.1, size = 12), axis.title = element_blank(),
         axis.text.x = element_blank(), axis.ticks = element_blank(), panel.grid = element_blank(),
         plot.margin = unit(c(12, 6, 6, 6), "pt"))
  
  p_forest <- ggplot(forest_data, aes(y = y_pos)) +
    geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = y_pos - 0.5, ymax = y_pos + 0.5, 
                 fill = factor(seq_along(predictor) %% 2)), alpha = 0.6, show.legend = FALSE) +
    scale_fill_manual(values = c("0" = "transparent", "1" = "gray95")) +
    geom_segment(aes(x = 1, xend = 1, y = 0.5, yend = max(forest_data$y_pos) + 0.75), 
                linetype = "33", color = "grey10", size = 0.7) +
    geom_errorbarh(data = forest_data, aes(xmin = or_lower, xmax = or_upper, y = y_pos), color = forest_data$errorbar_color, height = 0.15, size = 0.6, inherit.aes = FALSE) +
    geom_point(aes(x = or, color = significant), size = 2.5, shape = 16) +
    annotate("text", x = legend_x_left, y = max(forest_data$y_pos) + 1.5, 
            label = "● Significant (FDR < 0.05)", hjust = 0.35, size = 3, color = "black") +
    annotate("text", x = legend_x_right, y = max(forest_data$y_pos) + 1.5, 
            label = "● Non-significant", hjust = -0.65, size = 3, color = "gray80") +
    scale_color_manual(values = c("TRUE" = "black", "FALSE" = "gray80")) +
    scale_x_continuous(limits = x_limits, expand = c(0, 0)) +
    scale_y_continuous(breaks = NULL, labels = NULL, limits = c(0.2, max(forest_data$y_pos) + 1.5)) +
    labs(x = "Odds Ratio (95% CI)", y = NULL) +
    theme_minimal(base_size = 11) +
    theme(axis.text.y = element_blank(), axis.text.x = element_text(size = 9),
         axis.title.x = element_text(size = 10), panel.grid = element_blank(),
         plot.margin = unit(c(12, 12, 6, 0), "pt"), legend.position = "none") +
    coord_cartesian(clip = "off")
  
  p_table + p_forest + plot_layout(widths = c(2.5, 2))
}

# Forest tables for time windows
for (window_name in names(time_window_discordant)) {
  tw_data <- time_window_discordant[[window_name]]
  
  if (!is.null(tw_data$all) && nrow(tw_data$all) > 0) {
    diseases_to_plot <- unique(tw_data$all$disease_key)
    for (disease_key_name in diseases_to_plot) {
      disease_config <- diseases_config[[disease_key_name]]
      years_back <- as.numeric(str_remove(window_name, "y"))
      prev_data <- build_prevalent_time_window(disease_config$var, disease_config$date, years_back)
      counts <- calculate_prevalent_discordant_counts(prev_data, disease_config$name, mz_only = FALSE)
      plot_data <- tw_data$all |> filter(disease_key == disease_key_name) |> mutate(cases = counts$cases)
      plot <- create_discordant_forest(plot_data, disease_config$name, counts$n_pairs, "All Pairs")
      if (!is.null(plot)) {
        display_name <- disease_config$name
        filename <- paste0("forest_all_pairs_", tolower(str_replace_all(display_name, " ", "_")), ".svg")
        filepath <- file.path(prevalent_disease_base, "within", window_name, filename)
        save_plot(filepath, plot, width = 10, height = 5, dpi = 300)
      }
    }
  }
  
  if (!is.null(tw_data$mz) && nrow(tw_data$mz) > 0) {
    diseases_to_plot <- unique(tw_data$mz$disease_key)
    for (disease_key_name in diseases_to_plot) {
      disease_config <- diseases_config[[disease_key_name]]
      years_back <- as.numeric(str_remove(window_name, "y"))
      prev_data <- build_prevalent_time_window(disease_config$var, disease_config$date, years_back)
      counts <- calculate_prevalent_discordant_counts(prev_data, disease_config$name, mz_only = TRUE)
      plot_data <- tw_data$mz |> filter(disease_key == disease_key_name) |> mutate(cases = counts$cases)
      plot <- create_discordant_forest(plot_data, disease_config$name, counts$n_pairs, "MZ Pairs")
      if (!is.null(plot)) {
        display_name <- disease_config$name
        filename <- paste0("forest_mz_pairs_", tolower(str_replace_all(display_name, " ", "_")), ".svg")
        filepath <- file.path(prevalent_disease_base, "within", window_name, filename)
        save_plot(filepath, plot, width = 10, height = 5, dpi = 300)
      }
    }
  }
  
  # Create CSV tables directory for this time window - within-pair results
  csv_dir_within_prevalent <- file.path(prevalent_disease_base, "within", window_name, "tables")
  dir.create(csv_dir_within_prevalent, showWarnings = FALSE, recursive = TRUE)
  
  # Save CSV for all pairs
  if (!is.null(tw_data$all) && nrow(tw_data$all) > 0) {
    for (disease_name in unique(tw_data$all$disease)) {
      disease_data <- tw_data$all |> filter(disease == disease_name, !is.na(odds_ratio))
      
      if (nrow(disease_data) == 0) next
      
      tab <- disease_data |>
        mutate(
          use_sci = pmax(abs(odds_ratio), abs(ci_lower), abs(ci_upper), na.rm = TRUE) >= 10,
          use_sci = if_else(is.na(use_sci), FALSE, use_sci),
          or_formatted = if_else(use_sci,
            sprintf("%.1e (%.1e-%.1e)", odds_ratio, ci_lower, ci_upper),
            sprintf("%.2f (%.2f-%.2f)", odds_ratio, ci_lower, ci_upper)),
          Organ_Display = case_when(
            predictor == "Gastrointestinal_tract" ~ "Gastrointestinal",
            predictor == "Kidney_urinary" ~ "Kidney and Bladder",
            TRUE ~ str_to_title(predictor)
          )
        ) |>
        select(Organ = Organ_Display, `OR (95% CI)` = or_formatted, FDR)
      
      disease_config <- diseases_config[[disease_name]]
      display_name <- if (!is.null(disease_config)) disease_config$name else disease_name
      filename <- paste0("prevalent_", tolower(str_replace_all(display_name, " ", "_")), "_all_pairs.csv")
      write.csv(tab, file = file.path(csv_dir_within_prevalent, filename), row.names = FALSE)
    }
  }
  
  # Save CSV for MZ pairs
  if (!is.null(tw_data$mz) && nrow(tw_data$mz) > 0) {
    for (disease_name in unique(tw_data$mz$disease)) {
      disease_data <- tw_data$mz |> filter(disease == disease_name, !is.na(odds_ratio))
      
      if (nrow(disease_data) == 0) next
      
      tab <- disease_data |>
        mutate(
          use_sci = pmax(abs(odds_ratio), abs(ci_lower), abs(ci_upper), na.rm = TRUE) >= 10,
          use_sci = if_else(is.na(use_sci), FALSE, use_sci),
          or_formatted = if_else(use_sci,
            sprintf("%.1e (%.1e-%.1e)", odds_ratio, ci_lower, ci_upper),
            sprintf("%.2f (%.2f-%.2f)", odds_ratio, ci_lower, ci_upper)),
          Organ_Display = case_when(
            predictor == "Gastrointestinal_tract" ~ "Gastrointestinal",
            predictor == "Kidney_urinary" ~ "Kidney and Bladder",
            TRUE ~ str_to_title(predictor)
          )
        ) |>
        select(Organ = Organ_Display, `OR (95% CI)` = or_formatted, FDR)
      
      disease_config <- diseases_config[[disease_name]]
      display_name <- if (!is.null(disease_config)) disease_config$name else disease_name
      filename <- paste0("prevalent_", tolower(str_replace_all(display_name, " ", "_")), "_mz_pairs.csv")
      write.csv(tab, file = file.path(csv_dir_within_prevalent, filename), row.names = FALSE)
    }
  }
}

cat("\n=== Within-Pair Analysis Complete ===\n")
```

## Within-Pair Difference Analysis for Continuous Outcomes

**Analysis Goal:**
Examine associations between organ ages and continuous outcomes using within-pair difference regression. This approach controls for all shared genetic and environmental factors within twin pairs by regressing the within-pair difference in the outcome on the within-pair difference in organ age.

**Model:** `outcome_diff ~ organ_age_diff` (where differences are calculated within each pair)  
**Method:** Linear regression on within-pair differences  
**Multiple testing:** FDR correction applied across all tests

```{r within_pair_continuous_function}
analyze_continuous_within_pair <- function(predictor_df, outcome_vars = cont_outcomes, mz_only = FALSE) {
  map_dfr(outcome_vars, function(outcome) {
    if (!(outcome %in% names(twins_analysis))) {
      return(tibble(
        outcome = outcome, predictor = NA_character_,
        estimate = NA_real_, std_error = NA_real_, z_value = NA_real_, p_value = NA_real_,
        standardized_estimate = NA_real_, standardized_ci_lower = NA_real_, standardized_ci_upper = NA_real_,
        error_message = "Variable not found in dataset"
      ))
    }

    predictors <- setdiff(colnames(predictor_df), "twin_id")

    map_dfr(predictors, function(predictor) {
      # Prepare data with organ age
      analysis_data <- twins_analysis |>
        left_join(predictor_df |> select(twin_id, all_of(predictor)), by = "twin_id") |>
        filter(!is.na(!!sym(outcome)), !is.na(!!sym(predictor)))

      # Handle sex-specific organ ages
      if (predictor == "Ovary") {
        analysis_data <- analysis_data |> filter(sex == 2)
      } else if (predictor == "Prostate") {
        analysis_data <- analysis_data |> filter(sex == 1)
      }

      # Filter to complete pairs
      complete_pairs <- analysis_data |>
        group_by(pair_id) |>
        filter(
          n() == 2,
          if (mz_only) all(bestzyg == 1) else TRUE
        ) |>
        ungroup()

      if (n_distinct(complete_pairs$pair_id) < 3) {
        return(tibble(
          outcome = outcome, predictor = predictor,
          estimate = NA_real_, std_error = NA_real_, z_value = NA_real_, p_value = NA_real_,
          standardized_estimate = NA_real_, standardized_ci_lower = NA_real_, standardized_ci_upper = NA_real_,
          error_message = "Insufficient pairs"
        ))
      }

      # Calculate within-pair differences
      pair_diffs <- complete_pairs |>
        group_by(pair_id) |>
        summarise(
          outcome_diff = .data[[outcome]][1] - .data[[outcome]][2],
          predictor_diff = .data[[predictor]][1] - .data[[predictor]][2],
          .groups = "drop"
        ) |>
        filter(!is.na(outcome_diff), !is.na(predictor_diff))

      if (nrow(pair_diffs) < 3) {
        return(tibble(
          outcome = outcome, predictor = predictor,
          estimate = NA_real_, std_error = NA_real_, z_value = NA_real_, p_value = NA_real_,
          standardized_estimate = NA_real_, standardized_ci_lower = NA_real_, standardized_ci_upper = NA_real_,
          error_message = "Insufficient pairs after calculating differences"
        ))
      }

      tryCatch({
        # Fit model: outcome_diff ~ predictor_diff
        model <- lm(outcome_diff ~ predictor_diff, data = pair_diffs)
        
        # Extract coefficients (predictor_diff is the second coefficient after intercept)
        estimate <- coef(model)[2]
        std_error <- summary(model)$coefficients[2, "Std. Error"]
        t_value <- summary(model)$coefficients[2, "t value"]
        p_value <- summary(model)$coefficients[2, "Pr(>|t|)"]

        # Calculate standardized estimates using SD of differences
        sd_outcome_diff <- sd(pair_diffs$outcome_diff, na.rm = TRUE)
        sd_predictor_diff <- sd(pair_diffs$predictor_diff, na.rm = TRUE)
        standardized_estimate <- estimate * (sd_predictor_diff / sd_outcome_diff)
        standardized_ci_lower <- (estimate - 1.96 * std_error) * (sd_predictor_diff / sd_outcome_diff)
        standardized_ci_upper <- (estimate + 1.96 * std_error) * (sd_predictor_diff / sd_outcome_diff)

        tibble(
          outcome = outcome, predictor = predictor,
          estimate = estimate, std_error = std_error,
          z_value = t_value, p_value = p_value,
          standardized_estimate = standardized_estimate,
          standardized_ci_lower = standardized_ci_lower,
          standardized_ci_upper = standardized_ci_upper,
          error_message = NA_character_
        )
      }, error = function(e) {
        tibble(
          outcome = outcome, predictor = predictor,
          estimate = NA_real_, std_error = NA_real_, z_value = NA_real_, p_value = NA_real_,
          standardized_estimate = NA_real_, standardized_ci_lower = NA_real_, standardized_ci_upper = NA_real_,
          error_message = e$message
        )
      })
    })
  }) |>
    mutate(FDR = p.adjust(p_value, method = "fdr"))
}
```

```{r run_within_pair_continuous_analyses}
# Run within-pair analyses for all continuous outcomes
cont_within_pair_all <- analyze_continuous_within_pair(organ_age_mortality, cont_outcomes, mz_only = FALSE) |>
  mutate(
    model_type = "linear",
    organ_age_model = "mortality",
    analysis_type = "within_pair",
    pair_type = "all"
  )

cont_within_pair_mz <- analyze_continuous_within_pair(organ_age_mortality, cont_outcomes, mz_only = TRUE) |>
  mutate(
    model_type = "linear",
    organ_age_model = "mortality",
    analysis_type = "within_pair",
    pair_type = "mz"
  )
```

```{r combine_within_pair_results}
# Combine continuous and binary (smoking/exercise) within-pair results
all_within_pair_all <- bind_rows(
  cont_within_pair_all,
  smoking_within_pair_all,
  exercise_within_pair_all
)

all_within_pair_mz <- bind_rows(
  cont_within_pair_mz,
  smoking_within_pair_mz,
  exercise_within_pair_mz
)
```

```{r within_pair_continuous_heatmaps}
# Prepare heatmap data for within-pair analyses
within_pair_heatmap_data_all <- cont_within_pair_all |>
  filter(is.na(error_message)) |>
  mutate(
    effect_size = standardized_estimate,
    significance = case_when(
      FDR < 0.001 ~ "***",
      FDR < 0.01 ~ "**",
      FDR < 0.05 ~ "*",
      TRUE ~ ""
    ),
    outcome_group = case_when(
      outcome %in% lifestyle_outcomes ~ "Lifestyle",
      outcome %in% clinical_biomarkers ~ "Clinical Biomarkers",
      outcome %in% health_outcomes ~ "Health",
      TRUE ~ "Other"
    )
  ) |>
  select(outcome, predictor, effect_size, significance, outcome_group, model_type) |>
  clean_names()

# Add smoking and exercise results to heatmap data - All Pairs
smoking_exercise_heatmap_all <- bind_rows(
  smoking_within_pair_all,
  exercise_within_pair_all
) |>
  filter(is.na(error_message)) |>
  mutate(
    effect_size = standardized_estimate,
    significance = case_when(
      FDR < 0.001 ~ "***",
      FDR < 0.01 ~ "**",
      FDR < 0.05 ~ "*",
      TRUE ~ ""
    ),
    outcome_group = "Lifestyle"
  ) |>
  select(outcome, predictor, effect_size, significance, outcome_group, model_type) |>
  clean_names()

within_pair_heatmap_data_all <- bind_rows(
  within_pair_heatmap_data_all,
  smoking_exercise_heatmap_all
)

within_pair_heatmap_data_mz <- cont_within_pair_mz |>
  filter(is.na(error_message)) |>
  mutate(
    effect_size = standardized_estimate,
    significance = case_when(
      FDR < 0.001 ~ "***",
      FDR < 0.01 ~ "**",
      FDR < 0.05 ~ "*",
      TRUE ~ ""
    ),
    outcome_group = case_when(
      outcome %in% lifestyle_outcomes ~ "Lifestyle",
      outcome %in% clinical_biomarkers ~ "Clinical Biomarkers",
      outcome %in% health_outcomes ~ "Health",
      TRUE ~ "Other"
    )
  ) |>
  select(outcome, predictor, effect_size, significance, outcome_group, model_type) |>
  clean_names()

# Add smoking and exercise results to heatmap data - MZ Pairs
smoking_exercise_heatmap_mz <- bind_rows(
  smoking_within_pair_mz,
  exercise_within_pair_mz
) |>
  filter(is.na(error_message)) |>
  mutate(
    effect_size = standardized_estimate,
    significance = case_when(
      FDR < 0.001 ~ "***",
      FDR < 0.01 ~ "**",
      FDR < 0.05 ~ "*",
      TRUE ~ ""
    ),
    outcome_group = "Lifestyle"
  ) |>
  select(outcome, predictor, effect_size, significance, outcome_group, model_type) |>
  clean_names()

within_pair_heatmap_data_mz <- bind_rows(
  within_pair_heatmap_data_mz,
  smoking_exercise_heatmap_mz
)

# Create heatmaps for each group - All Pairs
within_pair_lifestyle_heatmap_all <- create_group_heatmap(within_pair_heatmap_data_all, "Lifestyle")
within_pair_clinical_heatmap_all <- create_group_heatmap(within_pair_heatmap_data_all, "Clinical Biomarkers")
within_pair_health_heatmap_all <- create_group_heatmap(within_pair_heatmap_data_all, "Health")

# Create heatmaps for each group - MZ Pairs
within_pair_lifestyle_heatmap_mz <- create_group_heatmap(within_pair_heatmap_data_mz, "Lifestyle")
within_pair_clinical_heatmap_mz <- create_group_heatmap(within_pair_heatmap_data_mz, "Clinical Biomarkers")
within_pair_health_heatmap_mz <- create_group_heatmap(within_pair_heatmap_data_mz, "Health")

# Print heatmaps - All Pairs
print(within_pair_lifestyle_heatmap_all)
print(within_pair_clinical_heatmap_all)
print(within_pair_health_heatmap_all)

# Save heatmaps - All Pairs
save_plot(
  filename = file.path(current_health_base, "within_pair", "heatmap", "all_pairs_lifestyle.svg"),
  plot = within_pair_lifestyle_heatmap_all,
  width = 12,
  height = 6,
  dpi = 300
)

save_plot(
  filename = file.path(current_health_base, "within_pair", "heatmap", "all_pairs_clinical.svg"),
  plot = within_pair_clinical_heatmap_all,
  width = 12,
  height = 6,
  dpi = 300
)

save_plot(
  filename = file.path(current_health_base, "within_pair", "heatmap", "all_pairs_health.svg"),
  plot = within_pair_health_heatmap_all,
  width = 12,
  height = 6,
  dpi = 300
)

# Save heatmaps - MZ Pairs
save_plot(
  filename = file.path(current_health_base, "within_pair", "heatmap", "mz_pairs_lifestyle.svg"),
  plot = within_pair_lifestyle_heatmap_mz,
  width = 12,
  height = 6,
  dpi = 300
)

save_plot(
  filename = file.path(current_health_base, "within_pair", "heatmap", "mz_pairs_clinical.svg"),
  plot = within_pair_clinical_heatmap_mz,
  width = 12,
  height = 6,
  dpi = 300
)

save_plot(
  filename = file.path(current_health_base, "within_pair", "heatmap", "mz_pairs_health.svg"),
  plot = within_pair_health_heatmap_mz,
  width = 12,
  height = 6,
  dpi = 300
)
```

```{r within_pair_continuous_forest_tables}
# Create output directory
output_dir_within_pair <- file.path(current_health_base, "within_pair", "forest_table")
dir.create(output_dir_within_pair, showWarnings = FALSE, recursive = TRUE)

# Helper function to create forest table for within-pair results
create_within_pair_forest_table <- function(data, outcome_name, pair_type_label, main_color = "black", n_pairs = NULL) {
  forest_data <- data |>
    filter(outcome == outcome_name, is.na(error_message))

  if (nrow(forest_data) == 0) return(NULL)

  display_name <- case_when(
    outcome_name == "whr" ~ "Waist-Hip Ratio",
    outcome_name == "bmi" ~ "Body Mass Index",
    outcome_name == "edyrs" ~ "Education Years",
    outcome_name == "glucose" ~ "Glucose",
    outcome_name == "triglycerides" ~ "Triglycerides",
    outcome_name == "hba1c" ~ "HbA1c",
    outcome_name == "crp" ~ "C-Reactive Protein",
    outcome_name == "total_hdl_ratio" ~ "Total/HDL Ratio",
    outcome_name == "egfr_cr_cys" ~ "eGFR",
    outcome_name == "fi_10" ~ "Frailty Index",
    outcome_name == "telomere_length" ~ "Telomere Length",
    outcome_name == "eversmok" ~ "Ever Smoked",
    outcome_name == "exercise_how_often" ~ "Exercise Frequency",
    TRUE ~ outcome_name
  )
  
  title <- if (is.null(n_pairs)) {
    paste0(display_name, " - ", pair_type_label)
  } else {
    paste0(display_name, " - ", pair_type_label, " (n = ", n_pairs, " pairs)")
  }

  forest_data <- forest_data |>
    mutate(
      effect_size = standardized_estimate,
      effect_lower = standardized_ci_lower,
      effect_upper = standardized_ci_upper,
      significant = FDR < 0.05,
      errorbar_color = if_else(FDR < 0.05, "grey30", "gray80"),
      Organ_Display = case_when(
        predictor == "Brain" ~ "Brain",
        predictor == "Cardiovascular" ~ "Cardiovascular",
        predictor == "Kidney_urinary" ~ "Kidney and Bladder",
        predictor == "Immune" ~ "Immune",
        predictor == "Liver" ~ "Liver",
        predictor == "Adipose" ~ "Adipose",
        predictor == "Endocrine" ~ "Endocrine",
        predictor == "Gastrointestinal_tract" ~ "Gastrointestinal",
        predictor == "Lung" ~ "Lung",
        predictor == "Muscle" ~ "Muscle",
        predictor == "Nerve" ~ "Nerve",
        predictor == "Pancreas" ~ "Pancreas",
        predictor == "Skin" ~ "Skin",
        predictor == "Ovary" ~ "Ovary",
        predictor == "Prostate" ~ "Prostate",
        TRUE ~ predictor
      )
    ) |>
    arrange(desc(effect_size)) |>
    mutate(
      y_pos = rev(seq_along(predictor)),
      Organ_Display = factor(Organ_Display, levels = unique(Organ_Display))
    )

  x_min <- min(forest_data$effect_lower, na.rm = TRUE)
  x_max <- max(forest_data$effect_upper, na.rm = TRUE)
  pad <- 0.1 * (x_max - x_min)
  x_limits <- c(min(-0.5, x_min - pad), max(0.5, x_max + pad))

  legend_x_left <- x_limits[1] + 0.05 * (x_limits[2] - x_limits[1])
  legend_x_right <- x_limits[1] + 0.55 * (x_limits[2] - x_limits[1])

  tab <- forest_data |>
    transmute(
      y_pos,
      `Organ age` = Organ_Display,
      `Effect Size` = sprintf("%.2f (%.2f-%.2f)", effect_size, effect_lower, effect_upper),
      `FDR` = sprintf("%.2e", FDR)
    )

  x_pos <- tibble(col = c("Organ age", "Effect Size", "FDR"), x = c(1.0, 3.5, 6.0))
  table_long <- tab |>
    pivot_longer(-y_pos, names_to = "col", values_to = "val") |>
    left_join(x_pos, by = "col")

  p_table <- ggplot(table_long, aes(x = x, y = y_pos, label = val)) +
    geom_text(hjust = c(0, 0, 1)[match(table_long$col, x_pos$col)], size = 3.2) +
    geom_text(
      data = x_pos |> mutate(y_pos = max(forest_data$y_pos) + 1),
      aes(x = x, y = y_pos, label = col),
      hjust = c(0, 0, 1),
      fontface = "bold",
      inherit.aes = FALSE,
      size = 3.3
    ) +
    scale_y_continuous(breaks = NULL, limits = c(0.5, max(forest_data$y_pos) + 1.5)) +
    scale_x_continuous(limits = c(0.5, 7.0), expand = c(0, 0)) +
    labs(title = title) +
    theme_minimal(base_size = 11) +
    theme(
      plot.title = element_text(hjust = 0.1, size = 12),
      axis.title = element_blank(),
      axis.text = element_blank(),
      axis.ticks = element_blank(),
      panel.grid = element_blank(),
      plot.margin = unit(c(12, 6, 6, 6), "pt")
    )

  p_forest <- ggplot(forest_data, aes(y = y_pos)) +
    geom_rect(
      aes(xmin = -Inf, xmax = Inf, ymin = y_pos - 0.5, ymax = y_pos + 0.5,
          fill = factor(seq_along(predictor) %% 2)),
      alpha = 0.6, show.legend = FALSE
    ) +
    scale_fill_manual(values = c("0" = "transparent", "1" = "gray95")) +
    geom_segment(
      aes(x = 0, xend = 0, y = 0.5, yend = max(forest_data$y_pos) + 0.75),
      linetype = "33", color = "grey10", size = 0.7
    ) +
    geom_errorbarh(
      data = forest_data, aes(xmin = effect_lower, xmax = effect_upper, y = y_pos),
      color = forest_data$errorbar_color, height = 0.15, size = 0.6, inherit.aes = FALSE
    ) +
    geom_point(aes(x = effect_size, color = significant), size = 2.5, shape = 16) +
    annotate(
      "text", x = legend_x_left, y = max(forest_data$y_pos) + 1.5,
      label = "● Significant (FDR < 0.05)", hjust = 0.35, size = 3, color = main_color
    ) +
    annotate(
      "text", x = legend_x_right, y = max(forest_data$y_pos) + 1.5,
      label = "● Non-significant", hjust = -0.65, size = 3, color = "gray80"
    ) +
    scale_color_manual(values = c("TRUE" = main_color, "FALSE" = "gray80")) +
    scale_x_continuous(limits = x_limits, expand = c(0, 0)) +
    scale_y_continuous(breaks = NULL, limits = c(0.2, max(forest_data$y_pos) + 1.5)) +
    labs(x = "Standardized Effect (95% CI)", y = NULL) +
    theme_minimal(base_size = 11) +
    theme(
      axis.text.y = element_blank(),
      axis.text.x = element_text(size = 9),
      axis.title.x = element_text(size = 10),
      panel.grid.major.y = element_blank(),
      panel.grid.minor = element_blank(),
      panel.grid.major.x = element_blank(),
      plot.margin = unit(c(12, 12, 6, 0), "pt"),
      legend.position = "none"
    ) +
    coord_cartesian(clip = "off")

  p_table + p_forest + plot_layout(widths = c(2.5, 2))
}

# Create and save forest plots for all continuous outcomes - All Pairs
for (outcome_name in cont_outcomes) {
  plot <- create_within_pair_forest_table(cont_within_pair_all, outcome_name, "All Pairs")

  if (!is.null(plot)) {
    save_plot(
      filename = file.path(output_dir_within_pair, paste0("forest_", outcome_name, "_all_pairs.svg")),
      plot = plot,
      width = 8,
      height = 5,
      dpi = 300
    )
  }
}

# Create CSV tables directory for within-pair results
csv_dir_within <- file.path(current_health_base, "within_pair", "tables")
dir.create(csv_dir_within, showWarnings = FALSE, recursive = TRUE)

# Save CSV for all pairs
for (outcome_name in cont_outcomes) {
  outcome_data <- cont_within_pair_all |> 
    filter(outcome == outcome_name, is.na(error_message))
  
  if (nrow(outcome_data) == 0) next
  
  tab <- outcome_data |>
    mutate(
      use_sci = pmax(abs(standardized_estimate), abs(standardized_ci_lower), abs(standardized_ci_upper), na.rm = TRUE) >= 10,
      use_sci = if_else(is.na(use_sci), FALSE, use_sci),
      effect_formatted = if_else(use_sci,
        sprintf("%.1e (%.1e-%.1e)", standardized_estimate, standardized_ci_lower, standardized_ci_upper),
        sprintf("%.2f (%.2f-%.2f)", standardized_estimate, standardized_ci_lower, standardized_ci_upper)),
      Organ_Display = predictor
    ) |>
    select(Organ = Organ_Display, `Effect Size (95% CI)` = effect_formatted, FDR)
  
  write.csv(tab, file = file.path(csv_dir_within, paste0(outcome_name, "_all_pairs.csv")), row.names = FALSE)
}

# Create and save forest plots for all continuous outcomes - MZ Pairs
for (outcome_name in cont_outcomes) {
  plot <- create_within_pair_forest_table(cont_within_pair_mz, outcome_name, "MZ Pairs")

  if (!is.null(plot)) {
    save_plot(
      filename = file.path(output_dir_within_pair, paste0("forest_", outcome_name, "_mz_pairs.svg")),
      plot = plot,
      width = 8,
      height = 5,
      dpi = 300
    )
  }
}

# Save CSV for MZ pairs  
for (outcome_name in cont_outcomes) {
  outcome_data <- cont_within_pair_mz |> 
    filter(outcome == outcome_name, is.na(error_message))
  
  if (nrow(outcome_data) == 0) next
  
  tab <- outcome_data |>
    mutate(
      use_sci = pmax(abs(standardized_estimate), abs(standardized_ci_lower), abs(standardized_ci_upper), na.rm = TRUE) >= 10,
      use_sci = if_else(is.na(use_sci), FALSE, use_sci),
      effect_formatted = if_else(use_sci,
        sprintf("%.1e (%.1e-%.1e)", standardized_estimate, standardized_ci_lower, standardized_ci_upper),
        sprintf("%.2f (%.2f-%.2f)", standardized_estimate, standardized_ci_lower, standardized_ci_upper)),
      Organ_Display = predictor
    ) |>
    select(Organ = Organ_Display, `Effect Size (95% CI)` = effect_formatted, FDR)
  
  write.csv(tab, file = file.path(csv_dir_within, paste0(outcome_name, "_mz_pairs.csv")), row.names = FALSE)
}
```

```{r create_binary_within_pair_forest_tables}
# Create forest tables for smoking and exercise using within-pair style
# Save to same directory as continuous outcomes
binary_outcomes_for_forest <- c("eversmok", "exercise_how_often")
binary_pair_counts_all <- c(eversmok = n_smoking_all, exercise_how_often = n_exercise_all)
binary_pair_counts_mz <- c(eversmok = n_smoking_mz, exercise_how_often = n_exercise_mz)

# Create and save forest plots for binary outcomes - All Pairs
for (outcome_name in binary_outcomes_for_forest) {
  plot <- create_within_pair_forest_table(
    all_within_pair_all,
    outcome_name,
    "All Pairs",
    n_pairs = unname(binary_pair_counts_all[[outcome_name]])
  )

  if (!is.null(plot)) {
    save_plot(
      filename = file.path(output_dir_within_pair, paste0("forest_", outcome_name, "_all_pairs.svg")),
      plot = plot,
      width = 8,
      height = 5,
      dpi = 300
    )
  }
}

# Create and save forest plots for binary outcomes - MZ Pairs
for (outcome_name in binary_outcomes_for_forest) {
  plot <- create_within_pair_forest_table(
    all_within_pair_mz,
    outcome_name,
    "MZ Pairs",
    n_pairs = unname(binary_pair_counts_mz[[outcome_name]])
  )

  if (!is.null(plot)) {
    save_plot(
      filename = file.path(output_dir_within_pair, paste0("forest_", outcome_name, "_mz_pairs.svg")),
      plot = plot,
      width = 8,
      height = 5,
      dpi = 300
    )
  }
}

# Save CSV for binary outcomes - all pairs
for (outcome_name in binary_outcomes_for_forest) {
  outcome_data <- all_within_pair_all |> 
    filter(outcome == outcome_name, is.na(error_message))
  
  if (nrow(outcome_data) == 0) next
  
  tab <- outcome_data |>
    mutate(
      use_sci = pmax(abs(standardized_estimate), abs(standardized_ci_lower), abs(standardized_ci_upper), na.rm = TRUE) >= 10,
      use_sci = if_else(is.na(use_sci), FALSE, use_sci),
      effect_formatted = if_else(use_sci,
        sprintf("%.1e (%.1e-%.1e)", standardized_estimate, standardized_ci_lower, standardized_ci_upper),
        sprintf("%.2f (%.2f-%.2f)", standardized_estimate, standardized_ci_lower, standardized_ci_upper)),
      Organ_Display = predictor
    ) |>
    select(Organ = Organ_Display, `Effect Size (95% CI)` = effect_formatted, FDR)
  
  write.csv(tab, file = file.path(csv_dir_within, paste0(outcome_name, "_all_pairs.csv")), row.names = FALSE)
}

# Save CSV for binary outcomes - MZ pairs
for (outcome_name in binary_outcomes_for_forest) {
  outcome_data <- all_within_pair_mz |> 
    filter(outcome == outcome_name, is.na(error_message))
  
  if (nrow(outcome_data) == 0) next
  
  tab <- outcome_data |>
    mutate(
      use_sci = pmax(abs(standardized_estimate), abs(standardized_ci_lower), abs(standardized_ci_upper), na.rm = TRUE) >= 10,
      use_sci = if_else(is.na(use_sci), FALSE, use_sci),
      effect_formatted = if_else(use_sci,
        sprintf("%.1e (%.1e-%.1e)", standardized_estimate, standardized_ci_lower, standardized_ci_upper),
        sprintf("%.2f (%.2f-%.2f)", standardized_estimate, standardized_ci_lower, standardized_ci_upper)),
      Organ_Display = predictor
    ) |>
    select(Organ = Organ_Display, `Effect Size (95% CI)` = effect_formatted, FDR)
  
  write.csv(tab, file = file.path(csv_dir_within, paste0(outcome_name, "_mz_pairs.csv")), row.names = FALSE)
}
```
