---
title: "Combined Olink and MS Mortality Clocks"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
    code_folding: hide
  pdf_document:
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, message = FALSE, warning = FALSE,
  fig.width = 10, fig.height = 6, fig.align = 'center'
)

# Set global seed for reproducibility
set.seed(350)
```

# Introduction

This notebook builds GLS-based organ mortality clocks from combined Mass Spectrometry (MS) and Olink protein measurements.

## Data Loading and Preparation

```{r load-libraries}
library(tidyverse)
library(tidymodels)
library(forcats)
library(survival)

# Prefer dplyr verbs in this notebook
select = dplyr::select
rename = dplyr::rename
```

```{r load-data}
# Input: protein measurements
input_protein_measurements_file <- "PATH/TO/input_protein_measurements.csv"

# Input: participant metadata / covariates
input_metadata_file <- "PATH/TO/input_metadata.csv"

# Input: shared model functions
input_model_functions_file <- "PATH/TO/model_functions.R"
if (!file.exists(input_model_functions_file)) {
  stop("Set `input_model_functions_file` to a valid path before running.")
}

comb <- read_csv(input_protein_measurements_file)
twins <- read_csv(input_metadata_file) |> 
  mutate(sex = as.factor(sex))

# Source model functions
source(input_model_functions_file)

# Prepare mortality data
mortality_data <- comb |> 
  left_join(twins |> select(twin_id, age, sex, pair_id, time = time_to_death, status = deceased), by = "twin_id")
```


# Utility Functions

```{r utility-functions}
ensure_parent_dir <- function(path) {
  dir.create(dirname(path), showWarnings = FALSE, recursive = TRUE)
}

plot_performance_metrics <- function(data, metric_col, title, color = "steelblue") {
  ggplot(data, aes(x = reorder(clock, !!sym(metric_col)), y = !!sym(metric_col))) +
    geom_bar(stat = "identity", fill = color, alpha = 0.7) +
    coord_flip() +
    theme_minimal() +
    labs(title = title, x = "Organ Clock", y = str_to_title(metric_col)) +
    theme(plot.title = element_text(hjust = 0.5), axis.text.y = element_text(size = 8)) +
    geom_text(aes(label = sprintf("%.3f", !!sym(metric_col))), hjust = -0.2, size = 3) +
    ylim(0, max(data[[metric_col]], na.rm = TRUE) * 1.1) +
    theme(panel.grid = element_blank())
}
```

# GLS-Based Organ-Specific Analysis

This section defines organ-specific predictor sets from GLS labels and trains mortality clocks with pair-aware out-of-fold (OOF) validation.

Modeling setup:
- Mortality clocks fit with Cox models
- Pair-aware outer and inner cross-validation
- Alpha tuning per outer fold by lowest CV deviance
- Sex-specific models for male and female participants
- OOF predictions used for performance summaries

## GLS Protein Set Preparation

```{r gls-analysis}
# Input: feature set definitions
input_feature_set_file <- "PATH/TO/input_feature_set_definitions.csv"
gls_info <- read_csv(input_feature_set_file)

gls_predictor_sets <- list()

gls_info |>
  na.omit(clean_label_string) |> 
  separate_rows(clean_label_string, sep = "\\.") |>
  mutate(clean_label_string = str_trim(clean_label_string)) |>
  group_by(clean_label_string) |>
  summarise(
    proteins = list(unique(protein)),
    n_proteins = n_distinct(protein),
    .groups = "drop"
  ) |>
  filter(n_proteins >= 2) |>
  pwalk(function(clean_label_string, proteins, n_proteins) {
    gls_predictor_sets[[clean_label_string]] <<- proteins
  })

```

# Model Training and Export

This section runs the OOF training pipeline, exports predictions and parameters for downstream analyses, and refits final models using OOF-selected alpha values.

```{r oof-train}
# Computationally intensive step: OOF mortality clocks
gls_oof_mortality <- create_oof_tuned_mortality_clock(
  df = mortality_data,
  predictors = gls_predictor_sets,
  time_col = "time",
  status_col = "status",
  age_col = "age",
  loess = TRUE,
  outer_folds = 5,
  inner_folds = 5,
  alpha_grid = seq(0, 1, by = 0.1),
  seed = 350
)
invisible(NULL)
```

```{r export-results}
# Exports and refit (depends on gls_oof_mortality from oof-train chunk)
gls_tuned_mortality_data <- gls_oof_mortality$oof_pred_wide

# Output: OOF predictions
output_predictions_file <- "PATH/TO/output_predictions.csv"
ensure_parent_dir(output_predictions_file)
write_csv(
  gls_tuned_mortality_data,
  output_predictions_file
)

# Output: alpha summary from OOF tuning
output_alpha_summary_file <- "PATH/TO/output_alpha_summary.csv"
ensure_parent_dir(output_alpha_summary_file)
write_csv(
  gls_oof_mortality$alpha_summary,
  output_alpha_summary_file
)

# OOF performance metrics in long format
oof_metrics_long <- gls_oof_mortality$oof_pred_long |>
  left_join(mortality_data |> select(twin_id, time, status, sex), by = "twin_id") |>
  tidyr::drop_na(time, status, .pred) |>
  mutate(sex = if_else(sex == 1, "male", "female")) |>
  group_by(organ, sex) |>
  summarise(
    concordance = 1 - survival::concordance(Surv(time, status) ~ .pred)$concordance,
    age_correlation = cor(age, .pred, use = "complete.obs"),
    .groups = "drop"
  ) |>
  pivot_longer(cols = c(concordance, age_correlation), names_to = ".metric", values_to = ".estimate") |>
  mutate(
    .estimator = if_else(.metric == "concordance", "standard", "pearson"),
    split = "oof",
    clock = organ
  ) |>
  select(clock, sex, split, .metric, .estimator, .estimate)

# Output: OOF metrics
output_metrics_oof_file <- "PATH/TO/output_metrics_oof.csv"
ensure_parent_dir(output_metrics_oof_file)
write_csv(
  oof_metrics_long,
  output_metrics_oof_file
)

# OOF performance plots
oof_concordance_data <- oof_metrics_long |>
  filter(.metric == "concordance") |>
  group_by(clock) |>
  summarise(concordance = mean(.estimate, na.rm = TRUE), .groups = "drop")

oof_age_corr_data <- oof_metrics_long |>
  filter(.metric == "age_correlation") |>
  group_by(clock) |>
  summarise(correlation = mean(.estimate, na.rm = TRUE), .groups = "drop")

gls_oof_concordance_plot <- plot_performance_metrics(
  oof_concordance_data, "concordance",
  "GLS OOF Mortality Model Performance - Concordance Values",
  "darkred"
)
gls_oof_concordance_plot

gls_oof_age_corr_plot <- plot_performance_metrics(
  oof_age_corr_data, "correlation",
  "GLS OOF Mortality Model Performance - Age Correlation Values",
  "darkgreen"
)
gls_oof_age_corr_plot

# Output: performance plots
output_plot_concordance_png <- "PATH/TO/output_concordance.png"
output_plot_age_correlation_png <- "PATH/TO/output_age_correlation.png"
ensure_parent_dir(output_plot_concordance_png)
ensure_parent_dir(output_plot_age_correlation_png)
ggsave(output_plot_concordance_png, gls_oof_concordance_plot, width = 10, height = 6, dpi = 150)
ggsave(output_plot_age_correlation_png, gls_oof_age_corr_plot, width = 10, height = 6, dpi = 150)

# Output: scaling information
output_scaling_info_file <- "PATH/TO/output_scaling_info.csv"
ensure_parent_dir(output_scaling_info_file)
gls_mortality_scaling_info <- extract_scaling_info_from_oof(gls_oof_mortality$oof_pred_long, model_type = "mortality")
write_csv(
  gls_mortality_scaling_info,
  output_scaling_info_file
)

# Output: canonical metrics table used downstream
output_metrics_main_file <- "PATH/TO/output_metrics_main.csv"
ensure_parent_dir(output_metrics_main_file)
write_csv(
  oof_metrics_long,
  output_metrics_main_file
)

# Alpha parameters from OOF tuning
gls_alpha_df_oof <- gls_oof_mortality$alpha_summary |>
  select(clock = organ, male_alpha = male_best_alpha_mean, female_alpha = female_best_alpha_mean)

# Output: selected alpha parameters
output_alpha_parameters_file <- "PATH/TO/output_alpha_parameters.csv"
ensure_parent_dir(output_alpha_parameters_file)
write_csv(
  gls_alpha_df_oof,
  output_alpha_parameters_file
)

# Refit on full data using OOF-selected alphas; save model object for downstream analyses
alpha_summary_refit <- gls_oof_mortality$alpha_summary |>
  select(organ, male_best_alpha_mean, female_best_alpha_mean)
alpha_results_refit <- set_names(
  map(seq_len(nrow(alpha_summary_refit)), function(i) list(
    male_best_alpha = alpha_summary_refit$male_best_alpha_mean[i],
    female_best_alpha = alpha_summary_refit$female_best_alpha_mean[i]
  )),
  alpha_summary_refit$organ
)
gls_refit_oof <- create_refit_tuned_mortality_clock(
  df = mortality_data,
  predictors = gls_predictor_sets,
  alpha_results = alpha_results_refit,
  time_col = "time",
  status_col = "status",
  age_col = "age",
  loess = TRUE,
  nfolds = 5,
  seed = 350
)
gls_tuned_mortality_clocks <- set_names(gls_refit_oof$models, names(gls_predictor_sets))

# Output: final fitted model object
output_model_rds_file <- "PATH/TO/output_model.rds"
ensure_parent_dir(output_model_rds_file)
saveRDS(gls_tuned_mortality_clocks, output_model_rds_file)

# OOF summary figures for results output
# Output: summary figures
output_plot_cindex_svg <- "PATH/TO/output_cindex.svg"
output_plot_cindex_pdf <- "PATH/TO/output_cindex.pdf"
output_plot_age_bar_svg <- "PATH/TO/output_age_bar.svg"
output_plot_age_bar_pdf <- "PATH/TO/output_age_bar.pdf"
ensure_parent_dir(output_plot_cindex_svg)
ensure_parent_dir(output_plot_cindex_pdf)
ensure_parent_dir(output_plot_age_bar_svg)
ensure_parent_dir(output_plot_age_bar_pdf)

oof_cindex_noconv <- oof_concordance_data |>
  filter(tolower(clock) != "conventional") |>
  arrange(concordance) |>
  mutate(clock = fct_inorder(clock))

gls_oof_cindex_lollipop <- ggplot(oof_cindex_noconv, aes(x = concordance, y = clock)) +
  geom_segment(aes(x = 0.65, xend = concordance, y = clock, yend = clock, color = concordance),
               linewidth = 1, show.legend = FALSE) +
  geom_point(aes(x = concordance, color = concordance), size = 4, alpha = 1, show.legend = FALSE) +
  scale_color_gradient(low = "lightpink", high = "darkred") +
  theme_minimal() +
  labs(x = "C-index", y = "") +
  theme(
    axis.text.y = element_text(size = 10, family = "Helvetica"),
    axis.text.x = element_text(size = 10, family = "Helvetica"),
    axis.title.x = element_text(family = "Helvetica"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank()
  ) +
  geom_text(aes(label = sprintf("%.2f", concordance), color = concordance),
            hjust = -0.3, size = 3.5, show.legend = FALSE) +
  scale_x_continuous(limits = c(0.65, 0.8), breaks = c(0.65, 0.7, 0.75, 0.8))
gls_oof_cindex_lollipop

ggsave(output_plot_cindex_svg, gls_oof_cindex_lollipop, device = "svg", width = 5, height = 3)
ggsave(output_plot_cindex_pdf, gls_oof_cindex_lollipop, device = "pdf", width = 4, height = 3)

oof_age_corr_noconv <- oof_age_corr_data |>
  filter(tolower(clock) != "conventional") |>
  arrange(desc(correlation)) |>
  mutate(clock = fct_inorder(clock))

gls_oof_age_corr_bar <- ggplot(oof_age_corr_noconv, aes(x = reorder(clock, -correlation), y = correlation, fill = correlation)) +
  geom_bar(stat = "identity", alpha = 1, show.legend = FALSE) +
  scale_fill_gradient(low = "lightblue", high = "darkblue") +
  geom_text(aes(label = sprintf("%.2f", correlation), color = correlation), vjust = -0.5, size = 4, show.legend = FALSE) +
  scale_color_gradient(low = "lightblue", high = "darkblue", guide = "none") +
  theme_minimal() +
  labs(x = "", y = "") +
  theme(
    axis.text.x = element_text(size = 12, family = "Helvetica", angle = 45, hjust = 1),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    plot.margin = margin(t = 10, r = 20, b = 40, l = 10, unit = "pt")
  ) +
  scale_y_continuous(limits = c(0, 0.75))
gls_oof_age_corr_bar

ggsave(output_plot_age_bar_svg, gls_oof_age_corr_bar, device = "svg", width = 5.5, height = 4.5)
ggsave(output_plot_age_bar_pdf, gls_oof_age_corr_bar, device = "pdf", width = 5.5, height = 4.5)

invisible(NULL)
```

## GLS OOF Mortality Performance

Summary of out-of-fold performance by clock (concordance and age correlation; means across sex). Concordance and age-correlation plots are shown above in Results Export.

```{r gls-oof-performance}
oof_summary <- oof_metrics_long |>
  group_by(clock, .metric) |>
  summarise(.estimate = mean(.estimate, na.rm = TRUE), .groups = "drop") |>
  pivot_wider(names_from = .metric, values_from = .estimate)

knitr::kable(as.data.frame(oof_summary),
             caption = "GLS OOF Mortality Model Performance (mean across sex)",
             digits = 4)
```

## GLS Scaling Information Analysis

```{r gls-scaling-info}
# OOF scaling info (written by export-results chunk)
# Set to the same path used for `output_scaling_info_file` above.
output_scaling_info_file <- "PATH/TO/output_scaling_info.csv"
gls_mortality_scaling_info <- read_csv(
  output_scaling_info_file,
  show_col_types = FALSE
)

knitr::kable(
  as.data.frame(gls_mortality_scaling_info |> 
    select(clock, sd_in_original_units, interpretation, mean_gap, median_gap, q25_gap, q75_gap)),
  caption = "Scaling Information for GLS Mortality Models - What 1 SD Represents in Mortality Units",
  digits = 3
)

ggplot(gls_mortality_scaling_info, aes(x = reorder(clock, sd_in_original_units), y = sd_in_original_units)) +
  geom_bar(stat = "identity", fill = "darkred", alpha = 0.7) +
  coord_flip() +
  labs(title = "Standard Deviation of Mortality Scores by GLS Organ Clock",
       subtitle = "What 1 SD represents in mortality units",
       x = "Organ Clock", y = "Standard Deviation (mortality units)") +
  theme_minimal() +
  geom_text(aes(label = sprintf("%.2f", sd_in_original_units)), hjust = -0.2, size = 3) +
  theme(plot.title = element_text(hjust = 0.5))
```
