---
title: "Incident outcome analyses"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r libraries}
library(tidyverse)
library(survival)
library(survminer)
library(haven)
library(readxl)
library(ggvenn)
library(patchwork)
library(lubridate)
library(lmtest)
library(sandwich)
select = dplyr::select
rename = dplyr::rename
slice = dplyr::slice
desc = dplyr::desc
```

# 1. Data Preparation

## 1.1 Load and Process Datasets

```{r data_loading}
# Input files (set these for your environment)
input_diagnosis_file <- "PATH/TO/input_diagnosis.csv"
input_cancer_file <- "PATH/TO/input_cancer.csv"
input_metadata_file <- "PATH/TO/input_metadata.csv"
input_organ_age_file <- "PATH/TO/input_organ_age.csv"

# Output root (set this for your environment)
output_core_dir <- "PATH/TO/output/core_cox"

# Core schema configuration
id_col <- "twin_id"
sex_col <- "sex"
pair_col <- "pair_id"
male_code <- 1
female_code <- 2

# Optional organ-specific columns (set to NULL if not present)
ovary_col <- "Ovary"
prostate_col <- "Prostate"

# Optional prefix to remove from organ-age columns
organ_age_prefix_to_strip <- "tuned_mortality_"

# Covariate sets (choose active set)
covariate_sets <- list(
  minimal = c("sex", "age"),
  cardiometabolic = c("sex", "age", "bmi"),
  extended = c("sex", "age", "edyrs", "eversmok", "bmi", "hba1c", "total_hdl_ratio", "crp")
)
active_covariate_set <- "extended"

active_covariates <- covariate_sets[[active_covariate_set]]
if (is.null(active_covariates)) {
  stop("Invalid `active_covariate_set` in data_loading.")
}
covariate_formula_terms <- paste(active_covariates, collapse = " + ")

# Load datasets
composite_diseases <- read_csv(input_diagnosis_file) |>
  # Convert NAs in numeric disease indicator columns to 0 (exclude id)
  mutate(across(where(is.numeric) & !any_of(id_col), ~ if_else(is.na(.), 0, .)))
cancer <- read_csv(input_cancer_file)
twins <- read_csv(input_metadata_file)

organ_age_mortality <- read_csv(input_organ_age_file)

## 1.2 Define Analysis Parameters
end_followup <- as.Date("2024-03-05")

## 1.3 Process Organ Age Data
if (!is.null(organ_age_prefix_to_strip) && nzchar(organ_age_prefix_to_strip)) {
  organ_age_mortality <- organ_age_mortality |>
    rename_with(~str_remove(., paste0("^", organ_age_prefix_to_strip)), everything())
}

## 1.4 Process Organ Ages Based on Sex
organ_age_mortality <- organ_age_mortality |>
  left_join(select(twins, all_of(c(id_col, sex_col))), by = id_col)

if (!is.null(ovary_col) && ovary_col %in% names(organ_age_mortality)) {
  organ_age_mortality <- organ_age_mortality |>
    mutate("{ovary_col}" := if_else(.data[[sex_col]] == male_code, NA_real_, .data[[ovary_col]]))
}

if (!is.null(prostate_col) && prostate_col %in% names(organ_age_mortality)) {
  organ_age_mortality <- organ_age_mortality |>
    mutate("{prostate_col}" := if_else(.data[[sex_col]] == female_code, NA_real_, .data[[prostate_col]]))
}

organ_age_mortality <- organ_age_mortality |>
  select(-all_of(sex_col))

## 1.5 Merge Main Datasets
twins_analysis <- twins |>
  left_join(composite_diseases, by = id_col) |>
  left_join(cancer, by = id_col) |> 
  mutate(
    across(ends_with("_date"), as.Date),
    birthdate = as.Date(birthdate),
    checkdate = as.Date(checkdate),
    deathdate = as.Date(deathdate),
    sex = as.factor(sex)
  ) |> 
  mutate(across(c(cvd, diabetes, dementia, parkinson_and_parkinsonism), ~ if_else(is.na(.), 0, .))) |>
  # Convert NA to 0 for cancer variables (missing = no cancer)
  mutate(across(c("Melanoma", "Prostate cancer", "Multiple myeloma", "Brain cancer", 
                  "Lung cancer", "Breast cancer", "Colorectal cancer", "Kidney cancer", 
                  "Bladder cancer", "Esophageal cancer", "Stomach cancer", "Liver cancer", 
                  "Lymphoma", "Leukemia", "Ovarian cancer", "Thyroid cancer", 
                  "Uterine cancer", "Pancreatic cancer", "Cervical cancer"), 
                ~ if_else(is.na(.), 0, .))) |> 
  # Treat missing healthspan_event as censored (0)
  mutate(healthspan_event = if_else(is.na(healthspan_event), 0, healthspan_event))

## 1.6 Create Analysis Datasets
twins_mortality <- twins_analysis |>
  left_join(organ_age_mortality, by = id_col)

## 1.7 Get Organ Age Columns
organ_age_cols_mortality <- names(organ_age_mortality)[names(organ_age_mortality) != id_col]

```

# 2. Disease Selection and Eligibility

```{r incident_case_filter}
## 2.1 Define Diseases to Analyze
# Disease configuration: list_key = list(var = "...", date = "...", name = "...")
diseases_config <- list(
  # Metabolic diseases
  diabetes = list(var = "diabetes", date = "diabetes_date", name = "Diabetes"),
  
  # Neurological diseases
  dementia = list(var = "dementia", date = "dementia_date", name = "Dementia"),
  parkinsons = list(var = "parkinson_and_parkinsonism", date = "parkinson_and_parkinsonism_date", name = "Parkinson"),
  
  # Cardiovascular diseases
  ischemic_heart_disease = list(var = "ischemic_heart_disease", date = "ischemic_heart_disease_date", name = "Ischemic heart disease"),
  atrial_fibrillation = list(var = "atrial_fibrillation", date = "atrial_fibrillation_date", name = "Atrial fibrillation"),
  cerebrovascular_disease = list(var = "cerebrovascular_disease", date = "cerebrovascular_disease_date", name = "Cerebrovascular disease"),
  heart_failure = list(var = "heart_failure", date = "heart_failure_date", name = "Heart failure"),
  
  # Cancer types
  melanoma = list(var = "Melanoma", date = "Melanoma_date", name = "Melanoma"),
  prostate_cancer = list(var = "Prostate cancer", date = "Prostate cancer_date", name = "Prostate cancer"),
  multiple_myeloma = list(var = "Multiple myeloma", date = "Multiple myeloma_date", name = "Multiple myeloma"),
  brain_cancer = list(var = "Brain cancer", date = "Brain cancer_date", name = "Brain cancer"),
  lung_cancer = list(var = "Lung cancer", date = "Lung cancer_date", name = "Lung cancer"),
  breast_cancer = list(var = "Breast cancer", date = "Breast cancer_date", name = "Breast cancer"),
  colorectal_cancer = list(var = "Colorectal cancer", date = "Colorectal cancer_date", name = "Colorectal cancer"),
  kidney_cancer = list(var = "Kidney cancer", date = "Kidney cancer_date", name = "Kidney cancer"),
  bladder_cancer = list(var = "Bladder cancer", date = "Bladder cancer_date", name = "Bladder cancer"),
  esophageal_cancer = list(var = "Esophageal cancer", date = "Esophageal cancer_date", name = "Esophageal cancer"),
  stomach_cancer = list(var = "Stomach cancer", date = "Stomach cancer_date", name = "Stomach cancer"),
  liver_cancer = list(var = "Liver cancer", date = "Liver cancer_date", name = "Liver cancer"),
  lymphoma = list(var = "Lymphoma", date = "Lymphoma_date", name = "Lymphoma"),
  leukemia = list(var = "Leukemia", date = "Leukemia_date", name = "Leukemia"),
  ovarian_cancer = list(var = "Ovarian cancer", date = "Ovarian cancer_date", name = "Ovarian cancer"),
  thyroid_cancer = list(var = "Thyroid cancer", date = "Thyroid cancer_date", name = "Thyroid cancer"),
  uterine_cancer = list(var = "Uterine cancer", date = "Uterine cancer_date", name = "Uterine cancer"),
  pancreatic_cancer = list(var = "Pancreatic cancer", date = "Pancreatic cancer_date", name = "Pancreatic cancer"),
  cervical_cancer = list(var = "Cervical cancer", date = "Cervical cancer_date", name = "Cervical cancer")
)
```

```{r filter_diseases_by_cases}
## 2.2 Examine Disease Case Counts and Filter Diseases Below Minimum Threshold
disease_case_counts <- twins_analysis |>
  summarise(
    across(
      map_chr(diseases_config, ~.x$var), 
      ~sum(. == 1, na.rm = TRUE), 
      .names = "{.col}_cases"
    )
  ) |>
  pivot_longer(everything(), names_to = "disease", values_to = "cases") |>
  mutate(
    disease_clean = str_remove(disease, "_cases"),
    pct_of_sample = cases / nrow(twins_analysis) * 100
  )

## 2.3 Calculate Minimum Threshold 
min_cases_threshold <- round(0.01 * nrow(twins))
diseases_to_keep <- disease_case_counts |>
  filter(cases >= min_cases_threshold) |>
  pull(disease_clean)

## 2.4 Keep Only Diseases That Meet the Minimum Case Threshold
diseases <- diseases_config[names(diseases_config) %in% diseases_to_keep]

## 2.5 Disease Case Summary
cat("Disease case counts and filtering summary:\n")
print(disease_case_counts)
cat("\nMinimum cases threshold:", min_cases_threshold, "\n")
cat("Diseases kept for analysis:", paste(names(diseases), collapse = ", "), "\n")
cat("Diseases excluded:", paste(setdiff(names(diseases_config), names(diseases)), collapse = ", "), "\n")



## 2.6 Recompute Eligible Diseases Using Incident Cases Only (Exclude Prevalent at Baseline)
incident_case_counts <- map_dfr(names(diseases_config), function(d) {
  spec <- diseases_config[[d]]
  var <- spec$var
  date_var <- spec$date
  tibble(
    disease = d,
    cases = sum(twins_analysis[[var]] == 1 & twins_analysis[[date_var]] > twins_analysis$checkdate, na.rm = TRUE)
  )
})

diseases_to_keep_incident <- incident_case_counts |>
  filter(cases >= min_cases_threshold) |>
  pull(disease)

## 2.7 Keep Diseases Meeting Incident-Case Threshold
diseases <- diseases_config[names(diseases_config) %in% diseases_to_keep_incident]
```

# 3. Analysis Functions

```{r functions}
## 3.1 Function to Create Age-Based Time-to-Event Variables
create_time_to_event_age <- function(data, disease_var, disease_date_var, disease_name) {
  
  # Validate disease label
  if (is.null(disease_name) || length(disease_name) == 0 || disease_name == "") {
    stop("disease_name is empty or null")
  }
  
  # Filter by sex for sex-specific diseases to restrict at-risk population
  data_filtered <- data
  if (grepl("prostate", disease_name, ignore.case = TRUE)) {
    data_filtered <- data_filtered |> filter(sex == 1)  # Males only
  } else if (grepl("breast|ovarian|uterine|cervical", disease_name, ignore.case = TRUE)) {
    data_filtered <- data_filtered |> filter(sex == 2)  # Females only
  }
  
  # Check if disease_date_var is a numeric age variable (like healthspan) or a date
  # For healthspan, the variable is already an age, not a date
  is_numeric_age <- disease_date_var == "healthspan"
  
  if (is_numeric_age) {
    # Numeric-age outcome (e.g., healthspan)
    data_clean <- data_filtered |>
      mutate(
        age_at_event = !!sym(disease_date_var),  # Already an age
        time_to_event = age_at_event - age,
        event = !!sym(disease_var)
      ) |>
      filter(!is.na(time_to_event), time_to_event > 0)
  } else {
    # Standard handling for date variables
    data_clean <- data_filtered |>
      filter(
        !!sym(disease_var) == 0 |
        (!!sym(disease_var) == 1 & !!sym(disease_date_var) > checkdate)
      ) |>
      mutate(
        age_at_event = case_when(
          !!sym(disease_var) == 1 ~ as.numeric(!!sym(disease_date_var) - birthdate) / 365.25,
          deceased == 1 & !!sym(disease_var) == 0 & !is.na(deathdate) & deathdate <= end_followup ~ as.numeric(deathdate - birthdate) / 365.25,
          TRUE ~ as.numeric(end_followup - birthdate) / 365.25
        ),
        time_to_event = age_at_event - age,
        event = case_when(
          !!sym(disease_var) == 1 ~ 1,
          TRUE ~ 0
        )
      ) |>
      filter(time_to_event > 0)
  }
  
  n_original <- nrow(data_filtered)
  n_events <- sum(data_clean$event, na.rm = TRUE)
  n_censored_death <- sum(data_clean$deceased == 1 & data_clean$event == 0, na.rm = TRUE)
  n_censored_followup <- sum(data_clean$deceased == 0 & data_clean$event == 0, na.rm = TRUE)
  
  cleaning_summary <- list(
    disease = disease_name,
    n_original = n_original,
    n_prevalent_removed = n_original - nrow(data_clean),
    n_incident_cases = n_events,
    n_censored_death = n_censored_death,
    n_censored_followup = n_censored_followup,
    n_final = nrow(data_clean)
  )
  
  return(list(data = data_clean, summary = cleaning_summary))
}

## 3.2 Function to Run Cox Analysis with Organ Ages
run_organ_age_cox_age <- function(data, disease_var, disease_date_var, disease_name, organ_age_col) {
  
  analysis_data <- create_time_to_event_age(data, disease_var, disease_date_var, disease_name)
  twins_clean <- analysis_data$data
  
  surv_obj <- Surv(twins_clean$time_to_event, twins_clean$event)
  cox_formula <- as.formula(paste("surv_obj ~", covariate_formula_terms, "+", organ_age_col))
  cox_model <- coxph(cox_formula, data = twins_clean)
  
  # Get cluster-robust standard errors
  cluster_se <- vcovCL(cox_model, cluster = ~pair_id)
  coeftest_model <- coeftest(cox_model, vcov = cluster_se)
  
  return(list(
    model = cox_model,
    summary = summary(cox_model),
    coeftest = coeftest_model,
    cluster_vcov = cluster_se,
    cleaning_summary = analysis_data$summary,
    data = twins_clean,
    organ_age_col = organ_age_col
  ))
}

## 3.3 Function to Run Mortality Cox Analysis
run_mortality_cox_age <- function(data, organ_age_col) {
  
  mortality_data <- data |>
    mutate(
      age_at_event = case_when(
        deceased == 1 & !is.na(deathdate) ~ as.numeric(deathdate - birthdate) / 365.25,
        TRUE ~ as.numeric(end_followup - birthdate) / 365.25
      ),
      time_to_event = age_at_event - age,
      event = deceased
    ) |>
    filter(time_to_event > 0)
  
  surv_obj <- Surv(mortality_data$time_to_event, mortality_data$event)
  cox_formula <- as.formula(paste("surv_obj ~", covariate_formula_terms, "+", organ_age_col))
  cox_model <- coxph(cox_formula, data = mortality_data)
  
  # Get cluster-robust standard errors
  cluster_se <- vcovCL(cox_model, cluster = ~pair_id)
  coeftest_model <- coeftest(cox_model, vcov = cluster_se)
  
  return(list(
    model = cox_model,
    summary = summary(cox_model),
    coeftest = coeftest_model,
    cluster_vcov = cluster_se,
    data = mortality_data,
    organ_age_col = organ_age_col
  ))
}

## 3.4 Function to Run Healthspan Cox Analysis (Age-Based Time Scale)
run_healthspan_cox_age <- function(data, organ_age_col) {
  
  healthspan_data <- data |>
    mutate(
      time_to_event = healthspan - age,
      event = healthspan_event
    ) |>
    filter(!is.na(time_to_event), time_to_event > 0)
  
  surv_obj <- Surv(healthspan_data$time_to_event, healthspan_data$event)
  cox_formula <- as.formula(paste("surv_obj ~", covariate_formula_terms, "+", organ_age_col))
  cox_model <- coxph(cox_formula, data = healthspan_data)
  
  # Get cluster-robust standard errors
  cluster_se <- vcovCL(cox_model, cluster = ~pair_id)
  coeftest_model <- coeftest(cox_model, vcov = cluster_se)
  
  return(list(
    model = cox_model,
    summary = summary(cox_model),
    coeftest = coeftest_model,
    cluster_vcov = cluster_se,
    data = healthspan_data,
    organ_age_col = organ_age_col
  ))
}

## 3.6 Function to Extract Results
extract_organ_age_results <- function(results_list, model_type) {
  all_results <- list()
  
  for (disease_name in names(results_list)) {
    for (organ_name in names(results_list[[disease_name]])) {
      result <- results_list[[disease_name]][[organ_name]]
      
      if (!is.null(result)) {
        # Use cluster-robust results
        coeftest_model <- result$coeftest
        organ_age_col <- result$organ_age_col
        
        # Find the organ age coefficient index (last coefficient)
        coef_names <- rownames(coeftest_model)
        organ_idx <- which(coef_names == organ_age_col)
        
        if (length(organ_idx) > 0) {
          # Extract cluster-robust coefficient and standard error
          coef_est <- coeftest_model[organ_idx, "Estimate"]
          coef_se <- coeftest_model[organ_idx, "Std. Error"]
          p_value <- coeftest_model[organ_idx, "Pr(>|z|)"]
          
          # Calculate HR and CI from cluster-robust results
          hr <- exp(coef_est)
          hr_lower <- exp(coef_est - 1.96 * coef_se)
          hr_upper <- exp(coef_est + 1.96 * coef_se)
          
          all_results[[paste(disease_name, organ_name, sep = "_")]] <- tibble(
            Disease = disease_name,
            Organ = organ_name,
            Model_Type = model_type,
            HR = hr,
            HR_lower = hr_lower,
            HR_upper = hr_upper,
            P_value = p_value
          )
        }
      }
    }
  }
  
  return(bind_rows(all_results))
}

## 3.7 Function to Extract Mortality Results
extract_mortality_results <- function(results_list, model_type) {
  all_results <- list()
  
  for (organ_name in names(results_list)) {
    result <- results_list[[organ_name]]
    
    if (!is.null(result)) {
      # Use cluster-robust results
      coeftest_model <- result$coeftest
      organ_age_col <- result$organ_age_col
      
      # Find the organ age coefficient index (last coefficient)
      coef_names <- rownames(coeftest_model)
      organ_idx <- which(coef_names == organ_age_col)
      
      if (length(organ_idx) > 0) {
        # Extract cluster-robust coefficient and standard error
        coef_est <- coeftest_model[organ_idx, "Estimate"]
        coef_se <- coeftest_model[organ_idx, "Std. Error"]
        p_value <- coeftest_model[organ_idx, "Pr(>|z|)"]
        
        # Calculate HR and CI from cluster-robust results
        hr <- exp(coef_est)
        hr_lower <- exp(coef_est - 1.96 * coef_se)
        hr_upper <- exp(coef_est + 1.96 * coef_se)
        
        all_results[[organ_name]] <- tibble(
          Disease = "Mortality",
          Organ = organ_name,
          Model_Type = model_type,
          HR = hr,
          HR_lower = hr_lower,
          HR_upper = hr_upper,
          P_value = p_value
        )
      }
    }
  }
  
  return(bind_rows(all_results))
}

## 3.8 Function to Extract Healthspan Results
extract_healthspan_results <- function(results_list, model_type) {
  all_results <- list()
  
  for (organ_name in names(results_list)) {
    result <- results_list[[organ_name]]
    
    if (!is.null(result)) {
      # Use cluster-robust results
      coeftest_model <- result$coeftest
      organ_age_col <- result$organ_age_col
      
      # Find the organ age coefficient index (last coefficient)
      coef_names <- rownames(coeftest_model)
      organ_idx <- which(coef_names == organ_age_col)
      
      if (length(organ_idx) > 0) {
        # Extract cluster-robust coefficient and standard error
        coef_est <- coeftest_model[organ_idx, "Estimate"]
        coef_se <- coeftest_model[organ_idx, "Std. Error"]
        p_value <- coeftest_model[organ_idx, "Pr(>|z|)"]
        
        # Calculate HR and CI from cluster-robust results
        hr <- exp(coef_est)
        hr_lower <- exp(coef_est - 1.96 * coef_se)
        hr_upper <- exp(coef_est + 1.96 * coef_se)
        
        all_results[[organ_name]] <- tibble(
          Disease = "Healthspan",
          Organ = organ_name,
          Model_Type = model_type,
          HR = hr,
          HR_lower = hr_lower,
          HR_upper = hr_upper,
          P_value = p_value
        )
      }
    }
  }
  
  return(bind_rows(all_results))
}
```

# 4. Cox Regression Analyses

Cox models for incident disease risk.  
Model: `Surv(time_to_event, event) ~ organ_age + selected_covariates` with pair-clustered robust SEs.

```{r disease_analyses}
## 4.1 Disease Risk Analyses (All Diseases Including Cancer)

# Diseases list is now defined in the data loading section above
# This includes both non-cancer and cancer diseases

### 4.1.2 Mortality-Calibrated Organ Age Models for Disease Risk
mortality_results <- list()
for (disease_name in names(diseases)) {
  disease <- diseases[[disease_name]]
  mortality_results[[disease_name]] <- list()
  
  for (organ_col in organ_age_cols_mortality) {
    # Skip impossible organ-disease combinations
    # Female-specific diseases: skip Prostate organ
    if (grepl("breast|ovarian|uterine|cervical", disease$name, ignore.case = TRUE) && organ_col == "Prostate") {
      next
    }
    # Prostate cancer: skip Ovary organ
    if (grepl("prostate", disease$name, ignore.case = TRUE) && organ_col == "Ovary") {
      next
    }
    
    result <- run_organ_age_cox_age(
      data = twins_mortality,
      disease_var = disease$var,
      disease_date_var = disease$date,
      disease_name = disease$name,
      organ_age_col = organ_col
    )
    mortality_results[[disease_name]][[organ_col]] <- result
  }
}
```

## 4.2 Mortality Risk Analyses

Univariate Cox models for all-cause mortality.  
Model: `Surv(time_to_death, death_event) ~ organ_age + selected_covariates` with pair-clustered robust SEs.

```{r mortality_analyses}
### 4.2.2 Mortality-Calibrated Organ Age Models for Mortality
mortality_mortality_results <- list()
for (organ_col in organ_age_cols_mortality) {
  result <- run_mortality_cox_age(data = twins_mortality, organ_age_col = organ_col)
  mortality_mortality_results[[organ_col]] <- result
}

```
## 4.3 Healthspan Risk Analyses

Univariate Cox models for healthspan (first major disease or death).  
Model: `Surv(time_to_first_disease_or_death, event) ~ organ_age + selected_covariates` with pair-clustered robust SEs.

```{r healthspan_analyses}
### 4.3.1 Mortality-Calibrated Organ Age Models for Healthspan

healthspan_mortality_results <- list()
for (organ_col in organ_age_cols_mortality) {
  result <- run_healthspan_cox_age(data = twins_mortality, organ_age_col = organ_col)
  healthspan_mortality_results[[organ_col]] <- result
}
```

## 4.4 Data Cleaning Summary

# 5. Results Compilation and Processing

```{r results_compilation}
## 5.1 Extract Disease Results (All Diseases Including Cancer)
mortality_summary <- extract_organ_age_results(mortality_results, "Mortality")

## 5.2 Extract Mortality Results
mortality_mortality_summary <- extract_mortality_results(mortality_mortality_results, "Mortality")

## 5.3 Extract Healthspan Results
healthspan_mortality_summary <- extract_healthspan_results(healthspan_mortality_results, "Mortality")

## 5.4 Combine All Results
all_organ_age_results <- bind_rows(
  mortality_summary
) |>
  group_by(Disease) |>
  mutate(P_value_FDR = p.adjust(P_value, method = "fdr")) |>
  ungroup()

all_organ_age_results_with_mortality <- bind_rows(
  all_organ_age_results,
  mortality_mortality_summary,
  healthspan_mortality_summary
) |>
  group_by(Disease) |>
  mutate(P_value_FDR = p.adjust(P_value, method = "fdr")) |>
  ungroup() |>
  # Mark impossible organ-disease combinations instead of filtering them out
  mutate(
    impossible = case_when(
      # Female-specific cancers with prostate organ
      Disease %in% c("ovarian_cancer", "uterine_cancer", "breast_cancer") & Organ == "Prostate" ~ TRUE,
      # Prostate cancer with ovary organ
      Disease == "prostate_cancer" & Organ == "Ovary" ~ TRUE,
      TRUE ~ FALSE
    )
  )
```

# 6. Visualization: Association Heatmaps

```{r association_heatmaps}
# Control variables for heatmap appearance
HEATMAP_TEXT_SIZE <- 14
HEATMAP_SQUARE_SIZE_DIVISOR <- 12

## 6.1 Create Standardized Ordering for All Plots

# Create dynamic standardized disease ordering based on available diseases
create_standardized_disease_order <- function(available_diseases = NULL) {
  # If no diseases provided, use the global diseases object
  if (is.null(available_diseases)) {
    available_diseases <- diseases
  }
  
  # Define preferred order for common diseases (using display names)
  preferred_order <- c(
    "Mortality", "End of Healthspan",
    # Cardiovascular diseases
    "Ischemic heart disease", "Heart failure", "Atrial fibrillation", "Cerebrovascular disease",
    # Metabolic diseases  
    "Diabetes",
    # Neurological diseases
    "Dementia", "Parkinson",
    # Cancer (by incidence/importance)
    "Breast cancer", "Prostate cancer", "Lung cancer", "Colorectal cancer", 
    "Melanoma", "Bladder cancer", "Kidney cancer", "Pancreatic cancer",
    "Liver cancer", "Stomach cancer", "Esophageal cancer", "Brain cancer",
    "Lymphoma", "Leukemia", "Multiple myeloma", "Ovarian cancer", 
    "Thyroid cancer", "Uterine cancer", "Cervical cancer"
  )
  
  # Get available disease display names
  available_display_names <- c(
    "Mortality", "End of Healthspan",
    map_chr(available_diseases, ~.x$name)
  )
  
  # Apply preferred ordering to available diseases
  ordered_diseases <- intersect(preferred_order, available_display_names)
  # Add any diseases not in preferred order at the end
  missing_diseases <- setdiff(available_display_names, preferred_order)
  c(ordered_diseases, missing_diseases)
}

# Define standardized organ ordering (by biological relevance)
standardized_organ_order <- c(
  "Brain", "Cardiovascular", "Kidney and Bladder", "Liver", "Lung",
  "Muscle", "Pancreas", "Endocrine", "Adipose", "Immune", 
  "Gastrointestinal", "Nerve", "Ovary", "Prostate", "Skin", "Arterial"
)

## 6.2 Create a Lookup Vector for Disease Names (Using the Filtered Diseases List)
disease_names_lookup <- setNames(
  map_chr(diseases, ~.x$name),
  names(diseases)
)

## 6.2 Prepare Data for Grouped Heatmaps Using Diseases Config Names
heatmap_data <- all_organ_age_results_with_mortality |>
  # Use proper disease names from diseases_config (consistent with forest table approach)
  mutate(
    Disease_Display = case_when(
      Disease == "Mortality" ~ "Mortality",
      Disease == "Healthspan" ~ "End of Healthspan",
      Disease %in% names(diseases) ~ disease_names_lookup[Disease],
      TRUE ~ str_to_title(str_replace_all(Disease, "_", " "))
    ),
    # Create disease groups (explicit cancer list to catch cancers without _cancer suffix)
    disease_group = {
      cancer_keys <- c(
        "melanoma","prostate_cancer","multiple_myeloma","brain_cancer","lung_cancer",
        "breast_cancer","colorectal_cancer","kidney_cancer","bladder_cancer","esophageal_cancer",
        "stomach_cancer","liver_cancer","lymphoma","leukemia","ovarian_cancer","thyroid_cancer",
        "uterine_cancer","pancreatic_cancer","cervical_cancer"
      )
      case_when(
        Disease == "Mortality" ~ "Non-Cancer Diseases",
        Disease == "Healthspan" ~ "Non-Cancer Diseases",
        Disease %in% cancer_keys ~ "Cancer",
        Disease %in% names(diseases) ~ "Non-Cancer Diseases",
        TRUE ~ "Other"
      )
    },
    # Create significance indicators
    significance = case_when(
      impossible ~ "",  # No significance for impossible combinations
      P_value_FDR < 0.001 ~ "***",
      P_value_FDR < 0.01 ~ "**", 
      P_value_FDR < 0.05 ~ "*",
      TRUE ~ ""
    ),
    # Create effect size for coloring (use HR directly with custom range)
    effect_size = if_else(impossible, NA_real_, HR),
    # Create color value based on effect size and significance
    effect_size_colored = if_else(impossible, NA_real_, if_else(significance != "", effect_size, NA_real_)),
    non_sig_marker = if_else(impossible, "", if_else(significance == "", "×", "")),
    # Clean up organ names for display (consistent with forest table)
    Organ_Display = case_when(
      Organ == "Gastrointestinal_tract" ~ "Gastrointestinal",
      Organ == "Kidney_urinary" ~ "Kidney and Bladder",
      TRUE ~ str_to_title(Organ)
    )
  ) |>
  # Arrange by disease group and disease
  arrange(disease_group, Disease_Display, Organ)

## 6.3 Function to Create Grouped Heatmap for Specific Disease Group and Model Type
create_grouped_heatmap <- function(data, disease_group_name, model_type) {
  group_data <- data |>
    filter(disease_group == disease_group_name, Model_Type == model_type)
  
  if (nrow(group_data) == 0) {
    return(NULL)
  }
  
  # Use standardized ordering instead of clustering
  available_diseases <- unique(group_data$Disease_Display)
  available_organs <- unique(group_data$Organ_Display)
  
  # Create dynamic disease ordering based on available diseases
  disease_order <- create_standardized_disease_order(diseases)
  # Keep only diseases present in the data
  disease_order <- intersect(disease_order, available_diseases)
  
  # Apply standardized organ ordering (keep only organs present in data)
  organ_order <- intersect(standardized_organ_order, available_organs)
  # Add any organs not in standardized order at the end
  missing_organs <- setdiff(available_organs, standardized_organ_order)
  organ_order <- c(organ_order, missing_organs)
  
  # Prepare data for plotting
  group_data_clustered <- group_data |>
    mutate(
      Disease_Display = factor(Disease_Display, levels = disease_order),
      Organ_Display = factor(Organ_Display, levels = organ_order)
    )
  
  # Calculate dynamic range based on actual data
  effect_range <- range(log(group_data$HR), na.rm = TRUE)
  buffer <- 0.1
  min_limit <- min(-1.5, effect_range[1] - buffer)
  max_limit <- max(1.5, effect_range[2] + buffer)
  
  # Create dynamic breaks (5 breaks for symmetric scale)
  breaks <- seq(min_limit, max_limit, length.out = 5)
  labels <- sprintf("%.1f", breaks)
  
  # Create heatmap
  ggplot(group_data_clustered, aes(x = Organ_Display, y = Disease_Display, fill = log(effect_size_colored))) +
    geom_tile() +
    # Add grey tiles for impossible combinations
    geom_tile(data = group_data_clustered |> filter(impossible), fill = "grey80", alpha = 0.7) +
    # Add white diagonal line through impossible combinations
    geom_segment(
      data = group_data_clustered |> filter(impossible),
      aes(x = as.numeric(Organ_Display) - 0.4, y = as.numeric(Disease_Display) - 0.4,
          xend = as.numeric(Organ_Display) + 0.4, yend = as.numeric(Disease_Display) + 0.4),
      color = "white", linewidth = 1
    ) +
    geom_text(aes(label = non_sig_marker), size = 5, color = "darkgrey") +
    scale_fill_gradientn(
      colors = c(
        "#2166AC",      # Blue for negative values
        "white",        # White at zero
        "#C64D4D",      # Red (mid-high)
        "#B71C1C"       # Darker red (extreme high)
      ),
      values = scales::rescale(c(min_limit, 0, max_limit * 0.5, max_limit)),
      limits = c(min_limit, max_limit),
      na.value = "white",
      name = "log(Hazard\nRatio)",
      breaks = breaks,
      labels = labels
    ) +
    theme_minimal() +
    theme(
      plot.title = element_text(size = 16, face = "bold"),
      plot.subtitle = element_text(size = 12),
      axis.text.x = element_text(angle = 45, hjust = 1, size = 11),
      axis.text.y = element_text(size = 11, hjust = 0, margin = margin(r = 15)),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      legend.position = "right",
      legend.title = element_text(size = 10),
      legend.text = element_text(size = 8),
      legend.key.height = unit(0.8, "cm"),
      legend.key.width = unit(0.5, "cm"),
      panel.grid.minor = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.major.y = element_blank(),
      plot.margin = margin(1, 1, 1, 1, "cm")
    ) +
    coord_fixed(ratio = 1)  # Force square tiles
}

## 6.5 Create Combined Heatmap for All Diseases - Mortality Model
# Create a function to make combined heatmap similar to within-pair analysis
create_combined_heatmap <- function(data, model_type) {
  # Filter data for the model type
  model_data <- data |> filter(Model_Type == model_type)
  
  if (nrow(model_data) == 0) {
    return(NULL)
  }
  
  # Use standardized ordering
  available_diseases <- unique(model_data$Disease_Display)
  available_organs <- unique(model_data$Organ_Display)
  
  # Create dynamic disease ordering based on available diseases
  disease_order <- create_standardized_disease_order(diseases)
  # Keep only diseases present in the data
  disease_order <- intersect(disease_order, available_diseases)
  
  # Apply standardized organ ordering (keep only organs present in data)
  organ_order <- intersect(standardized_organ_order, available_organs)
  # Add any organs not in standardized order at the end
  missing_organs <- setdiff(available_organs, standardized_organ_order)
  organ_order <- c(organ_order, missing_organs)
  
  if (length(disease_order) == 0 || length(organ_order) == 0) return(NULL)
  
  # Panel-style control variables
  text_size_pt <- HEATMAP_TEXT_SIZE
  square_size <- text_size_pt / HEATMAP_SQUARE_SIZE_DIVISOR
  
  # Prepare data for plotting with numeric coordinates
  model_data_plot <- model_data |>
    mutate(
      Disease_Display = factor(Disease_Display, levels = disease_order),
      Organ_Display = factor(Organ_Display, levels = organ_order),
      Disease_num = (as.numeric(Disease_Display) - 1) * square_size + square_size/2,
      Organ_num = (as.numeric(Organ_Display) - 1) * square_size + square_size/2
    )
  
  # Calculate dynamic range based on actual data (white-to-red only, no negative values)
  effect_range <- range(log(model_data$HR), na.rm = TRUE)
  buffer <- 0.1
  max_limit <- max(1.5, effect_range[2] + buffer)
  min_limit <- 0  # Start from 0 since no negative values
  
  breaks <- seq(0, max_limit, length.out = 4)
  labels <- sprintf("%.1f", breaks)
  
  # Create combined heatmap with panel styling
  ggplot(model_data_plot, aes(x = Organ_num, y = Disease_num, fill = log(effect_size_colored))) +
    geom_tile(width = square_size, height = square_size, color = NA) +
    # Add grey tiles for impossible combinations
    geom_tile(data = model_data_plot |> filter(impossible), fill = "grey80", alpha = 0.7, width = square_size, height = square_size, color = NA) +
    # Add white diagonal line through impossible combinations
    geom_segment(
      data = model_data_plot |> filter(impossible),
      aes(x = Organ_num - square_size/2, y = Disease_num - square_size/2,
          xend = Organ_num + square_size/2, yend = Disease_num + square_size/2),
      color = "white", linewidth = 0.8
    ) +
    geom_text(aes(x = Organ_num, y = Disease_num, label = non_sig_marker), size = 5.5, color = "darkgrey", family = "Helvetica", inherit.aes = FALSE) +
    scale_fill_gradientn(
      colors = c(
        "white",        # Start at 0
        "#C64D4D",      # Red (mid-high)
        "#B71C1C"       # Darker red (extreme high)
      ),
      values = scales::rescale(c(0, max_limit * 0.5, max_limit)),
      limits = c(0, max_limit),
      na.value = "white",
      name = "log(Hazard\nRatio)",
      breaks = breaks,
      labels = labels
    ) +
    scale_x_continuous(
      breaks = (seq_along(organ_order) - 1) * square_size + square_size/2,
      labels = organ_order,
      expand = c(0, 0),
      limits = c(0, length(organ_order) * square_size)
    ) +
    scale_y_continuous(
      breaks = (seq_along(disease_order) - 1) * square_size + square_size/2,
      labels = disease_order,
      expand = c(0, 0),
      limits = c(0, length(disease_order) * square_size)
    ) +
    theme_minimal(base_family = "Helvetica") +
    theme(
      text = element_text(family = "Helvetica", color = "black"),
      axis.text.x = element_text(angle = 45, hjust = 1, size = HEATMAP_TEXT_SIZE, color = "black", family = "Helvetica"),
      axis.text.y = element_text(size = HEATMAP_TEXT_SIZE, hjust = 0, margin = margin(r = 10), color = "black", family = "Helvetica"),
      axis.title = element_blank(),
      axis.ticks = element_blank(),
      legend.position = "right",
      legend.title = element_text(size = 11, color = "black", family = "Helvetica"),
      legend.text = element_text(size = 9, color = "black", family = "Helvetica"),
      legend.key.height = unit(0.8, "cm"),
      legend.key.width = unit(0.5, "cm"),
      panel.grid = element_blank(),
      panel.spacing = unit(0, "lines"),
      panel.border = element_blank(),
      plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm")
    ) +
    coord_fixed(ratio = 1, expand = FALSE)
}

## 6.6 Create Combined Heatmap - Mortality Model
mortality_combined_heatmap <- create_combined_heatmap(heatmap_data, "Mortality")

## 6.7 Display Combined Heatmap - Mortality Model
cat("\nMortality Organ Age Model Results:\n")
if (!is.null(mortality_combined_heatmap)) {
  print(mortality_combined_heatmap)
}

## 6.8 Save the Combined Heatmap with New Framework Structure - Mortality Model
# Create directories for the new framework structure
dir.create(file.path(output_core_dir, "heatmap", "main"), showWarnings = FALSE, recursive = TRUE)

if (!is.null(mortality_combined_heatmap)) {
  ggsave(
    filename = file.path(output_core_dir, "heatmap", "main", "mortality.svg"),
    plot = mortality_combined_heatmap,
    width = 10,
    height = 8,
    dpi = 300
  )
  ggsave(
    filename = file.path(output_core_dir, "heatmap", "main", "mortality.png"),
    plot = mortality_combined_heatmap,
    width = 10,
    height = 8,
    dpi = 300
  )
}

```

```{r mortality_heatmap_significant_only}
## 6.8.1 Save a compact heatmap with only significant associations (FDR < 0.05)

# Filter to significant associations for Mortality model only
heatmap_data_sig_only <- heatmap_data |>
  dplyr::filter(Model_Type == "Mortality", significance != "", !impossible)

# Rebuild the heatmap using the same helper, but with filtered data
mortality_heatmap_sig <- create_combined_heatmap(heatmap_data_sig_only, "Mortality")

# Create output directory if needed and save
if (!is.null(mortality_heatmap_sig)) {
  dir.create(file.path(output_core_dir, "heatmap", "main"), showWarnings = FALSE, recursive = TRUE)
  ggsave(
    filename = file.path(output_core_dir, "heatmap", "main", "mortality_significant_only.svg"),
    plot = mortality_heatmap_sig,
    width = 10,
    height = 8,
    dpi = 300
  )
  ggsave(
    filename = file.path(output_core_dir, "heatmap", "main", "mortality_significant_only.png"),
    plot = mortality_heatmap_sig,
    width = 10,
    height = 8,
    dpi = 300
  )
}
```

```{r}
## 6.9 Create Summary Tables for Each Model Type
mortality_summary <- heatmap_data |>
  filter(Model_Type == "Mortality") |>
  select(Disease_Display, Organ, HR, HR_lower, HR_upper, P_value_FDR, significance) |>
  mutate(
    HR_CI = sprintf("%.2f (%.2f-%.2f)", HR, HR_lower, HR_upper),
    P_value_FDR = sprintf("%.2e", P_value_FDR),
    Significant = if_else(significance != "", "Yes", "No")
  ) |>
  select(Disease_Display, Organ, HR_CI, P_value_FDR, Significant) |>
  arrange(Disease_Display, Organ)

## 6.10 Display Summary Tables

cat("\nMortality Model Results:\n")

print(mortality_summary)
```

# 7. Visualization: Forest Tables for Main Results

Forest tables summarize hazard ratios and 95% CIs across outcomes.

```{r main_forest_helpers}
forest_count_covariates <- active_covariates

filter_complete_covariates <- function(data, covariates) {
  if (length(covariates) == 0) {
    return(data)
  }

  data |>
    dplyr::filter(dplyr::if_all(dplyr::all_of(covariates), ~ !is.na(.)))
}

calculate_main_case_counts <- function(disease_name) {
  if (disease_name == "Mortality") {
    mortality_data <- twins_analysis |>
      mutate(
        age_at_event = case_when(
          deceased == 1 & !is.na(deathdate) ~ as.numeric(deathdate - birthdate) / 365.25,
          TRUE ~ as.numeric(end_followup - birthdate) / 365.25
        ),
        time_to_event = age_at_event - age,
        event = deceased
      ) |>
      filter(time_to_event > 0)

    mortality_data <- filter_complete_covariates(mortality_data, forest_count_covariates)

    return(list(
      cases = sum(mortality_data$event, na.rm = TRUE),
      n = nrow(mortality_data),
      display_name = "Mortality"
    ))
  }

  if (disease_name == "Healthspan") {
    healthspan_data <- twins_analysis |>
      mutate(
        time_to_event = healthspan - age,
        event = healthspan_event
      ) |>
      filter(!is.na(time_to_event), time_to_event > 0)

    healthspan_data <- filter_complete_covariates(healthspan_data, forest_count_covariates)

    return(list(
      cases = sum(healthspan_data$event, na.rm = TRUE),
      n = nrow(healthspan_data),
      display_name = "End of Healthspan"
    ))
  }

  spec <- diseases[[disease_name]]
  incident_data <- create_time_to_event_age(twins_analysis, spec$var, spec$date, spec$name)$data
  incident_data <- filter_complete_covariates(incident_data, forest_count_covariates)

  list(
    cases = sum(incident_data$event, na.rm = TRUE),
    n = nrow(incident_data),
    display_name = spec$name
  )
}

create_forest_table_combined_main <- function(data, 
                                           disease_name = "Dementia",
                                           model_type = "Mortality",
                                           title = NULL,
                                           main_color = "#2166AC") {
  forest_data <- data |> 
    filter(Model_Type == model_type, Disease == disease_name) |>
    filter(!(Disease %in% c("ovarian_cancer", "uterine_cancer", "breast_cancer") & Organ == "Prostate"),
           !(Disease == "prostate_cancer" & Organ == "Ovary"))

  case_counts <- calculate_main_case_counts(disease_name)
  disease_cases <- case_counts$cases
  sample_size <- case_counts$n
  display_name <- case_counts$display_name

  if (is.null(title)) title <- paste(display_name, "(cases =", disease_cases, ", n =", sample_size, ")")

  forest_data <- forest_data |>
    mutate(
      hr = HR,
      hr_lower = HR_lower,
      hr_upper = HR_upper,
      fdr = P_value_FDR,
      significant = P_value_FDR < 0.05,
      errorbar_color = if_else(P_value_FDR < 0.05, "grey30", "gray80"),
      Organ_Display = case_when(
        Organ == "Gastrointestinal_tract" ~ "Gastrointestinal",
        Organ == "Kidney_urinary" ~ "Kidney and Bladder",
        Organ == "Artery" ~ "Arterial",
        TRUE ~ str_to_title(Organ)
      )
    ) |>
    # Order by HR magnitude (descending - highest at top)
    arrange(desc(hr)) |>
    mutate(
      y_pos = rev(row_number()),
      Organ_Display = factor(Organ_Display, levels = Organ_Display)
    )

  # Dynamic x-axis limits with sensible defaults and breathing room
  base_min <- 0.25
  base_max <- 3
  hard_min <- 0.05
  hard_max <- 10

  if (nrow(forest_data) > 0) {
    hr_min <- suppressWarnings(min(forest_data$hr_lower, na.rm = TRUE))
    hr_max <- suppressWarnings(max(forest_data$hr_upper, na.rm = TRUE))

    if (!is.finite(hr_min)) hr_min <- base_min
    if (!is.finite(hr_max)) hr_max <- base_max

    hr_min <- max(hr_min, 0.001)

    lower_margin_factor <- 0.9
    upper_margin_factor <- 1.1

    x_min <- min(base_min, hr_min * lower_margin_factor)
    x_max <- max(base_max, hr_max * upper_margin_factor)

    x_min <- max(hard_min, x_min)
    x_max <- min(hard_max, x_max)
  } else {
    x_min <- base_min
    x_max <- base_max
  }

  x_breaks <- pretty(c(x_min, x_max), n = 6)
  x_breaks <- x_breaks[x_breaks >= x_min & x_breaks <= x_max]

  # Add formatted HR column and detect if scientific notation is needed
  forest_data <- forest_data |>
    mutate(
      use_sci = pmax(abs(hr), abs(hr_lower), abs(hr_upper), na.rm = TRUE) >= 10,
      hr_formatted = if_else(
        use_sci,
        sprintf("%.1e (%.1e-%.1e)", hr, hr_lower, hr_upper),
        sprintf("%.2f (%.2f-%.2f)", hr, hr_lower, hr_upper)
      )
    )

  # Detect if we need wider table for scientific notation
  has_sci_notation <- any(forest_data$use_sci)
  table_width_ratio <- if (has_sci_notation) 3.2 else 2.5

  tab <- forest_data |>
    transmute(y_pos, `Organ age` = Organ_Display, `HR (95% CI)` = hr_formatted, `FDR` = sprintf("%.2e", fdr))

  x_pos <- tibble(col = c("Organ age", "HR (95% CI)", "FDR"), x = c(1.0, 4.0, 7.5))
  table_long <- tab |>
    pivot_longer(-y_pos, names_to = "col", values_to = "val") |>
    left_join(x_pos, by = "col")

  p_table <- ggplot(table_long, aes(x = x, y = y_pos, label = val)) +
    geom_text(hjust = c(0, 0, 1)[match(table_long$col, x_pos$col)], size = 3) +
    geom_text(data = x_pos |> mutate(y_pos = max(forest_data$y_pos) + 1), aes(x = x, y = y_pos, label = col), hjust = c(0, 0, 1), fontface = "bold", inherit.aes = FALSE, size = 3.3) +
    scale_y_continuous(breaks = NULL, labels = NULL, limits = c(0.5, max(forest_data$y_pos) + 1.5)) +
    scale_x_continuous(limits = c(0.5, 9.0), expand = c(0, 0)) +
    labs(title = title) +
    theme_minimal(base_size = 11) +
    theme(plot.title = element_text(hjust = 0.1, size = 12), axis.title = element_blank(), axis.text.x = element_blank(), axis.ticks = element_blank(), panel.grid = element_blank(), plot.margin = unit(c(12, 6, 6, 6), "pt"))

  # Determine which points are out of bounds (based on HR only) and cap CIs to plot range
  forest_data <- forest_data |>
    mutate(
      out_of_bounds_point = hr < x_min | hr > x_max,
      hr_lower_capped = pmax(hr_lower, x_min),
      hr_upper_capped = pmin(hr_upper, x_max),
      has_any_value_outside = (hr < x_min | hr > x_max | hr_lower < x_min | hr_upper > x_max)
    )

  # Only plot data where the HR itself is within bounds
  data_in_bounds <- forest_data |> filter(!out_of_bounds_point)

  # Calculate legend positions (slightly separated)
  legend_y <- max(forest_data$y_pos) + 1.5
  legend_left_x <- x_min + (x_max - x_min) * 0.03
  legend_right_x <- x_min + (x_max - x_min) * 0.60
  legend_bottom_y <- 0.25
  legend_bottom_x <- x_min + (x_max - x_min) * 0.60

  p_forest <- ggplot(forest_data, aes(y = y_pos)) +
    geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = y_pos - 0.5, ymax = y_pos + 0.5, fill = factor(seq_along(Organ) %% 2)), alpha = 0.6, show.legend = FALSE) +
    scale_fill_manual(values = c("0" = "transparent", "1" = "gray95")) +
    geom_segment(aes(x = 1, xend = 1, y = 0.5, yend = max(forest_data$y_pos) + 0.75), linetype = "33", color = "grey10", size = 0.7) +
    {if (nrow(data_in_bounds) > 0) geom_errorbarh(data = data_in_bounds, aes(xmin = hr_lower_capped, xmax = hr_upper_capped), color = data_in_bounds$errorbar_color, height = 0.15, size = 0.6)} +
    {if (nrow(data_in_bounds) > 0) geom_point(data = data_in_bounds, aes(x = hr, color = significant), size = 2.5, shape = 16)} +
    {if (nrow(data_in_bounds |> filter(has_any_value_outside)) > 0) geom_text(data = data_in_bounds |> filter(has_any_value_outside), aes(x = hr, y = y_pos + 0.25), label = "*", size = 3.5, color = "black")} +
    annotate("text", x = legend_left_x, y = legend_y, label = "● Significant (FDR < 0.05)", hjust = 0, size = 2.6, color = main_color) +
    annotate("text", x = legend_right_x, y = legend_y, label = "● Non-significant", hjust = 0, size = 2.6, color = "gray80") +
    {if (nrow(data_in_bounds |> filter(has_any_value_outside)) > 0) annotate("text", x = legend_bottom_x, y = legend_bottom_y, label = "* Value outside plot range", hjust = 1, size = 2.4, color = "black")} +
    scale_color_manual(values = c("TRUE" = main_color, "FALSE" = "gray80")) +
    scale_x_continuous(
      limits = c(x_min, x_max),
      breaks = x_breaks,
      labels = format(x_breaks, digits = 3, trim = TRUE)
    ) +
    scale_y_continuous(breaks = NULL, labels = NULL, limits = c(0.2, max(forest_data$y_pos) + 1.5)) +
    labs(x = "Hazard Ratio (95% CI)", y = NULL) +
    theme_minimal(base_size = 11) +
    theme(axis.text.y = element_blank(), axis.text.x = element_text(size = 9), axis.title.x = element_text(size = 10), panel.grid.major.y = element_blank(), panel.grid.minor = element_blank(), panel.grid.major.x = element_blank(), plot.margin = unit(c(12, 12, 6, 0), "pt"), legend.position = "none") +
    coord_cartesian(clip = "off")

  p_table + p_forest + plot_layout(widths = c(table_width_ratio, 1.5))
}
```

```{r main_forest_plots}
disease_names <- names(diseases)


# Create directories for the new framework structure
dir.create(file.path(output_core_dir, "forest_table"), showWarnings = FALSE, recursive = TRUE)

# Create only black and white forest tables
main_all_disease_plots_bw <- list()
for (disease_name in disease_names) {
  disease_data <- all_organ_age_results_with_mortality |> filter(Model_Type == "Mortality", Disease == disease_name)
  if (nrow(disease_data) == 0) next
  plot <- create_forest_table_combined_main(all_organ_age_results_with_mortality, disease_name = disease_name, model_type = "Mortality", main_color = "black")
  main_all_disease_plots_bw[[diseases[[disease_name]]$name]] <- plot
}

for (disease_display in names(main_all_disease_plots_bw)) {
  filename <- paste0(tolower(str_replace_all(disease_display, " ", "_")), ".svg")
  ggsave(filename = filename, plot = main_all_disease_plots_bw[[disease_display]], path = file.path(output_core_dir, "forest_table"), device = "svg", width = 7, height = 5, dpi = 300)
}

main_mortality_plot_bw <- create_forest_table_combined_main(all_organ_age_results_with_mortality, disease_name = "Mortality", model_type = "Mortality", main_color = "black")
ggsave(filename = "mortality.svg", plot = main_mortality_plot_bw, path = file.path(output_core_dir, "forest_table"), device = "svg", width = 7, height = 5, dpi = 300)

main_healthspan_plot_bw <- create_forest_table_combined_main(all_organ_age_results_with_mortality, disease_name = "Healthspan", model_type = "Mortality", main_color = "black")
ggsave(filename = "healthspan.svg", plot = main_healthspan_plot_bw, path = file.path(output_core_dir, "forest_table"), device = "svg", width = 7, height = 5, dpi = 300)

# Create tables directory for main Cox results
dir.create(file.path(output_core_dir, "tables", "main"), showWarnings = FALSE, recursive = TRUE)

# Save table data as CSV - Individual diseases
for (disease_name in disease_names) {
  disease_data <- all_organ_age_results_with_mortality |> filter(Model_Type == "Mortality", Disease == disease_name)
  if (nrow(disease_data) == 0) next
  
  # Create table data
  tab <- disease_data |>
    mutate(
      use_sci = pmax(abs(HR), abs(HR_lower), abs(HR_upper), na.rm = TRUE) >= 10,
      hr_formatted = if_else(use_sci,
        sprintf("%.1e (%.1e-%.1e)", HR, HR_lower, HR_upper),
        sprintf("%.2f (%.2f-%.2f)", HR, HR_lower, HR_upper)),
      Organ_Display = case_when(
        Organ == "Gastrointestinal_tract" ~ "Gastrointestinal",
        Organ == "Kidney_urinary" ~ "Kidney and Bladder",
        Organ == "Artery" ~ "Arterial",
        TRUE ~ str_to_title(Organ)
      )
    ) |>
    select(Organ = Organ_Display, `HR (95% CI)` = hr_formatted, FDR = P_value_FDR)
  
  # Save CSV
  display_name <- diseases[[disease_name]]$name
  filename <- paste0(tolower(str_replace_all(display_name, " ", "_")), ".csv")
  write.csv(tab, file = file.path(output_core_dir, "tables", "main", filename), row.names = FALSE)
}

# Save table data as CSV - Mortality
mortality_data <- all_organ_age_results_with_mortality |> filter(Model_Type == "Mortality", Disease == "Mortality")
if (nrow(mortality_data) > 0) {
  tab <- mortality_data |>
    mutate(
      use_sci = pmax(abs(HR), abs(HR_lower), abs(HR_upper), na.rm = TRUE) >= 10,
      hr_formatted = if_else(use_sci,
        sprintf("%.1e (%.1e-%.1e)", HR, HR_lower, HR_upper),
        sprintf("%.2f (%.2f-%.2f)", HR, HR_lower, HR_upper)),
      Organ_Display = case_when(
        Organ == "Gastrointestinal_tract" ~ "Gastrointestinal",
        Organ == "Kidney_urinary" ~ "Kidney and Bladder",
        Organ == "Artery" ~ "Arterial",
        TRUE ~ str_to_title(Organ)
      )
    ) |>
    select(Organ = Organ_Display, `HR (95% CI)` = hr_formatted, FDR = P_value_FDR)
  
  write.csv(tab, file = file.path(output_core_dir, "tables", "main", "mortality.csv"), row.names = FALSE)
}

# Save table data as CSV - Healthspan
healthspan_data <- all_organ_age_results_with_mortality |> filter(Model_Type == "Mortality", Disease == "Healthspan")
if (nrow(healthspan_data) > 0) {
  tab <- healthspan_data |>
    mutate(
      use_sci = pmax(abs(HR), abs(HR_lower), abs(HR_upper), na.rm = TRUE) >= 10,
      hr_formatted = if_else(use_sci,
        sprintf("%.1e (%.1e-%.1e)", HR, HR_lower, HR_upper),
        sprintf("%.2f (%.2f-%.2f)", HR, HR_lower, HR_upper)),
      Organ_Display = case_when(
        Organ == "Gastrointestinal_tract" ~ "Gastrointestinal",
        Organ == "Kidney_urinary" ~ "Kidney and Bladder",
        Organ == "Artery" ~ "Arterial",
        TRUE ~ str_to_title(Organ)
      )
    ) |>
    select(Organ = Organ_Display, `HR (95% CI)` = hr_formatted, FDR = P_value_FDR)
  
  write.csv(tab, file = file.path(output_core_dir, "tables", "main", "healthspan.csv"), row.names = FALSE)
}
```

# 12. Forest Plot with Table for Mortality Results

```{r forest_plot_mortality}
## 12.1 Function to Create Forest Plot for a Single Disease Across All Organs
create_forest_table_combined <- function(data, 
                                        disease_name = "Dementia",
                                        model_type = "Mortality",
                                        title = NULL,
                                        main_color = "#2166AC") {
  
  # Filter and prepare data for single disease analysis
  forest_data <- data |>
    filter(Model_Type == model_type, Disease == disease_name) |>
    filter(!(Disease %in% c("ovarian_cancer", "uterine_cancer", "breast_cancer") & Organ == "Prostate"),
           !(Disease == "prostate_cancer" & Organ == "Ovary"))
  
  case_counts <- calculate_main_case_counts(disease_name)
  disease_cases <- case_counts$cases
  sample_size <- case_counts$n
  display_name <- case_counts$display_name
  
  # Create default title if none provided
  if (is.null(title)) {
    title <- paste(display_name, "(cases =", disease_cases, ", n =", sample_size, ")")
  }
  
  forest_data <- forest_data |>
    mutate(
      hr = HR,
      hr_lower = HR_lower,
      hr_upper = HR_upper,
      fdr = P_value_FDR,
      significant = P_value_FDR < 0.05,
      errorbar_color = if_else(P_value_FDR < 0.05, "grey30", "gray80"),
      # Clean up organ names for display
      Organ_Display = case_when(
        Organ == "Gastrointestinal_tract" ~ "Gastrointestinal",
        Organ == "Kidney_urinary" ~ "Kidney and Bladder",
        Organ == "Artery" ~ "Arterial",
        TRUE ~ str_to_title(Organ)
      )
    ) |>
    # Order by HR magnitude (descending - highest at top)
    arrange(desc(hr)) |>
    mutate(
      y_pos = rev(row_number()),
      Organ_Display = factor(Organ_Display, levels = Organ_Display)
    )
  
  # Dynamic x-axis limits with sensible defaults and breathing room
  base_min <- 0.25
  base_max <- 3
  hard_min <- 0.05
  hard_max <- 10

  if (nrow(forest_data) > 0) {
    hr_min <- suppressWarnings(min(forest_data$hr_lower, na.rm = TRUE))
    hr_max <- suppressWarnings(max(forest_data$hr_upper, na.rm = TRUE))

    if (!is.finite(hr_min)) hr_min <- base_min
    if (!is.finite(hr_max)) hr_max <- base_max

    hr_min <- max(hr_min, 0.001)

    lower_margin_factor <- 0.9
    upper_margin_factor <- 1.1

    x_min <- min(base_min, hr_min * lower_margin_factor)
    x_max <- max(base_max, hr_max * upper_margin_factor)

    x_min <- max(hard_min, x_min)
    x_max <- min(hard_max, x_max)
  } else {
    x_min <- base_min
    x_max <- base_max
  }

  x_breaks <- pretty(c(x_min, x_max), n = 6)
  x_breaks <- x_breaks[x_breaks >= x_min & x_breaks <= x_max]

  # Add formatted HR column and detect if scientific notation is needed
  forest_data <- forest_data |>
    mutate(
      use_sci = pmax(abs(hr), abs(hr_lower), abs(hr_upper), na.rm = TRUE) >= 10,
      hr_formatted = if_else(
        use_sci,
        sprintf("%.1e (%.1e-%.1e)", hr, hr_lower, hr_upper),
        sprintf("%.2f (%.2f-%.2f)", hr, hr_lower, hr_upper)
      )
    )

  # Detect if we need wider table for scientific notation
  has_sci_notation <- any(forest_data$use_sci)
  table_width_ratio <- if (has_sci_notation) 3.2 else 2.5
  
  # Create table data
  tab <- forest_data |>
    transmute(
      y_pos,
      `Organ age` = Organ_Display,
      `HR (95% CI)` = hr_formatted,
      `FDR` = sprintf("%.2e", fdr)
    )
  
  # Define table column positions
  x_pos <- tibble(
    col = c("Organ age", "HR (95% CI)", "FDR"),
    x   = c(1.0, 4.0, 7.5)
  )
  
  # Convert table to long format for plotting
  table_long <- tab |>
    select(y_pos, `Organ age`, `HR (95% CI)`, `FDR`) |>
    pivot_longer(-y_pos, names_to = "col", values_to = "val") |>
    left_join(x_pos, by = "col")
  
  # Create table plot
  p_table <- ggplot(table_long, aes(x = x, y = y_pos, label = val)) +
    geom_text(hjust = c(0, 0, 1)[match(table_long$col, x_pos$col)], size = 3) +
    geom_text(data = x_pos |> mutate(y_pos = max(forest_data$y_pos) + 1),
              aes(x = x, y = y_pos, label = col),
              hjust = c(0, 0, 1), fontface = "bold", inherit.aes = FALSE, size = 3.3) +
    scale_y_continuous(breaks = NULL, labels = NULL,
                       limits = c(0.5, max(forest_data$y_pos) + 1.5)) +
    scale_x_continuous(limits = c(0.5, 9.0), expand = c(0,0)) +
    labs(title = title) +
    theme_minimal(base_size = 11, base_family = "Helvetica") +
    theme(
      plot.title = element_text(hjust = 0.1, size = 12, family = "Helvetica"),
      axis.title = element_blank(),
      axis.text.x = element_blank(),
      axis.ticks = element_blank(),
      panel.grid = element_blank(),
      plot.margin = unit(c(12, 6, 6, 6), "pt"),
      panel.background = element_rect(fill = "white", colour = NA)
    )

  # Determine which points are out of bounds (based on HR only) and cap CIs to plot range
  forest_data <- forest_data |>
    mutate(
      out_of_bounds_point = hr < x_min | hr > x_max,
      hr_lower_capped = pmax(hr_lower, x_min),
      hr_upper_capped = pmin(hr_upper, x_max),
      has_any_value_outside = (hr < x_min | hr > x_max | hr_lower < x_min | hr_upper > x_max)
    )

  # Only plot data where the HR itself is within bounds
  data_in_bounds <- forest_data |> filter(!out_of_bounds_point)

  # Calculate legend positions (slightly separated)
  legend_y <- max(forest_data$y_pos) + 1.5
  legend_left_x <- x_min + (x_max - x_min) * 0.03
  legend_right_x <- x_min + (x_max - x_min) * 0.60
  legend_bottom_y <- 0.25
  legend_bottom_x <- x_min + (x_max - x_min) * 0.60

  p_forest <- ggplot(forest_data, aes(y = y_pos)) +
    # Add alternating row background colors
    geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = y_pos - 0.5, ymax = y_pos + 0.5, 
                  fill = factor(seq_along(Organ) %% 2)), 
              alpha = 0.6, show.legend = FALSE) +
    scale_fill_manual(values = c("0" = "transparent", "1" = "gray95")) +
    
    # Add reference line at HR = 1
    geom_segment(aes(x = 1, xend = 1, y = 0.5, yend = max(forest_data$y_pos) + 0.75), 
                 linetype = "33", color = "grey10", size = 0.7) +
    # Add confidence intervals and point estimates
    {if (nrow(data_in_bounds) > 0) geom_errorbarh(data = data_in_bounds, aes(xmin = hr_lower_capped, xmax = hr_upper_capped), color = data_in_bounds$errorbar_color, height = 0.15, size = 0.6)} +
    {if (nrow(data_in_bounds) > 0) geom_point(data = data_in_bounds, aes(x = hr, color = significant), size = 2.5, shape = 16)} +
    {if (nrow(data_in_bounds |> filter(has_any_value_outside)) > 0) geom_text(data = data_in_bounds |> filter(has_any_value_outside), aes(x = hr, y = y_pos + 0.25), label = "*", size = 3.5, color = "black")} +
    
    # Add legend annotations
    annotate("text", x = legend_left_x, y = legend_y, 
             label = "● Significant (FDR < 0.05)", hjust = 0, size = 2.6, color = main_color) +
    annotate("text", x = legend_right_x, y = legend_y, 
             label = "● Non-significant", hjust = 0, size = 2.6, color = "gray80") +
    {if (nrow(data_in_bounds |> filter(has_any_value_outside)) > 0) annotate("text", x = legend_bottom_x, y = legend_bottom_y, label = "* Value outside plot range", hjust = 1, size = 2.4, color = "black")} +
    
    scale_color_manual(values = c("TRUE" = main_color, "FALSE" = "gray80")) +
    scale_x_continuous(
      limits = c(x_min, x_max),
      breaks = x_breaks,
      labels = format(x_breaks, digits = 3, trim = TRUE)
    ) +
    scale_y_continuous(breaks = NULL, labels = NULL,
                       limits = c(0.2, max(forest_data$y_pos) + 1.5)) +
    labs(x = "Hazard Ratio (95% CI)", y = NULL) +
    theme_minimal(base_size = 11, base_family = "Helvetica") +
    theme(
      axis.text.y = element_blank(),
      axis.text.x = element_text(size = 9, family = "Helvetica"),
      axis.title.x = element_text(size = 10, family = "Helvetica"),
      panel.grid.major.y = element_blank(),
      panel.grid.minor = element_blank(),
      panel.grid.major.x = element_blank(),
      plot.margin = unit(c(12, 12, 6, 0), "pt"),
      legend.position = "none"
    ) +
    coord_cartesian(clip = "off")
  
  # Combine table and forest plot
  p_table + p_forest + plot_layout(widths = c(table_width_ratio, 1.5))
}
```

```{r loop_all_diseases_forest_plots}
## 12.2 Loop Through All Diseases to Create Forest Plots for Mortality Model
disease_names <- names(diseases)
all_disease_plots <- list()

for (i in seq_along(disease_names)) {
  disease_name <- disease_names[i]
  disease_display_name <- diseases[[disease_name]]$name
  
  # Check if data exists for this disease
  disease_data <- all_organ_age_results_with_mortality |>
    filter(Model_Type == "Mortality", Disease == disease_name)
  
  if (nrow(disease_data) == 0) {
    next
  }
  
  # Create the forest plot
  plot <- create_forest_table_combined(
    data = all_organ_age_results_with_mortality,
    disease_name = disease_name,
    model_type = "Mortality",
    main_color = "black"
  )
  
  # Store and display the plot
  all_disease_plots[[disease_display_name]] <- plot
  print(plot)
}

```


## 14.9 Within-pair Cox using all pairs

```{r withinpair_allpairs_dataset}
# Build per-disease, all-pairs dataset (incident-only), allowing 0/1/2 events per pair
create_withinpair_allpairs_dataset <- function(spec, mz_only = FALSE, dz_only = FALSE) {
  # Validate disease label
  if (is.null(spec$name) || length(spec$name) == 0 || spec$name == "") {
    stop("spec$name is empty or null")
  }
  
  df <- create_time_to_event_age(twins_analysis, spec$var, spec$date, spec$name)$data |>
    dplyr::group_by(pair_id) |>
    dplyr::filter(dplyr::n() == 2) |>
    dplyr::ungroup()
  if (mz_only) df <- df |> dplyr::filter(bestzyg == 1)
  if (dz_only) df <- df |> dplyr::filter(bestzyg == 2)
  df |> dplyr::group_by(pair_id) |> dplyr::filter(sum(event, na.rm = TRUE) >= 1) |> dplyr::ungroup()
}
```

```{r withinpair_allpairs_univariate}
library(survival)

fit_withinpair_uni <- function(df, organ_col, disease_key, label) {
  f <- as.formula(paste0("Surv(time_to_event, event) ~ ", covariate_formula_terms, " + scale(`", organ_col, "`) + strata(pair_id)"))
  fit <- coxph(f, data = df)
  s <- summary(fit)
  
  # Find the organ age coefficient (last coefficient before strata)
  n_coefs <- length(stats::coef(fit))
  organ_coef_idx <- n_coefs  # Last coefficient is the organ age
  
  tibble::tibble(
    Disease = disease_key,
    Organ = organ_col,
    HR = exp(stats::coef(fit)[organ_coef_idx]),
    HR_lower = exp(stats::confint(fit)[organ_coef_idx, 1]),
    HR_upper = exp(stats::confint(fit)[organ_coef_idx, 2]),
    P_value = s$coefficients[organ_coef_idx, "Pr(>|z|)"],
    Model_Type = label
  )
}

run_withinpair_univariate <- function(disease_list, organ_cols, label, mz_only = FALSE, dz_only = FALSE) {
  if (length(disease_list) == 0) return(tibble::tibble())
  out <- list()
  for (disease_key in names(disease_list)) {
    spec <- disease_list[[disease_key]]
    
    # Healthspan uses numeric age, not a date column
    if (disease_key == "healthspan") {
      # Create healthspan dataset similar to run_healthspan_cox_age
      df <- twins_analysis |>
        dplyr::mutate(
          time_to_event = healthspan - age,
          event = healthspan_event
        ) |>
        dplyr::filter(!is.na(time_to_event), time_to_event > 0) |>
        dplyr::group_by(pair_id) |>
        dplyr::filter(dplyr::n() == 2) |>
        dplyr::ungroup()
      
      if (mz_only) df <- df |> dplyr::filter(bestzyg == 1)
      if (dz_only) df <- df |> dplyr::filter(bestzyg == 2)
      df <- df |> dplyr::group_by(pair_id) |> dplyr::filter(sum(event, na.rm = TRUE) >= 1) |> dplyr::ungroup()
    } else {
      # Standard handling for other diseases
      df <- create_withinpair_allpairs_dataset(spec, mz_only = mz_only, dz_only = dz_only)
    }
    
    df <- df |>
      dplyr::left_join(dplyr::select(organ_age_mortality, twin_id, dplyr::all_of(organ_cols)), by = "twin_id")
    
    if (nrow(df) == 0 || dplyr::n_distinct(df$pair_id) < 2) next
    for (oc in organ_cols) {
      # Skip impossible organ-disease combinations
      # Female-specific diseases: skip Prostate organ
      if (grepl("breast|ovarian|uterine|cervical", spec$name, ignore.case = TRUE) && oc == "Prostate") {
        next
      }
      # Prostate cancer: skip Ovary organ
      if (grepl("prostate", spec$name, ignore.case = TRUE) && oc == "Ovary") {
        next
      }
      
      if (!oc %in% names(df)) next
      if (all(is.na(df[[oc]]))) next
      res <- try(fit_withinpair_uni(df, oc, disease_key, label), silent = TRUE)
      if (!inherits(res, "try-error")) out[[length(out) + 1]] <- res
    }
  }
  if (length(out) == 0) return(tibble::tibble())
  dplyr::bind_rows(out) |>
    dplyr::group_by(Disease) |>
    dplyr::mutate(P_value_FDR = p.adjust(P_value, method = "fdr")) |>
    dplyr::ungroup()
}

# Create extended disease list that includes mortality and healthspan for within-pair analysis
diseases_with_mortality_healthspan <- c(
  diseases,
  list(
    mortality = list(var = "deceased", date = "deathdate", name = "Mortality"),
    healthspan = list(var = "healthspan_event", date = "healthspan", name = "End of Healthspan")
  )
)

# Debug: Check for empty names in diseases_with_mortality_healthspan
cat("Checking diseases_with_mortality_healthspan:\n")
for (i in seq_along(diseases_with_mortality_healthspan)) {
  disease_name <- names(diseases_with_mortality_healthspan)[i]
  spec <- diseases_with_mortality_healthspan[[i]]
  cat("Disease:", disease_name, "Name:", spec$name, "Var:", spec$var, "Date:", spec$date, "\n")
}

# Run: all pairs, MZ-only, DZ-only (mortality-calibrated organ ages)
wp_uni_all <- run_withinpair_univariate(diseases_with_mortality_healthspan, organ_age_cols_mortality, "WithinPair_All")
wp_uni_mz  <- run_withinpair_univariate(diseases_with_mortality_healthspan, organ_age_cols_mortality, "WithinPair_MZ", mz_only = TRUE)
wp_uni_dz  <- run_withinpair_univariate(diseases_with_mortality_healthspan, organ_age_cols_mortality, "WithinPair_DZ", dz_only = TRUE)
```

## 14.10 Within-pair univariate heatmaps (All/MZ/DZ)

## 14.11 Forest Tables for Within-Pair Univariate Results

```{r withinpair_uni_forest_helpers}

# Function to calculate within-pair specific case counts
calculate_withinpair_case_counts <- function(disease_name, model_type) {
  # Determine zygosity filter based on model type
  zygosity_filter <- case_when(
    str_detect(model_type, "MZ") ~ 1,
    str_detect(model_type, "DZ") ~ 2,
    TRUE ~ NA_real_
  )
  
  # Determine sex filter based on model type
  sex_filter <- case_when(
    str_detect(model_type, "Male") ~ 1,
    str_detect(model_type, "Female") ~ 2,
    TRUE ~ NA_real_
  )
  
  # Get disease specification (support keys like "mortality"/"healthspan")
  if (exists("diseases_with_mortality_healthspan")) {
    # Prefer unified lookup including mortality/healthspan if available
    if (disease_name %in% names(diseases_with_mortality_healthspan)) {
      spec <- diseases_with_mortality_healthspan[[disease_name]]
    } else if (tolower(disease_name) %in% names(diseases_with_mortality_healthspan)) {
      spec <- diseases_with_mortality_healthspan[[tolower(disease_name)]]
    } else if (disease_name %in% names(diseases)) {
      spec <- diseases[[disease_name]]
    } else {
      spec <- NULL
    }
  } else {
    # Fallback to previous behaviour
    if (disease_name == "Mortality" || tolower(disease_name) == "mortality") {
      spec <- list(var = "deceased", date = "deathdate", name = "Mortality")
    } else if (disease_name == "Healthspan" || tolower(disease_name) == "healthspan") {
      spec <- list(var = "healthspan_event", date = "healthspan", name = "End of Healthspan")
    } else {
      spec <- diseases[[disease_name]]
    }
  }

  if (is.null(spec)) {
    return(list(cases = 0, pairs = 0, display_name = as.character(disease_name)))
  }
  
  # Create the within-pair dataset with appropriate filters
  # Healthspan uses numeric age, not a date column
  if (!is.null(spec$var) && spec$var == "healthspan_event") {
    # Create healthspan dataset similar to run_withinpair_univariate
    wp_data <- twins_analysis |>
      dplyr::mutate(
        time_to_event = healthspan - age,
        event = healthspan_event
      ) |>
      dplyr::filter(!is.na(time_to_event), time_to_event > 0) |>
      dplyr::group_by(pair_id) |>
      dplyr::filter(dplyr::n() == 2) |>
      dplyr::ungroup()
    
    # Apply zygosity filters
    if (!is.na(zygosity_filter)) {
      if (zygosity_filter == 1) {
        wp_data <- wp_data |> dplyr::filter(bestzyg == 1)  # MZ only
      } else {
        wp_data <- wp_data |> dplyr::filter(bestzyg == 2)  # DZ only
      }
    }
    
    # Apply sex filters
    if (!is.na(sex_filter)) {
      wp_data <- wp_data |> dplyr::filter(sex == sex_filter)
    }
    
    # Filter to pairs with at least one event
    wp_data <- wp_data |> 
      dplyr::group_by(pair_id) |> 
      dplyr::filter(sum(event, na.rm = TRUE) >= 1) |> 
      dplyr::ungroup()
    
  } else if (!is.null(spec$var) && spec$var == "deceased") {
    # Mortality model branch
    wp_data <- twins_analysis |>
      dplyr::mutate(
        age_at_event = dplyr::case_when(
          deceased == 1 & !is.na(deathdate) ~ as.numeric(deathdate - birthdate) / 365.25,
          TRUE ~ as.numeric(end_followup - birthdate) / 365.25
        ),
        time_to_event = age_at_event - age,
        event = deceased
      ) |>
      dplyr::filter(time_to_event > 0) |>
      dplyr::group_by(pair_id) |>
      dplyr::filter(dplyr::n() == 2) |>
      dplyr::ungroup()
    
    # Apply zygosity filters
    if (!is.na(zygosity_filter)) {
      if (zygosity_filter == 1) {
        wp_data <- wp_data |> dplyr::filter(bestzyg == 1)  # MZ only
      } else {
        wp_data <- wp_data |> dplyr::filter(bestzyg == 2)  # DZ only
      }
    }
    
    # Apply sex filters
    if (!is.na(sex_filter)) {
      wp_data <- wp_data |> dplyr::filter(sex == sex_filter)
    }
    
    # Filter to pairs with at least one event
    wp_data <- wp_data |> 
      dplyr::group_by(pair_id) |> 
      dplyr::filter(sum(event, na.rm = TRUE) >= 1) |> 
      dplyr::ungroup()
    
  } else {
    # Standard disease handling - use create_withinpair_allpairs_dataset
    # Apply zygosity first
    mz_flag <- (!is.na(zygosity_filter) && zygosity_filter == 1)
    dz_flag <- (!is.na(zygosity_filter) && zygosity_filter == 2)
    
    wp_data <- create_withinpair_allpairs_dataset(spec, mz_only = mz_flag, dz_only = dz_flag)
    
    # Apply sex filter if needed
    if (!is.na(sex_filter)) {
      wp_data <- wp_data |> dplyr::filter(sex == sex_filter)
    }
  }
  
  wp_data <- filter_complete_covariates(wp_data, forest_count_covariates) |>
    dplyr::group_by(pair_id) |>
    dplyr::filter(dplyr::n() == 2, sum(event, na.rm = TRUE) >= 1) |>
    dplyr::ungroup()

  if (nrow(wp_data) == 0) {
    return(list(cases = 0, pairs = 0, display_name = spec$name))
  }
  
  # Count cases and pairs
  cases <- sum(wp_data$event, na.rm = TRUE)
  pairs <- n_distinct(wp_data$pair_id)
  
  return(list(cases = cases, pairs = pairs, display_name = spec$name))
}

create_forest_table_combined_wp_uni <- function(data, disease_name = "Dementia", model_type = "WithinPair_All", title = NULL, main_color = "#2166AC") {
  forest_data <- data |>
    filter(Model_Type == model_type, Disease == disease_name) |>
    filter(!(Disease %in% c("ovarian_cancer", "uterine_cancer", "breast_cancer") & Organ == "Prostate"),
           !(Disease == "prostate_cancer" & Organ == "Ovary"))

  # Use within-pair specific case counting
  case_counts <- calculate_withinpair_case_counts(disease_name, model_type)
  disease_cases <- case_counts$cases
  sample_size <- case_counts$pairs
  display_name <- case_counts$display_name

  if (is.null(title)) title <- paste(display_name, "(cases =", disease_cases, ", pairs =", sample_size, ")")

  forest_data <- forest_data |>
    mutate(
      hr = HR,
      hr_lower = HR_lower,
      hr_upper = HR_upper,
      p_value = P_value_FDR,
      significant = P_value_FDR < 0.05,
      errorbar_color = if_else(P_value_FDR < 0.05, "grey30", "gray80"),
      Organ_Display = case_when(
        Organ == "Gastrointestinal_tract" ~ "Gastrointestinal",
        Organ == "Kidney_urinary" ~ "Kidney and Bladder",
        Organ == "Artery" ~ "Arterial",
        TRUE ~ str_to_title(Organ)
      )
    ) |>
    # Order by HR magnitude (descending - highest at top)
    arrange(desc(hr)) |>
    mutate(
      y_pos = rev(row_number()),
      Organ_Display = factor(Organ_Display, levels = Organ_Display)
    )

  # Dynamic x-axis limits with sensible defaults and breathing room
  base_min <- 0.25
  base_max <- 3
  hard_min <- 0.05
  hard_max <- 10

  if (nrow(forest_data) > 0) {
    hr_min <- suppressWarnings(min(forest_data$hr_lower, na.rm = TRUE))
    hr_max <- suppressWarnings(max(forest_data$hr_upper, na.rm = TRUE))

    if (!is.finite(hr_min)) hr_min <- base_min
    if (!is.finite(hr_max)) hr_max <- base_max

    hr_min <- max(hr_min, 0.001)

    lower_margin_factor <- 0.9
    upper_margin_factor <- 1.1

    x_min <- min(base_min, hr_min * lower_margin_factor)
    x_max <- max(base_max, hr_max * upper_margin_factor)

    x_min <- max(hard_min, x_min)
    x_max <- min(hard_max, x_max)
  } else {
    x_min <- base_min
    x_max <- base_max
  }

  x_breaks <- pretty(c(x_min, x_max), n = 6)
  x_breaks <- x_breaks[x_breaks >= x_min & x_breaks <= x_max]

  # Add formatted HR column and detect if scientific notation is needed
  forest_data <- forest_data |>
    mutate(
      use_sci = pmax(abs(hr), abs(hr_lower), abs(hr_upper), na.rm = TRUE) >= 10,
      hr_formatted = if_else(
        use_sci,
        sprintf("%.1e (%.1e-%.1e)", hr, hr_lower, hr_upper),
        sprintf("%.2f (%.2f-%.2f)", hr, hr_lower, hr_upper)
      )
    )

  # Detect if we need wider table for scientific notation
  has_sci_notation <- any(forest_data$use_sci)
  table_width_ratio <- if (has_sci_notation) 3.2 else 2.5

  tab <- forest_data |>
    transmute(y_pos, `Organ age` = Organ_Display, `HR (95% CI)` = hr_formatted, `FDR` = sprintf("%.2e", p_value))

  x_pos <- tibble(col = c("Organ age", "HR (95% CI)", "FDR"), x = c(1.0, 4.0, 7.5))
  table_long <- tab |>
    pivot_longer(-y_pos, names_to = "col", values_to = "val") |>
    left_join(x_pos, by = "col")

  p_table <- ggplot(table_long, aes(x = x, y = y_pos, label = val)) +
    geom_text(hjust = c(0, 0, 1)[match(table_long$col, x_pos$col)], size = 3) +
    geom_text(data = x_pos |> mutate(y_pos = max(forest_data$y_pos) + 1), aes(x = x, y = y_pos, label = col), hjust = c(0, 0, 1), fontface = "bold", inherit.aes = FALSE, size = 3.3) +
    scale_y_continuous(breaks = NULL, labels = NULL, limits = c(0.5, max(forest_data$y_pos) + 1.5)) +
    scale_x_continuous(limits = c(0.5, 9.0), expand = c(0, 0)) +
    labs(title = title) +
    theme_minimal(base_size = 11) +
    theme(plot.title = element_text(hjust = 0.1, size = 12), axis.title = element_blank(), axis.text.x = element_blank(), axis.ticks = element_blank(), panel.grid = element_blank(), plot.margin = unit(c(12, 6, 6, 6), "pt"))

  # Determine which points are out of bounds (based on HR only) and cap CIs to plot range
  forest_data <- forest_data |>
    mutate(
      out_of_bounds_point = hr < x_min | hr > x_max,
      hr_lower_capped = pmax(hr_lower, x_min),
      hr_upper_capped = pmin(hr_upper, x_max),
      has_any_value_outside = (hr < x_min | hr > x_max | hr_lower < x_min | hr_upper > x_max)
    )

  # Only plot data where the HR itself is within bounds
  data_in_bounds <- forest_data |> filter(!out_of_bounds_point)

  # Calculate legend positions (slightly separated)
  legend_y <- max(forest_data$y_pos) + 1.5
  legend_left_x <- x_min + (x_max - x_min) * 0.03
  legend_right_x <- x_min + (x_max - x_min) * 0.60
  legend_bottom_y <- 0.25
  legend_bottom_x <- x_min + (x_max - x_min) * 0.60

  p_forest <- ggplot(forest_data, aes(y = y_pos)) +
    geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = y_pos - 0.5, ymax = y_pos + 0.5, fill = factor(seq_along(Organ) %% 2)), alpha = 0.6, show.legend = FALSE) +
    scale_fill_manual(values = c("0" = "transparent", "1" = "gray95")) +
    geom_segment(aes(x = 1, xend = 1, y = 0.5, yend = max(forest_data$y_pos) + 0.75), linetype = "33", color = "grey10", size = 0.7) +
    {if (nrow(data_in_bounds) > 0) geom_errorbarh(data = data_in_bounds, aes(xmin = hr_lower_capped, xmax = hr_upper_capped), color = data_in_bounds$errorbar_color, height = 0.15, size = 0.6)} +
    {if (nrow(data_in_bounds) > 0) geom_point(data = data_in_bounds, aes(x = hr, color = significant), size = 2.5, shape = 16)} +
    {if (nrow(data_in_bounds |> filter(has_any_value_outside)) > 0) geom_text(data = data_in_bounds |> filter(has_any_value_outside), aes(x = hr, y = y_pos + 0.25), label = "*", size = 3.5, color = "black")} +
    annotate("text", x = legend_left_x, y = legend_y, label = "● Significant (FDR < 0.05)", hjust = 0, size = 2.6, color = main_color) +
    annotate("text", x = legend_right_x, y = legend_y, label = "● Non-significant", hjust = 0, size = 2.6, color = "gray80") +
    {if (nrow(data_in_bounds |> filter(has_any_value_outside)) > 0) annotate("text", x = legend_bottom_x, y = legend_bottom_y, label = "* Value outside plot range", hjust = 1, size = 2.4, color = "black")} +
    scale_color_manual(values = c("TRUE" = main_color, "FALSE" = "gray80")) +
    scale_x_continuous(
      limits = c(x_min, x_max),
      breaks = x_breaks,
      labels = format(x_breaks, digits = 3, trim = TRUE)
    ) +
    scale_y_continuous(breaks = NULL, labels = NULL, limits = c(0.2, max(forest_data$y_pos) + 1.5)) +
    labs(x = "Hazard Ratio (95% CI)", y = NULL) +
    theme_minimal(base_size = 11) +
    theme(axis.text.y = element_blank(), axis.text.x = element_text(size = 9), axis.title.x = element_text(size = 10), panel.grid.major.y = element_blank(), panel.grid.minor = element_blank(), panel.grid.major.x = element_blank(), plot.margin = unit(c(12, 12, 6, 0), "pt"), legend.position = "none") +
    coord_cartesian(clip = "off")

  p_table + p_forest + plot_layout(widths = c(table_width_ratio, 1.5))
}

create_forest_table_significant_only_wp_uni <- function(data, disease_name = "Dementia", model_type = "WithinPair_All", title = NULL, main_color = "#2166AC") {
  # Filter by FDR significance and impossible combinations
  forest_data <- data |>
    filter(Model_Type == model_type, Disease == disease_name, P_value_FDR < 0.05) |>
    filter(!(Disease %in% c("ovarian_cancer", "uterine_cancer", "breast_cancer") & Organ == "Prostate"),
           !(Disease == "prostate_cancer" & Organ == "Ovary"))
  if (nrow(forest_data) == 0) return(NULL)

  # Use within-pair specific case counting
  case_counts <- calculate_withinpair_case_counts(disease_name, model_type)
  disease_cases <- case_counts$cases
  sample_size <- case_counts$pairs
  display_name <- case_counts$display_name

  if (is.null(title)) title <- paste(display_name, "(cases =", disease_cases, ", pairs =", sample_size, ")")

  forest_data <- forest_data |>
    mutate(
      hr = HR,
      hr_lower = HR_lower,
      hr_upper = HR_upper,
      p_value = P_value_FDR,
      significant = TRUE, # All are significant by definition after filtering
      errorbar_color = "grey30", # All are significant, so all error bars are grey30
      Organ_Display = case_when(
        Organ == "Gastrointestinal_tract" ~ "Gastrointestinal",
        Organ == "Kidney_urinary" ~ "Kidney and Bladder",
        Organ == "Artery" ~ "Arterial",
        TRUE ~ str_to_title(Organ)
      )
    ) |>
    # Use standardized organ ordering instead of HR-based ordering
    mutate(
      Organ_Display = factor(Organ_Display, levels = standardized_organ_order),
      y_pos = as.numeric(Organ_Display)
    ) |>
    arrange(y_pos)

  # Dynamic x-axis limits with sensible defaults and breathing room
  base_min <- 0.25
  base_max <- 3
  hard_min <- 0.05
  hard_max <- 10

  if (nrow(forest_data) > 0) {
    hr_min <- suppressWarnings(min(forest_data$hr_lower, na.rm = TRUE))
    hr_max <- suppressWarnings(max(forest_data$hr_upper, na.rm = TRUE))

    if (!is.finite(hr_min)) hr_min <- base_min
    if (!is.finite(hr_max)) hr_max <- base_max

    hr_min <- max(hr_min, 0.001)

    lower_margin_factor <- 0.9
    upper_margin_factor <- 1.1

    x_min <- min(base_min, hr_min * lower_margin_factor)
    x_max <- max(base_max, hr_max * upper_margin_factor)

    x_min <- max(hard_min, x_min)
    x_max <- min(hard_max, x_max)
  } else {
    x_min <- base_min
    x_max <- base_max
  }

  x_breaks <- pretty(c(x_min, x_max), n = 6)
  x_breaks <- x_breaks[x_breaks >= x_min & x_breaks <= x_max]

  # Add formatted HR column and detect if scientific notation is needed
  forest_data <- forest_data |>
    mutate(
      use_sci = pmax(abs(hr), abs(hr_lower), abs(hr_upper), na.rm = TRUE) >= 10,
      hr_formatted = if_else(
        use_sci,
        sprintf("%.1e (%.1e-%.1e)", hr, hr_lower, hr_upper),
        sprintf("%.2f (%.2f-%.2f)", hr, hr_lower, hr_upper)
      )
    )

  # Detect if we need wider table for scientific notation
  has_sci_notation <- any(forest_data$use_sci)
  table_width_ratio <- if (has_sci_notation) 3.2 else 2.5

  tab <- forest_data |>
    transmute(y_pos, `Organ age` = Organ_Display, `HR (95% CI)` = hr_formatted, `FDR` = sprintf("%.2e", p_value))

  x_pos <- tibble(col = c("Organ age", "HR (95% CI)", "FDR"), x = c(1.0, 4.0, 7.5))
  table_long <- tab |>
    pivot_longer(-y_pos, names_to = "col", values_to = "val") |>
    left_join(x_pos, by = "col")

  p_table <- ggplot(table_long, aes(x = x, y = y_pos, label = val)) +
    geom_text(hjust = c(0, 0, 1)[match(table_long$col, x_pos$col)], size = 3) +
    geom_text(data = x_pos |> mutate(y_pos = max(forest_data$y_pos) + 1), aes(x = x, y = y_pos, label = col), hjust = c(0, 0, 1), fontface = "bold", inherit.aes = FALSE, size = 3.3) +
    scale_y_continuous(breaks = NULL, labels = NULL, limits = c(0.5, max(forest_data$y_pos) + 1.5)) +
    scale_x_continuous(limits = c(0.5, 9.0), expand = c(0, 0)) +
    labs(title = title) +
    theme_minimal(base_size = 11) +
    theme(plot.title = element_text(hjust = 0.1, size = 12), axis.title = element_blank(), axis.text.x = element_blank(), axis.ticks = element_blank(), panel.grid = element_blank(), plot.margin = unit(c(12, 6, 6, 6), "pt"))

  # Determine which points are out of bounds (based on HR only) and cap CIs to plot range
  forest_data <- forest_data |>
    mutate(
      out_of_bounds_point = hr < x_min | hr > x_max,
      hr_lower_capped = pmax(hr_lower, x_min),
      hr_upper_capped = pmin(hr_upper, x_max),
      has_any_value_outside = (hr < x_min | hr > x_max | hr_lower < x_min | hr_upper > x_max)
    )

  # Only plot data where the HR itself is within bounds
  data_in_bounds <- forest_data |> filter(!out_of_bounds_point)

  # Calculate legend position (only significant legend in this version, nudged slightly)
  legend_y <- max(forest_data$y_pos) + 1.5
  legend_left_x <- x_min + (x_max - x_min) * 0.04
  legend_bottom_y <- 0.25
  legend_bottom_x <- x_min + (x_max - x_min) * 0.60

  p_forest <- ggplot(forest_data, aes(y = y_pos)) +
    geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = y_pos - 0.5, ymax = y_pos + 0.5, fill = factor(seq_along(Organ) %% 2)), alpha = 0.6, show.legend = FALSE) +
    scale_fill_manual(values = c("0" = "transparent", "1" = "gray95")) +
    geom_segment(aes(x = 1, xend = 1, y = 0.5, yend = max(forest_data$y_pos) + 0.75), linetype = "33", color = "grey10", size = 0.7) +
    {if (nrow(data_in_bounds) > 0) geom_errorbarh(data = data_in_bounds, aes(xmin = hr_lower_capped, xmax = hr_upper_capped), color = data_in_bounds$errorbar_color, height = 0.15, size = 0.6)} +
    {if (nrow(data_in_bounds) > 0) geom_point(data = data_in_bounds, aes(x = hr, color = significant), size = 2.5, shape = 16)} +
    {if (nrow(data_in_bounds |> filter(has_any_value_outside)) > 0) geom_text(data = data_in_bounds |> filter(has_any_value_outside), aes(x = hr, y = y_pos + 0.25), label = "*", size = 3.5, color = "black")} +
    annotate("text", x = legend_left_x, y = legend_y, label = "● Significant (FDR < 0.05)", hjust = 0, size = 2.6, color = main_color) +
    {if (nrow(data_in_bounds |> filter(has_any_value_outside)) > 0) annotate("text", x = legend_bottom_x, y = legend_bottom_y, label = "* Value outside plot range", hjust = 1, size = 2.4, color = "black")} +
    scale_color_manual(values = c("TRUE" = main_color, "FALSE" = "gray80")) +
    scale_x_continuous(
      limits = c(x_min, x_max),
      breaks = x_breaks,
      labels = format(x_breaks, digits = 3, trim = TRUE)
    ) +
    scale_y_continuous(breaks = NULL, labels = NULL, limits = c(0.2, max(forest_data$y_pos) + 1.5)) +
    labs(x = "Hazard Ratio (95% CI)", y = NULL) +
    theme_minimal(base_size = 11) +
    theme(axis.text.y = element_blank(), axis.text.x = element_text(size = 9), axis.title.x = element_text(size = 10), panel.grid.major.y = element_blank(), panel.grid.minor = element_blank(), panel.grid.major.x = element_blank(), plot.margin = unit(c(12, 12, 6, 0), "pt"), legend.position = "none") +
    coord_cartesian(clip = "off")

  p_table + p_forest + plot_layout(widths = c(table_width_ratio, 1.5))
}
```

```{r withinpair_uni_forest_plots}
# Create directories for within-pair forest tables
dir.create(file.path(output_core_dir, "forest_table", "within_pair"), showWarnings = FALSE, recursive = TRUE)

# All pairs forest plots
if (exists("wp_uni_all") && nrow(wp_uni_all) > 0) {
  wp_uni_all_disease_plots <- list()
  for (disease_name in names(diseases_with_mortality_healthspan)) {
    disease_data <- wp_uni_all |> filter(Model_Type == "WithinPair_All", Disease == disease_name)
    if (nrow(disease_data) == 0) next
    plot <- create_forest_table_combined_wp_uni(wp_uni_all, disease_name = disease_name, model_type = "WithinPair_All", main_color = "black")
    wp_uni_all_disease_plots[[diseases_with_mortality_healthspan[[disease_name]]$name]] <- plot
  }
  
  # Save all pairs forest plots
  for (disease_display in names(wp_uni_all_disease_plots)) {
    filename <- paste0(tolower(str_replace_all(disease_display, " ", "_")), "_all_pairs.svg")
    filename <- str_replace(filename, "^end_of_healthspan_", "healthspan_")
    ggsave(filename = filename, plot = wp_uni_all_disease_plots[[disease_display]], path = file.path(output_core_dir, "forest_table", "within_pair"), device = "svg", width = 8, height = 5, dpi = 300)
  }
}

# MZ twins forest plots
if (exists("wp_uni_mz") && nrow(wp_uni_mz) > 0) {
  wp_uni_mz_disease_plots <- list()
  for (disease_name in names(diseases_with_mortality_healthspan)) {
    disease_data <- wp_uni_mz |> filter(Model_Type == "WithinPair_MZ", Disease == disease_name)
    if (nrow(disease_data) == 0) next
    plot <- create_forest_table_combined_wp_uni(wp_uni_mz, disease_name = disease_name, model_type = "WithinPair_MZ", main_color = "black")
    wp_uni_mz_disease_plots[[diseases_with_mortality_healthspan[[disease_name]]$name]] <- plot
  }
  
  # Save MZ twins forest plots
  for (disease_display in names(wp_uni_mz_disease_plots)) {
    filename <- paste0(tolower(str_replace_all(disease_display, " ", "_")), "_mz_twins.svg")
    filename <- str_replace(filename, "^end_of_healthspan_", "healthspan_")
    ggsave(filename = filename, plot = wp_uni_mz_disease_plots[[disease_display]], path = file.path(output_core_dir, "forest_table", "within_pair"), device = "svg", width = 8, height = 5, dpi = 300)
  }
}

# DZ twins forest plots
if (exists("wp_uni_dz") && nrow(wp_uni_dz) > 0) {
  wp_uni_dz_disease_plots <- list()
  for (disease_name in names(diseases_with_mortality_healthspan)) {
    disease_data <- wp_uni_dz |> filter(Model_Type == "WithinPair_DZ", Disease == disease_name)
    if (nrow(disease_data) == 0) next
    plot <- create_forest_table_combined_wp_uni(wp_uni_dz, disease_name = disease_name, model_type = "WithinPair_DZ", main_color = "black")
    wp_uni_dz_disease_plots[[diseases_with_mortality_healthspan[[disease_name]]$name]] <- plot
  }
  
  # Save DZ twins forest plots
  for (disease_display in names(wp_uni_dz_disease_plots)) {
    filename <- paste0(tolower(str_replace_all(disease_display, " ", "_")), "_dz_twins.svg")
    filename <- str_replace(filename, "^end_of_healthspan_", "healthspan_")
    ggsave(filename = filename, plot = wp_uni_dz_disease_plots[[disease_display]], path = file.path(output_core_dir, "forest_table", "within_pair"), device = "svg", width = 8, height = 5, dpi = 300)
  }
}

# Create tables directory
dir.create(file.path(output_core_dir, "tables", "within_pair"), showWarnings = FALSE, recursive = TRUE)

# Save table data as CSV - All pairs
if (exists("wp_uni_all") && nrow(wp_uni_all) > 0) {
  for (disease_name in names(diseases_with_mortality_healthspan)) {
    disease_data <- wp_uni_all |> filter(Model_Type == "WithinPair_All", Disease == disease_name)
    if (nrow(disease_data) == 0) next
    
    # Create table data
    tab <- disease_data |>
      mutate(
        use_sci = pmax(abs(HR), abs(HR_lower), abs(HR_upper), na.rm = TRUE) >= 10,
        hr_formatted = if_else(use_sci,
          sprintf("%.1e (%.1e-%.1e)", HR, HR_lower, HR_upper),
          sprintf("%.2f (%.2f-%.2f)", HR, HR_lower, HR_upper)),
        Organ_Display = case_when(
          Organ == "Gastrointestinal_tract" ~ "Gastrointestinal",
          Organ == "Kidney_urinary" ~ "Kidney and Bladder",
          Organ == "Artery" ~ "Arterial",
          TRUE ~ str_to_title(Organ)
        )
      ) |>
      select(Organ = Organ_Display, `HR (95% CI)` = hr_formatted, FDR = P_value_FDR)
    
    # Save CSV
    display_name <- diseases_with_mortality_healthspan[[disease_name]]$name
    filename <- paste0(tolower(str_replace_all(display_name, " ", "_")), "_all_pairs.csv")
    filename <- str_replace(filename, "^end_of_healthspan_", "healthspan_")
    write.csv(tab, file = file.path(output_core_dir, "tables", "within_pair", filename), row.names = FALSE)
  }
}

# Save table data as CSV - MZ twins
if (exists("wp_uni_mz") && nrow(wp_uni_mz) > 0) {
  for (disease_name in names(diseases_with_mortality_healthspan)) {
    disease_data <- wp_uni_mz |> filter(Model_Type == "WithinPair_MZ", Disease == disease_name)
    if (nrow(disease_data) == 0) next
    
    # Create table data
    tab <- disease_data |>
      mutate(
        use_sci = pmax(abs(HR), abs(HR_lower), abs(HR_upper), na.rm = TRUE) >= 10,
        hr_formatted = if_else(use_sci,
          sprintf("%.1e (%.1e-%.1e)", HR, HR_lower, HR_upper),
          sprintf("%.2f (%.2f-%.2f)", HR, HR_lower, HR_upper)),
        Organ_Display = case_when(
          Organ == "Gastrointestinal_tract" ~ "Gastrointestinal",
          Organ == "Kidney_urinary" ~ "Kidney and Bladder",
          Organ == "Artery" ~ "Arterial",
          TRUE ~ str_to_title(Organ)
        )
      ) |>
      select(Organ = Organ_Display, `HR (95% CI)` = hr_formatted, FDR = P_value_FDR)
    
    # Save CSV
    display_name <- diseases_with_mortality_healthspan[[disease_name]]$name
    filename <- paste0(tolower(str_replace_all(display_name, " ", "_")), "_mz_twins.csv")
    filename <- str_replace(filename, "^end_of_healthspan_", "healthspan_")
    write.csv(tab, file = file.path(output_core_dir, "tables", "within_pair", filename), row.names = FALSE)
  }
}

# Save table data as CSV - DZ twins
if (exists("wp_uni_dz") && nrow(wp_uni_dz) > 0) {
  for (disease_name in names(diseases_with_mortality_healthspan)) {
    disease_data <- wp_uni_dz |> filter(Model_Type == "WithinPair_DZ", Disease == disease_name)
    if (nrow(disease_data) == 0) next
    
    # Create table data
    tab <- disease_data |>
      mutate(
        use_sci = pmax(abs(HR), abs(HR_lower), abs(HR_upper), na.rm = TRUE) >= 10,
        hr_formatted = if_else(use_sci,
          sprintf("%.1e (%.1e-%.1e)", HR, HR_lower, HR_upper),
          sprintf("%.2f (%.2f-%.2f)", HR, HR_lower, HR_upper)),
        Organ_Display = case_when(
          Organ == "Gastrointestinal_tract" ~ "Gastrointestinal",
          Organ == "Kidney_urinary" ~ "Kidney and Bladder",
          Organ == "Artery" ~ "Arterial",
          TRUE ~ str_to_title(Organ)
        )
      ) |>
      select(Organ = Organ_Display, `HR (95% CI)` = hr_formatted, FDR = P_value_FDR)
    
    # Save CSV
    display_name <- diseases_with_mortality_healthspan[[disease_name]]$name
    filename <- paste0(tolower(str_replace_all(display_name, " ", "_")), "_dz_twins.csv")
    filename <- str_replace(filename, "^end_of_healthspan_", "healthspan_")
    write.csv(tab, file = file.path(output_core_dir, "tables", "within_pair", filename), row.names = FALSE)
  }
}
```

```{r withinpair_heatmaps_univariate}
make_wp_heatmap <- function(df, disease_list = NULL) {
  if (nrow(df) == 0) return(NULL)
  
  # Use provided disease list or fall back to global diseases
  diseases_to_use <- if (!is.null(disease_list)) disease_list else diseases
  
  # Panel-style control variables
  text_size_pt <- HEATMAP_TEXT_SIZE
  square_size <- text_size_pt / HEATMAP_SQUARE_SIZE_DIVISOR
  
  # Prepare data with display names
  df_plot <- df |>
    dplyr::mutate(
      Disease_Display = dplyr::case_when(
        Disease %in% names(diseases_to_use) ~ purrr::map_chr(Disease, ~ diseases_to_use[[.x]]$name),
        TRUE ~ stringr::str_to_title(stringr::str_replace_all(Disease, "_", " "))
      ),
      Organ_Display = dplyr::case_when(
        Organ == "Gastrointestinal_tract" ~ "Gastrointestinal",
        Organ == "Kidney_urinary" ~ "Kidney and Bladder",
        TRUE ~ stringr::str_to_title(Organ)
      ),
      # Create effect size for coloring (use HR directly, consistent with regular heatmaps)
      effect_size = HR,
      significance = dplyr::case_when(
        P_value_FDR < 0.001 ~ "***",
        P_value_FDR < 0.01 ~ "**",
        P_value_FDR < 0.05 ~ "*",
        TRUE ~ ""
      ),
      effect_size_colored = dplyr::if_else(significance != "", effect_size, NA_real_),
      non_sig_marker = dplyr::if_else(significance == "", "×", "")
    )
  
  # Get available diseases and organs from data
  available_diseases <- unique(df_plot$Disease_Display) |> na.omit()
  available_organs <- unique(df_plot$Organ_Display) |> na.omit()
  
  # Get standardized orders and filter to available items
  disease_order <- create_standardized_disease_order(diseases_to_use)
  disease_order <- intersect(disease_order, available_diseases)
  
  organ_order <- standardized_organ_order
  organ_order <- intersect(organ_order, available_organs)
  # Add any organs not in standardized order at the end
  missing_organs <- setdiff(available_organs, standardized_organ_order)
  organ_order <- c(organ_order, missing_organs)
  
  if (length(disease_order) == 0 || length(organ_order) == 0) return(NULL)
  
  # Now apply ordering and calculate numeric positions
  df_plot <- df_plot |>
    dplyr::mutate(
      Disease_Display = factor(Disease_Display, levels = disease_order),
      Organ_Display = factor(Organ_Display, levels = organ_order),
      Disease_num = (as.numeric(Disease_Display) - 1) * square_size + square_size/2,
      Organ_num = (as.numeric(Organ_Display) - 1) * square_size + square_size/2
    )
  
  # Calculate dynamic range (white-to-red only, no negative values)
  effect_range <- range(log(df_plot$HR), na.rm = TRUE)
  buffer <- 0.1
  max_limit <- max(1.5, effect_range[2] + buffer)
  min_limit <- 0  # Start from 0 since no negative values
  
  breaks <- seq(0, max_limit, length.out = 4)
  labels <- sprintf("%.1f", breaks)
  
  ggplot2::ggplot(df_plot, ggplot2::aes(x = Organ_num, y = Disease_num, fill = log(effect_size_colored))) +
    ggplot2::geom_tile(width = square_size, height = square_size, color = NA) +
    ggplot2::geom_text(ggplot2::aes(x = Organ_num, y = Disease_num, label = non_sig_marker), size = 5.5, color = "darkgrey", family = "Helvetica", inherit.aes = FALSE) +
    ggplot2::scale_fill_gradientn(
      colors = c(
        "white",        # Start at 0
        "#C64D4D",      # Red (mid-high)
        "#B71C1C"       # Darker red (extreme high)
      ),
      values = scales::rescale(c(0, max_limit * 0.5, max_limit)),
      limits = c(0, max_limit),
      na.value = "white",
      name = "log(Hazard\nRatio)",
      breaks = breaks,
      labels = labels
    ) +
    ggplot2::scale_x_continuous(
      breaks = (seq_along(organ_order) - 1) * square_size + square_size/2,
      labels = organ_order,
      expand = c(0, 0),
      limits = c(0, length(organ_order) * square_size)
    ) +
    ggplot2::scale_y_continuous(
      breaks = (seq_along(disease_order) - 1) * square_size + square_size/2,
      labels = disease_order,
      expand = c(0, 0),
      limits = c(0, length(disease_order) * square_size)
    ) +
    ggplot2::labs(x = NULL, y = NULL) +
    ggplot2::theme_minimal(base_family = "Helvetica") +
    ggplot2::theme(
      text = ggplot2::element_text(family = "Helvetica", color = "black"),
      axis.text.x = ggplot2::element_text(angle = 45, hjust = 1, size = HEATMAP_TEXT_SIZE, color = "black", family = "Helvetica"),
      axis.text.y = ggplot2::element_text(size = HEATMAP_TEXT_SIZE, hjust = 0, margin = ggplot2::margin(r = 10), color = "black", family = "Helvetica"),
      axis.title = ggplot2::element_blank(),
      axis.ticks = ggplot2::element_blank(),
      legend.position = "right",
      legend.title = ggplot2::element_text(size = 11, color = "black", family = "Helvetica"),
      legend.text = ggplot2::element_text(size = 9, color = "black", family = "Helvetica"),
      legend.key.height = ggplot2::unit(0.8, "cm"),
      legend.key.width = ggplot2::unit(0.5, "cm"),
      panel.grid = ggplot2::element_blank(),
      panel.spacing = ggplot2::unit(0, "lines"),
      panel.border = ggplot2::element_blank(),
      plot.margin = ggplot2::margin(0.5, 0.5, 0.5, 0.5, "cm")
    ) +
    ggplot2::coord_fixed(ratio = 1, expand = FALSE)
}

dir.create(file.path(output_core_dir, "heatmap", "within_pair"), showWarnings = FALSE, recursive = TRUE)

if (exists("wp_uni_all") && nrow(wp_uni_all) > 0) {
  p_all <- make_wp_heatmap(wp_uni_all, diseases_with_mortality_healthspan)
  if (!is.null(p_all)) {
    ggplot2::ggsave(filename = "all_pairs.svg", plot = p_all, path = file.path(output_core_dir, "heatmap", "within_pair"), device = "svg", width = 10, height = 8, dpi = 300)
    ggplot2::ggsave(filename = "all_pairs.png", plot = p_all, path = file.path(output_core_dir, "heatmap", "within_pair"), device = "png", width = 10, height = 8, dpi = 300)
  }
}
if (exists("wp_uni_mz") && nrow(wp_uni_mz) > 0) {
  p_mz <- make_wp_heatmap(wp_uni_mz, diseases_with_mortality_healthspan)
  if (!is.null(p_mz)) {
    ggplot2::ggsave(filename = "mz_twins.svg", plot = p_mz, path = file.path(output_core_dir, "heatmap", "within_pair"), device = "svg", width = 10, height = 8, dpi = 300)
    ggplot2::ggsave(filename = "mz_twins.png", plot = p_mz, path = file.path(output_core_dir, "heatmap", "within_pair"), device = "png", width = 10, height = 8, dpi = 300)
  }
}
if (exists("wp_uni_dz") && nrow(wp_uni_dz) > 0) {
  p_dz <- make_wp_heatmap(wp_uni_dz, diseases_with_mortality_healthspan)
  if (!is.null(p_dz)) {
    ggplot2::ggsave(filename = "dz_twins.svg", plot = p_dz, path = file.path(output_core_dir, "heatmap", "within_pair"), device = "svg", width = 10, height = 8, dpi = 300)
    ggplot2::ggsave(filename = "dz_twins.png", plot = p_dz, path = file.path(output_core_dir, "heatmap", "within_pair"), device = "png", width = 10, height = 8, dpi = 300)
  }
}

# Significant-only within-pair heatmaps (filter out outcomes with no significant associations)
if (exists("wp_uni_all") && nrow(wp_uni_all) > 0) {
  # Find outcomes that have at least one significant association
  outcomes_with_sig <- wp_uni_all |>
    dplyr::filter(P_value_FDR < 0.05) |>
    dplyr::distinct(Disease) |>
    dplyr::pull(Disease)
  
  # Filter to only include outcomes that have significant associations
  wp_uni_all_sig <- wp_uni_all |>
    dplyr::filter(Disease %in% outcomes_with_sig)
  
  if (nrow(wp_uni_all_sig) > 0) {
    p_all_sig <- make_wp_heatmap(wp_uni_all_sig, diseases_with_mortality_healthspan)
    if (!is.null(p_all_sig)) {
      ggplot2::ggsave(filename = "all_pairs_significant_only.svg", plot = p_all_sig, path = file.path(output_core_dir, "heatmap", "within_pair"), device = "svg", width = 10, height = 8, dpi = 300)
      ggplot2::ggsave(filename = "all_pairs_significant_only.png", plot = p_all_sig, path = file.path(output_core_dir, "heatmap", "within_pair"), device = "png", width = 10, height = 8, dpi = 300)
    }
  }
}
if (exists("wp_uni_mz") && nrow(wp_uni_mz) > 0) {
  outcomes_with_sig <- wp_uni_mz |>
    dplyr::filter(P_value_FDR < 0.05) |>
    dplyr::distinct(Disease) |>
    dplyr::pull(Disease)
  
  wp_uni_mz_sig <- wp_uni_mz |>
    dplyr::filter(Disease %in% outcomes_with_sig)
  
  if (nrow(wp_uni_mz_sig) > 0) {
    p_mz_sig <- make_wp_heatmap(wp_uni_mz_sig, diseases_with_mortality_healthspan)
    if (!is.null(p_mz_sig)) {
      ggplot2::ggsave(filename = "mz_twins_significant_only.svg", plot = p_mz_sig, path = file.path(output_core_dir, "heatmap", "within_pair"), device = "svg", width = 10, height = 8, dpi = 300)
      ggplot2::ggsave(filename = "mz_twins_significant_only.png", plot = p_mz_sig, path = file.path(output_core_dir, "heatmap", "within_pair"), device = "png", width = 10, height = 8, dpi = 300)
    }
  }
}
if (exists("wp_uni_dz") && nrow(wp_uni_dz) > 0) {
  outcomes_with_sig <- wp_uni_dz |>
    dplyr::filter(P_value_FDR < 0.05) |>
    dplyr::distinct(Disease) |>
    dplyr::pull(Disease)
  
  wp_uni_dz_sig <- wp_uni_dz |>
    dplyr::filter(Disease %in% outcomes_with_sig)
  
  if (nrow(wp_uni_dz_sig) > 0) {
    p_dz_sig <- make_wp_heatmap(wp_uni_dz_sig, diseases_with_mortality_healthspan)
    if (!is.null(p_dz_sig)) {
      ggplot2::ggsave(filename = "dz_twins_significant_only.svg", plot = p_dz_sig, path = file.path(output_core_dir, "heatmap", "within_pair"), device = "svg", width = 10, height = 8, dpi = 300)
      ggplot2::ggsave(filename = "dz_twins_significant_only.png", plot = p_dz_sig, path = file.path(output_core_dir, "heatmap", "within_pair"), device = "png", width = 10, height = 8, dpi = 300)
    }
  }
}

```

## Panel Heatmaps: Significant Diseases Only

```{r panel_heatmap_functions_cox}
# Control variables for heatmap appearance
HEATMAP_TEXT_SIZE <- 10
HEATMAP_SQUARE_SIZE_DIVISOR <- 10

create_panel_cox_heatmap <- function(data, model_type) {
  model_data <- data |> filter(Model_Type == model_type)
  if (nrow(model_data) == 0) return(NULL)
  
  available_organs <- unique(model_data$Organ_Display) |> na.omit()
  organ_order <- c(intersect(standardized_organ_order, available_organs), setdiff(available_organs, standardized_organ_order))
  
  available_diseases <- unique(model_data$Disease_Display)
  disease_order <- create_standardized_disease_order(diseases)
  disease_order <- intersect(disease_order, available_diseases)
  
  if (length(disease_order) == 0 || length(organ_order) == 0) return(NULL)
  
  text_size_pt <- HEATMAP_TEXT_SIZE
  square_size <- text_size_pt / HEATMAP_SQUARE_SIZE_DIVISOR
  
  model_data_plot <- model_data |>
    mutate(
      Disease_Display = factor(Disease_Display, levels = disease_order),
      Organ_Display = factor(Organ_Display, levels = organ_order),
      Disease_num = (as.numeric(Disease_Display) - 1) * square_size + square_size/2,
      Organ_num = (as.numeric(Organ_Display) - 1) * square_size + square_size/2,
      effect_size_colored = if_else(impossible, NA_real_, if_else(significance != "", log(HR), NA_real_)),
      non_sig_marker = if_else(impossible, "", if_else(significance == "", "×", ""))
    )
  
  effect_range <- range(log(model_data$HR), na.rm = TRUE)
  buffer <- 0.1
  max_limit <- max(1.5, effect_range[2] + buffer)
  min_limit <- 0  # Start from 0 since no negative values
  
  breaks <- seq(0, max_limit, length.out = 4)
  labels <- sprintf("%.1f", breaks)
  
  max_y <- length(disease_order) * square_size
  max_x <- length(organ_order) * square_size
  
  ggplot(model_data_plot, aes(x = Organ_num, y = Disease_num, fill = effect_size_colored)) +
    geom_tile(width = square_size, height = square_size, color = NA) +
    geom_tile(data = model_data_plot |> filter(impossible), fill = "grey80", alpha = 0.7, width = square_size, height = square_size, color = NA) +
    geom_segment(
      data = model_data_plot |> filter(impossible),
      aes(x = Organ_num - square_size/2, y = Disease_num - square_size/2,
          xend = Organ_num + square_size/2, yend = Disease_num + square_size/2),
      color = "white", linewidth = 0.8
    ) +
    geom_text(aes(x = Organ_num, y = Disease_num, label = non_sig_marker), size = 3.5, color = "darkgrey", inherit.aes = FALSE) +
    scale_fill_gradientn(
      colors = c(
        "white",        # Start at 0
        "#C64D4D",      # Red (mid-high)
        "#B71C1C"       # Slightly darker red (extreme high)
      ),
      values = scales::rescale(c(0, max_limit * 0.5, max_limit)),
      limits = c(0, max_limit),
      na.value = "white",
      name = "log(Hazard\nRatio)",
      breaks = breaks,
      labels = labels
    ) +
    scale_x_continuous(
      breaks = (seq_along(organ_order) - 1) * square_size + square_size/2,
      labels = organ_order,
      expand = c(0, 0),
      limits = c(0, length(organ_order) * square_size)
    ) +
    scale_y_continuous(
      breaks = (seq_along(disease_order) - 1) * square_size + square_size/2,
      labels = disease_order,
      expand = c(0, 0),
      limits = c(0, length(disease_order) * square_size)
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1, size = HEATMAP_TEXT_SIZE, color = "black"),
      axis.text.y = element_text(size = HEATMAP_TEXT_SIZE, hjust = 0, margin = margin(r = 10), color = "black"),
      axis.title = element_blank(),
      axis.ticks = element_blank(),
      legend.position = "right",
      legend.title = element_text(size = 9),
      legend.text = element_text(size = 7),
      legend.key.height = unit(0.6, "cm"),
      legend.key.width = unit(0.4, "cm"),
      panel.grid = element_blank(),
      panel.spacing = unit(0, "lines"),
      panel.border = element_blank(),
      plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm")
    ) +
    coord_fixed(ratio = 1, expand = FALSE)
}

filter_significant_diseases_cox <- function(heatmap_data) {
  significant_diseases <- heatmap_data |>
    filter(significance != "", !impossible) |>
    distinct(Disease_Display) |>
    pull(Disease_Display)
  
  heatmap_data |>
    filter(Disease_Display %in% significant_diseases)
}
```

```{r create_cohort_panel_heatmap}
# Filter cohort level results for significant diseases only
# Version WITHOUT Mortality: Exclude Mortality and Healthspan (shown separately as KM curves)
cohort_sig_data_no_mort <- heatmap_data |>
  filter(Model_Type == "Mortality") |>
  filter(Disease != "Mortality", Disease != "Healthspan") |>
  filter_significant_diseases_cox()

if (nrow(cohort_sig_data_no_mort) > 0) {
  cohort_panel_heatmap_no_mort <- create_panel_cox_heatmap(cohort_sig_data_no_mort, "Mortality")
  
  if (!is.null(cohort_panel_heatmap_no_mort)) {
    print(cohort_panel_heatmap_no_mort)
    
    panel_dir <- file.path(output_core_dir, "heatmap", "panel")
    dir.create(panel_dir, showWarnings = FALSE, recursive = TRUE)
    
    # Calculate proportional height based on number of rows
    # WP sig only has 6 rows with height = 3, so height per row = 0.5
    # Cohort sig only should scale proportionally
    cohort_n_rows <- length(unique(cohort_sig_data_no_mort$Disease_Display))
    wp_n_rows <- 6  # Reference: WP sig only has 6 rows
    wp_height <- 3  # Reference height for WP
    height_per_row <- wp_height / wp_n_rows
    cohort_height <- cohort_n_rows * height_per_row
    
    ggsave(
      filename = file.path(panel_dir, "cohort_significant_diseases.pdf"),
      plot = cohort_panel_heatmap_no_mort,
      width = 7,
      height = cohort_height,
      dpi = 300,
      device = "pdf"
    )
    ggsave(
      filename = file.path(panel_dir, "cohort_significant_diseases.svg"),
      plot = cohort_panel_heatmap_no_mort,
      width = 7,
      height = cohort_height,
      dpi = 300,
      device = "svg"
    )
    ggsave(
      filename = file.path(panel_dir, "cohort_significant_diseases.png"),
      plot = cohort_panel_heatmap_no_mort,
      width = 7,
      height = cohort_height,
      dpi = 300,
      device = "png"
    )
    
    cat(paste("Cohort panel heatmap (without mortality) saved (", cohort_n_rows, "rows, height =", round(cohort_height, 2), ")\n", sep = ""))
  }
  
  # Get list of significant diseases from cohort level (without mortality)
  sig_diseases_cohort <- unique(cohort_sig_data_no_mort$Disease_Display)
} else {
  sig_diseases_cohort <- character(0)
}

# Version WITH Mortality: Exclude only Healthspan (shown separately as KM curves)
cohort_sig_data_with_mort <- heatmap_data |>
  filter(Model_Type == "Mortality") |>
  filter(Disease != "Healthspan") |>
  filter_significant_diseases_cox()

if (nrow(cohort_sig_data_with_mort) > 0) {
  cohort_panel_heatmap_with_mort <- create_panel_cox_heatmap(cohort_sig_data_with_mort, "Mortality")
  
  if (!is.null(cohort_panel_heatmap_with_mort)) {
    print(cohort_panel_heatmap_with_mort)
    
    panel_dir <- file.path(output_core_dir, "heatmap", "panel")
    dir.create(panel_dir, showWarnings = FALSE, recursive = TRUE)
    
    # Calculate proportional height based on number of rows
    cohort_n_rows_mort <- length(unique(cohort_sig_data_with_mort$Disease_Display))
    wp_n_rows <- 6  # Reference: WP sig only has 6 rows
    wp_height <- 3  # Reference height for WP
    height_per_row <- wp_height / wp_n_rows
    cohort_height_mort <- cohort_n_rows_mort * height_per_row
    
    ggsave(
      filename = file.path(panel_dir, "cohort_significant_diseases_with_mortality.pdf"),
      plot = cohort_panel_heatmap_with_mort,
      width = 7,
      height = cohort_height_mort,
      dpi = 300,
      device = "pdf"
    )
    ggsave(
      filename = file.path(panel_dir, "cohort_significant_diseases_with_mortality.svg"),
      plot = cohort_panel_heatmap_with_mort,
      width = 7,
      height = cohort_height_mort,
      dpi = 300,
      device = "svg"
    )
    ggsave(
      filename = file.path(panel_dir, "cohort_significant_diseases_with_mortality.png"),
      plot = cohort_panel_heatmap_with_mort,
      width = 7,
      height = cohort_height_mort,
      dpi = 300,
      device = "png"
    )
    
    cat(paste("Cohort panel heatmap (with mortality) saved (", cohort_n_rows_mort, "rows, height =", round(cohort_height_mort, 2), ")\n", sep = ""))
  }
  
  # Get list of significant diseases from cohort level (with mortality)
  sig_diseases_cohort_with_mort <- unique(cohort_sig_data_with_mort$Disease_Display)
} else {
  sig_diseases_cohort_with_mort <- character(0)
}
```

```{r create_withinpair_panel_heatmap}
# Create within-pair heatmap using same diseases as cohort level
if (exists("wp_uni_all") && nrow(wp_uni_all) > 0 && length(sig_diseases_cohort) > 0) {
  # Prepare within-pair data similar to heatmap_data structure
  wp_heatmap_data <- wp_uni_all |>
    mutate(
      Disease_Display = case_when(
        Disease == "Mortality" ~ "Mortality",
        Disease == "Healthspan" ~ "End of Healthspan",
        Disease %in% names(diseases_with_mortality_healthspan) ~ map_chr(Disease, ~ diseases_with_mortality_healthspan[[.x]]$name),
        Disease %in% names(diseases) ~ disease_names_lookup[Disease],
        TRUE ~ str_to_title(str_replace_all(Disease, "_", " "))
      ),
      Organ_Display = case_when(
        Organ == "Gastrointestinal_tract" ~ "Gastrointestinal",
        Organ == "Kidney_urinary" ~ "Kidney and Bladder",
        TRUE ~ str_to_title(Organ)
      ),
      significance = case_when(
        P_value_FDR < 0.001 ~ "***",
        P_value_FDR < 0.01 ~ "**",
        P_value_FDR < 0.05 ~ "*",
        TRUE ~ ""
      ),
      HR = HR,
      non_sig_marker = if_else(significance == "", "×", ""),
      impossible = case_when(
        Disease %in% c("ovarian_cancer", "uterine_cancer", "breast_cancer") & Organ == "Prostate" ~ TRUE,
        Disease == "prostate_cancer" & Organ == "Ovary" ~ TRUE,
        TRUE ~ FALSE
      ),
      Model_Type = "WithinPair_All"
    ) |>
    filter(Disease_Display %in% sig_diseases_cohort) |>
    filter(Disease != "Mortality", Disease != "Healthspan")
  
  if (nrow(wp_heatmap_data) > 0) {
    wp_panel_heatmap <- create_panel_cox_heatmap(wp_heatmap_data, "WithinPair_All")
    
    if (!is.null(wp_panel_heatmap)) {
      print(wp_panel_heatmap)
      
      panel_dir <- file.path(output_core_dir, "heatmap", "panel")
      dir.create(panel_dir, showWarnings = FALSE, recursive = TRUE)
      
      ggsave(
        filename = file.path(panel_dir, "withinpair_significant_diseases.pdf"),
        plot = wp_panel_heatmap,
        width = 7,
        height = 3,
        dpi = 300,
        device = "pdf"
      )
      ggsave(
        filename = file.path(panel_dir, "withinpair_significant_diseases.svg"),
        plot = wp_panel_heatmap,
        width = 7,
        height = 3,
        dpi = 300,
        device = "svg"
      )
      ggsave(
        filename = file.path(panel_dir, "withinpair_significant_diseases.png"),
        plot = wp_panel_heatmap,
        width = 7,
        height = 3,
        dpi = 300,
        device = "png"
      )
      
      cat("Within-pair panel heatmap saved\n")
    }
  }
}
```


## Within-Pair Significant Only Heatmap

```{r create_withinpair_sig_only_heatmap}
# Filter within-pair results for WP-significant diseases only
# This shows only diseases that have at least one WP-significant association
if (exists("wp_uni_all") && nrow(wp_uni_all) > 0) {
  # Prepare WP data similar to heatmap_data structure
  wp_all_data <- wp_uni_all |>
    mutate(
      Disease_Display = case_when(
        Disease == "Mortality" ~ "Mortality",
        Disease == "Healthspan" ~ "End of Healthspan",
        Disease %in% names(diseases_with_mortality_healthspan) ~ map_chr(Disease, ~ diseases_with_mortality_healthspan[[.x]]$name),
        Disease %in% names(diseases) ~ disease_names_lookup[Disease],
        TRUE ~ str_to_title(str_replace_all(Disease, "_", " "))
      ),
      Organ_Display = case_when(
        Organ == "Gastrointestinal_tract" ~ "Gastrointestinal",
        Organ == "Kidney_urinary" ~ "Kidney and Bladder",
        TRUE ~ str_to_title(Organ)
      ),
      significance = case_when(
        P_value_FDR < 0.001 ~ "***",
        P_value_FDR < 0.01 ~ "**",
        P_value_FDR < 0.05 ~ "*",
        TRUE ~ ""
      ),
      HR = HR,
      non_sig_marker = if_else(significance == "", "×", ""),
      impossible = case_when(
        Disease %in% c("ovarian_cancer", "uterine_cancer", "breast_cancer") & Organ == "Prostate" ~ TRUE,
        Disease == "prostate_cancer" & Organ == "Ovary" ~ TRUE,
        TRUE ~ FALSE
      ),
      Model_Type = "WithinPair_All"
    )
  
  # Filter for WP-significant diseases (diseases with at least one WP-significant association)
  wp_sig_diseases <- wp_all_data |>
    filter(significance != "", !impossible) |>
    distinct(Disease_Display) |>
    pull(Disease_Display)
  
  wp_sig_only_data <- wp_all_data |>
    filter(Disease_Display %in% wp_sig_diseases) |>
    filter(tolower(Disease) != "mortality", tolower(Disease) != "healthspan")
  
  if (nrow(wp_sig_only_data) > 0) {
    wp_sig_only_heatmap <- create_panel_cox_heatmap(wp_sig_only_data, "WithinPair_All")
    
    if (!is.null(wp_sig_only_heatmap)) {
      print(wp_sig_only_heatmap)
      
      panel_dir <- file.path(output_core_dir, "heatmap", "panel")
      dir.create(panel_dir, showWarnings = FALSE, recursive = TRUE)
      
      ggsave(
        filename = file.path(panel_dir, "withinpair_significant_only.pdf"),
        plot = wp_sig_only_heatmap,
        width = 7,
        height = 3,
        dpi = 300,
        device = "pdf"
      )
      ggsave(
        filename = file.path(panel_dir, "withinpair_significant_only.svg"),
        plot = wp_sig_only_heatmap,
        width = 7,
        height = 3,
        dpi = 300,
        device = "svg"
      )
      ggsave(
        filename = file.path(panel_dir, "withinpair_significant_only.png"),
        plot = wp_sig_only_heatmap,
        width = 7,
        height = 3,
        dpi = 300,
        device = "png"
      )
      
      cat("Within-pair significant only heatmap saved\n")
    }
  } else {
    cat("No WP-significant diseases found\n")
  }
} else {
  cat("WP data not available\n")
}
```
