---
title: "Multimorbidity Analysis"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}
library(tidyverse)
library(survival)
library(survminer)
library(broom)
library(haven)
library(readxl)
library(ggvenn)
library(patchwork)
library(lubridate)
library(lmtest)
library(sandwich)
library(ggrepel)
select = dplyr::select
rename = dplyr::rename
slice = dplyr::slice
```

```{r config}
# Input files (set these for your environment)
input_diagnosis_file <- "PATH/TO/input_diagnosis.csv"
input_cancer_file <- "PATH/TO/input_cancer.csv"
input_metadata_file <- "PATH/TO/input_metadata.csv"
input_timeline_file <- "PATH/TO/input_diagnosis_timeline.csv"
input_organ_age_file <- "PATH/TO/input_organ_age.csv"
input_extreme_organ_file <- "PATH/TO/input_extreme_organ_quantiles.csv"

# Output root (set this for your environment)
output_multimorbidity_core_dir <- "PATH/TO/output/core_multimorbidity"

# Core schema configuration
id_col <- "twin_id"
pair_col <- "pair_id"
sex_col <- "sex"
male_code <- 1
female_code <- 2

# Covariate sets (choose active set)
covariate_sets <- list(
  minimal = c("age", "sex"),
  cardiometabolic = c("age", "sex", "bmi"),
  extended = c("age", "sex", "edyrs", "eversmok", "bmi", "hba1c", "total_hdl_ratio", "crp")
)
active_covariate_set <- "extended"
active_covariates <- covariate_sets[[active_covariate_set]]
if (is.null(active_covariates)) stop("Invalid `active_covariate_set` in config.")
covariate_formula_terms <- paste(active_covariates, collapse = " + ")
covariate_formula_terms_nosex <- paste(setdiff(active_covariates, "sex"), collapse = " + ")
```

# Data Loading

```{r}
composite_diseases <- read_csv(input_diagnosis_file)
cancer <- read_csv(input_cancer_file)
twins <- read_csv(input_metadata_file)
timeline <- read_csv(input_timeline_file) |>
  filter(twin_id %in% twins$twin_id) |> 
  left_join(twins |> 
              select(age, twin_id),
            by = "twin_id")

# Ensure has_disease column exists (all rows in timeline represent diseases)
if (!"has_disease" %in% names(timeline)) {
  timeline <- timeline |>
    mutate(has_disease = 1)
}

organ_age_mortality <- read_csv(input_organ_age_file)
```

# Negative Binomial Models

```{r}
# Disease grouping definitions

cvd_multimorbidity <- c(
  "Other cardiovascular diseases",
  "Heart failure",
  "Atrial fibrillation",
  "Hypertension",
  "Ischemic heart disease",
  "Cerebrovascular diseases",
  "Peripheral vascular disease"
)

neuropsychiatric_multimorbidity <- c(
  "Depression",
  "Dementia",
  "Schizophrenia and delusional diseases",
  "Other psychiatric and behavioral diseases"
)

digestive_multimorbidity <- c(
  "Colitis and related diseases",
  "Chronic liver diseases",
  "Chronic pancreas, biliary tract and gallbladder diseases",
  "Esophagus, stomach and duodenum diseases",
  "Other digestive diseases",
  "Inflammatory bowel disease"
)

endocrine_multimorbidity <- c(
  "Thyroid diseases",
  "Diabetes"
)

malignancy_multimorbidity <- c(
  "Solid neoplasms",
  "Hematological neoplasms"
)

musculoskeletal_multimorbidity <- c(
  "Osteoporosis",
  "Osteoarthrisis",
  "Inflammatory arthropathies",
  "Other musculoskeletal joint diseases"
)

neurosensorial_multimorbidity <- c(
  "Deafness, Hearing impairment",
  "Other eye diseases",
  "Glaucoma",
  "Migraine and facial pain syndromes",
  "Peripheral neuropathy",
  "Parkinson and Parkinsonism",
  "Epilepsy",
  "Multiple sclerosis"
)

respiratory_multimorbidity <- c(
  "COPD, Emphysema, Chronic bronchitis",
  "Other respiratory diseases",
  "Asthma"
)

urological_multimorbidity <- c(
  "Chronic kidney diseases",
  "Prostate diseases",
  "Other genitourinary diseases"
)

```

```{r}
# Build prevalent counts per expanded grouping from `timeline`

# Collect grouping vectors that actually exist
group_names_all <- c(
  "cvd_multimorbidity",
  "neuropsychiatric_multimorbidity",
  "digestive_multimorbidity",
  "endocrine_multimorbidity",
  "malignancy_multimorbidity",
  "musculoskeletal_multimorbidity",
  "neurosensorial_multimorbidity",
  "respiratory_multimorbidity",
  "urological_multimorbidity"
)

group_vectors <- mget(group_names_all, ifnotfound = as.list(rep(list(NULL), length(group_names_all)))) |>
  Filter(f = function(x) !is.null(x) && length(x) > 0)

# Detect the timeline column that holds disease labels matching our group vectors
group_label_values <- unique(unlist(group_vectors, use.names = FALSE))

# Try explicit column names first
possible_label_cols <- c("Chronic disease", "Chronic Disease", "chronic_disease", "disease", "Disease")
label_col <- NULL
for (col in possible_label_cols) {
  if (col %in% names(timeline)) {
    # Check if this column has matching values
    vals <- unique(timeline[[col]])
    if (sum(vals %in% group_label_values, na.rm = TRUE) > 0) {
      label_col <- col
      break
    }
  }
}

# If explicit names didn't work, try auto-detection
if (is.null(label_col)) {
  candidate_label_cols <- names(timeline)[vapply(timeline, inherits, logical(1), what = "character")]
  
  detect_label_col <- function(df, candidates, targets) {
    if (length(candidates) == 0L) return(NA_character_)
    overlaps <- vapply(candidates, function(col) {
      vals <- unique(df[[col]])
      sum(vals %in% targets, na.rm = TRUE)
    }, numeric(1))
    if (max(overlaps, na.rm = TRUE) == 0) return(NA_character_)
    candidates[which.max(overlaps)]
  }
  
  label_col <- detect_label_col(timeline, candidate_label_cols, group_label_values)
}

# Error handling if label column not found
if (is.null(label_col) || is.na(label_col)) {
  stop("Could not find disease label column in timeline. Expected columns: ", 
       paste(possible_label_cols, collapse = ", "), 
       ". Available columns: ", paste(names(timeline), collapse = ", "))
}

# Restrict to baseline-prevalent records; prefer explicit `prevalent` flag if available
timeline_base <- timeline |>
  dplyr::mutate(.is_prevalent = dplyr::case_when(
    "prevalent" %in% names(timeline) ~ prevalent == 1,
    TRUE ~ earliest_date <= checkdate
  )) |>
  dplyr::filter(.is_prevalent)

# Filter by label column using safe extraction
if (label_col %in% names(timeline_base)) {
  timeline_base <- timeline_base |>
    dplyr::filter(!is.na(.data[[label_col]]))
} else {
  stop("Label column '", label_col, "' not found in timeline_base. Available columns: ", 
       paste(names(timeline_base), collapse = ", "))
}

# Helper to compute counts for a single grouping vector
count_group <- function(df, label_column, labels, new_name) {
  df |>
    dplyr::filter(.data[[label_column]] %in% labels) |>
    dplyr::distinct(twin_id, .data[[label_column]]) |>
    dplyr::count(twin_id, name = new_name)
}

# Compute counts for all available groupings and combine
mm_counts_list <- lapply(names(group_vectors), function(nm) {
  count_group(timeline_base, label_col, group_vectors[[nm]], nm)
})

mm_counts <- purrr::reduce(mm_counts_list, ~dplyr::full_join(.x, .y, by = "twin_id")) |>
  dplyr::mutate(dplyr::across(-twin_id, ~dplyr::coalesce(.x, 0L)))

# Ensure the full cohort (including individuals with zero diagnoses) is present
mm_counts_full <- twins |>
  dplyr::select(twin_id) |>
  dplyr::left_join(mm_counts, by = "twin_id") |>
  dplyr::mutate(dplyr::across(-twin_id, ~dplyr::coalesce(.x, 0L)))
```

```{r}
# Ensure required objects exist
if (!exists("composite_diseases")) {
  composite_diseases <- readr::read_csv(input_diagnosis_file)
}
if (!exists("organ_age_mortality")) {
  organ_age_mortality <- readr::read_csv(input_organ_age_file)
}

org_clean <- organ_age_mortality |> janitor::clean_names()

# Define all disease groupings to analyze based on available vectors
label_map <- c(
  cvd_multimorbidity = "Cardiovascular",
  neuropsychiatric_multimorbidity = "Neuropsychiatric",
  digestive_multimorbidity = "Digestive",
  endocrine_multimorbidity = "Endocrine",
  malignancy_multimorbidity = "Malignancy",
  musculoskeletal_multimorbidity = "Musculoskeletal",
  neurosensorial_multimorbidity = "Neurosensorial",
  respiratory_multimorbidity = "Respiratory",
  urological_multimorbidity = "Urological"
)

available_group_names <- names(group_vectors)
disease_groupings <- as.list(unname(label_map[available_group_names]))
names(disease_groupings) <- available_group_names

# Get organ age predictors for univariate models (include all organs)
predictors_uni <- org_clean |>
  dplyr::select(-twin_id) |>
  names()

# Get organ age predictors for multivariate models (excluding ovary and prostate)
predictors_mv <- org_clean |>
  dplyr::select(-twin_id) |>
  names() |>
  (
    function(nms) nms[!grepl("ovary|prostate", nms, ignore.case = TRUE)]
  )()

# Define consistent outcome order for all heatmaps
outcome_order_standard <- c(
  "Cardiovascular",
  "Neuropsychiatric", 
  "Digestive",
  "Endocrine",
  "Malignancy",
  "Musculoskeletal",
  "Neurosensorial",
  "Respiratory",
  "Urological"
)

# NB model with cluster-robust standard errors
fit_nb_uni <- function(data, outcome, predictor) {
  # Handle sex-specific organs
  if (grepl("ovary", predictor, ignore.case = TRUE)) {
    # Filter to females
    data <- data |> dplyr::filter(sex == 2, !is.na(!!rlang::sym(predictor)))
  } else if (grepl("prostate", predictor, ignore.case = TRUE)) {
    # Filter to males
    data <- data |> dplyr::filter(sex == 1, !is.na(!!rlang::sym(predictor)))
  } else {
    # Remove missing values for this organ
    data <- data |> dplyr::filter(!is.na(!!rlang::sym(predictor)))
  }
  
  # Check for sufficient data and variation
  if (nrow(data) < 10) {
    return(tibble::tibble(
      outcome = outcome,
      organ_age = predictor,
      irr = NA_real_,
      ci_low = NA_real_,
      ci_high = NA_real_,
      p_value = NA_real_,
      aic = NA_real_,
      n = nrow(data)
    ))
  }
  
  # For sex-specific organs, don't include sex as a covariate
  if (grepl("ovary|prostate", predictor, ignore.case = TRUE)) {
    fml <- stats::as.formula(paste(outcome, "~", predictor, "+", covariate_formula_terms_nosex))
  } else {
    # Check if sex has sufficient variation for non-sex-specific organs
    if (length(unique(data$sex)) < 2) {
      return(tibble::tibble(
        outcome = outcome,
        organ_age = predictor,
        irr = NA_real_,
        ci_low = NA_real_,
        ci_high = NA_real_,
        p_value = NA_real_,
        aic = NA_real_,
        n = nrow(data)
      ))
    }
    fml <- stats::as.formula(paste(outcome, "~", predictor, "+", covariate_formula_terms))
  }
  
  # Fit model with error handling
  mdl <- tryCatch({
    MASS::glm.nb(fml, data = data)
  }, error = function(e) {
    return(NULL)
  })
  
  if (is.null(mdl)) {
    return(tibble::tibble(
      outcome = outcome,
      organ_age = predictor,
      irr = NA_real_,
      ci_low = NA_real_,
      ci_high = NA_real_,
      p_value = NA_real_,
      aic = NA_real_,
      n = nrow(data)
    ))
  }
  
  # Try cluster-robust SE by pair_id if present
  vc <- tryCatch(sandwich::vcovCL(mdl, cluster = data$pair_id), error = function(e) NULL)
  if (!is.null(vc)) {
    ct <- tryCatch(lmtest::coeftest(mdl, vcov. = vc), error = function(e) NULL)
    if (!is.null(ct) && predictor %in% rownames(ct)) {
      est <- ct[predictor, "Estimate"]
      se <- ct[predictor, "Std. Error"]
      pval <- ct[predictor, "Pr(>|z|)"]
    } else {
      est <- NA_real_; se <- NA_real_; pval <- NA_real_
    }
  } else {
    sm <- tryCatch(summary(mdl)$coefficients, error = function(e) NULL)
    if (!is.null(sm) && predictor %in% rownames(sm)) {
      est <- sm[predictor, "Estimate"]; se <- sm[predictor, "Std. Error"]; pval <- sm[predictor, "Pr(>|z|)"]
    } else {
      est <- NA_real_; se <- NA_real_; pval <- NA_real_
    }
  }
  
  tibble::tibble(
    outcome = outcome,
    organ_age = predictor,
    irr = exp(est),
    ci_low = exp(est - 1.96 * se),
    ci_high = exp(est + 1.96 * se),
    p_value = pval,
    aic = stats::AIC(mdl),
    n = stats::nobs(mdl)
  )
}

# Loop through all disease groupings
nb_all_results <- purrr::map_dfr(names(disease_groupings), function(outcome_var) {
  # Create dataset for this outcome
  df_outcome <- twins |>
    dplyr::select(twin_id, pair_id, age, sex, edyrs, eversmok, bmi, hba1c, total_hdl_ratio, crp) |>
    dplyr::left_join(mm_counts_full |> dplyr::select(twin_id, !!outcome_var), by = "twin_id") |>
    dplyr::mutate(
      !!outcome_var := dplyr::coalesce(!!rlang::sym(outcome_var), 0L),
      sex = as.factor(sex)
    ) |>
    dplyr::left_join(org_clean, by = "twin_id")
  
  # Fit models for all predictors
  purrr::map_dfr(predictors_uni, ~fit_nb_uni(df_outcome, outcome_var, .x))
})

# Format results
nb_all_results <- nb_all_results |>
  dplyr::arrange(outcome, aic) |>
  dplyr::group_by(outcome) |>
  dplyr::mutate(
    irr = round(irr, 3),
    ci_low = round(ci_low, 3),
    ci_high = round(ci_high, 3),
    aic = round(aic, 1),
    p_value = signif(p_value, 3),
    fdr = p.adjust(p_value, method = "fdr")
  ) |>
  dplyr::ungroup()
```

# Overall Burden vs Organ Aging

```{r}
# Prepare data for overall multimorbidity burden plot
# Join multimorbidity counts with organ ages
burden_data <- mm_counts_full |>
  dplyr::left_join(org_clean, by = "twin_id")

# Calculate total baseline multimorbidity count (sum across all disease groupings)
disease_group_cols <- names(mm_counts_full)[names(mm_counts_full) != "twin_id"]
burden_data <- burden_data |>
  dplyr::mutate(
    total_mm_count = rowSums(dplyr::across(dplyr::all_of(disease_group_cols)), na.rm = TRUE)
  )

# Calculate mean standardized organ age per individual
# Exclude sex-specific organs (Ovary, Prostate) for overall mean
organ_cols <- org_clean |>
  dplyr::select(-twin_id) |>
  names()
organ_cols_exclude_sex <- organ_cols[!grepl("ovary|prostate", organ_cols, ignore.case = TRUE)]

burden_data <- burden_data |>
  dplyr::rowwise() |>
  dplyr::mutate(
    mean_organ_age = mean(dplyr::c_across(dplyr::all_of(organ_cols_exclude_sex)), na.rm = TRUE)
  ) |>
  dplyr::ungroup() |>
  dplyr::filter(!is.na(mean_organ_age), is.finite(mean_organ_age))

# Categorize total multimorbidity count into bins
burden_data <- burden_data |>
  dplyr::mutate(
    mm_count_cat = dplyr::case_when(
      total_mm_count == 0 ~ "0",
      total_mm_count == 1 ~ "1",
      total_mm_count == 2 ~ "2",
      total_mm_count == 3 ~ "3",
      total_mm_count == 4 ~ "4",
      total_mm_count >= 5 ~ "≥5",
      TRUE ~ NA_character_
    ),
    mm_count_cat = factor(mm_count_cat, levels = c("0", "1", "2", "3", "4", "≥5"))
  )

# Calculate summary statistics by multimorbidity count category
burden_summary <- burden_data |>
  dplyr::group_by(mm_count_cat) |>
  dplyr::summarise(
    n = dplyr::n(),
    mean_organ_age = mean(mean_organ_age, na.rm = TRUE),
    se_organ_age = sd(mean_organ_age, na.rm = TRUE) / sqrt(n),
    ci_low = mean_organ_age - 1.96 * se_organ_age,
    ci_high = mean_organ_age + 1.96 * se_organ_age,
    .groups = "drop"
  ) |>
  dplyr::filter(!is.na(mm_count_cat))

# Create publication plot
burden_plot <- burden_summary |>
  ggplot2::ggplot(ggplot2::aes(x = mm_count_cat, y = mean_organ_age)) +
  # Reference line at y=0 (very light grey)
  ggplot2::geom_hline(yintercept = 0, color = "grey85", linewidth = 0.3, linetype = "solid") +
  # Bars: desaturated blue, narrower with more spacing
  ggplot2::geom_col(fill = "#6B8FA3", alpha = 0.85, width = 0.45) +
  # Error bars: light grey, thin, no caps
  ggplot2::geom_errorbar(
    ggplot2::aes(ymin = ci_low, ymax = ci_high),
    width = 0.15,
    linewidth = 0.4,
    color = "grey50"
  ) +
  # Add sample size labels below x-axis labels
  ggplot2::geom_text(
    data = burden_summary,
    ggplot2::aes(x = mm_count_cat, y = -Inf, label = paste0("(n=", n, ")")),
    vjust = 2.5,
    size = 3.2,
    color = "grey50",
    inherit.aes = FALSE
  ) +
  ggplot2::labs(
    x = "Baseline multimorbidity count",
    y = "Mean organ age"
  ) +
  ggplot2::theme_minimal(base_size = 14) +
  ggplot2::theme(
    panel.grid.minor = ggplot2::element_blank(),
    panel.grid.major.x = ggplot2::element_blank(),
    panel.grid.major.y = ggplot2::element_line(color = "grey95", linewidth = 0.3),
    legend.position = "none",
    axis.title = ggplot2::element_text(size = 14, face = "plain"),
    axis.text.x = ggplot2::element_text(size = 12, color = "black", hjust = 0.5),
    axis.text.y = ggplot2::element_text(size = 12, color = "black"),
    plot.margin = ggplot2::margin(b = 25, unit = "pt")
  )

print(burden_plot)

# Save figure
dir.create(file.path(output_multimorbidity_core_dir, "other"), 
           recursive = TRUE, showWarnings = FALSE)
ggplot2::ggsave(
  filename = file.path(output_multimorbidity_core_dir, "other", 
                       "overall_mm_burden_organ_aging.pdf"),
  plot = burden_plot,
  width = 6,
  height = 4,
  dpi = 300
)
ggplot2::ggsave(
  filename = file.path(output_multimorbidity_core_dir, "other", 
                       "overall_mm_burden_organ_aging.png"),
  plot = burden_plot,
  width = 6,
  height = 4,
  dpi = 300
)
ggplot2::ggsave(
  filename = file.path(output_multimorbidity_core_dir, "other", 
                       "overall_mm_burden_organ_aging.svg"),
  plot = burden_plot,
  width = 6,
  height = 4
)
```

```{r}
# Panel C: Trend plot - dose-response relationship
# Convert categorical to numeric ordinal for smooth trend fitting
burden_summary_numeric <- burden_summary |>
  dplyr::mutate(
    mm_count_numeric = dplyr::case_when(
      mm_count_cat == "0" ~ 0,
      mm_count_cat == "1" ~ 1,
      mm_count_cat == "2" ~ 2,
      mm_count_cat == "3" ~ 3,
      mm_count_cat == "4" ~ 4,
      mm_count_cat == "≥5" ~ 5,
      TRUE ~ NA_real_
    )
  ) |>
  dplyr::filter(!is.na(mm_count_numeric))

# Create Panel C trend plot
burden_trend_plot <- burden_summary_numeric |>
  ggplot2::ggplot(ggplot2::aes(x = mm_count_numeric, y = mean_organ_age)) +
  # Reference line at y=0 (thin, neutral grey)
  ggplot2::geom_hline(yintercept = 0, color = "grey75", linewidth = 0.25, linetype = "solid") +
  # Lollipop stems from 0 to mean (light grey)
  ggplot2::geom_segment(
    ggplot2::aes(x = mm_count_numeric, xend = mm_count_numeric, y = 0, yend = mean_organ_age),
    color = "grey40",
    linewidth = 0.5,
    alpha = 0.6
  ) +
  # Points for mean organ age per category (gradient: darker as organ age increases)
  ggplot2::geom_point(
    ggplot2::aes(color = mean_organ_age),
    size = 4.5,
    alpha = 1
  ) +
  # Sample size labels below x-axis
  ggplot2::geom_text(
    data = burden_summary_numeric,
    ggplot2::aes(x = mm_count_numeric, y = -Inf, label = paste0("(n=", n, ")")),
    vjust = 2.5,
    size = 3.2,
    color = "grey50",
    inherit.aes = FALSE
  ) +
  ggplot2::scale_x_continuous(
    breaks = 0:5,
    labels = c("0", "1", "2", "3", "4", "5+")
  ) +
  ggplot2::scale_color_gradient(
    low = "#6BA3D1",
    high = "#2166AC",
    guide = "none"
  ) +
  ggplot2::labs(
    x = "Baseline multimorbidity count",
    y = "Mean organ age"
  ) +
  ggplot2::theme_minimal(base_size = 14) +
  ggplot2::theme(
    panel.grid.minor = ggplot2::element_blank(),
    panel.grid.major.x = ggplot2::element_blank(),
    panel.grid.major.y = ggplot2::element_blank(),
    legend.position = "none",
    axis.title = ggplot2::element_text(size = 14, face = "plain"),
    axis.text.x = ggplot2::element_text(size = 12, color = "black", hjust = 0.5),
    axis.text.y = ggplot2::element_text(size = 12, color = "black"),
    plot.margin = ggplot2::margin(t = 15, r = 15, b = 30, l = 15, unit = "pt")
  )

print(burden_trend_plot)

c_width <- 4

# Save figure
ggplot2::ggsave(
  filename = file.path(output_multimorbidity_core_dir, "other", 
                       "overall_mm_burden_organ_aging_trend.pdf"),
  plot = burden_trend_plot,
  width = c_width,
  height = 4,
  dpi = 300
)
ggplot2::ggsave(
  filename = file.path(output_multimorbidity_core_dir, "other", 
                       "overall_mm_burden_organ_aging_trend.png"),
  plot = burden_trend_plot,
  width = c_width,
  height = 4,
  dpi = 300
)
ggplot2::ggsave(
  filename = file.path(output_multimorbidity_core_dir, "other", 
                       "overall_mm_burden_organ_aging_trend.svg"),
  plot = burden_trend_plot,
  width = c_width,
  height = 4
)
```

```{r}
# Summary of results by disease grouping
nb_summary <- nb_all_results |>
  dplyr::group_by(outcome) |>
  dplyr::summarise(
    n_models = n(),
    min_aic = min(aic, na.rm = TRUE),
    max_aic = max(aic, na.rm = TRUE),
    significant_models = sum(p_value < 0.05, na.rm = TRUE),
    fdr_significant = sum(fdr < 0.05, na.rm = TRUE),
    .groups = "drop"
  ) |>
  dplyr::mutate(
    outcome_clean = disease_groupings[outcome] |> unlist()
  )

# Summary
nb_summary |>
  dplyr::select(outcome_clean, n_models, significant_models, fdr_significant) |>
  kableExtra::kable(col.names = c("Disease Group", "Models", "Significant (p<0.05)", "FDR Significant")) |>
  kableExtra::kable_styling()
```

```{r}
# Control variables for heatmap appearance
HEATMAP_TEXT_SIZE <- 14
HEATMAP_SQUARE_SIZE_DIVISOR <- 12

# Prepare data for heatmap with all disease groupings
heatmap_df <- nb_all_results |>
  dplyr::mutate(
    outcome_clean = disease_groupings[outcome] |> unlist(),
    organ_age_clean = stringr::str_replace_all(organ_age, "_", " ") |> stringr::str_to_title(),
    effect_size = irr,
    significance = dplyr::case_when(
      is.na(fdr) ~ "",
      fdr < 0.001 ~ "***",
      fdr < 0.01 ~ "**",
      fdr < 0.05 ~ "*",
      TRUE ~ ""
    ),
    effect_size_colored = dplyr::if_else(significance != "", effect_size, NA_real_),
    non_sig_marker = dplyr::if_else(significance == "", "×", "")
  ) |>
  dplyr::select(outcome_clean, organ_age_clean, effect_size, effect_size_colored, significance, non_sig_marker) |>
  dplyr::filter(!is.na(effect_size))

# Create consistent organ order
preferred_order <- c(
  "Brain", "Heart", "Kidney And Bladder", "Liver", "Lung",
  "Muscle", "Pancreas", "Gastrointestinal Tract", "Ovary", "Prostate"
)

all_organs <- unique(heatmap_df$organ_age_clean)
available_preferred <- intersect(preferred_order, all_organs)
other_organs <- setdiff(all_organs, preferred_order)
static_organ_order <- c(available_preferred, other_organs)

# Use standard outcome order for consistency
plot_df <- heatmap_df |>
  dplyr::mutate(
    outcome_clean = factor(outcome_clean, levels = outcome_order_standard),
    organ_age_clean = factor(organ_age_clean, levels = static_organ_order)
  )

if (length(unique(plot_df$outcome_clean)) == 0 || length(unique(plot_df$organ_age_clean)) == 0) {
  heatmap_plot <- NULL
} else {
  # Panel-style control variables
  text_size_pt <- HEATMAP_TEXT_SIZE
  square_size <- text_size_pt / HEATMAP_SQUARE_SIZE_DIVISOR
  
  # Calculate dynamic range (white-to-red only, no negative values)
  # Use effect_size (all values) not effect_size_colored (only significant) to capture full range
  effect_range <- range(log(plot_df$effect_size), na.rm = TRUE)
  buffer <- 0.1
  max_limit <- max(1.5, effect_range[2] + buffer)
  min_limit <- 0  # Start from 0 since no negative values
  
  breaks <- seq(0, max_limit, length.out = 4)
  labels <- sprintf("%.1f", breaks)
  
  # Prepare data with numeric coordinates
  plot_df <- plot_df |>
    dplyr::mutate(
      outcome_num = (as.numeric(outcome_clean) - 1) * square_size + square_size/2,
      organ_num = (as.numeric(organ_age_clean) - 1) * square_size + square_size/2
    )
  
  outcome_order <- levels(plot_df$outcome_clean)
  organ_order <- levels(plot_df$organ_age_clean)
  
  # Heatmap: use IRR for color; only significant cells get color, non-significant get an "×" on white
  heatmap_plot <- ggplot2::ggplot(plot_df, ggplot2::aes(x = organ_num, y = outcome_num, fill = log(effect_size_colored))) +
    ggplot2::geom_tile(width = square_size, height = square_size, color = NA) +
    ggplot2::geom_text(ggplot2::aes(x = organ_num, y = outcome_num, label = non_sig_marker), size = 5.5, color = "darkgrey", family = "Helvetica", inherit.aes = FALSE) +
    ggplot2::scale_fill_gradientn(
      colors = c(
        "white",        # Start at 0
        "#C64D4D",      # Red (mid-high)
        "#B71C1C"       # Darker red (extreme high)
      ),
      values = scales::rescale(c(0, max_limit * 0.5, max_limit)),
      limits = c(0, max_limit),
      na.value = "white",
      name = "log(IRR)",
      breaks = breaks,
      labels = labels
    ) +
    ggplot2::scale_x_continuous(
      breaks = (seq_along(organ_order) - 1) * square_size + square_size/2,
      labels = organ_order,
      expand = c(0, 0),
      limits = c(-square_size/2, length(organ_order) * square_size + square_size/2)
    ) +
    ggplot2::scale_y_continuous(
      breaks = (seq_along(outcome_order) - 1) * square_size + square_size/2,
      labels = outcome_order,
      expand = c(0, 0),
      limits = c(-square_size/2, length(outcome_order) * square_size + square_size/2)
    ) +
    ggplot2::theme_minimal(base_family = "Helvetica") +
    ggplot2::theme(
      text = ggplot2::element_text(family = "Helvetica", color = "black"),
      plot.title = ggplot2::element_text(size = 16, face = "bold"),
      plot.subtitle = ggplot2::element_text(size = 12),
      axis.text.x = ggplot2::element_text(angle = 45, hjust = 1, size = HEATMAP_TEXT_SIZE, color = "black", family = "Helvetica"),
      axis.text.y = ggplot2::element_text(size = HEATMAP_TEXT_SIZE, hjust = 0, margin = ggplot2::margin(r = 10), color = "black", family = "Helvetica"),
      axis.title = ggplot2::element_blank(),
      axis.ticks = ggplot2::element_blank(),
      legend.position = "right",
      legend.title = ggplot2::element_text(size = 11, color = "black", family = "Helvetica"),
      legend.text = ggplot2::element_text(size = 9, color = "black", family = "Helvetica"),
      legend.key.height = grid::unit(0.8, "cm"),
      legend.key.width = grid::unit(0.5, "cm"),
      panel.grid = ggplot2::element_blank(),
      panel.spacing = grid::unit(0, "lines"),
      panel.border = ggplot2::element_blank(),
      plot.margin = ggplot2::margin(0.5, 0.5, 0.5, 0.5, "cm")
    ) +
    ggplot2::coord_fixed(ratio = 1, expand = FALSE)
}

print(heatmap_plot)

# Save heatmap
dir.create(file.path(output_multimorbidity_core_dir, "nb", "main"), recursive = TRUE, showWarnings = FALSE)
if (!is.null(heatmap_plot)) {
  ggplot2::ggsave(
    filename = file.path(output_multimorbidity_core_dir, "nb", "main", "nb_full_main_irr_heatmap.svg"),
    plot = heatmap_plot,
    width = 10,
    height = 8,
    dpi = 300
  )
}
```

## Forest tables (helpers)
```{r nb_ag_forest_helpers}
make_bw_forest_table <- function(df, organ_col, eff_col, low_col, high_col, fdr_col, title, main_color = "black", x_upper_cap = 3, axis_label = "Hazard Ratio (95% CI)") {
  d <- df |>
    dplyr::mutate(
      hr = .data[[eff_col]],
      hr_lower = .data[[low_col]],
      hr_upper = .data[[high_col]],
      fdr = .data[[fdr_col]],
      significant = fdr < 0.05,
      errorbar_color = if_else(fdr < 0.05, "grey30", "gray80"),
      Organ_Display = .data[[organ_col]]
    ) |>
    dplyr::filter(is.finite(hr), is.finite(hr_lower), is.finite(hr_upper)) |>
    dplyr::arrange(dplyr::desc(hr)) |>
    dplyr::mutate(y_pos = rev(dplyr::row_number()), Organ_Display = factor(Organ_Display, levels = Organ_Display))

  if (nrow(d) == 0) return(NULL)

  # Dynamic x-axis limits with hard caps
  base_min <- 0.25
  base_max <- 3
  hard_min <- 0.05
  hard_max <- 10
  
  x_min <- suppressWarnings(min(d$hr_lower, na.rm = TRUE))
  x_max <- suppressWarnings(max(d$hr_upper, na.rm = TRUE))
  
  if (!is.finite(x_min)) x_min <- base_min
  if (!is.finite(x_max)) x_max <- base_max
  
  x_min <- max(x_min, 0.001)
  
  lower_margin_factor <- 0.9
  upper_margin_factor <- 1.1
  
  x_min <- min(base_min, x_min * lower_margin_factor)
  x_max <- max(base_max, x_max * upper_margin_factor)
  
  x_min <- max(hard_min, x_min)
  x_max <- min(hard_max, x_max)
  
  x_breaks <- pretty(c(x_min, x_max), n = 6)
  x_breaks <- x_breaks[x_breaks >= x_min & x_breaks <= x_max]
  
  # Add scientific notation formatting
  d <- d |>
    dplyr::mutate(
      use_sci = pmax(abs(hr), abs(hr_lower), abs(hr_upper), na.rm = TRUE) >= 10,
      use_sci = if_else(is.na(use_sci), FALSE, use_sci),
      hr_formatted = if_else(
        use_sci,
        sprintf("%.1e (%.1e-%.1e)", hr, hr_lower, hr_upper),
        sprintf("%.2f (%.2f-%.2f)", hr, hr_lower, hr_upper)
      )
    )
  
  # Detect if we need wider table for scientific notation
  has_sci_notation <- any(d$use_sci, na.rm = TRUE)
  table_width_ratio <- if (has_sci_notation) 3.2 else 2.5
  
  # Create table data
  tab <- d |>
    dplyr::transmute(y_pos, `Organ age` = Organ_Display, `Effect (95% CI)` = hr_formatted, `FDR` = sprintf("%.2e", fdr))

  x_pos <- tibble::tibble(col = c("Organ age", "Effect (95% CI)", "FDR"), x = c(1.0, 4.0, 7.5))
  table_long <- tab |>
    tidyr::pivot_longer(-y_pos, names_to = "col", values_to = "val") |>
    dplyr::left_join(x_pos, by = "col")

  p_table <- ggplot2::ggplot(table_long, ggplot2::aes(x = x, y = y_pos, label = val)) +
    ggplot2::geom_text(hjust = c(0, 0, 1)[match(table_long$col, x_pos$col)], size = 3) +
    ggplot2::geom_text(data = x_pos |> dplyr::mutate(y_pos = max(d$y_pos) + 1), ggplot2::aes(x = x, y = y_pos, label = col), hjust = c(0, 0, 1), fontface = "bold", inherit.aes = FALSE, size = 3.3) +
    ggplot2::scale_y_continuous(breaks = NULL, labels = NULL, limits = c(0.5, max(d$y_pos) + 1.5)) +
    ggplot2::scale_x_continuous(limits = c(0.5, 9.0), expand = c(0, 0)) +
    ggplot2::labs(title = title) +
    ggplot2::theme_minimal(base_size = 11) +
    ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.1, size = 12), axis.title = ggplot2::element_blank(), axis.text.x = ggplot2::element_blank(), axis.ticks = ggplot2::element_blank(), panel.grid = ggplot2::element_blank(), plot.margin = grid::unit(c(12, 6, 6, 6), "pt"))

  # Determine which points are out of bounds and cap CIs to plot range
  d <- d |>
    dplyr::mutate(
      out_of_bounds_point = hr < x_min | hr > x_max,
      hr_lower_capped = pmax(hr_lower, x_min),
      hr_upper_capped = pmin(hr_upper, x_max),
      has_any_value_outside = (hr < x_min | hr > x_max | hr_lower < x_min | hr_upper > x_max)
    )
  
  # Only plot data where the effect size itself is within bounds
  data_in_bounds <- d |> dplyr::filter(!out_of_bounds_point)
  
  # Calculate legend positions
  legend_y <- max(d$y_pos) + 1.5
  legend_left_x <- x_min + (x_max - x_min) * 0.03
  legend_right_x <- x_min + (x_max - x_min) * 0.60
  legend_bottom_y <- 0.25
  legend_bottom_x <- x_min + (x_max - x_min) * 0.60

  p_forest <- ggplot2::ggplot(d, ggplot2::aes(y = y_pos)) +
    ggplot2::geom_rect(ggplot2::aes(xmin = -Inf, xmax = Inf, ymin = y_pos - 0.5, ymax = y_pos + 0.5, fill = factor(seq_along(Organ_Display) %% 2)), alpha = 0.6, show.legend = FALSE) +
    ggplot2::scale_fill_manual(values = c("0" = "transparent", "1" = "gray95")) +
    ggplot2::geom_segment(ggplot2::aes(x = 1, xend = 1, y = 0.5, yend = max(d$y_pos) + 0.75), linetype = "33", color = "grey10", linewidth = 0.7) +
    {if (nrow(data_in_bounds) > 0) ggplot2::geom_errorbarh(data = data_in_bounds, ggplot2::aes(xmin = hr_lower_capped, xmax = hr_upper_capped), color = data_in_bounds$errorbar_color, height = 0.15, linewidth = 0.6)} +
    {if (nrow(data_in_bounds) > 0) ggplot2::geom_point(data = data_in_bounds, ggplot2::aes(x = hr, color = significant), size = 2.5, shape = 16)} +
    {if (nrow(data_in_bounds |> dplyr::filter(has_any_value_outside)) > 0) ggplot2::geom_text(data = data_in_bounds |> dplyr::filter(has_any_value_outside), ggplot2::aes(x = hr, y = y_pos + 0.25), label = "*", size = 3.5, color = "black")} +
    ggplot2::annotate("text", x = legend_left_x, y = legend_y, label = "● Significant (FDR < 0.05)", hjust = 0, size = 2.6, color = main_color) +
    ggplot2::annotate("text", x = legend_right_x, y = legend_y, label = "● Non-significant", hjust = 0, size = 2.6, color = "gray80") +
    {if (nrow(data_in_bounds |> dplyr::filter(has_any_value_outside)) > 0) ggplot2::annotate("text", x = legend_bottom_x, y = legend_bottom_y, label = "* Value outside plot range", hjust = 1, size = 2.4, color = "black")} +
    ggplot2::scale_color_manual(values = c("TRUE" = main_color, "FALSE" = "gray80")) +
    ggplot2::scale_x_continuous(
      limits = c(x_min, x_max),
      breaks = x_breaks,
      labels = format(x_breaks, digits = 3, trim = TRUE)
    ) +
    ggplot2::scale_y_continuous(breaks = NULL, labels = NULL, limits = c(0.2, max(d$y_pos) + 1.5)) +
    ggplot2::labs(x = axis_label, y = NULL) +
    ggplot2::theme_minimal(base_size = 11) +
    ggplot2::theme(axis.text.y = ggplot2::element_blank(), axis.text.x = ggplot2::element_text(size = 9), axis.title.x = ggplot2::element_text(size = 10), panel.grid.major.y = ggplot2::element_blank(), panel.grid.minor = ggplot2::element_blank(), panel.grid.major.x = ggplot2::element_blank(), plot.margin = grid::unit(c(12, 12, 6, 0), "pt"), legend.position = "none") +
    ggplot2::coord_cartesian(clip = "off")

  p_table + p_forest + patchwork::plot_layout(widths = c(table_width_ratio, 1.5))
}

clean_organ_display <- function(x) {
  dplyr::case_when(
    x == "Gastrointestinal_tract" ~ "Gastrointestinal",
    x == "Kidney_urinary" ~ "Kidney and Bladder",
    TRUE ~ stringr::str_to_title(stringr::str_replace_all(x, "_", " "))
  )
}
```

## Forest tables: NB main
```{r nb_forest_tables_main}
# NB main
if (exists("nb_all_results") && nrow(nb_all_results) > 0) {
  out_keys <- unique(nb_all_results$outcome)
  dir.create(file.path(output_multimorbidity_core_dir, "nb", "main"), recursive = TRUE, showWarnings = FALSE)
  purrr::walk(out_keys, function(ok) {
    df <- nb_all_results |>
      dplyr::filter(outcome == ok) |>
      dplyr::mutate(Organ_Display = clean_organ_display(organ_age))
    p <- make_bw_forest_table(df, organ_col = "Organ_Display", eff_col = "irr", low_col = "ci_low", high_col = "ci_high", fdr_col = "fdr", title = unname(disease_groupings[ok]), axis_label = "Incidence Rate Ratio (95% CI)")
    if (!is.null(p)) {
      fn <- paste0("nb_forest_", stringr::str_replace_all(tolower(unname(disease_groupings[ok])), " ", "_"), ".svg")
      ggplot2::ggsave(filename = fn, plot = p, path = file.path(output_multimorbidity_core_dir, "nb", "main"), device = "svg", width = 7, height = 5, dpi = 300)
    }
  })
  
  # Create CSV tables directory
  csv_dir <- file.path(output_multimorbidity_core_dir, "nb", "main", "tables")
  dir.create(csv_dir, showWarnings = FALSE, recursive = TRUE)
  
  # Save table data as CSV
  purrr::walk(out_keys, function(ok) {
    csv_data <- nb_all_results |>
      dplyr::filter(outcome == ok) |>
      dplyr::mutate(
        use_sci = pmax(abs(irr), abs(ci_low), abs(ci_high), na.rm = TRUE) >= 10,
        use_sci = if_else(is.na(use_sci), FALSE, use_sci),
        irr_formatted = if_else(use_sci,
          sprintf("%.1e (%.1e-%.1e)", irr, ci_low, ci_high),
          sprintf("%.2f (%.2f-%.2f)", irr, ci_low, ci_high)),
        Organ_Display = clean_organ_display(organ_age)
      ) |>
      dplyr::select(Organ = Organ_Display, `Effect (95% CI)` = irr_formatted, FDR = fdr)
    
    if (nrow(csv_data) > 0) {
      fn <- paste0("nb_", stringr::str_replace_all(tolower(unname(disease_groupings[ok])), " ", "_"), ".csv")
      write.csv(csv_data, file = file.path(csv_dir, fn), row.names = FALSE)
    }
  })
}
```

# Within-Pair Negative Binomial Models

```{r}
# Within-pair NB fitting functions
fit_nb_uni_within <- function(data, outcome, predictor) {
  # Handle sex-specific organs
  if (grepl("ovary", predictor, ignore.case = TRUE)) {
    # Filter to females
    data <- data |> dplyr::filter(sex == 2, !is.na(!!rlang::sym(predictor)))
  } else if (grepl("prostate", predictor, ignore.case = TRUE)) {
    # Filter to males
    data <- data |> dplyr::filter(sex == 1, !is.na(!!rlang::sym(predictor)))
  } else {
    # Remove missing values for this organ
    data <- data |> dplyr::filter(!is.na(!!rlang::sym(predictor)))
  }
  
  # skip if no within-pair variation in predictor or outcome
  if (!("pair_id" %in% names(data))) return(tibble::tibble())
  by_pair <- data |>
    dplyr::group_by(pair_id) |>
    dplyr::summarise(var_pred = stats::var(.data[[predictor]], na.rm = TRUE), var_out = stats::var(.data[[outcome]], na.rm = TRUE), .groups = "drop")
  if (all(is.na(by_pair$var_pred)) || sum(by_pair$var_pred > 0, na.rm = TRUE) == 0) return(tibble::tibble())
  if (all(is.na(by_pair$var_out)) || sum(by_pair$var_out > 0, na.rm = TRUE) == 0) return(tibble::tibble())
  
  fml <- stats::as.formula(paste(outcome, "~", predictor, "+", covariate_formula_terms_nosex))
  mdl <- tryCatch({
    MASS::glm.nb(fml, data = data)
  }, error = function(e) {
    return(NULL)
  })
  
  if (is.null(mdl)) return(tibble::tibble())
  
  # Try cluster-robust SE by pair_id if present
  vc <- tryCatch(sandwich::vcovCL(mdl, cluster = data$pair_id), error = function(e) NULL)
  if (!is.null(vc)) {
    ct <- lmtest::coeftest(mdl, vcov. = vc)
    if (predictor %in% rownames(ct)) {
      est <- ct[predictor, "Estimate"]
      se <- ct[predictor, "Std. Error"]
      pval <- ct[predictor, "Pr(>|z|)"]
    } else {
      est <- NA_real_; se <- NA_real_; pval <- NA_real_
    }
  } else {
    sm <- summary(mdl)$coefficients
    if (predictor %in% rownames(sm)) {
      est <- sm[predictor, "Estimate"]; se <- sm[predictor, "Std. Error"]; pval <- sm[predictor, "Pr(>|z|)"]
    } else {
      est <- NA_real_; se <- NA_real_; pval <- NA_real_
    }
  }
  
  tibble::tibble(
    outcome = outcome,
    organ_age = predictor,
    irr = exp(est),
    ci_low = exp(est - 1.96 * se),
    ci_high = exp(est + 1.96 * se),
    p_value = pval,
    aic = stats::AIC(mdl),
    n = stats::nobs(mdl)
  )
}

# Run within-pair NB univariate and multivariate for all groupings
nb_wp_uni_group_results <- purrr::map_dfr(names(disease_groupings), function(outcome_var) {
  df_outcome <- twins |>
    dplyr::select(twin_id, pair_id, age, sex, edyrs, eversmok, bmi, hba1c, total_hdl_ratio, crp) |>
    dplyr::left_join(mm_counts_full |> dplyr::select(twin_id, !!outcome_var), by = "twin_id") |>
    dplyr::mutate(
      !!outcome_var := dplyr::coalesce(!!rlang::sym(outcome_var), 0L),
      sex = as.factor(sex)
    ) |>
    dplyr::left_join(org_clean, by = "twin_id")
  
  purrr::map_dfr(predictors_uni, ~fit_nb_uni_within(df_outcome, outcome_var, .x))
}) |>
  dplyr::group_by(outcome) |>
  dplyr::mutate(fdr = p.adjust(p_value, method = "fdr")) |>
  dplyr::ungroup() |>
  dplyr::mutate(
    outcome_clean = disease_groupings[outcome] |> unlist(),
    organ_age_clean = stringr::str_replace_all(organ_age, "_", " ") |> stringr::str_to_title()
  )
```

```{r}
# Heatmaps for within-pair NB
make_nb_wp_heatmap <- function(df, title_suffix) {
  if (nrow(df) == 0) return(NULL)
  preferred_order <- c(
    "Brain", "Heart", "Kidney And Bladder", "Liver", "Lung",
    "Muscle", "Pancreas", "Gastrointestinal Tract"
  )
  all_orgs <- unique(df$organ_age_clean)
  available_pref <- intersect(preferred_order, all_orgs)
  other_orgs <- setdiff(all_orgs, preferred_order)
  organ_order <- c(available_pref, other_orgs)
  
  # Get available outcomes and filter to standard order
  available_outcomes <- unique(df$outcome_clean)
  outcome_order <- intersect(outcome_order_standard, available_outcomes)
  
  if (length(outcome_order) == 0 || length(organ_order) == 0) return(NULL)
  
  # Panel-style control variables
  text_size_pt <- HEATMAP_TEXT_SIZE
  square_size <- text_size_pt / HEATMAP_SQUARE_SIZE_DIVISOR
  
  plot_df <- df |>
    dplyr::mutate(
      outcome_clean = factor(outcome_clean, levels = outcome_order),
      organ_age_clean = factor(organ_age_clean, levels = organ_order),
      outcome_num = (as.numeric(outcome_clean) - 1) * square_size + square_size/2,
      organ_num = (as.numeric(organ_age_clean) - 1) * square_size + square_size/2,
      effect_size_colored = dplyr::if_else(fdr < 0.05, irr, NA_real_),
      non_sig_marker = dplyr::if_else(fdr < 0.05, "", "×")
    )
  
  # Calculate dynamic range (white-to-red only, no negative values)
  # Use irr (all values) not effect_size_colored (only significant) to capture full range
  effect_range_all <- range(log(plot_df$irr), na.rm = TRUE)
  buffer <- 0.1
  max_limit <- max(1.5, effect_range_all[2] + buffer)
  min_limit <- 0  # Start from 0 since no negative values
  
  breaks <- seq(0, max_limit, length.out = 4)
  labels <- sprintf("%.1f", breaks)
  
  ggplot2::ggplot(plot_df, ggplot2::aes(x = organ_num, y = outcome_num, fill = log(effect_size_colored))) +
    ggplot2::geom_tile(width = square_size, height = square_size, color = NA) +
    ggplot2::geom_text(ggplot2::aes(x = organ_num, y = outcome_num, label = non_sig_marker), size = 5.5, color = "darkgrey", family = "Helvetica", inherit.aes = FALSE) +
    ggplot2::scale_fill_gradientn(
      colors = c(
        "white",        # Start at 0
        "#C64D4D",      # Red (mid-high)
        "#B71C1C"       # Darker red (extreme high)
      ),
      values = scales::rescale(c(0, max_limit * 0.5, max_limit)),
      limits = c(0, max_limit),
      na.value = "white",
      name = "log(IRR)",
      breaks = breaks,
      labels = labels
    ) +
    ggplot2::scale_x_continuous(
      breaks = (seq_along(organ_order) - 1) * square_size + square_size/2,
      labels = organ_order,
      expand = c(0, 0),
      limits = c(-square_size/2, length(organ_order) * square_size + square_size/2)
    ) +
    ggplot2::scale_y_continuous(
      breaks = (seq_along(outcome_order) - 1) * square_size + square_size/2,
      labels = outcome_order,
      expand = c(0, 0),
      limits = c(-square_size/2, length(outcome_order) * square_size + square_size/2)
    ) +
    ggplot2::theme_minimal(base_family = "Helvetica") +
    ggplot2::theme(
      text = ggplot2::element_text(family = "Helvetica", color = "black"),
      axis.text.x = ggplot2::element_text(angle = 45, hjust = 1, size = HEATMAP_TEXT_SIZE, color = "black", family = "Helvetica"),
      axis.text.y = ggplot2::element_text(size = HEATMAP_TEXT_SIZE, hjust = 0, margin = ggplot2::margin(r = 10), color = "black", family = "Helvetica"),
      axis.title = ggplot2::element_blank(),
      axis.ticks = ggplot2::element_blank(),
      legend.position = "right",
      legend.title = ggplot2::element_text(size = 11, color = "black", family = "Helvetica"),
      legend.text = ggplot2::element_text(size = 9, color = "black", family = "Helvetica"),
      legend.key.height = grid::unit(0.8, "cm"),
      legend.key.width = grid::unit(0.5, "cm"),
      panel.grid = ggplot2::element_blank(),
      panel.spacing = grid::unit(0, "lines"),
      panel.border = ggplot2::element_blank(),
      plot.margin = ggplot2::margin(0.5, 0.5, 0.5, 0.5, "cm")
    ) +
    ggplot2::coord_fixed(ratio = 1, expand = FALSE) +
    ggplot2::labs(title = title_suffix)
}

nb_wp_uni_heatmap <- make_nb_wp_heatmap(nb_wp_uni_group_results, NULL)

if (!is.null(nb_wp_uni_heatmap)) print(nb_wp_uni_heatmap)

if (!is.null(nb_wp_uni_heatmap)) {
  dir.create(file.path(output_multimorbidity_core_dir, "nb", "within_pair"), recursive = TRUE, showWarnings = FALSE)
  ggplot2::ggsave(filename = file.path(output_multimorbidity_core_dir, "nb", "within_pair", "nb_full_withinpair_irr_heatmap.svg"), plot = nb_wp_uni_heatmap, width = 10, height = 8, dpi = 300)
}
```

```{r nb_forest_tables_withinpair}
# NB within-pair
if (exists("nb_wp_uni_group_results") && nrow(nb_wp_uni_group_results) > 0) {
  dir.create(file.path(output_multimorbidity_core_dir, "nb", "within_pair"), recursive = TRUE, showWarnings = FALSE)
  out_keys <- unique(nb_wp_uni_group_results$outcome)
  purrr::walk(out_keys, function(ok) {
    df <- nb_wp_uni_group_results |>
      dplyr::filter(outcome == ok) |>
      dplyr::mutate(Organ_Display = clean_organ_display(organ_age))
    p <- make_bw_forest_table(df, organ_col = "Organ_Display", eff_col = "irr", low_col = "ci_low", high_col = "ci_high", fdr_col = "fdr", title = unname(disease_groupings[ok]), axis_label = "Incidence Rate Ratio (95% CI)")
    if (!is.null(p)) {
      fn <- paste0("nb_forest_", stringr::str_replace_all(tolower(unname(disease_groupings[ok])), " ", "_"), "_all_pairs.svg")
      ggplot2::ggsave(filename = fn, plot = p, path = file.path(output_multimorbidity_core_dir, "nb", "within_pair"), device = "svg", width = 7, height = 5, dpi = 300)
    }
  })
  
  # Create CSV tables directory
  csv_dir <- file.path(output_multimorbidity_core_dir, "nb", "within_pair", "tables")
  dir.create(csv_dir, showWarnings = FALSE, recursive = TRUE)
  
  # Save table data as CSV
  purrr::walk(out_keys, function(ok) {
    csv_data <- nb_wp_uni_group_results |>
      dplyr::filter(outcome == ok) |>
      dplyr::mutate(
        use_sci = pmax(abs(irr), abs(ci_low), abs(ci_high), na.rm = TRUE) >= 10,
        use_sci = if_else(is.na(use_sci), FALSE, use_sci),
        irr_formatted = if_else(use_sci,
          sprintf("%.1e (%.1e-%.1e)", irr, ci_low, ci_high),
          sprintf("%.2f (%.2f-%.2f)", irr, ci_low, ci_high)),
        Organ_Display = clean_organ_display(organ_age)
      ) |>
      dplyr::select(Organ = Organ_Display, `Effect (95% CI)` = irr_formatted, FDR = fdr)
    
    if (nrow(csv_data) > 0) {
      fn <- paste0("nb_", stringr::str_replace_all(tolower(unname(disease_groupings[ok])), " ", "_"), "_all_pairs.csv")
      write.csv(csv_data, file = file.path(csv_dir, fn), row.names = FALSE)
    }
  })
}
```

## Within-Pair Negative Binomial Models (MZ Only)

```{r}
# Run within-pair NB univariate and multivariate for all groupings
nb_wp_uni_group_results_mz <- purrr::map_dfr(names(disease_groupings), function(outcome_var) {
  df_outcome <- twins |>
    dplyr::select(twin_id, pair_id, age, sex, bestzyg, edyrs, eversmok, bmi, hba1c, total_hdl_ratio, crp) |>
    dplyr::filter(bestzyg == 1) |>
    dplyr::left_join(mm_counts_full |> dplyr::select(twin_id, !!outcome_var), by = "twin_id") |>
    dplyr::mutate(
      !!outcome_var := dplyr::coalesce(!!rlang::sym(outcome_var), 0L),
      sex = as.factor(sex)
    ) |>
    dplyr::left_join(org_clean, by = "twin_id")
  
  purrr::map_dfr(predictors_uni, ~fit_nb_uni_within(df_outcome, outcome_var, .x))
}) |>
  dplyr::group_by(outcome) |>
  dplyr::mutate(fdr = p.adjust(p_value, method = "fdr")) |>
  dplyr::ungroup() |>
  dplyr::mutate(
    outcome_clean = disease_groupings[outcome] |> unlist(),
    organ_age_clean = stringr::str_replace_all(organ_age, "_", " ") |> stringr::str_to_title()
  )

# Heatmaps for MZ-only within-pair NB
nb_wp_uni_heatmap_mz <- make_nb_wp_heatmap(nb_wp_uni_group_results_mz, NULL)

if (!is.null(nb_wp_uni_heatmap_mz)) print(nb_wp_uni_heatmap_mz)

if (!is.null(nb_wp_uni_heatmap_mz)) {
  dir.create(file.path(output_multimorbidity_core_dir, "nb", "within_pair"), recursive = TRUE, showWarnings = FALSE)
  ggplot2::ggsave(filename = file.path(output_multimorbidity_core_dir, "nb", "within_pair", "nb_full_withinpair_mz_irr_heatmap.svg"), plot = nb_wp_uni_heatmap_mz, width = 10, height = 8, dpi = 300)
}
```

```{r nb_forest_tables_withinpair_mz}
# NB within-pair (MZ)
if (exists("nb_wp_uni_group_results_mz") && nrow(nb_wp_uni_group_results_mz) > 0) {
  dir.create(file.path(output_multimorbidity_core_dir, "nb", "within_pair"), recursive = TRUE, showWarnings = FALSE)
  out_keys <- unique(nb_wp_uni_group_results_mz$outcome)
  purrr::walk(out_keys, function(ok) {
    df <- nb_wp_uni_group_results_mz |>
      dplyr::filter(outcome == ok) |>
      dplyr::mutate(Organ_Display = clean_organ_display(organ_age))
    p <- make_bw_forest_table(df, organ_col = "Organ_Display", eff_col = "irr", low_col = "ci_low", high_col = "ci_high", fdr_col = "fdr", title = unname(disease_groupings[ok]), axis_label = "Incidence Rate Ratio (95% CI)")
    if (!is.null(p)) {
      fn <- paste0("nb_forest_", stringr::str_replace_all(tolower(unname(disease_groupings[ok])), " ", "_"), "_mz_twins.svg")
      ggplot2::ggsave(filename = fn, plot = p, path = file.path(output_multimorbidity_core_dir, "nb", "within_pair"), device = "svg", width = 7, height = 5, dpi = 300)
    }
  }  )
  
  # Save CSV for MZ twins
  purrr::walk(out_keys, function(ok) {
    csv_data <- nb_wp_uni_group_results_mz |>
      dplyr::filter(outcome == ok) |>
      dplyr::mutate(
        use_sci = pmax(abs(irr), abs(ci_low), abs(ci_high), na.rm = TRUE) >= 10,
        use_sci = if_else(is.na(use_sci), FALSE, use_sci),
        irr_formatted = if_else(use_sci,
          sprintf("%.1e (%.1e-%.1e)", irr, ci_low, ci_high),
          sprintf("%.2f (%.2f-%.2f)", irr, ci_low, ci_high)),
        Organ_Display = clean_organ_display(organ_age)
      ) |>
      dplyr::select(Organ = Organ_Display, `Effect (95% CI)` = irr_formatted, FDR = fdr)
    
    if (nrow(csv_data) > 0) {
      fn <- paste0("nb_", stringr::str_replace_all(tolower(unname(disease_groupings[ok])), " ", "_"), "_mz_twins.csv")
      write.csv(csv_data, file = file.path(csv_dir, fn), row.names = FALSE)
    }
  })
}
```

# Andersen-Gill Models

```{r}
# Prepare start–stop data
organ_age_mortality_clean <- org_clean

twins_fu <- twins |>
  dplyr::select(twin_id, age, sex, time_to_death, edyrs, eversmok, bmi, hba1c, total_hdl_ratio, crp) |>
  dplyr::mutate(
    person_years = time_to_death / 365.25,
    sex = as.factor(sex)
  ) |>
  dplyr::left_join(
    composite_diseases |> janitor::clean_names() |> dplyr::select(twin_id, prevalent_mm),
    by = "twin_id"
  ) |>
  dplyr::mutate(prevalent_mm = dplyr::coalesce(prevalent_mm, 0))

events <- timeline |>
  dplyr::select(twin_id, earliest_date, checkdate, has_disease, prevalent) |>
  dplyr::filter(has_disease == 1, prevalent == 0, earliest_date > checkdate) |>
  dplyr::mutate(event_time = as.numeric(earliest_date - checkdate) / 365.25) |>
  dplyr::arrange(twin_id, event_time) |>
  dplyr::group_by(twin_id) |>
  dplyr::mutate(start = dplyr::lag(event_time, default = 0), stop = event_time, event = 1L) |>
  dplyr::ungroup()

censor <- twins_fu |>
  dplyr::select(twin_id, person_years) |>
  dplyr::left_join(events |>
    dplyr::group_by(twin_id) |>
    dplyr::summarise(last_stop = max(stop, na.rm = TRUE), .groups = "drop"), by = "twin_id") |>
  dplyr::mutate(start = dplyr::coalesce(last_stop, 0), stop = pmax(person_years, start), event = 0L) |>
  dplyr::select(twin_id, start, stop, event)

ag_df <- dplyr::bind_rows(
  events |> dplyr::select(twin_id, start, stop, event),
  censor
) |>
  dplyr::filter(stop > start, is.finite(stop)) |>
  dplyr::left_join(twins_fu |> dplyr::select(twin_id, age, sex, prevalent_mm, edyrs, eversmok, bmi, hba1c, total_hdl_ratio, crp), by = "twin_id") |>
  dplyr::left_join(twins |> dplyr::select(twin_id, pair_id), by = "twin_id") |>
  dplyr::left_join(organ_age_mortality_clean, by = "twin_id")

# Organ columns for univariate models (include all organs)
organ_cols_ag_uni <- organ_age_mortality_clean |>
  dplyr::select(-twin_id) |>
  names()

fit_ag_uni <- function(data, predictor) {
  fml <- stats::as.formula(paste("survival::Surv(start, stop, event) ~", predictor, "+ prevalent_mm +", covariate_formula_terms, "+ cluster(twin_id)"))
  out <- tryCatch({
    mdl <- survival::coxph(fml, data = data, ties = "efron")
    s <- summary(mdl)
    coefs <- s$coefficients
    rn <- rownames(coefs)
    term <- if (predictor %in% rn) predictor else {
      hit <- grep(predictor, rn, fixed = TRUE, value = TRUE)
      if (length(hit) > 0) hit[1] else NA_character_
    }
    if (is.na(term)) {
      return(dplyr::tibble(
        organ_age = predictor,
        hr = NA_real_, ci_low = NA_real_, ci_high = NA_real_, p_value = NA_real_
      ))
    }
    se_col <- if ("robust se" %in% colnames(coefs)) "robust se" else if ("se(coef)" %in% colnames(coefs)) "se(coef)" else colnames(coefs)[grepl("se", colnames(coefs), ignore.case = TRUE)][1]
    coef_val <- coefs[term, "coef"]
    se_val <- coefs[term, se_col]
    p_col <- if ("Pr(>|z|)" %in% colnames(coefs)) "Pr(>|z|)" else NA_character_
    p_val <- if (!is.na(p_col)) coefs[term, p_col] else 2 * stats::pnorm(-abs(coef_val / se_val))
    dplyr::tibble(
      organ_age = predictor,
      hr = exp(coef_val),
      ci_low = exp(coef_val - 1.96 * se_val),
      ci_high = exp(coef_val + 1.96 * se_val),
      p_value = p_val
    )
  }, error = function(e) {
    dplyr::tibble(
      organ_age = predictor,
      hr = NA_real_, ci_low = NA_real_, ci_high = NA_real_, p_value = NA_real_
    )
  })
  out
}

ag_uni_results <- purrr::map_dfr(organ_cols_ag_uni, ~fit_ag_uni(ag_df, .x)) |>
  dplyr::mutate(
    fdr = p.adjust(p_value, method = "fdr")
  )
```

## Andersen-Gill Models Across Disease Groupings

### Sensitivity: Healthy Baseline Cohort

```{r}
# Create healthy baseline cohort
twins_fu_healthy <- twins_fu |>
  dplyr::filter(prevalent_mm == 0)

# Build AG data per grouping for healthy cohort only
build_ag_df_for_group_healthy <- function(disease_labels) {
  events_g <- timeline |>
    dplyr::filter(.data[[label_col]] %in% disease_labels) |>
    dplyr::select(twin_id, earliest_date, checkdate, has_disease, prevalent) |>
    dplyr::filter(has_disease == 1, prevalent == 0, earliest_date > checkdate) |>
    dplyr::mutate(event_time = as.numeric(earliest_date - checkdate) / 365.25) |>
    dplyr::arrange(twin_id, event_time) |>
    dplyr::group_by(twin_id) |>
    dplyr::mutate(start = dplyr::lag(event_time, default = 0), stop = event_time, event = 1L) |>
    dplyr::ungroup()

  censor_g <- twins_fu_healthy |>
    dplyr::select(twin_id, person_years) |>
    dplyr::left_join(events_g |>
      dplyr::group_by(twin_id) |>
      dplyr::summarise(last_stop = max(stop, na.rm = TRUE), .groups = "drop"), by = "twin_id") |>
    dplyr::mutate(start = dplyr::coalesce(last_stop, 0), stop = pmax(person_years, start), event = 0L) |>
    dplyr::select(twin_id, start, stop, event)

  dplyr::bind_rows(events_g |> dplyr::select(twin_id, start, stop, event), censor_g) |>
    dplyr::filter(stop > start, is.finite(stop)) |>
    dplyr::left_join(twins_fu_healthy |> dplyr::select(twin_id, age, sex, edyrs, eversmok, bmi, hba1c, total_hdl_ratio, crp), by = "twin_id") |>
    dplyr::left_join(twins |> dplyr::select(twin_id, pair_id), by = "twin_id") |>
    dplyr::left_join(organ_age_mortality_clean, by = "twin_id")
}

# AG univariate function for healthy cohort (no prevalent_mm needed)
fit_ag_uni_healthy <- function(data, predictor) {
  fml <- stats::as.formula(paste("survival::Surv(start, stop, event) ~", predictor, "+", covariate_formula_terms, "+ cluster(twin_id)"))
  out <- tryCatch({
    mdl <- survival::coxph(fml, data = data, ties = "efron")
    s <- summary(mdl)
    coefs <- s$coefficients
    rn <- rownames(coefs)
    term <- if (predictor %in% rn) predictor else {
      hit <- grep(predictor, rn, fixed = TRUE, value = TRUE)
      if (length(hit) > 0) hit[1] else NA_character_
    }
    if (is.na(term)) {
      return(dplyr::tibble(
        organ_age = predictor,
        hr = NA_real_, ci_low = NA_real_, ci_high = NA_real_, p_value = NA_real_
      ))
    }
    se_col <- if ("robust se" %in% colnames(coefs)) "robust se" else if ("se(coef)" %in% colnames(coefs)) "se(coef)" else colnames(coefs)[grepl("se", colnames(coefs), ignore.case = TRUE)][1]
    coef_val <- coefs[term, "coef"]
    se_val <- coefs[term, se_col]
    p_col <- if ("Pr(>|z|)" %in% colnames(coefs)) "Pr(>|z|)" else NA_character_
    p_val <- if (!is.na(p_col)) coefs[term, p_col] else 2 * stats::pnorm(-abs(coef_val / se_val))
    dplyr::tibble(
      organ_age = predictor,
      hr = exp(coef_val),
      ci_low = exp(coef_val - 1.96 * se_val),
      ci_high = exp(coef_val + 1.96 * se_val),
      p_value = p_val
    )
  }, error = function(e) {
    dplyr::tibble(
      organ_age = predictor,
      hr = NA_real_, ci_low = NA_real_, ci_high = NA_real_, p_value = NA_real_
    )
  })
  out
}

# Run AG univariate models for healthy cohort
ag_uni_healthy_results <- purrr::map_dfr(names(disease_groupings), function(nm) {
  df_g <- build_ag_df_for_group_healthy(group_vectors[[nm]])
  if (nrow(df_g) == 0) return(tibble::tibble())
  purrr::map_dfr(organ_cols_ag_uni, ~fit_ag_uni_healthy(df_g, .x)) |>
    dplyr::mutate(group_key = nm)
}) |>
  dplyr::group_by(group_key) |>
  dplyr::mutate(fdr = p.adjust(p_value, method = "fdr")) |>
  dplyr::ungroup()

# Create heatmap for healthy cohort AG univariate results
ag_healthy_heatmap_df <- ag_uni_healthy_results |>
  dplyr::mutate(
    outcome_clean = disease_groupings[group_key] |> unlist(),
    organ_age_clean = stringr::str_replace_all(organ_age, "_", " ") |> stringr::str_to_title(),
    effect_size = hr,
    effect_size_colored = dplyr::if_else(fdr < 0.05, hr, NA_real_),
    non_sig_marker = dplyr::if_else(fdr < 0.05, "", "×")
  ) |>
  dplyr::select(outcome_clean, organ_age_clean, effect_size, effect_size_colored, non_sig_marker, fdr) |>
  dplyr::filter(!is.na(effect_size))

# Organ order for healthy cohort
all_orgs_healthy <- unique(ag_healthy_heatmap_df$organ_age_clean)
available_pref_healthy <- intersect(preferred_order, all_orgs_healthy)
other_orgs_healthy <- setdiff(all_orgs_healthy, preferred_order)
organ_order_healthy <- c(available_pref_healthy, other_orgs_healthy)

plot_ag_healthy_df <- ag_healthy_heatmap_df |>
  dplyr::mutate(
    outcome_clean = factor(outcome_clean, levels = outcome_order_standard),
    organ_age_clean = factor(organ_age_clean, levels = organ_order_healthy)
  )

if (length(unique(plot_ag_healthy_df$outcome_clean)) == 0 || length(unique(plot_ag_healthy_df$organ_age_clean)) == 0) {
  ag_healthy_heatmap <- NULL
} else {
  # Panel-style control variables
  text_size_pt <- HEATMAP_TEXT_SIZE
  square_size <- text_size_pt / HEATMAP_SQUARE_SIZE_DIVISOR
  
  # Calculate dynamic range (white-to-red only, no negative values)
  # Use effect_size (all values) not effect_size_colored (only significant) to capture full range
  effect_range <- range(log(plot_ag_healthy_df$effect_size), na.rm = TRUE)
  buffer <- 0.1
  max_limit <- max(1.5, effect_range[2] + buffer)
  min_limit <- 0  # Start from 0 since no negative values
  
  breaks <- seq(0, max_limit, length.out = 4)
  labels <- sprintf("%.1f", breaks)
  
  # Prepare data with numeric coordinates
  plot_ag_healthy_df <- plot_ag_healthy_df |>
    dplyr::mutate(
      outcome_num = (as.numeric(outcome_clean) - 1) * square_size + square_size/2,
      organ_num = (as.numeric(organ_age_clean) - 1) * square_size + square_size/2
    )
  
  outcome_order <- levels(plot_ag_healthy_df$outcome_clean)
  organ_order <- levels(plot_ag_healthy_df$organ_age_clean)
  
  ag_healthy_heatmap <- ggplot2::ggplot(plot_ag_healthy_df, ggplot2::aes(x = organ_num, y = outcome_num, fill = log(effect_size_colored))) +
    ggplot2::geom_tile(width = square_size, height = square_size, color = NA) +
    ggplot2::geom_text(ggplot2::aes(x = organ_num, y = outcome_num, label = non_sig_marker), size = 5.5, color = "darkgrey", family = "Helvetica", inherit.aes = FALSE) +
    ggplot2::scale_fill_gradientn(
      colors = c(
        "white",        # Start at 0
        "#C64D4D",      # Red (mid-high)
        "#B71C1C"       # Darker red (extreme high)
      ),
      values = scales::rescale(c(0, max_limit * 0.5, max_limit)),
      limits = c(0, max_limit),
      na.value = "white",
      name = "log(HR)",
      breaks = breaks,
      labels = labels
    ) +
    ggplot2::scale_x_continuous(
      breaks = (seq_along(organ_order) - 1) * square_size + square_size/2,
      labels = organ_order,
      expand = c(0, 0),
      limits = c(-square_size/2, length(organ_order) * square_size + square_size/2)
    ) +
    ggplot2::scale_y_continuous(
      breaks = (seq_along(outcome_order) - 1) * square_size + square_size/2,
      labels = outcome_order,
      expand = c(0, 0),
      limits = c(-square_size/2, length(outcome_order) * square_size + square_size/2)
    ) +
    ggplot2::theme_minimal(base_family = "Helvetica") +
    ggplot2::theme(
      text = ggplot2::element_text(family = "Helvetica", color = "black"),
      axis.text.x = ggplot2::element_text(angle = 45, hjust = 1, size = HEATMAP_TEXT_SIZE, color = "black", family = "Helvetica"),
      axis.text.y = ggplot2::element_text(size = HEATMAP_TEXT_SIZE, hjust = 0, margin = ggplot2::margin(r = 10), color = "black", family = "Helvetica"),
      axis.title = ggplot2::element_blank(),
      axis.ticks = ggplot2::element_blank(),
      legend.position = "right",
      legend.title = ggplot2::element_text(size = 11, color = "black", family = "Helvetica"),
      legend.text = ggplot2::element_text(size = 9, color = "black", family = "Helvetica"),
      legend.key.height = grid::unit(0.8, "cm"),
      legend.key.width = grid::unit(0.5, "cm"),
      panel.grid = ggplot2::element_blank(),
      panel.spacing = grid::unit(0, "lines"),
      panel.border = ggplot2::element_blank(),
      plot.margin = ggplot2::margin(0.5, 0.5, 0.5, 0.5, "cm")
    ) +
    ggplot2::coord_fixed(ratio = 1, expand = FALSE) +
    ggplot2::labs(title = "AG Univariate: Healthy at Baseline Only")
}

print(ag_healthy_heatmap)

# Save healthy cohort heatmap
dir.create(file.path(output_multimorbidity_core_dir, "ag", "main"), recursive = TRUE, showWarnings = FALSE)
if (!is.null(ag_healthy_heatmap)) {
  ggplot2::ggsave(
    filename = file.path(output_multimorbidity_core_dir, "ag", "main", "ag_healthy_main_hr_heatmap.svg"),
    plot = ag_healthy_heatmap,
    width = 10,
    height = 8,
    dpi = 300
  )
}
```

## Full Cohort AG Models

```{r}
# Build AG data per grouping
build_ag_df_for_group <- function(disease_labels) {
  events_g <- timeline |>
    dplyr::filter(.data[[label_col]] %in% disease_labels) |>
    dplyr::select(twin_id, earliest_date, checkdate, has_disease, prevalent) |>
    dplyr::filter(has_disease == 1, prevalent == 0, earliest_date > checkdate) |>
    dplyr::mutate(event_time = as.numeric(earliest_date - checkdate) / 365.25) |>
    dplyr::arrange(twin_id, event_time) |>
    dplyr::group_by(twin_id) |>
    dplyr::mutate(start = dplyr::lag(event_time, default = 0), stop = event_time, event = 1L) |>
    dplyr::ungroup()

  censor_g <- twins_fu |>
    dplyr::select(twin_id, person_years) |>
    dplyr::left_join(events_g |>
      dplyr::group_by(twin_id) |>
      dplyr::summarise(last_stop = max(stop, na.rm = TRUE), .groups = "drop"), by = "twin_id") |>
    dplyr::mutate(start = dplyr::coalesce(last_stop, 0), stop = pmax(person_years, start), event = 0L) |>
    dplyr::select(twin_id, start, stop, event)

  dplyr::bind_rows(
    events_g |> dplyr::select(twin_id, start, stop, event),
    censor_g
  ) |>
    dplyr::filter(stop > start, is.finite(stop)) |>
    dplyr::left_join(twins_fu |> dplyr::select(twin_id, age, sex, prevalent_mm, edyrs, eversmok, bmi, hba1c, total_hdl_ratio, crp), by = "twin_id") |>
    dplyr::left_join(organ_age_mortality_clean, by = "twin_id")
}

ag_group_results <- purrr::map_dfr(names(group_vectors), function(nm) {
  df_g <- build_ag_df_for_group(group_vectors[[nm]])
  if (nrow(df_g) == 0) return(tibble::tibble())
  purrr::map_dfr(organ_cols_ag_uni, ~fit_ag_uni(df_g, .x)) |>
    dplyr::mutate(group_key = nm)
}) |>
  dplyr::group_by(group_key) |>
  dplyr::mutate(fdr = p.adjust(p_value, method = "fdr")) |>
  dplyr::ungroup() |>
  dplyr::mutate(
    group_display = unname(disease_groupings[group_key]),
    organ_age_clean = stringr::str_replace_all(organ_age, "_", " ") |> stringr::str_to_title()
  )
```

```{r}
# Heatmap across all disease groupings
ag_groups_heatmap_df <- ag_group_results |>
  dplyr::transmute(
    outcome_clean = group_display,
    organ_age_clean,
    effect_size = hr,
    significance = dplyr::case_when(
      fdr < 0.001 ~ "***",
      fdr < 0.01 ~ "**",
      fdr < 0.05 ~ "*",
      TRUE ~ ""
    ),
    effect_size_colored = dplyr::if_else(significance != "", effect_size, NA_real_),
    non_sig_marker = dplyr::if_else(significance == "", "×", "")
  ) |>
  dplyr::filter(!is.na(effect_size))

# Organ order reused
preferred_order <- c(
  "Brain", "Heart", "Kidney And Bladder", "Liver", "Lung",
  "Muscle", "Pancreas", "Gastrointestinal Tract"
)
all_orgs_groups <- unique(ag_groups_heatmap_df$organ_age_clean)
available_pref_groups <- intersect(preferred_order, all_orgs_groups)
other_orgs_groups <- setdiff(all_orgs_groups, preferred_order)
organ_order_groups <- c(available_pref_groups, other_orgs_groups)

plot_ag_groups_df <- ag_groups_heatmap_df |>
  dplyr::mutate(
    outcome_clean = factor(outcome_clean, levels = outcome_order_standard),
    organ_age_clean = factor(organ_age_clean, levels = organ_order_groups)
  )

if (length(unique(plot_ag_groups_df$outcome_clean)) == 0 || length(unique(plot_ag_groups_df$organ_age_clean)) == 0) {
  ag_groups_heatmap <- NULL
} else {
  # Panel-style control variables
  text_size_pt <- HEATMAP_TEXT_SIZE
  square_size <- text_size_pt / HEATMAP_SQUARE_SIZE_DIVISOR
  
  # Calculate dynamic range (white-to-red only, no negative values)
  # Use effect_size (all values) not effect_size_colored (only significant) to capture full range
  effect_range <- range(log(plot_ag_groups_df$effect_size), na.rm = TRUE)
  buffer <- 0.1
  max_limit <- max(1.5, effect_range[2] + buffer)
  min_limit <- 0  # Start from 0 since no negative values
  
  breaks <- seq(0, max_limit, length.out = 4)
  labels <- sprintf("%.1f", breaks)
  
  # Prepare data with numeric coordinates
  plot_ag_groups_df <- plot_ag_groups_df |>
    dplyr::mutate(
      outcome_num = (as.numeric(outcome_clean) - 1) * square_size + square_size/2,
      organ_num = (as.numeric(organ_age_clean) - 1) * square_size + square_size/2
    )
  
  outcome_order <- levels(plot_ag_groups_df$outcome_clean)
  organ_order <- levels(plot_ag_groups_df$organ_age_clean)
  
  ag_groups_heatmap <- ggplot2::ggplot(plot_ag_groups_df, ggplot2::aes(x = organ_num, y = outcome_num, fill = log(effect_size_colored))) +
    ggplot2::geom_tile(width = square_size, height = square_size, color = NA) +
    ggplot2::geom_text(ggplot2::aes(x = organ_num, y = outcome_num, label = non_sig_marker), size = 5.5, color = "darkgrey", family = "Helvetica", inherit.aes = FALSE) +
    ggplot2::scale_fill_gradientn(
      colors = c(
        "white",        # Start at 0
        "#C64D4D",      # Red (mid-high)
        "#B71C1C"       # Darker red (extreme high)
      ),
      limits = c(min_limit, max_limit),
      na.value = "white",
      name = "log(HR)",
      breaks = breaks,
      labels = labels
    ) +
    ggplot2::scale_x_continuous(
      breaks = (seq_along(organ_order) - 1) * square_size + square_size/2,
      labels = organ_order,
      expand = c(0, 0),
      limits = c(-square_size/2, length(organ_order) * square_size + square_size/2)
    ) +
    ggplot2::scale_y_continuous(
      breaks = (seq_along(outcome_order) - 1) * square_size + square_size/2,
      labels = outcome_order,
      expand = c(0, 0),
      limits = c(-square_size/2, length(outcome_order) * square_size + square_size/2)
    ) +
    ggplot2::theme_minimal(base_family = "Helvetica") +
    ggplot2::theme(
      text = ggplot2::element_text(family = "Helvetica", color = "black"),
      axis.text.x = ggplot2::element_text(angle = 45, hjust = 1, size = HEATMAP_TEXT_SIZE, color = "black", family = "Helvetica"),
      axis.text.y = ggplot2::element_text(size = HEATMAP_TEXT_SIZE, hjust = 0, margin = ggplot2::margin(r = 10), color = "black", family = "Helvetica"),
      axis.title = ggplot2::element_blank(),
      axis.ticks = ggplot2::element_blank(),
      legend.position = "right",
      legend.title = ggplot2::element_text(size = 11, color = "black", family = "Helvetica"),
      legend.text = ggplot2::element_text(size = 9, color = "black", family = "Helvetica"),
      legend.key.height = grid::unit(0.8, "cm"),
      legend.key.width = grid::unit(0.5, "cm"),
      panel.grid = ggplot2::element_blank(),
      panel.spacing = grid::unit(0, "lines"),
      panel.border = ggplot2::element_blank(),
      plot.margin = ggplot2::margin(0.5, 0.5, 0.5, 0.5, "cm")
    ) +
    ggplot2::coord_fixed(ratio = 1, expand = FALSE)
}

print(ag_groups_heatmap)

dir.create(file.path(output_multimorbidity_core_dir, "ag", "main"), recursive = TRUE, showWarnings = FALSE)
if (!is.null(ag_groups_heatmap)) {
  ggplot2::ggsave(
    filename = file.path(output_multimorbidity_core_dir, "ag", "main", "ag_full_main_hr_heatmap.svg"),
    plot = ag_groups_heatmap,
    width = 10,
    height = 8,
    dpi = 300
  )
}
```

## Forest tables: AG main and within-pair
```{r ag_forest_tables}
# AG main
if (exists("ag_group_results") && nrow(ag_group_results) > 0) {
  dir.create(file.path(output_multimorbidity_core_dir, "ag", "main"), recursive = TRUE, showWarnings = FALSE)
  out_keys <- unique(ag_group_results$group_display)
  purrr::walk(out_keys, function(lbl) {
    df <- ag_group_results |>
      dplyr::filter(group_display == lbl) |>
      dplyr::mutate(Organ_Display = clean_organ_display(organ_age))
    p <- make_bw_forest_table(df, organ_col = "Organ_Display", eff_col = "hr", low_col = "ci_low", high_col = "ci_high", fdr_col = "fdr", title = lbl, axis_label = "Hazard Ratio (95% CI)")
    if (!is.null(p)) {
      fn <- paste0("ag_forest_", stringr::str_replace_all(tolower(lbl), " ", "_"), ".svg")
      ggplot2::ggsave(filename = fn, plot = p, path = file.path(output_multimorbidity_core_dir, "ag", "main"), device = "svg", width = 7, height = 5, dpi = 300)
    }
  })
  
  # Create CSV tables directory
  csv_dir <- file.path(output_multimorbidity_core_dir, "ag", "main", "tables")
  dir.create(csv_dir, showWarnings = FALSE, recursive = TRUE)
  
  # Save table data as CSV
  purrr::walk(out_keys, function(lbl) {
    csv_data <- ag_group_results |>
      dplyr::filter(group_display == lbl) |>
      dplyr::mutate(
        use_sci = pmax(abs(hr), abs(ci_low), abs(ci_high), na.rm = TRUE) >= 10,
        use_sci = if_else(is.na(use_sci), FALSE, use_sci),
        hr_formatted = if_else(use_sci,
          sprintf("%.1e (%.1e-%.1e)", hr, ci_low, ci_high),
          sprintf("%.2f (%.2f-%.2f)", hr, ci_low, ci_high)),
        Organ_Display = clean_organ_display(organ_age)
      ) |>
      dplyr::select(Organ = Organ_Display, `Effect (95% CI)` = hr_formatted, FDR = fdr)
    
    if (nrow(csv_data) > 0) {
      fn <- paste0("ag_", stringr::str_replace_all(tolower(lbl), " ", "_"), ".csv")
      write.csv(csv_data, file = file.path(csv_dir, fn), row.names = FALSE)
    }
  })
}

# AG within-pair
if (exists("ag_wp_uni_group_results") && nrow(ag_wp_uni_group_results) > 0) {
  dir.create(file.path(output_multimorbidity_core_dir, "ag", "within_pair"), recursive = TRUE, showWarnings = FALSE)
  out_keys <- unique(ag_wp_uni_group_results$group_display)
  purrr::walk(out_keys, function(lbl) {
    df <- ag_wp_uni_group_results |>
      dplyr::filter(group_display == lbl) |>
      dplyr::mutate(Organ_Display = clean_organ_display(organ_age))
    p <- make_bw_forest_table(df, organ_col = "Organ_Display", eff_col = "hr", low_col = "ci_low", high_col = "ci_high", fdr_col = "fdr", title = lbl, axis_label = "Hazard Ratio (95% CI)")
    if (!is.null(p)) {
      fn <- paste0("ag_forest_", stringr::str_replace_all(tolower(lbl), " ", "_"), "_all_pairs.svg")
      ggplot2::ggsave(filename = fn, plot = p, path = file.path(output_multimorbidity_core_dir, "ag", "within_pair"), device = "svg", width = 7, height = 5, dpi = 300)
    }
  })
  
  # Create CSV tables directory
  csv_dir <- file.path(output_multimorbidity_core_dir, "ag", "within_pair", "tables")
  dir.create(csv_dir, showWarnings = FALSE, recursive = TRUE)
  
  # Save table data as CSV
  purrr::walk(out_keys, function(lbl) {
    csv_data <- ag_wp_uni_group_results |>
      dplyr::filter(group_display == lbl) |>
      dplyr::mutate(
        use_sci = pmax(abs(hr), abs(ci_low), abs(ci_high), na.rm = TRUE) >= 10,
        use_sci = if_else(is.na(use_sci), FALSE, use_sci),
        hr_formatted = if_else(use_sci,
          sprintf("%.1e (%.1e-%.1e)", hr, ci_low, ci_high),
          sprintf("%.2f (%.2f-%.2f)", hr, ci_low, ci_high)),
        Organ_Display = clean_organ_display(organ_age)
      ) |>
      dplyr::select(Organ = Organ_Display, `Effect (95% CI)` = hr_formatted, FDR = fdr)
    
    if (nrow(csv_data) > 0) {
      fn <- paste0("ag_", stringr::str_replace_all(tolower(lbl), " ", "_"), "_all_pairs.csv")
      write.csv(csv_data, file = file.path(csv_dir, fn), row.names = FALSE)
    }
  })
}

# AG within-pair (MZ)
if (exists("ag_wp_uni_group_results_mz") && nrow(ag_wp_uni_group_results_mz) > 0) {
  dir.create(file.path(output_multimorbidity_core_dir, "ag", "within_pair"), recursive = TRUE, showWarnings = FALSE)
  out_keys <- unique(ag_wp_uni_group_results_mz$group_display)
  purrr::walk(out_keys, function(lbl) {
    df <- ag_wp_uni_group_results_mz |>
      dplyr::filter(group_display == lbl) |>
      dplyr::mutate(Organ_Display = clean_organ_display(organ_age))
    p <- make_bw_forest_table(df, organ_col = "Organ_Display", eff_col = "hr", low_col = "ci_low", high_col = "ci_high", fdr_col = "fdr", title = lbl, axis_label = "Hazard Ratio (95% CI)")
    if (!is.null(p)) {
      fn <- paste0("ag_forest_", stringr::str_replace_all(tolower(lbl), " ", "_"), "_mz_twins.svg")
      ggplot2::ggsave(filename = fn, plot = p, path = file.path(output_multimorbidity_core_dir, "ag", "within_pair"), device = "svg", width = 7, height = 5, dpi = 300)
    }
  })
  
  # Create CSV tables directory for MZ twins
  csv_dir <- file.path(output_multimorbidity_core_dir, "ag", "within_pair", "tables")
  dir.create(csv_dir, showWarnings = FALSE, recursive = TRUE)
  
  # Save CSV for MZ twins
  purrr::walk(out_keys, function(lbl) {
    csv_data <- ag_wp_uni_group_results_mz |>
      dplyr::filter(group_display == lbl) |>
      dplyr::mutate(
        use_sci = pmax(abs(hr), abs(ci_low), abs(ci_high), na.rm = TRUE) >= 10,
        use_sci = if_else(is.na(use_sci), FALSE, use_sci),
        hr_formatted = if_else(use_sci,
          sprintf("%.1e (%.1e-%.1e)", hr, ci_low, ci_high),
          sprintf("%.2f (%.2f-%.2f)", hr, ci_low, ci_high)),
        Organ_Display = clean_organ_display(organ_age)
      ) |>
      dplyr::select(Organ = Organ_Display, `Effect (95% CI)` = hr_formatted, FDR = fdr)
    
    if (nrow(csv_data) > 0) {
      fn <- paste0("ag_", stringr::str_replace_all(tolower(lbl), " ", "_"), "_mz_twins.csv")
      write.csv(csv_data, file = file.path(csv_dir, fn), row.names = FALSE)
    }
  })
}
```

# Within-Pair Andersen-Gill Models

```{r}
# Build within-pair AG data for a disease grouping
essential_withinpair_ag_df_for_group <- function(disease_labels) {
  events_g <- timeline |>
    dplyr::filter(.data[[label_col]] %in% disease_labels) |>
    dplyr::select(twin_id, earliest_date, checkdate, has_disease, prevalent) |>
    dplyr::filter(has_disease == 1, prevalent == 0, earliest_date > checkdate) |>
    dplyr::mutate(event_time = as.numeric(earliest_date - checkdate) / 365.25) |>
    dplyr::arrange(twin_id, event_time) |>
    dplyr::group_by(twin_id) |>
    dplyr::mutate(start = dplyr::lag(event_time, default = 0), stop = event_time, event = 1L) |>
    dplyr::ungroup()

  censor_g <- twins_fu |>
    dplyr::select(twin_id, person_years) |>
    dplyr::left_join(events_g |>
      dplyr::group_by(twin_id) |>
      dplyr::summarise(last_stop = max(stop, na.rm = TRUE), .groups = "drop"), by = "twin_id") |>
    dplyr::mutate(start = dplyr::coalesce(last_stop, 0), stop = pmax(person_years, start), event = 0L) |>
    dplyr::select(twin_id, start, stop, event)

  dplyr::bind_rows(
    events_g |> dplyr::select(twin_id, start, stop, event),
    censor_g
  ) |>
    dplyr::filter(stop > start, is.finite(stop)) |>
    dplyr::left_join(twins_fu |> dplyr::select(twin_id, age, sex, prevalent_mm, edyrs, eversmok, bmi, hba1c, total_hdl_ratio, crp), by = "twin_id") |>
    dplyr::left_join(twins |> dplyr::select(twin_id, pair_id), by = "twin_id") |>
    dplyr::left_join(organ_age_mortality_clean, by = "twin_id")
}

fit_ag_uni_within <- function(data, predictor) {
  fml <- stats::as.formula(paste("survival::Surv(start, stop, event) ~", predictor, "+ prevalent_mm +", covariate_formula_terms, "+ strata(pair_id) + cluster(pair_id)"))
  out <- tryCatch({
    mdl <- survival::coxph(fml, data = data, ties = "efron")
    s <- summary(mdl)
    coefs <- s$coefficients
    rn <- rownames(coefs)
    term <- if (predictor %in% rn) predictor else { hit <- grep(predictor, rn, fixed = TRUE, value = TRUE); if (length(hit) > 0) hit[1] else NA_character_ }
    if (is.na(term)) return(tibble::tibble(organ_age = predictor, hr = NA_real_, ci_low = NA_real_, ci_high = NA_real_, p_value = NA_real_))
    se_col <- if ("robust se" %in% colnames(coefs)) "robust se" else if ("se(coef)" %in% colnames(coefs)) "se(coef)" else colnames(coefs)[grepl("se", colnames(coefs), ignore.case = TRUE)][1]
    coef_val <- coefs[term, "coef"]; se_val <- coefs[term, se_col]
    p_col <- if ("Pr(>|z|)" %in% colnames(coefs)) "Pr(>|z|)" else NA_character_
    p_val <- if (!is.na(p_col)) coefs[term, p_col] else 2 * stats::pnorm(-abs(coef_val / se_val))
    tibble::tibble(
      organ_age = predictor,
      hr = exp(coef_val),
      ci_low = exp(coef_val - 1.96 * se_val),
      ci_high = exp(coef_val + 1.96 * se_val),
      p_value = p_val
    )
  }, error = function(e) tibble::tibble(organ_age = predictor, hr = NA_real_, ci_low = NA_real_, ci_high = NA_real_, p_value = NA_real_))
  out
}

# Run within-pair univariate and multivariate for all groupings
ag_wp_uni_group_results <- purrr::map_dfr(names(group_vectors), function(nm) {
  df_g <- essential_withinpair_ag_df_for_group(group_vectors[[nm]])
  if (nrow(df_g) == 0) return(tibble::tibble())
  purrr::map_dfr(organ_cols_ag_uni, ~fit_ag_uni_within(df_g, .x)) |>
    dplyr::mutate(group_key = nm)
}) |>
  dplyr::group_by(group_key) |>
  dplyr::mutate(fdr = p.adjust(p_value, method = "fdr")) |>
  dplyr::ungroup() |>
  dplyr::mutate(
    group_display = unname(disease_groupings[group_key]),
    organ_age_clean = stringr::str_replace_all(organ_age, "_", " ") |> stringr::str_to_title()
  )
```

```{r}
# Heatmaps (within-pair):
make_wp_heatmap <- function(df, title_suffix) {
  if (nrow(df) == 0) return(NULL)
  preferred_order <- c(
    "Brain", "Heart", "Kidney And Bladder", "Liver", "Lung",
    "Muscle", "Pancreas", "Gastrointestinal Tract"
  )
  all_orgs <- unique(df$organ_age_clean)
  available_pref <- intersect(preferred_order, all_orgs)
  other_orgs <- setdiff(all_orgs, preferred_order)
  organ_order <- c(available_pref, other_orgs)
  
  # Get available outcomes and filter to standard order
  available_outcomes <- unique(df$group_display)
  outcome_order <- intersect(outcome_order_standard, available_outcomes)
  
  if (length(outcome_order) == 0 || length(organ_order) == 0) return(NULL)
  
  # Panel-style control variables
  text_size_pt <- HEATMAP_TEXT_SIZE
  square_size <- text_size_pt / HEATMAP_SQUARE_SIZE_DIVISOR
  
  plot_df <- df |>
    dplyr::mutate(
      outcome_clean = factor(group_display, levels = outcome_order),
      organ_age_clean = factor(organ_age_clean, levels = organ_order),
      outcome_num = (as.numeric(outcome_clean) - 1) * square_size + square_size/2,
      organ_num = (as.numeric(organ_age_clean) - 1) * square_size + square_size/2,
      effect_size_colored = dplyr::if_else(fdr < 0.05, hr, NA_real_),
      non_sig_marker = dplyr::if_else(fdr < 0.05, "", "×")
    )
  
  # Calculate dynamic range (white-to-red only, no negative values)
  # Use hr (all values) not effect_size_colored (only significant) to capture full range
  effect_range_all <- range(log(plot_df$hr), na.rm = TRUE)
  buffer <- 0.1
  max_limit <- max(1.5, effect_range_all[2] + buffer)
  min_limit <- 0  # Start from 0 since no negative values
  
  breaks <- seq(0, max_limit, length.out = 4)
  labels <- sprintf("%.1f", breaks)
  
  ggplot2::ggplot(plot_df, ggplot2::aes(x = organ_num, y = outcome_num, fill = log(effect_size_colored))) +
    ggplot2::geom_tile(width = square_size, height = square_size, color = NA) +
    ggplot2::geom_text(ggplot2::aes(x = organ_num, y = outcome_num, label = non_sig_marker), size = 5.5, color = "darkgrey", family = "Helvetica", inherit.aes = FALSE) +
    ggplot2::scale_fill_gradientn(
      colors = c(
        "white",        # Start at 0
        "#C64D4D",      # Red (mid-high)
        "#B71C1C"       # Darker red (extreme high)
      ),
      values = scales::rescale(c(0, max_limit * 0.5, max_limit)),
      limits = c(0, max_limit),
      na.value = "white",
      name = "log(HR)",
      breaks = breaks,
      labels = labels
    ) +
    ggplot2::scale_x_continuous(
      breaks = (seq_along(organ_order) - 1) * square_size + square_size/2,
      labels = organ_order,
      expand = c(0, 0),
      limits = c(-square_size/2, length(organ_order) * square_size + square_size/2)
    ) +
    ggplot2::scale_y_continuous(
      breaks = (seq_along(outcome_order) - 1) * square_size + square_size/2,
      labels = outcome_order,
      expand = c(0, 0),
      limits = c(-square_size/2, length(outcome_order) * square_size + square_size/2)
    ) +
    ggplot2::theme_minimal(base_family = "Helvetica") +
    ggplot2::theme(
      text = ggplot2::element_text(family = "Helvetica", color = "black"),
      axis.text.x = ggplot2::element_text(angle = 45, hjust = 1, size = HEATMAP_TEXT_SIZE, color = "black", family = "Helvetica"),
      axis.text.y = ggplot2::element_text(size = HEATMAP_TEXT_SIZE, hjust = 0, margin = ggplot2::margin(r = 10), color = "black", family = "Helvetica"),
      axis.title = ggplot2::element_blank(),
      axis.ticks = ggplot2::element_blank(),
      legend.position = "right",
      legend.title = ggplot2::element_text(size = 11, color = "black", family = "Helvetica"),
      legend.text = ggplot2::element_text(size = 9, color = "black", family = "Helvetica"),
      legend.key.height = grid::unit(0.8, "cm"),
      legend.key.width = grid::unit(0.5, "cm"),
      panel.grid = ggplot2::element_blank(),
      panel.spacing = grid::unit(0, "lines"),
      panel.border = ggplot2::element_blank(),
      plot.margin = ggplot2::margin(0.5, 0.5, 0.5, 0.5, "cm")
    ) +
    ggplot2::coord_fixed(ratio = 1, expand = FALSE) +
    ggplot2::labs(title = title_suffix)
}

wp_uni_heatmap <- make_wp_heatmap(ag_wp_uni_group_results, NULL)

if (!is.null(wp_uni_heatmap)) print(wp_uni_heatmap)

if (!is.null(wp_uni_heatmap)) {
  dir.create(file.path(output_multimorbidity_core_dir, "ag", "within_pair"), recursive = TRUE, showWarnings = FALSE)
  ggplot2::ggsave(filename = file.path(output_multimorbidity_core_dir, "ag", "within_pair", "ag_full_withinpair_hr_heatmap.svg"), plot = wp_uni_heatmap, width = 10, height = 8, dpi = 300)
}
```

```{r ag_forest_tables_withinpair}
# AG within-pair
if (exists("ag_wp_uni_group_results") && nrow(ag_wp_uni_group_results) > 0) {
  dir.create(file.path(output_multimorbidity_core_dir, "ag", "within_pair"), recursive = TRUE, showWarnings = FALSE)
  out_keys <- unique(ag_wp_uni_group_results$group_display)
  purrr::walk(out_keys, function(lbl) {
    df <- ag_wp_uni_group_results |>
      dplyr::filter(group_display == lbl) |>
      dplyr::mutate(Organ_Display = clean_organ_display(organ_age))
    p <- make_bw_forest_table(df, organ_col = "Organ_Display", eff_col = "hr", low_col = "ci_low", high_col = "ci_high", fdr_col = "fdr", title = lbl, axis_label = "Hazard Ratio (95% CI)")
    if (!is.null(p)) {
      fn <- paste0("ag_forest_", stringr::str_replace_all(tolower(lbl), " ", "_"), "_all_pairs.svg")
      ggplot2::ggsave(filename = fn, plot = p, path = file.path(output_multimorbidity_core_dir, "ag", "within_pair"), device = "svg", width = 7, height = 5, dpi = 300)
    }
  })
  
  # Create CSV tables directory
  csv_dir <- file.path(output_multimorbidity_core_dir, "ag", "within_pair", "tables")
  dir.create(csv_dir, showWarnings = FALSE, recursive = TRUE)
  
  # Save CSV for all pairs
  purrr::walk(out_keys, function(lbl) {
    csv_data <- ag_wp_uni_group_results |>
      dplyr::filter(group_display == lbl) |>
      dplyr::mutate(
        use_sci = pmax(abs(hr), abs(ci_low), abs(ci_high), na.rm = TRUE) >= 10,
        use_sci = if_else(is.na(use_sci), FALSE, use_sci),
        hr_formatted = if_else(use_sci,
          sprintf("%.1e (%.1e-%.1e)", hr, ci_low, ci_high),
          sprintf("%.2f (%.2f-%.2f)", hr, ci_low, ci_high)),
        Organ_Display = clean_organ_display(organ_age)
      ) |>
      dplyr::select(Organ = Organ_Display, `Effect (95% CI)` = hr_formatted, FDR = fdr)
    
    if (nrow(csv_data) > 0) {
      fn <- paste0("ag_", stringr::str_replace_all(tolower(lbl), " ", "_"), "_all_pairs.csv")
      write.csv(csv_data, file = file.path(csv_dir, fn), row.names = FALSE)
    }
  })
}
```

## Within-Pair Andersen-Gill Models (MZ Only)

```{r}
# Build within-pair AG data (MZ) for a disease grouping
essential_withinpair_ag_df_for_group_mz <- function(disease_labels) {
  events_g <- timeline |>
    dplyr::filter(.data[[label_col]] %in% disease_labels) |>
    dplyr::select(twin_id, earliest_date, checkdate, has_disease, prevalent) |>
    dplyr::filter(has_disease == 1, prevalent == 0, earliest_date > checkdate) |>
    dplyr::mutate(event_time = as.numeric(earliest_date - checkdate) / 365.25) |>
    dplyr::arrange(twin_id, event_time) |>
    dplyr::group_by(twin_id) |>
    dplyr::mutate(start = dplyr::lag(event_time, default = 0), stop = event_time, event = 1L) |>
    dplyr::ungroup()

  censor_g <- twins_fu |>
    dplyr::select(twin_id, person_years) |>
    dplyr::left_join(events_g |>
      dplyr::group_by(twin_id) |>
      dplyr::summarise(last_stop = max(stop, na.rm = TRUE), .groups = "drop"), by = "twin_id") |>
    dplyr::mutate(start = dplyr::coalesce(last_stop, 0), stop = pmax(person_years, start), event = 0L) |>
    dplyr::select(twin_id, start, stop, event)

  dplyr::bind_rows(
    events_g |> dplyr::select(twin_id, start, stop, event),
    censor_g
  ) |>
    dplyr::filter(stop > start, is.finite(stop)) |>
    dplyr::left_join(twins_fu |> dplyr::select(twin_id, age, sex, prevalent_mm, edyrs, eversmok, bmi, hba1c, total_hdl_ratio, crp), by = "twin_id") |>
    dplyr::left_join(twins |> dplyr::select(twin_id, pair_id, bestzyg), by = "twin_id") |>
    dplyr::filter(bestzyg == 1) |>
    dplyr::left_join(organ_age_mortality_clean, by = "twin_id")
}

# Run within-pair
ag_wp_uni_group_results_mz <- purrr::map_dfr(names(group_vectors), function(nm) {
  df_g <- essential_withinpair_ag_df_for_group_mz(group_vectors[[nm]])
  if (nrow(df_g) == 0) return(tibble::tibble())
  purrr::map_dfr(organ_cols_ag_uni, ~fit_ag_uni_within(df_g, .x)) |>
    dplyr::mutate(group_key = nm)
}) |>
  dplyr::group_by(group_key) |>
  dplyr::mutate(fdr = p.adjust(p_value, method = "fdr")) |>
  dplyr::ungroup() |>
  dplyr::mutate(
    group_display = unname(disease_groupings[group_key]),
    organ_age_clean = stringr::str_replace_all(organ_age, "_", " ") |> stringr::str_to_title()
  )

# Heatmaps for MZ only
wp_uni_heatmap_mz <- make_wp_heatmap(ag_wp_uni_group_results_mz, NULL)

if (!is.null(wp_uni_heatmap_mz)) print(wp_uni_heatmap_mz)

if (!is.null(wp_uni_heatmap_mz)) {
  dir.create(file.path(output_multimorbidity_core_dir, "ag", "within_pair"), recursive = TRUE, showWarnings = FALSE)
  ggplot2::ggsave(filename = file.path(output_multimorbidity_core_dir, "ag", "within_pair", "ag_full_withinpair_mz_hr_heatmap.svg"), plot = wp_uni_heatmap_mz, width = 10, height = 8, dpi = 300)
}
```

```{r ag_forest_tables_withinpair_mz}
# AG within-pair (MZ)
if (exists("ag_wp_uni_group_results_mz") && nrow(ag_wp_uni_group_results_mz) > 0) {
  dir.create(file.path(output_multimorbidity_core_dir, "ag", "within_pair"), recursive = TRUE, showWarnings = FALSE)
  out_keys <- unique(ag_wp_uni_group_results_mz$group_display)
  purrr::walk(out_keys, function(lbl) {
    df <- ag_wp_uni_group_results_mz |>
      dplyr::filter(group_display == lbl) |>
      dplyr::mutate(Organ_Display = clean_organ_display(organ_age))
    p <- make_bw_forest_table(df, organ_col = "Organ_Display", eff_col = "hr", low_col = "ci_low", high_col = "ci_high", fdr_col = "fdr", title = lbl, axis_label = "Hazard Ratio (95% CI)")
    if (!is.null(p)) {
      fn <- paste0("ag_forest_", stringr::str_replace_all(tolower(lbl), " ", "_"), "_mz_twins.svg")
      ggplot2::ggsave(filename = fn, plot = p, path = file.path(output_multimorbidity_core_dir, "ag", "within_pair"), device = "svg", width = 7, height = 5, dpi = 300)
    }
  })
  
  # Create CSV tables directory
  csv_dir <- file.path(output_multimorbidity_core_dir, "ag", "within_pair", "tables")
  dir.create(csv_dir, showWarnings = FALSE, recursive = TRUE)
  
  # Save CSV for MZ twins
  purrr::walk(out_keys, function(lbl) {
    csv_data <- ag_wp_uni_group_results_mz |>
      dplyr::filter(group_display == lbl) |>
      dplyr::mutate(
        use_sci = pmax(abs(hr), abs(ci_low), abs(ci_high), na.rm = TRUE) >= 10,
        use_sci = if_else(is.na(use_sci), FALSE, use_sci),
        hr_formatted = if_else(use_sci,
          sprintf("%.1e (%.1e-%.1e)", hr, ci_low, ci_high),
          sprintf("%.2f (%.2f-%.2f)", hr, ci_low, ci_high)),
        Organ_Display = clean_organ_display(organ_age)
      ) |>
      dplyr::select(Organ = Organ_Display, `Effect (95% CI)` = hr_formatted, FDR = fdr)
    
    if (nrow(csv_data) > 0) {
      fn <- paste0("ag_", stringr::str_replace_all(tolower(lbl), " ", "_"), "_mz_twins.csv")
      write.csv(csv_data, file = file.path(csv_dir, fn), row.names = FALSE)
    }
  })
}
```

# Mean Cumulative Function by Aging Group

```{r mcf_by_extreme_ager, echo=TRUE}
# Parameters
extreme_csv_path <- input_extreme_organ_file
extreme_definition <- "n_aged >= 1"  # e.g., "n_aged >= 1", "n_extreme >= 2"
use_all_diseases <- TRUE             # TRUE = use any incident disease (uses existing ag_df)
# Set to FALSE to restrict to a specific disease grouping
group_labels <- NULL                 # e.g., cvd_multimorbidity (character vector of labels)

# Ensure AG data is available
if (!exists("ag_df")) {
  twins_fu <- twins |>
    dplyr::select(twin_id, age, sex, time_to_death, edyrs, eversmok, bmi, hba1c, total_hdl_ratio, crp) |>
    dplyr::mutate(person_years = time_to_death / 365.25, sex = as.factor(sex)) |>
    dplyr::left_join(
      composite_diseases |> janitor::clean_names() |> dplyr::select(twin_id, prevalent_mm),
      by = "twin_id"
    ) |>
    dplyr::mutate(prevalent_mm = dplyr::coalesce(prevalent_mm, 0))

  events_any <- timeline |>
    dplyr::select(twin_id, earliest_date, checkdate, has_disease, prevalent) |>
    dplyr::filter(has_disease == 1, prevalent == 0, earliest_date > checkdate) |>
    dplyr::mutate(event_time = as.numeric(earliest_date - checkdate) / 365.25) |>
    dplyr::arrange(twin_id, event_time) |>
    dplyr::group_by(twin_id) |>
    dplyr::mutate(start = dplyr::lag(event_time, default = 0), stop = event_time, event = 1L) |>
    dplyr::ungroup()

  censor_any <- twins_fu |>
    dplyr::select(twin_id, person_years) |>
    dplyr::left_join(
      events_any |>
        dplyr::group_by(twin_id) |>
        dplyr::summarise(last_stop = max(stop, na.rm = TRUE), .groups = "drop"),
      by = "twin_id"
    ) |>
    dplyr::mutate(start = dplyr::coalesce(last_stop, 0), stop = pmax(person_years, start), event = 0L) |>
    dplyr::select(twin_id, start, stop, event)

  ag_df <- dplyr::bind_rows(
    events_any |> dplyr::select(twin_id, start, stop, event),
    censor_any
  ) |>
    dplyr::filter(stop > start, is.finite(stop)) |>
    dplyr::left_join(twins_fu |> dplyr::select(twin_id, age, sex, prevalent_mm, edyrs, eversmok, bmi, hba1c, total_hdl_ratio, crp), by = "twin_id")
}

# Optionally restrict to one disease grouping
if (!use_all_diseases) {
  stopifnot(!is.null(group_labels), exists("label_col"))
  events_g <- timeline |>
    dplyr::filter(.data[[label_col]] %in% group_labels) |>
    dplyr::select(twin_id, earliest_date, checkdate, has_disease, prevalent) |>
    dplyr::filter(has_disease == 1, prevalent == 0, earliest_date > checkdate) |>
    dplyr::mutate(event_time = as.numeric(earliest_date - checkdate) / 365.25) |>
    dplyr::arrange(twin_id, event_time) |>
    dplyr::group_by(twin_id) |>
    dplyr::mutate(start = dplyr::lag(event_time, default = 0), stop = event_time, event = 1L) |>
    dplyr::ungroup()

  censor_g <- ag_df |>
    dplyr::group_by(twin_id) |>
    dplyr::summarise(person_years = max(stop, na.rm = TRUE), .groups = "drop") |>
    dplyr::left_join(
      events_g |>
        dplyr::group_by(twin_id) |>
        dplyr::summarise(last_stop = max(stop, na.rm = TRUE), .groups = "drop"),
      by = "twin_id"
    ) |>
    dplyr::mutate(start = dplyr::coalesce(last_stop, 0), stop = pmax(person_years, start), event = 0L) |>
    dplyr::select(twin_id, start, stop, event)

  ag_df <- dplyr::bind_rows(
    events_g |> dplyr::select(twin_id, start, stop, event),
    censor_g
  ) |>
    dplyr::filter(stop > start, is.finite(stop)) |>
    dplyr::left_join(ag_df |> dplyr::select(twin_id, age, sex, prevalent_mm, edyrs, eversmok, bmi, hba1c, total_hdl_ratio, crp) |> dplyr::distinct(), by = "twin_id")
}

# Load extreme-ager flags
extreme_organs <- readr::read_csv(extreme_csv_path, show_col_types = FALSE)

# Define baseline aging groups
extreme_with_flags <- extreme_organs |>
  dplyr::mutate(
    extreme_aged = !! rlang::parse_expr(extreme_definition),
    extreme_young = n_young >= 1
  ) |>
  dplyr::select(twin_id, extreme_aged, extreme_young)

ag_df_strat <- ag_df |>
  dplyr::left_join(extreme_with_flags, by = "twin_id") |>
  dplyr::mutate(
    extreme_aged = dplyr::coalesce(extreme_aged, FALSE),
    extreme_young = dplyr::coalesce(extreme_young, FALSE),
    # Create 3-level grouping
    aging_group = dplyr::case_when(
      extreme_aged ~ "Extreme aged",
      extreme_young ~ "Extreme young", 
      TRUE ~ "Normal"
    )
  )

# Mean Cumulative Function (nonparametric)
compute_mcf <- function(df) {
  ev <- df |>
    dplyr::filter(event == 1L) |>
    dplyr::select(time = stop)

  if (nrow(ev) == 0) return(tibble::tibble(time = numeric(), mcf = numeric()))
  t_unique <- sort(unique(ev$time))

  # Risk set at time t: intervals covering t
  at_risk <- vapply(
    t_unique,
    function(t) sum(df$start < t & df$stop >= t),
    numeric(1)
  )
  d_t <- vapply(
    t_unique,
    function(t) sum(ev$time == t),
    numeric(1)
  )
  incr <- ifelse(at_risk > 0, d_t / at_risk, 0)
  tibble::tibble(time = t_unique, mcf = cumsum(incr))
}

# MCF with confidence intervals using Greenwood-like variance
compute_mcf_with_ci <- function(df) {
  ev <- df |>
    dplyr::filter(event == 1L) |>
    dplyr::select(time = stop)

  if (nrow(ev) == 0) return(tibble::tibble(time = numeric(), mcf = numeric(), ci_low = numeric(), ci_high = numeric()))
  t_unique <- sort(unique(ev$time))

  at_risk <- vapply(
    t_unique,
    function(t) sum(df$start < t & df$stop >= t),
    numeric(1)
  )
  d_t <- vapply(
    t_unique,
    function(t) sum(ev$time == t),
    numeric(1)
  )
  incr <- ifelse(at_risk > 0, d_t / at_risk, 0)
  
  # Variance estimate (Greenwood-like)
  var_incr <- ifelse(at_risk > 1, d_t / (at_risk * (at_risk - 1)), 0)
  cumvar <- cumsum(var_incr)
  se <- sqrt(cumvar)
  
  mcf_vals <- cumsum(incr)
  tibble::tibble(
    time = t_unique, 
    mcf = mcf_vals,
    ci_low = pmax(0, mcf_vals - 1.96 * se),
    ci_high = mcf_vals + 1.96 * se
  )
}

mcf_by_stratum <- ag_df_strat |>
  dplyr::group_split(aging_group) |>
  purrr::map_dfr(function(g) {
    est <- compute_mcf(g)
    if (nrow(est) == 0) return(tibble::tibble())
    est |>
      dplyr::mutate(aging_group = unique(g$aging_group))
  })

# Plot
mcf_plot <- mcf_by_stratum |>
  ggplot2::ggplot(ggplot2::aes(x = time, y = mcf, color = aging_group)) +
  ggplot2::geom_step(linewidth = 1) +
  ggplot2::scale_color_manual(
    values = c(
      "Extreme aged" = "#D6604D", 
      "Extreme young" = "#2166AC", 
      "Normal" = "#2E8B57"
    ),
    breaks = c("Extreme young", "Normal", "Extreme aged")
  ) +
  ggplot2::labs(x = "Years since baseline", y = "Mean cumulative count", color = NULL) +
  ggplot2::theme_minimal(base_size = 13) +
  ggplot2::theme(legend.position = "bottom", panel.grid.minor = ggplot2::element_blank())

mcf_plot


```

# Organ-Specific MCF

```{r flexible_mcf_analysis, echo=TRUE}
# Parameters for flexible analysis
target_organ <- "Brain"  # e.g., "Brain", "Heart", "Liver", "Lung", etc. (capitalized)
target_disease_group <- "neuropsychiatric_multimorbidity"  # or NULL for all diseases
extreme_definition_young <- paste0("young_", target_organ, " == 1")
extreme_definition_aged <- paste0("aged_", target_organ, " == 1")

# Load extreme-ager flags for specific organ
extreme_organs_specific <- extreme_organs |>
  dplyr::mutate(
    extreme_young_specific = !! rlang::parse_expr(extreme_definition_young),
    extreme_aged_specific = !! rlang::parse_expr(extreme_definition_aged)
  ) |>
  dplyr::select(twin_id, extreme_young_specific, extreme_aged_specific)

# Build AG data for specific disease group if specified
if (!is.null(target_disease_group)) {
  # Use existing disease grouping vectors
  disease_labels <- group_vectors[[target_disease_group]]
  
  events_specific <- timeline |>
    dplyr::filter(.data[[label_col]] %in% disease_labels) |>
    dplyr::select(twin_id, earliest_date, checkdate, has_disease, prevalent) |>
    dplyr::filter(has_disease == 1, prevalent == 0, earliest_date > checkdate) |>
    dplyr::mutate(event_time = as.numeric(earliest_date - checkdate) / 365.25) |>
    dplyr::arrange(twin_id, event_time) |>
    dplyr::group_by(twin_id) |>
    dplyr::mutate(start = dplyr::lag(event_time, default = 0), stop = event_time, event = 1L) |>
    dplyr::ungroup()

  censor_specific <- ag_df |>
    dplyr::group_by(twin_id) |>
    dplyr::summarise(person_years = max(stop, na.rm = TRUE), .groups = "drop") |>
    dplyr::left_join(
      events_specific |>
        dplyr::group_by(twin_id) |>
        dplyr::summarise(last_stop = max(stop, na.rm = TRUE), .groups = "drop"),
      by = "twin_id"
    ) |>
    dplyr::mutate(start = dplyr::coalesce(last_stop, 0), stop = pmax(person_years, start), event = 0L) |>
    dplyr::select(twin_id, start, stop, event)

  ag_df_specific <- dplyr::bind_rows(
    events_specific |> dplyr::select(twin_id, start, stop, event),
    censor_specific
  ) |>
    dplyr::filter(stop > start, is.finite(stop)) |>
    dplyr::left_join(ag_df |> dplyr::select(twin_id, age, sex, prevalent_mm, edyrs, eversmok, bmi, hba1c, total_hdl_ratio, crp) |> dplyr::distinct(), by = "twin_id")
} else {
  # Use all diseases
  ag_df_specific <- ag_df
}

# Create organ-specific aging groups
ag_df_specific_strat <- ag_df_specific |>
  dplyr::left_join(extreme_organs_specific, by = "twin_id") |>
  dplyr::mutate(
    extreme_young_specific = dplyr::coalesce(extreme_young_specific, FALSE),
    extreme_aged_specific = dplyr::coalesce(extreme_aged_specific, FALSE),
    # Create 3-level grouping for specific organ
    aging_group_specific = dplyr::case_when(
      extreme_aged_specific ~ "Extremely aged",
      extreme_young_specific ~ "Extremely young", 
      TRUE ~ "Normal"
    )
  )

# Compute MCF with confidence intervals for specific organ and disease group
mcf_specific <- ag_df_specific_strat |>
  dplyr::group_split(aging_group_specific) |>
  purrr::map_dfr(function(g) {
    est <- compute_mcf_with_ci(g)
    if (nrow(est) == 0) return(tibble::tibble())
    est |>
      dplyr::mutate(aging_group_specific = unique(g$aging_group_specific))
  })

# Create color mapping dynamically
aged_label <- paste0("Extreme aged (", target_organ, ")")
young_label <- paste0("Extreme young (", target_organ, ")")

color_mapping <- c(
  "Extremely aged" = "#D6604D",  # red for aged
  "Extremely young" = "#2166AC", # blue for young  
  "Normal" = "#2E8B57"           # green for normal
)

# Plot specific analysis with confidence intervals
mcf_specific_plot <- mcf_specific |>
  ggplot2::ggplot(ggplot2::aes(x = time, y = mcf, color = aging_group_specific)) +
  ggplot2::geom_ribbon(ggplot2::aes(ymin = ci_low, ymax = ci_high, fill = aging_group_specific), 
                       alpha = 0.2, color = NA) +
  ggplot2::geom_step(linewidth = 1) +
  ggplot2::scale_color_manual(
    values = color_mapping,
    breaks = c("Extremely young", "Normal", "Extremely aged")
  ) +
  ggplot2::scale_fill_manual(
    values = color_mapping,
    breaks = c("Extremely young", "Normal", "Extremely aged")
  ) +
  ggplot2::scale_y_continuous(limits = c(0, NA), expand = ggplot2::expansion(mult = c(0, 0.1))) +
  ggplot2::labs(
    x = "Years since baseline", 
    y = "Mean cumulative count", 
    color = NULL,
    fill = NULL,
  ) +
  ggplot2::theme_minimal(base_size = 13) +
  ggplot2::theme(
    legend.position = "bottom", 
    panel.grid.minor = ggplot2::element_blank(),
    legend.text = ggplot2::element_text(size = 9),
    plot.margin = ggplot2::margin(t = 5, r = 5, b = 35, l = 5, unit = "pt")
  )

mcf_specific_plot

# Age distribution for specific analysis
age_summary_specific <- ag_df_specific_strat |>
  dplyr::group_by(aging_group_specific) |>
  dplyr::summarise(
    n_people = n_distinct(twin_id),
    mean_age = mean(age, na.rm = TRUE),
    median_age = median(age, na.rm = TRUE),
    .groups = "drop"
  )


# Save specific analysis
dir.create(file.path(output_multimorbidity_core_dir, "other"), recursive = TRUE, showWarnings = FALSE)
ggplot2::ggsave(
  filename = file.path(output_multimorbidity_core_dir, "other", 
                       paste0("mcf_", tolower(target_organ), "_", target_disease_group, ".pdf")),
  plot = mcf_specific_plot, width = 5, height = 5, dpi = 300
)
ggplot2::ggsave(
  filename = file.path(output_multimorbidity_core_dir, "other", 
                       paste0("mcf_", tolower(target_organ), "_", target_disease_group, ".png")),
  plot = mcf_specific_plot, width = 5, height = 5, dpi = 400
)
```

# Granular MCF
```{r granular_mcf_analysis, echo=TRUE}
# Create granular aging groups based on number of extreme organs
ag_df_granular <- ag_df |>
  dplyr::left_join(extreme_organs, by = "twin_id") |>
  dplyr::mutate(
    # Handle missing values
    n_aged = dplyr::coalesce(n_aged, 0),
    n_young = dplyr::coalesce(n_young, 0),
    n_extreme = dplyr::coalesce(n_extreme, 0),
    
    # Create granular aging groups
    aging_group_granular = dplyr::case_when(
      n_aged >= 6 ~ "6+ aged organs",
      n_aged >= 5 ~ "5 aged organs", 
      n_aged >= 4 ~ "4 aged organs",
      n_aged >= 3 ~ "3 aged organs",
      n_aged >= 2 ~ "2 aged organs",
      n_aged >= 1 ~ "1 aged organ",
      n_young >= 6 ~ "6+ young organs",
      n_young >= 5 ~ "5 young organs",
      n_young >= 4 ~ "4 young organs", 
      n_young >= 3 ~ "3 young organs",
      n_young >= 2 ~ "2 young organs",
      n_young >= 1 ~ "1 young organ",
      TRUE ~ "Normal (0 extreme)"
    ),
    
    # Create simplified groups for plotting
    aging_group_simple = dplyr::case_when(
      n_aged >= 2 ~ "2+ aged organs",
      n_aged == 1 ~ "1 aged organ",
      n_young >= 1 ~ "Young",
      TRUE ~ "Normal"
    ),
    aging_group_simple = factor(
      aging_group_simple,
      levels = c("Young", "Normal", "1 aged organ", "2+ aged organs")
    )
  )

# Compute MCF for granular analysis with confidence intervals
mcf_granular_ci <- ag_df_granular |>
  dplyr::group_split(aging_group_simple) |>
  purrr::map_dfr(function(g) {
    est <- compute_mcf_with_ci(g)
    if (nrow(est) == 0) return(tibble::tibble())
    est |>
      dplyr::mutate(aging_group_simple = unique(g$aging_group_simple))
  })

# Define color palette for granular groups
granular_colors <- c(
  "Normal" = "#2E8B57",            # Green (healthiest)
  "Young" = "#4169E1",             # Blue (young)
  "1 aged organ" = "#FFA500",      # Orange (mild aging)
  "2+ aged organs" = "#DC143C"     # Crimson (severe aging)
)

# Plot granular MCF with confidence intervals
mcf_granular_plot <- mcf_granular_ci |>
  ggplot2::ggplot(ggplot2::aes(x = time, y = mcf, color = aging_group_simple)) +
  ggplot2::geom_ribbon(ggplot2::aes(ymin = ci_low, ymax = ci_high, fill = aging_group_simple), 
                       alpha = 0.2, color = NA) +
  ggplot2::geom_step(linewidth = 1) +
  ggplot2::scale_color_manual(
    values = granular_colors,
    breaks = c("Young", "Normal", "1 aged organ", "2+ aged organs")
  ) +
  ggplot2::scale_fill_manual(
    values = granular_colors,
    breaks = c("Young", "Normal", "1 aged organ", "2+ aged organs")
  ) +
  ggplot2::scale_y_continuous(limits = c(0, NA), expand = ggplot2::expansion(mult = c(0, 0.1))) +
  ggplot2::labs(
    x = "Years since baseline", 
    y = "Mean cumulative count",
    color = NULL,
    fill = NULL
  ) +
  ggplot2::theme_minimal(base_size = 13) +
  ggplot2::theme(
    legend.position = "bottom", 
    panel.grid.minor = ggplot2::element_blank(),
    legend.text = ggplot2::element_text(size = 9),
    plot.margin = ggplot2::margin(t = 5, r = 5, b = 35, l = 5, unit = "pt")
  ) +
  ggplot2::guides(
    color = ggplot2::guide_legend(nrow = 2, byrow = TRUE),
    fill = ggplot2::guide_legend(nrow = 2, byrow = TRUE)
  )

mcf_granular_plot

# Summary statistics for granular groups
granular_summary <- ag_df_granular |>
  dplyr::group_by(aging_group_simple) |>
  dplyr::summarise(
    n_people = n_distinct(twin_id),
    mean_age = mean(age, na.rm = TRUE),
    median_age = median(age, na.rm = TRUE),
    mean_n_aged = mean(n_aged, na.rm = TRUE),
    mean_n_young = mean(n_young, na.rm = TRUE),
    .groups = "drop"
  ) |>
  dplyr::arrange(desc(mean_n_aged), mean_n_young)


# Save granular analysis
dir.create(file.path(output_multimorbidity_core_dir, "other"), recursive = TRUE, showWarnings = FALSE)
ggplot2::ggsave(
  filename = file.path(output_multimorbidity_core_dir, "other", "mcf_granular_organ_aging.pdf"),
  plot = mcf_granular_plot, width = 5, height = 5, dpi = 300
)
ggplot2::ggsave(
  filename = file.path(output_multimorbidity_core_dir, "other", "mcf_granular_organ_aging.png"),
  plot = mcf_granular_plot, width = 5, height = 5, dpi = 400
)
```

# Kaplan-Meier: Granular Aging Patterns
```{r km_granular_organ_aging, echo=TRUE}
# Create survival dataset with death indicator and aging groups
km_survival_data <- twins |>
  dplyr::select(twin_id, deathdate, checkdate, birthdate, time_to_death) |>
  dplyr::mutate(
    deceased = dplyr::if_else(!is.na(deathdate), 1, 0),
    person_years = time_to_death / 365.25
  ) |>
  dplyr::left_join(extreme_organs, by = "twin_id") |>
  dplyr::mutate(
    n_aged = dplyr::coalesce(n_aged, 0),
    n_young = dplyr::coalesce(n_young, 0),
    aging_group_simple = dplyr::case_when(
      n_aged >= 2 ~ "2+ aged organs",
      n_aged == 1 ~ "1 aged organ",
      n_young >= 1 ~ "Young",
      TRUE ~ "Normal"
    ),
    aging_group_simple = factor(
      aging_group_simple, 
      levels = c("Young", "Normal", "1 aged organ", "2+ aged organs")
    )
  ) |>
  dplyr::filter(!is.na(person_years), person_years > 0)

# Fit Kaplan-Meier model
km_fit <- survival::survfit(
  survival::Surv(time = person_years, event = deceased) ~ aging_group_simple,
  data = km_survival_data
)

# Define color palette
km_colors <- c(
  "Normal" = "#2E8B57",            # Green (healthiest)
  "Young" = "#4169E1",             # Blue (young)
  "1 aged organ" = "#E53935",      # Light red (mild aging)
  "2+ aged organs" = "#B71C1C"     # Dark red (severe aging)
)

# Extract survival data from survfit object for ggplot2
km_data_plot <- broom::tidy(km_fit) |>
  dplyr::mutate(
    aging_group_simple = factor(
      stringr::str_remove(strata, "aging_group_simple="),
      levels = c("Young", "Normal", "1 aged organ", "2+ aged organs")
    )
  )

# Create survival plot with ggplot2
km_plot <- km_data_plot |>
  ggplot2::ggplot(ggplot2::aes(x = time, y = estimate, color = aging_group_simple)) +
  ggplot2::geom_ribbon(
    ggplot2::aes(ymin = conf.low, ymax = conf.high, fill = aging_group_simple), 
    alpha = 0.1, 
    color = NA
  ) +
  ggplot2::geom_step(linewidth = 1.5) +
  ggplot2::scale_x_continuous(limits = c(0, 22), breaks = seq(0, 20, 5)) +
  ggplot2::scale_y_continuous(limits = c(0, 1), expand = ggplot2::expansion(mult = c(0, 0.02))) +
  ggplot2::scale_color_manual(
    values = km_colors,
    breaks = c("Young", "Normal", "1 aged organ", "2+ aged organs"),
    name = "Organ aging"
  ) +
  ggplot2::scale_fill_manual(
    values = km_colors,
    breaks = c("Young", "Normal", "1 aged organ", "2+ aged organs"),
    name = "Organ aging"
  ) +
  ggplot2::labs(
    x = "Years since baseline", 
    y = "Survival probability"
  ) +
  ggplot2::theme_minimal(base_size = 16) +
  ggplot2::theme(
    legend.position = c(0.02, 0.02),
    legend.justification = c(0, 0),
    legend.background = ggplot2::element_rect(fill = scales::alpha("white", 0.8), color = NA),
    legend.box.margin = ggplot2::margin(5, 5, 5, 5),
    panel.grid.minor = ggplot2::element_blank(),
    panel.grid.major = ggplot2::element_blank(),
    panel.background = ggplot2::element_rect(fill = "white", color = NA),
    axis.title.y = ggplot2::element_text(size = 16, face = "plain"),
    axis.title.x = ggplot2::element_text(size = 16, face = "plain"),
    axis.text = ggplot2::element_text(size = 14),
    legend.text = ggplot2::element_text(size = 12),
    legend.title = ggplot2::element_text(size = 14, face = "plain")
  )

print(km_plot)

# Summary statistics
km_summary_stats <- km_survival_data |>
  dplyr::group_by(aging_group_simple) |>
  dplyr::summarise(
    n_individuals = n(),
    n_deaths = sum(deceased),
    death_rate = round(sum(deceased) / n() * 100, 1),
    mean_followup = round(mean(person_years, na.rm = TRUE), 2),
    .groups = "drop"
  )

# Log-rank test
km_logrank <- survival::survdiff(
  survival::Surv(time = person_years, event = deceased) ~ aging_group_simple,
  data = km_survival_data
)

# Extract median survival times
km_median_survival <- summary(km_fit)$table |>
  as.data.frame() |>
  tibble::rownames_to_column("group") |>
  dplyr::mutate(
    group = stringr::str_remove(group, "aging_group_simple=")
  ) |>
  dplyr::select(group, median, `0.95LCL`, `0.95UCL`)
# Save KM plot
dir.create(file.path(output_multimorbidity_core_dir, "other"), 
           recursive = TRUE, showWarnings = FALSE)

ggplot2::ggsave(
  filename = file.path(output_multimorbidity_core_dir, "other", 
                       "km_granular_organ_aging.pdf"),
  plot = km_plot,
  width = 5,
  height = 5,
  dpi = 300
)
ggplot2::ggsave(
  filename = file.path(output_multimorbidity_core_dir, "other", 
                       "km_granular_organ_aging.png"),
  plot = km_plot,
  width = 5,
  height = 5,
  dpi = 400
)
```

# GI Aging vs Digestive Disease
```{r gi_aging_digestive, echo=TRUE}
# Parameters for GI aging vs. digestive diseases
target_organ <- "Gastrointestinal Tract"  # Note: capitalized as in the data
target_disease_group <- "digestive_multimorbidity"

# Load extreme-ager flags for GI tract
extreme_organs_gi <- extreme_organs |>
  dplyr::mutate(
    extreme_young_gi = young_Gastrointestinal == 1,
    extreme_aged_gi = aged_Gastrointestinal == 1
  ) |>
  dplyr::select(twin_id, extreme_young_gi, extreme_aged_gi)

# Build AG data for digestive diseases
disease_labels <- group_vectors[[target_disease_group]]

events_gi <- timeline |>
  dplyr::filter(.data[[label_col]] %in% disease_labels) |>
  dplyr::select(twin_id, earliest_date, checkdate, has_disease, prevalent) |>
  dplyr::filter(has_disease == 1, prevalent == 0, earliest_date > checkdate) |>
  dplyr::mutate(event_time = as.numeric(earliest_date - checkdate) / 365.25) |>
  dplyr::arrange(twin_id, event_time) |>
  dplyr::group_by(twin_id) |>
  dplyr::mutate(start = dplyr::lag(event_time, default = 0), stop = event_time, event = 1L) |>
  dplyr::ungroup()

censor_gi <- ag_df |>
  dplyr::group_by(twin_id) |>
  dplyr::summarise(person_years = max(stop, na.rm = TRUE), .groups = "drop") |>
  dplyr::left_join(
    events_gi |>
      dplyr::group_by(twin_id) |>
      dplyr::summarise(last_stop = max(stop, na.rm = TRUE), .groups = "drop"),
    by = "twin_id"
  ) |>
  dplyr::mutate(start = dplyr::coalesce(last_stop, 0), stop = pmax(person_years, start), event = 0L) |>
  dplyr::select(twin_id, start, stop, event)

ag_df_gi <- dplyr::bind_rows(
  events_gi |> dplyr::select(twin_id, start, stop, event),
  censor_gi
) |>
  dplyr::filter(stop > start, is.finite(stop)) |>
  dplyr::left_join(ag_df |> dplyr::select(twin_id, age, sex, prevalent_mm) |> dplyr::distinct(), by = "twin_id")

# Create GI-specific aging groups
ag_df_gi_strat <- ag_df_gi |>
  dplyr::left_join(extreme_organs_gi, by = "twin_id") |>
  dplyr::mutate(
    extreme_young_gi = dplyr::coalesce(extreme_young_gi, FALSE),
    extreme_aged_gi = dplyr::coalesce(extreme_aged_gi, FALSE),
    # Create 3-level grouping for GI tract
    aging_group_gi = dplyr::case_when(
      extreme_aged_gi ~ "Extremely aged",
      extreme_young_gi ~ "Extremely young", 
      TRUE ~ "Normal"
    )
  )

# Compute MCF for GI aging and digestive diseases
mcf_gi <- ag_df_gi_strat |>
  dplyr::group_split(aging_group_gi) |>
  purrr::map_dfr(function(g) {
    est <- compute_mcf_with_ci(g)
    if (nrow(est) == 0) return(tibble::tibble())
    est |>
      dplyr::mutate(aging_group_gi = unique(g$aging_group_gi))
  })

# Create color mapping for GI analysis
gi_colors <- c(
  "Extremely aged" = "#D6604D", 
  "Extremely young" = "#2166AC", 
  "Normal" = "#2E8B57"
)

# Plot GI aging vs. digestive diseases
mcf_gi_plot <- mcf_gi |>
  ggplot2::ggplot(ggplot2::aes(x = time, y = mcf, color = aging_group_gi)) +
  ggplot2::geom_ribbon(ggplot2::aes(ymin = ci_low, ymax = ci_high, fill = aging_group_gi), 
                       alpha = 0.2, color = NA) +
  ggplot2::geom_step(linewidth = 1) +
  ggplot2::scale_color_manual(
    values = gi_colors,
    breaks = c("Extremely young", "Normal", "Extremely aged")
  ) +
  ggplot2::scale_fill_manual(
    values = gi_colors,
    breaks = c("Extremely young", "Normal", "Extremely aged")
  ) +
  ggplot2::scale_y_continuous(limits = c(0, NA), expand = ggplot2::expansion(mult = c(0, 0.1))) +
  ggplot2::labs(
    x = "Years since baseline", 
    y = "Mean cumulative count",
    color = NULL,
    fill = NULL
  ) +
  ggplot2::theme_minimal(base_size = 13) +
  ggplot2::theme(
    legend.position = "bottom", 
    panel.grid.minor = ggplot2::element_blank(),
    legend.text = ggplot2::element_text(size = 9),
    plot.margin = ggplot2::margin(t = 5, r = 5, b = 35, l = 5, unit = "pt")
  ) +
  ggplot2::guides(
    color = ggplot2::guide_legend(nrow = 2, byrow = TRUE),
    fill = ggplot2::guide_legend(nrow = 2, byrow = TRUE)
  )

mcf_gi_plot

# Age distribution for GI analysis
age_summary_gi <- ag_df_gi_strat |>
  dplyr::group_by(aging_group_gi) |>
  dplyr::summarise(
    n_people = n_distinct(twin_id),
    mean_age = mean(age, na.rm = TRUE),
    median_age = median(age, na.rm = TRUE),
    .groups = "drop"
  )


# Save GI analysis
dir.create(file.path(output_multimorbidity_core_dir, "other"), recursive = TRUE, showWarnings = FALSE)
ggplot2::ggsave(
  filename = file.path(output_multimorbidity_core_dir, "other", "mcf_gi_aging_digestive.pdf"),
  plot = mcf_gi_plot, width = 5, height = 5, dpi = 300
)
ggplot2::ggsave(
  filename = file.path(output_multimorbidity_core_dir, "other", "mcf_gi_aging_digestive.png"),
  plot = mcf_gi_plot, width = 5, height = 5, dpi = 400
)
```

